---
title: "Tidy text analysis example: web scraping with `rvest`"
subtitle: "Companies that lobby the U.S. Federal Energy Regulatory Commission (FERC)"
author:
output:
    html_document:
      toc: true
      toc_float: true
      # code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
## Run a setup.R script to load R packages and set defaults
#source(here::here("setup.R")) ## Alternatively: source("https://raw.githubusercontent.com/judgelord/PS811/master/setup.R")

## Modify some defaults for this example
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 8,
                      warning = FALSE,
                      message = FALSE)
```


In addition to `rvest`, this example uses the `stringr`, `purrr`, and `magrittr` packages.

```{r libraries}
library(tidyverse)
library(rvest)
library(magrittr)
library(here)
```

The aim is to get the names of oil, gas, electric, and hydropower companies that lobby FERC from the FERC website.

## 1: Instpect the URLs and source html 
(in Chrome: view->developer->view source)

Here is the first page under the "Oil Matters" tab; [oil companies with "A" names](https://www.ferc.gov/docs-filing/corp-off/oil.asp):
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/oil.asp") 

html %>% 
  html_nodes("strong") %>% # company names are in bold (HTML tag "<strong>")
  html_text() %>% # to plain text
  .[1:6] # the first 3 rows seem to be web page headers
```

Gas companies with "A" names. Notice how the URL changed:
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/gas.asp") 

html %>% 
  html_nodes("strong") %>%
  html_text() %>% 
  .[4:6]
```


Gas companies with "B" names. *Notice how the URL changed:*
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/gas/gas-B.asp") 

html %>% 
  html_nodes("strong") %>% 
  html_text() %>%
  .[4:6]
```

In addition to "oil" and "gas," we have "electric" and "hydro" with pages A-Z (4 x 26 = 104 pages!), so let's make a function to grab the names from each page. 

## 2. Make a function, turning things that vary into variables.

A test run using `str_c` to combine strings:
```{r}
industry <- "gas"
letter <- "B"
str_c("https://www.ferc.gov/docs-filing/corp-off/", industry, "/", industry, "-", letter, ".asp")
```

Looks good! Forward!

`cross()` lists each possible combination of URL parts. Because it returns a list, we use `lift()` to allow `str_c()` to take a list and paste it together. `map()` then does this for each. 

```{r}
url_parts <- list(
  base_url <- "https://www.ferc.gov/docs-filing/corp-off/",
  industry = c("oil/oil-", "gas/gas-", "electric/electric-", "hydro/hydro-"),
  letter = LETTERS,
  end = ".asp"
)

url <- url_parts %>%
  cross() %>%
  map(lift(str_c)) %>%
  str_remove("/[a-z]*-A") # remove "/industry-A"

head(url)
```

Define a function to apply to each URL.
```{r, include = TRUE}
scraper <- function(url){
  html <-  read_html(url) 

  # Extract company names
  corps <- html %>% 
    html_nodes("strong") %>% 
    html_text() %>%
    .[-c(1:3)]
  
  # Extract the industry back out of the URL
  industry <- str_extract(url, "off/[a-z]*") %>% 
    str_remove("off/")

  ## Return a data frame with two variables, company and industry
  d <- tibble(company = corps,
              industry = industry)
  return(d)
}
```

## 3. Apply the function to each URL

`map()` each URL into the function, i.e. *apply* the function to each. I wrap the `scraper` function in `possibly()` so that if a URL does not work, it keeps going, just returning `NA` rather than stopping at an error. Specifically, I use `map_dfr` which returns a *data frame*, combining results with `rbind()`. See `?map()` and the `purrr` [cheatsheet](https://www.rstudio.com/resources/cheatsheets/#purrr).


```{r}
# map(.x = vector, .f = function)
corps_all <- map_dfr(url, possibly(scraper, NA_real_) ) 

## Clean up a bit [[:cntrl:]]
corps_all$company %<>% str_replace_all("\r\n", ", ") %>% 
  trimws() # trim white space before and after company names

corps_all %<>% 
  filter(nchar(company)>1) %>% # filter out names less than 2 characters 
  filter(!company %in% c("FERC Online Support", "Note:","LLC")) %>% # not companies
  distinct() # drop duplicates

# For matching, remove endings like ", Inc." etc. 
trim <- function(d){
d%>%
  str_remove_all(",.*| Pipe.*| Company.*| Corp.*|  Co.| Gen.| LLC| L.L.C.|  L.P.| Inc.| L.P.| Ltd.| \\(.*") %>% 
    str_remove(" Energy.*| Holdings.*| Gas$| Project.*| -.*|Village of |\\(.*")
}

corps_all$company_short <- trim(corps_all$company)

# Inspect over-trimmed company names
corps_all %>% filter(company_short %in% c("LLC", "Energy", "Pipeline", "Natural", "North", "New", "Express", "American", "Electric", "System", "Direct", "DC", "PS", "CT", "Forest", "International", "Tennessee", "Salt Lake", "Lakeside", "NW", "Jackson", "Public Service", "Peak", "Independence", "Select", "Portland", "Michigan", "Boundary", "Coastal", "Minnesota", "Midwest", "Columbia", "Plains", "Stream", "Mitchell", "AP", "Southern", "Ohio River", "Northwest", "Rio Grande"))

# Correct over-trimmed names
corps_all %<>% mutate(company_short = ifelse(company == "Natural Gas Pipeline Company of America", "Natural Gas Pipeline Company of America", company_short))%>%
  mutate(company_short = ifelse(company == "Natural Gas Trading Corporation", "Natural Gas Trading Corporation", company_short))%>%
    mutate(company_short = ifelse(company == "Energy, USA-TPC Corp.", "TPC", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Partners, L.L.C.", "New Energy Partners", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Service, LLC", "New Energy Service", company_short))%>%
  mutate(company_short = ifelse(company == "North Energy Associates, A Limited Partnership", "North Energy Associates", company_short))%>%
  mutate(company_short = ifelse(company == "Pipeline Company LLC", "Pipeline Company LLC", company_short))%>%
  mutate(company_short = ifelse(company == "Express Pipeline LLC", "Express Pipeline LLC", company_short))%>%
  mutate(company_short = ifelse(company == "American Energy Savings, Inc.", "American Energy Savings", company_short))%>%
  mutate(company_short = ifelse(company == "Electric Energy, Inc.", "Electric Energy, Inc.", company_short))%>%
  mutate(company_short = ifelse(company == "System Energy Resources, Inc., Llano Estacado Wind, LLC, System Energy Resources, Inc., Northern Iowa Windpower, LLC, and RS Cogen, L.L.C.", "System Energy Resources", company_short))%>%
  mutate(company_short = ifelse(company == "Public Service Company of Colorado", "Public Service Company of Colorado", company_short))%>%
    mutate(company_short = ifelse(company == "Southern Company Services, Inc.", "Southern Company", company_short))%>%
      mutate(company_short = ifelse(company == "International Energy Consultants", "International Energy Consultants", company_short))%>%
        mutate(company_short = ifelse(company == "Jackson Pipeline Company", "Jackson Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Southern Energy California", "Southern Energy California", company_short))%>%
  mutate(company_short = ifelse(company == "Tennessee Gas Pipeline Company, L.L.C.", "Tennessee Gas Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Select Energy New York, Inc.", "Select Energy New York", company_short))%>%
  mutate(company_short = ifelse(company_short == "Direct", "Direct Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "DC", "DC Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "PS", "PS Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Coastal", "Coastal Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "CT", "CT Corporation", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Forest", "Forest Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Minnesota", "Minnesota Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "NW", "NW Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Rio Grande", "Rio Grande Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Plains", "Plains Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Portland", "Portland Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "AP", "AP Holdings", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Boundary", "Boundary Gas", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Columbia Energy", "Columbia", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Independence", "Independence Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Lakeside", "Lakeside Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Mitchell", "Mitchell Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Stream", "Stream Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short))%>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short))%>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short))%>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short))%>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short))%>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short))%>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short))


# Save
save(corps_all, file =  here("data", "DOE_FERC-corps.Rdata"))

# To load these data: 
# load(here("data", "DOE_FERC-corps.Rdata"))

corps_all
```


# Find company names in letters texts
```{r}
load(url("https://github.com/judgelord/correspondence/raw/master/data/FERC_files.Rdata")) # potentially change to google sheet

# Make a single string of short corp names
FERC_corps <- str_c(corps_all$company_short, collapse = "|")

FERC_files %<>% mutate(corp = str_c(str_extract_all(summary, FERC_corps),sep = "; ")) 

unique(FERC_files$corp)
```


# Match company names with campaign donations.
Using DIME: 
```{r}
# Fortune 500 companies
download.file("https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/6R1HAS/DP6TOL", destfile = here("data", "DIME500.csv") )

dime <- DIME500 <- read_csv(here("data", "DIME500.csv"))

# dime %<>% extractMemberName(members, recipient.name)
  
fortune500 <- unique(dime$corpname) %>% 
  str_c(sep = "|", collapse = "|")
ferc <- corps_all
ferc_short <- unique(ferc$company_short) %>% 
  str_c(sep = "|", collapse = "|")

ferc %<>% mutate(f500 = str_extract(company_short, fortune500) )

ferc %<>% mutate(f500_short = str_extract(fortune500, company_short) )

unique(ferc$f500_short)
unique(ferc$f500)

# DIME records that exactly match a FERC company name
dime_1 <- dime %>% filter(corpname %in% unique(ferc$f500) )

# DIME records that match a shortened version
dime_2 <- dime %>% filter(str_detect(corpname, ferc_short))

# Join the two DIME subsets
dime_ferc <- full_join(dime_1, dime_2)

# ID member names among donation recipients 
dime %<>% extractMemberName(members = members, col_name =  recipient.name)
```


## Match indivdual campaign donations from Fortune 500
```{r}
# GET DIME DATA (careful, this is >3GB)
# download.file("https://dataverse.harvard.edu/api/access/datafile/2865300?gbrecs=true", 
#              destfile = here("data/dime_contributors.gz") ) 
# 
# DIME DATA
# dime <- read.csv(here("data/dime_contributors.csv"))

# TRIM DOWN
# dime %<>% filter(contributor.type == "I")
# dime %<>% mutate(last_name = str_extract(dime$most.recent.contributor.name, "[a-z]*") )

# SUBSET TO PEOPLE IN FERC DATA 
# dime %<>% filter(last_name %in% d$last_name)

# Clean up DIME names 
# dime %<>% mutate(name = str_replace(most.recent.contributor.name, " dr | jr |[0-9]", " ") )
# dime %<>% mutate(name = str_replace(most.recent.contributor.name, "  ", " ") )
# dime %<>% mutate(first_name = str_extract(name, ", [a-z][a-z]*") )
# dime %<>% mutate(first_name = str_replace(first_name, ", ", ""))
# dime %<>% mutate(first_name2 = str_extract(dime$most.recent.contributor.name, ", [a-z]{2}*") )
# dime %<>% mutate(middle_initial = str_extract(name, " [a-z]$") )
# dime %<>% mutate(middle_initial = str_replace(middle_initial, " ", "") )
# dime$first_initial <- str_sub(dime$first_name, 1,1)

# SAVE
# save(dime, file = here("data/dime_CGS_matches.Rdata"))

# LOAD

```




