---
title: "Tidy text analysis example: web scraping tables and files with `rvest`"
subtitle: "U.S. Legislators' correspondence with the Federal Energy Regulatory Commission"
author: 
output:
    html_document:
    toc: true
    code_folding: hide
---

```{r setup, include=FALSE}
## Run a setup.R script to load R packages and set defaults
source(here::here("setup.R")) ## Alternatively: source("https://raw.githubusercontent.com/judgelord/PS811/master/setup.R")

## Modify some defaults for this example
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 8)
```


This example uses the `magrittr`, `stringr`, `rvest`.

```{r libraries}
library(tidyverse)
library(magrittr)
```

The aim is make a table with both the text of letters and information from the FERC website, such as the date the letter was recieved. 

Here are the steps
1. Scrape the table of letters recieved
2. I extract the links to download the files
3. Convert the pdfs to text and add it to the table

Some challenges: 
- FERC's database can only be accessed in an interactive .asp session where the URL does not vary. SOLUTION: I just downloaded the raw html for the results pages. One could use the navigation functions of `rvest` or `selenium` but with ~30 pages, it was faster to click through and download them.
- Some lines in the table include links to more than one file (for example when a legislator included a letter from a constituent, it was scanned as a seperate file), so there are more files than rows in the table. SOLUTION: use `dplyr`'s `gather()` make the table into one row per file, and then reverse this with `spread()` after merging in the text from the pdfs. 
- 

Load saved html files from a [search](https://elibrary.ferc.gov/idmws/search/fercgensearch.asp)
```{r}
web_pages <- list.files(here("FERC", "html"), pattern = ".htm")

# web_pages <- web_pages[2] ## for testing the whole function
# web_page <- web_pages[2] ## for testing parts of the function
web_pages
```

---

# Scrape the table

1. Get the raw html
```{r}
  html <- read_html(here("FERC", "html", web_page))
```

2. Extract the "<table>" nodes (I want 3rd table on this page), use `html_table` to turn it into a data frame, and give the columns names. 

I then use `gather()` to turn "wide" data  with one observation per letter and a column for each file type into "long data" with one observation per letter-per-file with "key" and "value" pairs where the "value" is the file type (the new `link_text` column).

The `date` column has two dates in it, so I `separate()` it into two columns.

Here and there, I use `dplyr` and `stringr` to clean up the table, keeping rows with a congressional submission and with certian document types (for now) and using `mutate()` + `str_replace` to edit the text. 
```{r}
  table <- html %>% 
    html_nodes("table") %>%
    .[[3]] %>% # I happen to be interested in the third table on this page
    html_table(fill = T) %>% # turn html in to a data frame
    rename(id = X1,
           date = X2,
           docket = X3,
           summary = X4) %>% 
    filter(str_detect(id, "Submittal")) %>% # clean it up a bit
    gather(key = key, value = link_text, -id, -date, -docket, -summary) %>% #FIXME get private/public
    select(-key) %>% 
    filter(link_text %in% c("Image", "PDF", "FERC Generated PDF", "MicroFilm") ) %>% #FIXME add doc types
    separate(date, c("doc_date", "filed_date"), sep = "\n\t") %>%
    mutate(doc_date = as.Date(doc_date, "%m/%d/%Y"),
           filed_date = as.Date(filed_date, "%m/%d/%Y") ) %>%
    mutate(id = str_remove(id, "Submittal")) %>% 
    mutate(id = str_replace(id, "Document Components", "(partial)"))
```

Now I subset that table to exclude "MicroFilm" files because there is nothing to download. This makes the table the same length as the list of URLs I'll extract, so I make sure it is arranged in the same way the URLs will appear and give it an index number to merge on. 
```{r}
  table_files <- table %>%
    filter(link_text %in% c("Image", "PDF", "FERC Generated PDF") ) %>% #FIXME
    arrange(id) %>% # id numbers count up
    arrange(desc(filed_date)) %>% # dates count down 
    mutate(index = row_number()) # add an index
  
```


```{r}
  urls <- html %>% 
    html_nodes("table") %>%
    html_nodes("a") # "a" nodes contain url linked text
  
  urls <- tibble(
    link_text = html_text(urls), # the linked text 
    url = html_attr(urls, "href") ) %>% # the url (an html attribute)
    mutate(fileID = str_extract(url, "[0-9].*"), # the url contains the file name, but in this case, not the extension
           file_extention = str_replace(link_text, ".*PDF", ".pdf"), # but the linked text tells us the file type
           file_extention = str_replace(file_extention, "Image", ".tif") ) %>%
    filter(str_detect(url, "opennat")) %>%  # filter to get rows that have the files we want
    filter(link_text %in% c("Image", "PDF", "FERC Generated PDF") ) %>% # filter to pdf files
    mutate(index = row_number()) # add index 

  # merge with table by index
  d <- full_join(table_files, urls)  %>%
    # add the file name and file extension
    mutate(file_name = paste0(id, "-", fileID, file_extention) ) 

  # filter out files we already have
  to_download <- d %>% 
    filter(!file_name %in% list.files(here("FERC")) ) 
    
  ## Now we can use the function download.file(url, destfile)
  ## walk2() takes two vectors, .x and .y, and applies the function .f(.x, .y)
  ## Here, .x is url, .y is destfile, and .f is download.file():
  walk2(to_download$url, here("FERC", to_download$file_name), download.file)

  # Finally, select the columns we want and merge with the full table
  d %<>% 
    select(id, doc_date, filed_date, docket, summary, file_name, url, link_text) %>% 
    filter(!is.na(id)) %>%
    full_join(table) %>% 
    distinct()

  return(d)
}
```

Put all of the above together into a new function `scraper()`: 
```{r}
scraper <- function(web_page){
  
  # Get raw html
  html <- read_html(here("FERC", "html", web_page))

  table <- html %>% 
    html_nodes("table") %>%
    .[[3]] %>% # I happen to be interested in the third table on this page
    html_table(fill = T) %>% # turn html in to a data frame
    rename(id = X1,
           date = X2,
           docket = X3,
           summary = X4) %>% 
    filter(str_detect(id, "Submittal")) %>% # clean it up a bit
    gather(key = key, value = link_text, -id, -date, -docket, -summary) %>% #FIXME get private/public
    filter(link_text %in% c("Image", "PDF", "FERC Generated PDF", "MicroFilm") ) %>% #FIXME add doc types
    separate(date, c("doc_date", "filed_date"), sep = "\n\t") %>%
    mutate(doc_date = as.Date(doc_date, "%m/%d/%Y"),
           filed_date = as.Date(filed_date, "%m/%d/%Y") ) %>%
    # arrange(desc(link_text)) %>% # image before pdf
    arrange(id) %>% # id numbers count up
    arrange(desc(filed_date)) %>% # dates count down 
    mutate(id = str_remove(id, "Submittal")) %>% 
    mutate(id = str_replace(id, "Document Components", "(partial)")) %>% 
    select(-key)
  
  table_files <- table %>%
    filter(link_text %in% c("Image", "PDF", "FERC Generated PDF") ) %>% #FIXME
    mutate(index = row_number()) # add an index
  
  urls <- html %>% 
    html_nodes("table") %>%
    html_nodes("a") # "a" nodes contain url linked text
  
  urls <- tibble(
    link_text = html_text(urls), # the linked text 
    url = html_attr(urls, "href") ) %>% # the url (an html attribute)
    mutate(fileID = str_extract(url, "[0-9].*"), # the url contains the file name, but in this case, not the extension
           file_extention = str_replace(link_text, ".*PDF", ".pdf"), # but the linked text tells us the file type
           file_extention = str_replace(file_extention, "Image", ".tif") ) %>%
    filter(str_detect(url, "opennat")) %>%  # filter to get rows that have the files we want
    filter(link_text %in% c("Image", "PDF", "FERC Generated PDF") ) %>% # filter to pdf files
    mutate(index = row_number()) # add index 

  # merge with table by index
  d <- full_join(table_files, urls)  %>%
    # add the file name and file extension
    mutate(file_name = paste0(id, "-", fileID, file_extention) ) 

  # filter out files we already have
  to_download <- d %>% 
    filter(!file_name %in% list.files(here("FERC")) ) 
    
  ## Now we can use the function download.file(url, destfile)
  ## walk2() takes two vectors, .x and .y, and applies the function .f(.x, .y)
  ## Here, .x is url, .y is destfile, and .f is download.file():
  walk2(to_download$url, here("FERC", to_download$file_name), download.file)

  # Finally, select the columns we want and merge with the full table
  d %<>% 
    select(id, doc_date, filed_date, docket, summary, file_name, url, link_text) %>% 
    filter(!is.na(id)) %>%
    full_join(table) %>% 
    distinct()

  return(d)
}
```



```{r}
## map_dfr() takes a vector, .x and applies the function .f(.x), 
## binding the results as rows in a data frame
tables <- map_dfr(web_pages, scraper)

tables %<>% mutate(file_downloaded = file_name %in% list.files(here("FERC")))
tables %<>% mutate(file_nameNA = is.na(file_name))

dim(tables)
list.files(here("FERC"))
tables %>% group_by(link_text, file_nameNA) %>% tally()
tables %>% group_by(link_text, file_downloaded) %>% tally() %>% ungroup()


# pdf letters to text (note: could also OCR images, see html for image doc ids)
d <- tables



totext <- function(file_name){
  # paste pages
  text <- NA
  if(str_detect(file_name, "pdf")){
  text <- pdf_text(here("FERC", file_name))  %>% 
    paste(collapse = "<pagebreak>")
  }
  return(text)
}
# If possible, read text
d$text <- map(d$file_name, possibly(totext, NA_real_, quiet = T))
 
dim(d)
FERC_files <- d
save(FERC_files, file = here("data", "FERC_files.Rdata"))

##################################################################################
# FOR GOOGLE SHEET 
###################

# helper function
Clean_String <- function(string){
  string %<>% 
    stringr::str_replace_all("[^a-zA-Z\\s]", " ") %>% 
    stringr::str_replace_all("[\\s]+", " ")
  return(string)
}

# collapse to one obs per ID
log <- d %>%
  group_by(id) %>% 
  mutate(link_text = paste(link_text, collapse = "; "),
         file_name = paste(file_name, collapse = "; "),
         url = paste(url, collapse = "; "),
         text = paste(text, collapse = "<pagebreak>")) %>% 
  distinct() %>% 
  mutate(text_clean = Clean_String(text)) %>% 
  mutate(text_clean = str_remove_all(text_clean, "NA pagebreak|pagebreak NA|FERC PDF Unofficial |Document Conten| s tif ")) %>%
  arrange(desc(id)) %>%
  ungroup() 

head(log$text_clean)
```