---
title: "Tidy text analysis example: web scraping with `rvest`"
subtitle: "Companies that lobby the Federal Energy Regulatory Commission"
author: 
output:
    html_document:
    toc: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
## Run a setup.R script to load R packages and set defaults
#source(here::here("setup.R")) ## Alternatively: source("https://raw.githubusercontent.com/judgelord/PS811/master/setup.R")

## Modify some defaults for this example
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 8)
```


In addition to `rvest`, this example uses the `stringr`, `purrr`, and `magrittr` packages.

```{r libraries}
library(tidyverse)
library(rvest)
library(magrittr)
```

The aim is get the names of oil, gas, electric, and hydropower companies that lobby FERC from the FERC website.

Step 1: Instpect the URLs and source html (in Chrome: view->developer->view source)

Here is the first page under the "Oil Matters" tab; oil companies with "A" names
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/oil.asp") 

html %>% 
  html_nodes("strong") %>% # company names are in bold (HTML tag "<strong>")
  html_text() %>% # to plain text
  .[1:6] # the first 3 rows are web page headers
```

Gas companies with "A" names. Notice how the URL changed:
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/gas.asp") 

html %>% 
  html_nodes("strong") %>%
  html_text() %>% 
  .[4:6]
```


Gas companies with "B" names. Notice how the URL changed:
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/gas/gas-B.asp") 

html %>% 
  html_nodes("strong") %>% 
  html_text() %>%
  .[4:6]
```

In addition to "oil" and "gas," we have "electric" and "hydro" with pages A-Z (4 x 26 = 104 pages!), so lets make a function to grab the names from each page: 

2. Make a function, turning things that vary into variables.

A test run using `str_c` to combine strings:
```{r}
industry <- "gas"
letter <- "B"
str_c("https://www.ferc.gov/docs-filing/corp-off/", industry, "/", industry, "-", letter, ".asp")
```

Looks good! Forward!

`cross()` lists each possible combination of URL parts. Because it returns a list, we use `lift()` to allow `str_c()` to take a list and paste it together. `map()` then does this for each. 

```{r}
url_parts <- list(
  base_url <- "https://www.ferc.gov/docs-filing/corp-off/",
  industry = c("oil/oil-", "gas/gas-", "electric/electric-", "hydro/hydro-"),
  letter = LETTERS,
  end = ".asp"
)

url <- url_parts %>%
  cross() %>%
  map(lift(str_c)) %>%
  str_remove("/[a-z]*-A") # remove "/industry-A"

head(url)
```

Now we define a function to apply to each URL.
```{r}
scraper <- function(url){
  html <-  read_html(url) 

  corps <- html %>% 
    html_nodes("strong") %>% 
    html_text() %>%
    .[-c(1:3)]
  
  industry <- str_extract(url, "off/[a-z]*") %>% 
    str_remove("off/")

  ## Return a data frame with two variables, company and industry
  d <- tibble(company = corps,
              industry = industry)
  return(d)
}
```

`map()` each url into the function, i.e. *apply* the function to each. I wrap the `scraper` function in `possibly()` so that if a URL does not work, it keeps going, just returning `NA` rather than stopping at an error. Specifically I use `map_dfr` which returns a *data frame*, combining results with `rbind()`. See `?map()` and the `purrr` [cheatsheet](https://www.rstudio.com/resources/cheatsheets/#purrr).


```{r}
# map(.x = vector, .f = function)
corps_all <- map_dfr(url, possibly(scraper, NA_real_) ) 

corps_all %<>% 
  mutate(company = trimws(company) ) %>% # trim white space before and after company names
  filter(nchar(company)>1) %>% # filter out names less than 2 characters
  distinct() # drop duplicates

# save(corps_all, here("data", "DOE_FERC-corps.Rdata"))

corps_all
```


