---
title: "Tidy text example: web scraping and RegEx"
subtitle: "Companies that lobby the U.S. Federal Energy Regulatory Commission (FERC)"
author:
output:
    html_document:
      toc: true
      toc_float: true
      # code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE}
## Run a setup.R script to load R packages and set defaults
#source(here::here("setup.R")) ## Alternatively: source("https://raw.githubusercontent.com/judgelord/PS811/master/setup.R")

## Modify some defaults for this example
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 8,
                      warning = FALSE,
                      message = FALSE)
```


This example uses the `rvest`, `stringr`, `purrr`, `here` and `magrittr` packages. 

- [`stringr` cheatsheet](https://www.rstudio.com/resources/cheatsheets/#stringr)

- [RegEx cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/regex.pdf)  

- [`rvest` tutorial](https://www.datacamp.com/community/tutorials/r-web-scraping-rvest) 

- [`purrr` cheatsheet](https://www.rstudio.com/resources/cheatsheets/#purrr)

```{r libraries}
library(tidyverse)
library(rvest)
library(magrittr)
library(here)
```

The aim is to get the names of oil, gas, electric, and hydropower companies that lobby FERC from the [FERC website](https://www.ferc.gov/docs-filing/corp-off.asp?csrt=16593465655017166281) and match them to (1) [letters Members of Congress wrote to FERC](https://judgelord.github.io/correspondence/functions/DOE_FERC-scraper.html) and (2) [corporate and executive campaign contributions from DIME](https://data.stanford.edu/dime#download-data).

# Get corportations and corporate officials from the FERC website

### 1: Instpect the URLs and source html 
(in Chrome: view -> developer -> view source)

Here is the first page under the "Oil Matters" tab, [oil companies with "A" names](https://www.ferc.gov/docs-filing/corp-off/oil.asp):
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/oil.asp") 

html %>% 
  html_nodes("strong") %>% # company names appear with the HTML tag "<strong>"
  html_text() %>% # to plain text
  .[1:6] # the first 3 rows seem to be web page headers
```

Gas companies with "A" names. Notice how the URL changed:
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/gas.asp") 

html %>% 
  html_nodes("strong") %>%
  html_text() %>% 
  .[4:6]
```


Gas companies with "B" names. *Notice how the URL changed:*
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/gas/gas-B.asp") 

html %>% 
  html_nodes("strong") %>% 
  html_text() %>%
  .[4:6]
```

In addition to "oil" and "gas," we have "electric" and "hydro" with pages A-Z (4 x 26 = 104 pages!), so let's make a function to grab the names from each page. 

### 2. Make a function, turning things that vary into variables.

A test run using `str_c` to combine strings:
```{r}
industry <- "gas"
letter <- "B"
str_c("https://www.ferc.gov/docs-filing/corp-off/", industry, "/", industry, "-", letter, ".asp")
```

Looks good! Forward!

`cross()` lists each possible combination of URL parts. Because it returns a list, we use `lift()` to allow `str_c()` to take a list and paste it together. `map()` then does this for each. 

```{r}
url_parts <- list(
  base_url <- "https://www.ferc.gov/docs-filing/corp-off/",
  industry = c("oil/oil-", "gas/gas-", "electric/electric-", "hydro/hydro-"),
  letter = LETTERS, # LETTERS (A-Z) is built in to R
  end = ".asp"
)

url <- url_parts %>%
  cross() %>%
  map(lift(str_c)) %>%
  str_remove("/[a-z]*-A") # remove "/industry-A"

## Add odd ULS
url <- c(url,
         "https://www.ferc.gov/docs-filing/corp-off/gas/gas-U-V.asp",
         "https://www.ferc.gov/docs-filing/corp-off/gas/gas-X-Y-Z.asp")

head(url)
```

Define a function to apply to each URL.
```{r, include = TRUE}
scraper <- function(url){
  html <-  read_html(url) 

  ## Extract company names
  corps <- html %>% 
    html_nodes("strong") %>% 
    html_text() %>%
    .[-c(1:3)]
  
  ## Extract the industry back out of the URL
  industry <- str_extract(url, "off/[a-z]*") %>% 
    str_remove("off/")

  ## Return a data frame with two variables, company and industry
  d <- tibble(company = corps,
              industry = industry)
  return(d)
}
```

### 3. Apply the function to each URL

`map()` each URL into the function, i.e. *apply* the function to each. I wrap the `scraper` function in `possibly()` so that if a URL does not work, it keeps going, just returning `NA` rather than stopping at an error. Specifically, I use `map_dfr` which returns a *data frame*, combining results with `rbind()`. See `?map()` and the `purrr` [cheatsheet](https://www.rstudio.com/resources/cheatsheets/#purrr).


```{r}
FERC_corps <- map_dfr(url, possibly(scraper, NA_real_) ) 
head(FERC_corps)
```

Clean up a bit, using `stringr` functions to make this list of companies more likely to be found in other datasets.
```{r}
FERC_corps$company %<>% 
  str_replace_all("\r\n", ", ") %>% 
  str_remove_all("^, ") %>%
  trimws() # trim white space before and after company names

FERC_corps %<>% 
  filter(nchar(company)>1) %>% # filter out names less than 2 characters 
  filter(!company %in% c("FERC Online Support", "Note:","LLC", "Transportation, LLC")) %>% # not companies
  filter(!str_detect(company, "[0-9]{2}/[0-9]{2}/[0-9]{4}")) %>% # dates not companies
  distinct() # drop duplicates

## For matching, remove endings like ", Inc." etc. 
trim <- function(d){
d %>%
  str_remove_all("Village of |\\(.*|,.*| -.*| Pipe.*| Company.*| Corp.*| Energy.*| Holdings.*| Gas$| Project.*| Co.| Gen.| LLC| L.L.C.|  L.P.| Inc.| L.P.| Ltd.")
}

FERC_corps$company_short <- trim(FERC_corps$company) %>% trim()

head(FERC_corps)
```


```{r, include = FALSE}
## Correct over-trimmed names
FERC_corps %<>% 
  mutate(company_short = ifelse(company == "Columbia Energy Power Marketing Corporation", "Columbia Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Michigan Energy Exchange, LLC", "Michigan Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Midwest Energy, Inc.", "Midwest Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Northwest Pipeline LLC", "Northwest Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Peak Energy, Inc.", "Peak Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Public Service Company of New Mexico", "Public Service Company of New Mexico", company_short))%>%
  mutate(company_short = ifelse(company == "Salt Lake Energy Systems, LLC", "Salt Lake Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Natural Gas Pipeline Company of America", "Natural Gas Pipeline Company of America", company_short))%>%
  mutate(company_short = ifelse(company == "Natural Gas Trading Corporation", "Natural Gas Trading Corporation", company_short))%>%
  mutate(company_short = ifelse(company == "Energy, USA-TPC Corp.", "TPC", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Partners, L.L.C.", "New Energy Partners", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Service, LLC", "New Energy Service", company_short))%>%
  mutate(company_short = ifelse(company == "North Energy Associates, A Limited Partnership", "North Energy Associates", company_short))%>%
  mutate(company_short = ifelse(company == "Pipeline Company LLC", "Pipeline Company LLC", company_short))%>%
  mutate(company_short = ifelse(company == "Express Pipeline LLC", "Express Pipeline LLC", company_short))%>%
  mutate(company_short = ifelse(company == "American Energy Savings, Inc.", "American Energy Savings", company_short))%>%
  mutate(company_short = ifelse(company == "Electric Energy, Inc.", "Electric Energy, Inc.", company_short))%>%
  mutate(company_short = ifelse(company == "System Energy Resources, Inc., Llano Estacado Wind, LLC, System Energy Resources, Inc., Northern Iowa Windpower, LLC, and RS Cogen, L.L.C.", "System Energy Resources", company_short))%>%
  mutate(company_short = ifelse(company == "Public Service Company of Colorado", "Public Service Company of Colorado", company_short))%>%
  mutate(company_short = ifelse(company == "Southern Company Services, Inc.", "Southern Company", company_short))%>%
  mutate(company_short = ifelse(company == "International Energy Consultants", "International Energy Consultants", company_short))%>%
  mutate(company_short = ifelse(company == "Jackson Pipeline Company", "Jackson Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Southern Energy California", "Southern Energy California", company_short))%>%
  mutate(company_short = ifelse(company == "Tennessee Gas Pipeline Company, L.L.C.", "Tennessee Gas Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Select Energy New York, Inc.", "Select Energy New York", company_short))%>%
  mutate(company_short = ifelse(company == "Inland Corporation", "Inland Corporation", company_short))%>%
  mutate(company_short = ifelse(company == "Advanced Energy Systems, Inc.", "Advanced Energy Systems", company_short))%>%
  mutate(company_short = ifelse(company == "Consumers Energy Company", "Consumers Energy Company", company_short))%>%
  mutate(company_short = ifelse(company == "Boston Energy Trading and Marketing LLC", "Boston Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Complete Energy Services, Inc.", "Complete Energy Services", company_short))%>%
  mutate(company_short = ifelse(company == "El Paso Energy Intrastate, L.P.", "El Paso Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Houston Pipe Line Company LP", "Houston Pipe Line", company_short))%>%
  mutate(company_short = ifelse(company == "North American Energy, Inc.", "North American Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Spokane Energy, LLC", "Spokane Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Salem Energy Systems, LLC", "Salem Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "Direct", "Direct Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "DC", "DC Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "PS", "PS Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Coastal", "Coastal Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "CT", "CT Corporation", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Forest", "Forest Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Minnesota", "Minnesota Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "NW", "NW Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Rio Grande", "Rio Grande Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Plains", "Plains Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Portland", "Portland Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "AP", "AP Holdings", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Boundary", "Boundary Gas", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Columbia", "Columbia Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Independence", "Independence Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Lakeside", "Lakeside Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Mitchell", "Mitchell Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Stream", "Stream Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "AI", "AI Energy", company_short))

## Inspect over-trimmed company names
FERC_corps %>% filter(company_short %in% c("", "LLC", "Energy", "Pipeline", "Natural", "North", "New", "Express", "American", "Electric", "System", "Direct", "DC", "PS", "CT", "Forest", "International", "Tennessee", "Salt Lake", "Lakeside", "NW", "Jackson", "Public Service", "Peak", "Independence", "Select", "Portland", "Michigan", "Boundary", "Coastal", "Minnesota", "Midwest", "Columbia", "Plains", "Stream", "Mitchell", "AP", "Southern", "Ohio River", "Northwest", "Rio Grande", "AI", "Transportation", "12/20/2018", "Salem", "Boston", "Spokane", "El Paso", "Houston", "North American", "Consumers", "Advanced", "Complete", "Inland"))

FERC_corps %>% filter(str_detect(company_short, ","))

FERC_corps %>% group_by(company_short) %>% tally() %>% arrange(-n) 
```

```{r}
## Short to long names refrence variable
FERC_corps %<>% group_by(company_short) %>% mutate(company_short_refs = str_c(company, collapse = "; ")) %>% ungroup()

FERC_corps %>% group_by(company_short) %>% mutate(n=n()) %>% arrange(-n)
```


# Find company names in congressional letter texts
```{r}
## Make a single string of short corp names
ferc_short <- unique(FERC_corps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

## Load congressional letters data "FERC_files"
load(url("https://github.com/judgelord/correspondence/raw/master/data/FERC_files.Rdata")) # potentially change to google sheet

## Rename it
FERC_letters <- FERC_files

## Split availability status from summary
FERC_letters %<>% separate(summary, into = c("summary", "availability"), sep = "Availability: ")

## Combine letter summary and letter text
FERC_letters %<>% 
  mutate(text = str_c(text, sep = "; ")) %>%
  mutate(text = str_c(summary, text, sep = ". Letter Text: ")) 

## A helper function to select and combine a set of unique strings
str_unique <- function(x){
  str_c(unique(x), collapse="; ")
}

## Find corporation names in combined summary and text
FERC_letters$company_short <- str_extract_all(FERC_letters$text, ferc_short) %>% map_chr(str_unique) %>% str_remove_all("^; |; ; |; $")

## Number of letters where a company from the FERC website was found:
sum(FERC_letters$company_short!="")

## Companies found
unique(FERC_letters$company_short)
```


# Match corporations and officials to their campaign donations.

## Campaign contributions of companies listed on the FERC website
```{r}
## GET DIME DATA (caution, this is >3GB)
# download.file("https://dataverse.harvard.edu/api/access/datafile/2865300?gbrecs=true", 
#              destfile = here("data/dime_contributors.gz") ) 
# 
## DIME DATA
# dime <- read.csv(here("data/dime_contributors.csv"))

## TRIM DOWN TO POSSIBLE MATCHES
# dime %<>% filter(contributor.type == "C") # type C = corporation
# dime %<>% filter(str_detect(corpname, ferc_short))

## SAVE
# save(dime, file = here("data/dime_ferc_corporation_matches.Rdata"))
```

## Campaign contributions of individuals at Fortune 500 companies listed on the FERC website

#### Step 1. Match companies from the FERC webiste to DIME Fortune 500 dataset
```{r}
## Fortune 500 companies
download.file("https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/6R1HAS/DP6TOL", destfile = here("data", "DIME500.csv") )

dime500 <- read_csv(here("data", "DIME500.csv"))

# dime %<>% extractMemberName(members, recipient.name)

fortune500 <- unique(dime500$corpname) %>% 
  str_c(sep = "|", collapse = "|")


## DIME records that match a shortened version of a FERC company name
dime500_ferc <- dime500 %>% filter(str_detect(corpname, ferc_short))
save(dime500_ferc, file = here("data", "FERC_DIME-corps.Rdata"))

dime500_ferc_corps <- str_c(unique(dime500_ferc$corpname), collapse = "|")

## Fortune 500 indicator in corps data 
FERC_corps %<>% mutate(Fortune500 = str_detect(company, dime500_ferc_corps))
sum(FERC_corps$Fortune500)
save(FERC_corps, file = here("data", "DOE_FERC-corps.Rdata"))

## Fortune 500 indicator in letters data 
FERC_letters %<>% mutate(Fortune500 = str_detect(company_short, dime500_ferc_corps))
sum(FERC_letters$Fortune500)
save(FERC_letters, file = here("data", "DOE_FERC-letters-corps.Rdata"))
```


#### Step 2: Identify contributions to Members of Congress in DIME Fortune 500 data:
```{r}
## ID member names among donation recipients 
# dime500_ferc %<>% extractMemberName(members = members, col_name =  recipient.name)
```

## Campaign contributions of individuals listed on the FERC website

### Step 1: Get corporate contacts from FERC website

```{r}
#TO DO
```

### Step 2: Match with DIME contributors
```{r}
# DIME DATA
# dime <- read.csv(here("data/dime_contributors.csv"))

# TRIM DOWN TO INDIVIDUALS FROM FERC WEBSITE
# dime %<>% filter(contributor.type == "I") # type I = individual
# dime %<>% mutate(last_name = str_extract(dime$most.recent.contributor.name, "[a-z]*") )

# SUBSET TO PEOPLE IN FERC DATA 
# dime %<>% filter(last_name %in% ferc$last_name)

# Clean up DIME names 
# dime %<>% mutate(name = str_replace(most.recent.contributor.name, " dr | jr |[0-9]", " ") )
# dime %<>% mutate(name = str_replace(most.recent.contributor.name, "  ", " ") )
# dime %<>% mutate(first_name = str_extract(name, ", [a-z][a-z]*") )
# dime %<>% mutate(first_name = str_replace(first_name, ", ", ""))
# dime %<>% mutate(first_name2 = str_extract(dime$most.recent.contributor.name, ", [a-z]{2}*") )
# dime %<>% mutate(middle_initial = str_extract(name, " [a-z]$") )
# dime %<>% mutate(middle_initial = str_replace(middle_initial, " ", "") )
# dime$first_initial <- str_sub(dime$first_name, 1,1)

# SAVE
# save(dime, file = here("data/dime_ferc_fortune500_people_matches.Rdata"))
```




