---
title: "Tidy campaign contributions by industry (using CRP and DIME data)"
author:
output:
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, eval = FALSE}
ssh -Y judgelord@linstat.ssc.wisc.edu
cd ../../../project/judgelord/correspondence
ls
git pull
R
```

```{r setup, echo = FALSE}
library(tidyverse)
library(here)
library(magrittr)

  knitr::opts_chunk$set(echo = TRUE, # echo = TRUE means that your code will show
                        warning = FALSE,
                        message = FALSE,
                        fig.align = "center", 
                        fig.path= 'Figs/', ## where to save figures
                        fig.height = 3,
                        fig.width = 3)
```

# Compaign contributions from DIME
DIME SQL Query:
```{}
SELECT cycle, recipient_icpsr, recipient_type, recipient_name, recipient_icpsr, contributor_ext_id, bonica_rid, bonica_id2, contributor_category, sum(amount) AS sum_amount FROM newconts WHERE  recipient_type = 'CAND' AND seat IN ('federal:house', 'federal:senate') GROUP BY cycle, contributor_ext_id, recipient_icpsr INTO OUTFILE '/home/groups/andyhall/np_dime/GrimQuery.csv' FIELDS TERMINATED BY ',' ENCLOSED BY '"' LINES TERMINATED BY '\n';
```

```{r data}
# https://www.dropbox.com/s/m4bz7sbxebzowhp/GrimQuery.csv?dl=0
dime <- read_csv(here("data/GrimQuery.csv"), col_names = FALSE)

names(dime) <- c("cycle", "recipient_icpsr", "recipient_type", "recipient_name", "recipient_icpsr1", "contributor_ext_id", "bonica_rid", "bonica_id2", "contributor_category", "amount")

d <- dime
```

### 2012 and 2014 cycles are not correct due to some incorrect numbers for GRAYSON, ALAN MARK

[FEC cycle summaries](https://transition.fec.gov/press/campaign_finance_statistics.shtml)

For example, [this is what the 2014 cycle looks like](https://transition.fec.gov/press/summaries/2014/ElectionCycle/24m_CongCand.shtml)

```{r sum}
d %>% 
  group_by(cycle) %>% 
  tally(amount) %>% 
  knitr::kable() # %>% ggplot() + geom_col(x = cycle, y = n)

d %>% 
  arrange(-amount)

d %>% 
  arrange(-amount) %>% 
  head() %>% 
  knitr::kable()

d %<>% filter(amount < 1000000000)
```

### Drop negative contributions
```{r negative}
d %<>% filter(amount > -1)

```

## Select Industry PACs


(see money-matching script for now)

For all contributions, skip this step.

Missing contributor data for recent cycles:
```{r}
d %>% 
  filter(cycle > 1999) %>% 
  count(is.na(contributor_ext_id), cycle) %>% 
  knitr::kable()

# delete NA contributors for now
d %<>% filter(!is.na(contributor_ext_id))
```

Total industry PAC contributions per cycle
```{r crp}
# Energy sector PACs
crp <- read_csv(here("CRP Data/crpEnergy.csv"))
head(crp)

# New data just of contributions from selected industries
d %<>%
  filter(contributor_ext_id %in% crp$comid) %>%
  mutate(industry = "energy")

d %>% 
  #filter(cycle >1990) %>%
  group_by(cycle) %>% 
  tally(amount) %>% 
  knitr::kable() # %>% ggplot() + geom_col(x = cycle, y = n)
```

# Merge with voteview data
```{r voteview}
  
  #source(here("members/nameCongress.R")) # augments voteview member names
  ## Load augmented member names without having to load voteview package
  load(here("members/members.Rdata"))


# merge with voteview data 
join_members <- . %>% 
  mutate(icpsr = as.numeric(recipient_icpsr)) %>% 
  right_join(members %>% 
               select(icpsr, bioname, congress) %>% 
               mutate(cycle = (congress - 107)*2 + 2000) %>% 
               distinct()
             ) %>% 
  # where a member is not observed in a cycle in DIME, replace ammount with na
  mutate(amount = replace_na(amount, 0))

d %<>% join_members() %>% distinct()

# incpect 
# nrow(d)
head(d)
```



# Tally contributions per member per cycle per industry 
```{r sumarize}
# sum up by ICPSR and cycle
d %<>%
  mutate(industry = "energy") %>% 
  group_by(icpsr, congress, cycle, bioname, recipient_name, industry) %>%
  tally(amount) %>%
  ungroup()
nrow(d)


d_other <- dime %>%
  # PACs not in industry
  filter(!contributor_ext_id %in% crp$comid) %>%
  mutate(industry = "other") %>% 
  join_members() %>% 
  group_by(icpsr, congress, cycle, bioname, recipient_name, industry) %>%
  tally(amount) %>%
  ungroup()

# nrow(d)

d %<>% full_join(d_other) %>% 
  mutate(amounts = n)

# Make sure there are indeed 0 counts if we expect them
d %>% 
  filter(amounts == 0) %>%
  arrange(bioname)

# Make sure we have equal numbers of observations per industry
d %>% count(industry)

# inspect
head(d)  
# nrow(d)
```

## Voteview-DIME ICPSR name mismatches
```{r names}
# problem names
d %>% 
  ungroup() %>% 
  mutate(bioname = toupper(bioname),
         recipient_name = toupper(recipient_name)) %>% 
  filter(str_sub(bioname, 1,3) != str_sub(recipient_name,1 , 3),
         cycle > 1999) %>% 
  filter(!str_detect("SANCHEZ", recipient_name)) %>% 
  knitr::kable()
```


```{r}
d %<>% 
  distinct() %>%
  full_join(members %>% select(icpsr, congress, party_name)) %>% 
  # rename(party = party_name) %>% 
  distinct()

# inspect coverage 
d %>%
  group_by(cycle, icpsr, party_name, industry) %>% 
  summarise(total = sum(amounts, na.rm = TRUE)/1000000) %>% 
  ungroup() %>% 
  group_by(cycle, party_name, industry) %>% 
  summarise(mean = mean(total)) %>% 
  ggplot() + 
  aes(x = factor(cycle), y = mean, fill = party_name) + 
  geom_col() + 
  facet_grid(. ~ "industry") %>% 
  labs(y = "Average Energy-sector PAC contributions (millions) \n (ommitting energy extraction companies)", 
       x = "FEC Electoral Cycle")
```


# Save results
```{r save}
pac_amounts <- d
save(pac_amounts, file = here("data/pac_amounts.Rdata"))
```


```{r, echo = FALSE, eval = FALSE, include = FALSE}
q()
n
git pull
Rscript -e 'library(rmarkdown); rmarkdown::render("functions/read-dime.Rmd", "html_document")'
git add "data/pac_amounts.Rdata"
git add "functions/read-dime.html"
git commit -m "add pac data"
git pull
git push
judgelord
```