---
title: "Tidy campaign contributions by industry (using CRP and DIME data)"
author:
output:
    html_document:
      toc: true
      toc_float: true
      # code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, eval = FALSE}
ssh -Y judgelord@linstat.ssc.wisc.edu

cd ../../../project/judgelord/correspondence
ls
git pull
R
```

```{r setup, echo = FALSE}
  knitr::opts_chunk$set(echo = TRUE, # echo = TRUE means that your code will show
                        warning = FALSE,
                        message = FALSE,
                        fig.align = "center", 
                        fig.path= 'Figs/', ## where to save figures
                        fig.height = 4,
                        fig.width = 8)
```

# Compaign contributions from DIME
DIME SQL Query:
```{}
SELECT cycle, recipient_type, recipient_name, recipient_icpsr, bonica_cid, contributor_crp_id, contributor_nimsp_id, contributor_type, contributor_name, contributor_city, contributor_address, contributor_employer, contributor_occupation, contributor_ext_id, bonica_rid, bonica_id2, contributor_category, sum(amount) AS sum_amount FROM newconts WHERE  recipient_type = 'CAND' AND seat IN ('federal:house', 'federal:senate') GROUP BY cycle, bonica_cid, bonica_rid INTO OUTFILE '/home/groups/andyhall/np_dime/GrimQuery.csv' FIELDS TERMINATED BY ',' ENCLOSED BY '"' LINES TERMINATED BY '\n';
```

```{r libraries}
options(stringsAsFactors = F)
library(magrittr)
library(tidyverse)
library(here)
```

# DIME Data

## Different results from different parsing functions
```{r sql}
# https://www.dropbox.com/s/m4bz7sbxebzowhp/GrimQuery.csv?dl=0

dime_vars <- "cycle, recipient_type, recipient_name, recipient_icpsr, bonica_cid, contributor_crp_or_nimsp_id, contributor_type, contributor_name, contributor_city, contributor_address, contributor_employer, contributor_occupation, contributor_ext_id, bonica_rid, bonica_id2, contributor_category, sum(amount)"

dime_vars %<>% str_split(", ", simplify = T)
```

```{r read_lines, eval=FALSE, warning=TRUE}
dime.read.lines <- readLines(here("data/GrimQuery2.csv"))
dime.read.lines %>%
  length()

dime.read.lines %>% tail()

# problem lines
problemlines <- c(317397, 317398, 317399, 317400, 317401, 580138, 580139, 665253, 1588208, 3105970, 3238566, 3238567, 3238568, 3238569, 3238570, 3238571, 3238572, 3238573, 3238574, 3551218)

dime.read.lines[problemlines]

dime.read.lines %<>%
  #remove quotes at the begining and end of lines
  # str_remove_all("^\"|\"$") %>% 
  as_tibble() %>% 
  # head() %>% 
    # split out columns by quote comma quote
  separate(col = value, into= dime_vars, sep = "\",\"") # %>% .[1:100,]

dime.read.lines[problemlines,] %>% head()

# Make sure cycle is numeric
#head(d$cycle)
dime.read.lines$cycle %<>% 
  str_sub(2,5) %>% 
  # str_extract("[0-9]*") %>%
  as.numeric()
# head(d$cycle)

sum(is.na(dime.read.lines$contributor_ext_id))

## WORSE PARSING METHODS: 
dime.read.table <- read.table(here("data/GrimQuery2.csv"), header = FALSE, sep = ",", quote = "\"", col.names = dime_vars)

dim(dime.read.table)
sum(is.na(dime.read.table$contributor_ext_id))
```


```{r read_csv}
# Alternative parsing 
dime.read_csv <- read_csv(here("data/GrimQuery2.csv"), 
                          col_names = dime_vars,
                          quote = "\"")

dim(dime.read_csv)
tail(dime.read_csv) 
sum(is.na(dime.read_csv$contributor_crp_or_nimsp_id)) # CRP ID 
sum(is.na(dime.read_csv$contributor_ext_id)) # FEC ID
sum(is.na(dime.read_csv$bonica_cid)) # Bonica ID 

d <- dime.read_csv %>% rename("amount" = "sum(amount)") %>% as_tibble()
```

### Parsing errors

Some lines are failing to parse correctly. 

This is due to "EOF within quoted strings." (In python, pandas' `read.csv` has EOF errors unless I include `error_bad_lines=False`).

```
import pandas as pd 

data = pd.read_csv("data/GrimQuery.csv", delimiter=",", header = None, quoting=3, error_bad_lines=False)
```

The only special strings I've found are in empty strings `,\N,` or in names, indicating parenthesis around nicknames:
```
SMYSER, CHARLES A \SKIP\""
BOUCHER, FREDERICK C \RICK\""
```

These strings cause parsing errors but don't explain the missing contributor FEC IDs (`contributor_ext_id`):

```
"2016","20712","CAND","JOHNSON, HENRY C \"HANK\" JR","20712","","cand977","4044287089","X1200","445689.40000000055"

"2016","H0CA00082","CAND","PORTANTINO, ANTHONY","H0CA00082","",\N,"33334775774","","288494.78
```

Notice the empty `contributor_id` before `cand_id`: 

```
"2014","UT9458","CAND","ROBLES, LUZ M","UT9458","","cand143616","33309085731","X1200","500"
"2014","VA412936","CAND","SARVIS, ROBERT CHRISTOPHER","VA412936","","cand192377","4143347693","X1200","2580.4700000000003"
"2016","","CAND","crowley for congress nys","","","cand1529","3787846060","","110546.11000000002"
"2016","10713","CAND","CONYERS, JOHN JR","10713","","cand53","33489434680","","638116.7000000033"
```

### Ammount errors

2012 and 2014 cycles are not correct due to some incorrect numbers for GRAYSON, ALAN MARK

DIME data: 
```{r sum, echo= FALSE, include=FALSE}
head(d$amount)
# Make sure amount is numeric if using read.lines
d$amount %<>% 
  str_extract("[0-9]*") %>%
  as.numeric()
head(d$amount)
nrow(d)
```

Inspect for `NA` contribution amounts, very large amounts, and annual totals.
```{r}
d %>% count(is.na(amount))

# drop NA amounts 
d %<>% filter(!is.na(amount))

dim(d)

# Largest amounts
d %>% 
  arrange(-amount) %>% 
  head() %>% 
  knitr::kable()
```

Compare these totals to [FEC cycle summaries](https://transition.fec.gov/press/campaign_finance_statistics.shtml), e.g. [2014](https://transition.fec.gov/press/summaries/2014/ElectionCycle/24m_CongCand.shtml). 
```{r}
# total contributions by cycle
d %>% 
  group_by(cycle) %>% 
  summarise(total_amount = sum(amount)) %>% 
  knitr::kable() # %>% ggplot() + geom_col(x = cycle, y = n)
```


### Solution: Drop contributions over $1 billion

Largest contributions afer dropping those over $1 billion:
```{r}
d %<>% filter(amount < 1000000000)
dim(d)

d %>% 
  arrange(-amount) %>% 
  head() %>% 
  knitr::kable()

# total contributions by cycle
d %>% 
  filter(cycle>1999) %>% 
  group_by(cycle) %>% 
  summarise(total_amount = sum(amount)) %>% 
  knitr::kable()
```

### Drop negative contributions
```{r negative}
d %<>% filter(amount > -1)
dim(d)
```

### Missing contributor data for recent cycles?

`contributor_id` is missing post 2012. This is not a parsing error. 

Thus we need to merge in FEC IDs from elsewhere crosswalked with `bonica_cid`.
```{r missing_data}
# drop bonica cid "-1" because these seem to be errors
d %<>% filter(bonica_cid != "-1")
dim(d)

d %>% 
  filter(cycle > 1999) %>% 
  group_by(cycle) %>%
  summarise(unique_pacs = length(unique(bonica_cid))) %>%
  knitr::kable()


# Count NA contributor IDs
d %>% 
  filter(cycle > 1999) %>% 
  count(is.na(contributor_ext_id), cycle) %>% 
  knitr::kable()

# Count NA contributor IDs
d %>% 
  filter(cycle > 1999) %>% 
  count(is.na(contributor_crp_or_nimsp_id), cycle) %>% 
  knitr::kable()

# Count NA contributor IDs
d %>% 
  filter(cycle > 1999) %>% 
  count(is.na(bonica_cid), cycle) %>% 
  knitr::kable()
```


### Multiple `recipient_name`s per `icpsr`
```{r icpsrXnamesPx}
d %>% 
  group_by(recipient_icpsr) %>% 
  summarise(n = length(unique(recipient_name)),
            names = str_c(unique(recipient_name),  collapse = ";")) %>% 
  filter(n > 1)  %>% 
  distinct()
```

### Solution: Consolidate names by icpsr
```{r icpsr_names} 
d %<>% 
  group_by(recipient_icpsr) %>% 
  mutate(recipient_name = str_c(unique(recipient_name), collapse = ";")) %>% 
  ungroup()
dim(d)
```


### Correct incorrect ICPSRs to match voteview (TO DO)

Assuming DIME names are correct and ICPSRs are wrong.
```{r icpsr_corrections}
icpsr_errors <- c(21109, 20528, 21109, 21122, 21301, 21522, 41700)

d %>% 
  mutate(icpsr = as.numeric(recipient_icpsr)) %>% 
  select(icpsr, recipient_name) %>% 
  filter(icpsr %in% icpsr_errors) %>% 
  distinct()

# correct problem ICPSRs
DIME_corrections <- tribble(
  ~recipient_name, ~icpsr_correct,
"BABIN, BRIAN", "",   
"CLAWSON, CURTIS J","",
"DESAULNIER, MARK","",  
"HICE, JODY B MR", "",   
"WESTERMAN, BRUCE","",          
"WESTERMAN, BRUCE MR.","",     
"MCALLISTER, VANCE MICHAEL",""
)

```

# Select Industry PACs

(see pacs-from-crp for now)

For total contributions, skip this step.

## Top PAC donations in a cycle

> Why is `bonica_cid` "0" so often? (for 67 different FEC IDs)

```{r crp}
# Sector PACs
CRPindustry = "energy"
crp <- read_csv(here("CRP Data/crpEnergy.csv")) #FIXME make general path for any industry code. This script should just load in a universal crosswalk
head(crp)

# Crosswalk CRP ID--FEC ID--Bonica ID
crosswalk <- d %>% 
  select(contributor_ext_id, bonica_cid) %>% 
  distinct() %>% 
  left_join(crp %>% rename(contributor_ext_id = comid)) %>% 
  distinct() %>% 
  mutate(contributor_ext_id = replace_na(contributor_ext_id, "MISSSING"))

crosswalk %>% filter(!is.na(PACShort))

# how many FEC_IDs have the same bonica_cid?
crosswalk %>% # filter(!is.na(PACShort)) %>% 
  count(bonica_cid, sort = T)  %>% 
  filter(n >1)

#FIXME why is bonica ID is 0 for these FEC IDs
crosswalk %>% filter(bonica_cid == 0)
crosswalk %<>% filter(bonica_cid != 0)

# FIXME for now take take only the top 1 FEC ID per bonica ID
crosswalk %<>% 
  group_by(bonica_cid) %>% 
  top_n(1) 

# now how many FEC_IDs have the same bonica_cid? Should be 1 to 1
crosswalk %>% # filter(!is.na(PACShort)) %>% 
  count(bonica_cid, sort = T) %>% 
  filter(n >1)

# number of observations before merge
dim(d)

# join in crosswalk
d %<>% 
  select(-contributor_ext_id) %>% # drop the incomplete FEC ID
  left_join(crosswalk, by = "bonica_cid") %>%  # fill in with more complete version
  distinct() 

# check number of observations
dim(d)
dim(d %>% filter(amount >0))

# We now have new variables for select PACs
d %>%
  head() %>% 
  knitr::kable()

# check to make sure there are reasonable numbers of packs per cycle
d %>%   
  group_by(cycle) %>% 
  filter(contributor_ext_id == "MISSING") %>% 
  summarise(number_of_PACs = length(unique(d$UltOrg)),
            total_spending = sum(amount)) %>% 
  distinct() %>% 
  knitr::kable()
```


## There are  `r unique(d$contributor_ext_id) %>% length()` PACs in the DIME data and `r unique(crp$comid)%>% length()` PACs in the CRP energy-sector data.

## Top PACs
```{r top_pacs}
d %>% 
  group_by(UltOrg) %>% 
  summarise(number_of_contributions = n(),
            total_spending = sum(amount)) %>% 
  distinct() %>% 
  arrange(-total_spending) %>% 
  head() %>% 
  knitr::kable()

d %>% filter(cycle == 2016) %>% select(UltOrg) %>% filter(!is.na(UltOrg)) %>%  distinct()
```


# Merge with voteview data
```{r voteview}
  #source(here("members/nameCongress.R")) # augments voteview member names
  ## Load augmented member names without having to load voteview package
  load(here("members/members.Rdata"))

# function to merge DIME with voteview data 
join_members <- . %>% 
  mutate(icpsr = as.numeric(recipient_icpsr)) %>% 
  right_join(members %>% 
               select(icpsr, bioname, congress) %>% 
               mutate(cycle = (congress - 107)*2 + 2000) %>% 
               distinct()
             ) %>% 
  # where a member is not observed in a cycle in DIME, replace ammount with na
  mutate(amount = replace_na(amount, 0))

# add in voteview data
d %<>% join_members() %>% distinct()

# check number of observations
dim(d)
```

## Sum contributions per member per cycle per industry 
```{r sumarize}
# Make industry variable based on CRP industry codes
d %<>% mutate(industry = ifelse(contributor_ext_id %in% crp$comid, CRPindustry, "other"))

# Number of distinct pacs 
d %>% group_by(cycle, industry) %>%
  summarise(PACs = length(unique(contributor_ext_id))) %>% 
  filter(cycle > 2000) %>% 
    knitr::kable()

d %>% group_by(cycle, industry) %>%
  summarise(total_contributions = sum(amount)) %>% 
    filter(cycle > 2000) %>% 
    knitr::kable()

d %>% filter(cycle == 2012) %>% distinct() %>% 
  arrange(-amount) %>% head() %>% 
  select(cycle, recipient_name, bonica_cid, amount)
  kable()

# Tally contributions per member per cycle per industry 
d1 <- d %>%
  group_by(icpsr, congress, cycle, bioname, recipient_name, industry) %>%
  tally(amount) %>%
  ungroup() %>% 
  rename(amounts = n) %>% 
  distinct()
```

Check for zero counts
```{r zero}
# Make sure there are indeed 0 counts if we expect them
d1 %>% 
  mutate(zeros = amounts == 0) %>%
  count(industry, zeros)

# Make sure we have equal numbers of observations per industry
d1 %>% count(industry)
```


Duplicated member-year total observations?
```{r duplicated_names}
# count observations (there should be one per industry)
d1 %>% group_by(bioname, icpsr, congress, industry) %>% 
  mutate(n = n()) %>% 
  arrange(bioname) %>%
  filter(n > 1)

# inspect
# head(d1)  
# nrow(d)
```

## Voteview-DIME ICPSR name mismatches
```{r names}
# problem names
d1 %>% 
  ungroup() %>% 
  # split back out recipient name to compare to bioname
  mutate(recipient_name = str_split(recipient_name, ";")) %>% 
  unnest(recipient_name) %>% 
  # match cases
  mutate(bioname = toupper(bioname),
         recipient_name = toupper(recipient_name)) %>% 
  # identify cases where the first three letters don't match
  filter(str_sub(bioname, 1,3) != str_sub(recipient_name,1 , 3),
         cycle > 1999) %>% 
  # drop cases where mismatch is due to name formatting (usually maiden name)
  filter(!str_detect(recipient_name, "SANCHEZ|CARDENAS|JACKSON|LUJAN|BETO|WATSON|O HALLERAN|MASTO|WASSERMAN")) %>% 
  select(icpsr, bioname, recipient_name) %>% 
  distinct() %>% 
  knitr::kable()
```

name mismatches after correcting DIME ICPSRs (WE ARE ASSUMING DIME NAMES ARE CORRECT, RIGHT?)



```{r FERC-DIME-new, fig.width=10}
d1 %<>% 
  distinct() %>%
  full_join(members %>% select(icpsr, congress, party_name)) %>% 
  distinct()

d1 %>% group_by(cycle, industry, party_name) %>% 
  summarise(total = sum(amounts)) %>% filter(cycle >2010, industry == "energy") %>% arrange(party_name)

# inspect coverage 
d1 %>%
  group_by(cycle, icpsr, party_name, industry) %>% 
  summarise(total = sum(amounts, na.rm = TRUE)/1000000) %>% 
  ungroup() %>% 
  group_by(cycle, party_name, industry) %>% 
  summarise(mean = mean(total)) %>% # filter(cycle >2008, industry == "energy") %>% arrange(party_name)
  ggplot() + 
  aes(x = factor(cycle), y = mean, fill = party_name) + 
  geom_col() + 
  facet_wrap("industry", scales = "free") +
  labs(y = "Average Industry PAC contributions (millions)", 
       x = "FEC Electoral Cycle")
```


# Save results
```{r save}
pac_contributions <- d
save(pac_contributions, file = here("data/pac_contributions.Rdata"))

pac_amounts <- d1
save(pac_amounts, file = here("data/pac_amounts.Rdata"))
```

```{r load, include=FALSE, eval=FALSE}

load(here("data/pac_contributions.Rdata"))
d <- pac_contributions

load(here("data/pac_amounts.Rdata"))
d1 <- pac_amounts
```

```{r, echo = FALSE, eval = FALSE, include = FALSE}
q()
n
git pull
Rscript -e 'library(rmarkdown); rmarkdown::render("functions/read-dime.Rmd", "html_document")'
git add "data/pac_amounts.Rdata"
git add "functions/read-dime.html"
git commit -m "update pac data"
git pull
git push
judgelord
```