---
title: "Lobbying the U.S. Federal Energy Regulatory Commission (FERC)"
subtitle:
author:
output:
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
## Run a setup.R script to load R packages and set defaults
source("setup.R") 
## Alternatively: source("https://raw.githubusercontent.com/judgelord/PS811/master/setup.R")

## Modify some defaults for this example
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 8,
                      warning = FALSE,
                      message = FALSE)
```

# TO DO 
- add clean text from scraper to google sheet 
- add company names from company scraper to google sheet
- fix clean function to use new data
- match company names to donation (lobbyview)
- match company names to industry codes (center for responsive politics)

# Data

```{r cosigned}
data %>% 
  mutate(OCRsuccess = ifelse(str_detect(SUBJECT, "et al"), "et al",
                                 ifelse(str_detect(SUBJECT, "&"), "&", " neither"))) %>%
  group_by(year, OCRsuccess) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = maybe_cosigned) +
  geom_col() + theme_minimal()
```

```{r}
file.name <- "DOE_FERC Extended" # for testing
 
  data <- gs_title(file.name) %>% gs_read() # get data from google sheet
  
  # create agency column
  data$agency <- file.name
  
  # Format date, year, Congress, member name etc. 
  data$DATE %<>% as.Date("%m/%d/%Y")
  data %<>% mutate(year = as.numeric(substring(DATE,1,4) ))
  data %<>% mutate(congress = as.numeric(round((year - 2001.1)/2)) + 107) # the 107th congress began in 2001
  
  data %<>%
    mutate(chamber = ifelse(grepl("(Senate|Senator)",SUBJECT), 'Senate', NA)) %>% 
    mutate(chamber = ifelse(grepl("Represenatative|Representative|US Rep|Congressman|Congresswoman|Congresswomen", SUBJECT), "House", chamber)) %>% 
    # if both
    mutate(chamber = ifelse(grepl("(Senate|Senator)",
                                  data$SUBJECT) & grepl("Represenatative|Representative|US Rep|Congressman|Congresswoman|Congresswomen", data$SUBJECT),
                            'FIXME', chamber ))
```

## Types of requests: 
Rule-based coding of constituent type:
```{code, eval = FALSE}
data%<>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CONSTITUENT", SUBJECT, ignore.case = TRUE), "1", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CONSTITUENT", SUBJECT, ignore.case = TRUE), "1", CERTAINTY)) %>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), "5", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), "3", CERTAINTY)) %>%
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), "2", ALT_TYPE)) %>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", SUBJECT, ignore.case = TRUE), "5", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", SUBJECT, ignore.case = TRUE), "1", CERTAINTY)) %>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", SUBJECT, ignore.case = TRUE), "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", SUBJECT, ignore.case = TRUE), "1", CERTAINTY)) %>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), "4", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), "2", CERTAINTY)) %>%
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), "5", ALT_TYPE)) %>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("PUBLIC UTILITIES COMMISSION", SUBJECT, ignore.case = TRUE), "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("PUBLIC UTILITIES COMMISSION", SUBJECT, ignore.case = TRUE), "1", CERTAINTY)) 

data %<>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CONSTITUENT", text, ignore.case = TRUE), "1", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CONSTITUENT", text, ignore.case = TRUE), "1", CERTAINTY)) %>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", text, ignore.case = TRUE), "5", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", text, ignore.case = TRUE), "3", CERTAINTY)) %>%
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", text, ignore.case = TRUE), "2", ALT_TYPE)) %>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", text, ignore.case = TRUE), "5", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", text, ignore.case = TRUE), "1", CERTAINTY)) %>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", text, ignore.case = TRUE), "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", text, ignore.case = TRUE), "1", CERTAINTY)) %>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("NEW COAL", text, ignore.case = TRUE), "4", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("NEW COAL", text, ignore.case = TRUE), "2", CERTAINTY)) %>%
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("NEW COAL", text, ignore.case = TRUE), "5", ALT_TYPE)) %>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("PUBLIC UTILITIES COMMISSION", text, ignore.case = TRUE), "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("PUBLIC UTILITIES COMMISSION", text, ignore.case = TRUE), "1", CERTAINTY)) 
```


```{r data-coverage-by-type}
d %>% 
  filter(Type != "To be coded") %>%  
  mutate(total = n()) %>% 
  group_by(Type, total) %>% summarise(nT = n()) %>% 
  mutate(percent = paste0(nT, " = ", 100*round(nT/total, 2), "%")) %>% 
  ggplot() + 
  geom_col(aes(x = Type, y = nT)) + 
  geom_text(aes(x = Type, y = nT, label = percent), vjust = -.1) +
  labs(x = "",
       y = paste("Number of Contacts, N =", sum(nrow(df))),
       title = "") +
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x.top = element_text())
```




## Energy committee members
TODO
```{r committees}
# per capita per year, energy committee, non-energy committee

```

## Members who write FERC the most
TODO
```{r top-members}
# Top members + committee membership and companies 
```

## Most 
```{r top-companies}
# companies + members 
```

## Members often co-sign letters 
FIXME, calculate real data when we have coding. This is a rough under-estimate: 
```{r cosigned}
data %>% 
  mutate(probably_cosigned = ifelse(str_detect(SUBJECT, "et al"), "et al",
                                 ifelse(str_detect(SUBJECT, "&"), "&", " neither"))) %>%
  group_by(year, probably_cosigned) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = maybe_cosigned) +
  geom_col() + theme_minimal()
```


## Many letters are on behalf of projects in their districts
TODO

## Some letters are on behalf of donors
TODO

# Comparing FERC to other agencies
TODO 
```{r}

```
