---
title: "Lobbying the U.S. Federal Energy Regulatory Commission (FERC)"
subtitle:
author:
output:
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
## Run a setup.R script to load R packages and set defaults
source("setup.R") 
## Alternatively: source("https://raw.githubusercontent.com/judgelord/PS811/master/setup.R")

## Modify some defaults for this example
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 8,
                      warning = FALSE,
                      message = FALSE)
```

# TO DO 
- add clean text from scraper to google sheet 
- add company names from company scraper to google sheet
- fix clean function to use new data
- match company names to donation (lobbyview)
- match company names to industry codes (center for responsive politics)

# Data

```{r cosigned}
data %>% 
  mutate(OCRsuccess = ifelse(str_detect(SUBJECT, "et al"), "et al",
                                 ifelse(str_detect(SUBJECT, "&"), "&", " neither"))) %>%
  group_by(year, OCRsuccess) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = maybe_cosigned) +
  geom_col() + theme_minimal()
```

```{r}
load(here("data/correspondence.Rdata"))

data <- filter(d, agency == "DOE_FERC Extended")
```

<<<<<<< HEAD


Rule-based coding of constituent type (click `CODE` to see inductive coding rules):
```{code}
data %<>%
  ## Individual constituent service
=======
## Types of requests: 
Rule-based coding of constituent type:
```{code, eval = FALSE}
data%<>%
>>>>>>> f597251b33ffaf90cacc56a0f7109dc578fc2329
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CONSTITUENT", SUBJECT, ignore.case = TRUE), "1", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CONSTITUENT", SUBJECT, ignore.case = TRUE), "1", CERTAINTY)) %>%
  ## Policy work?
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), "5", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), "3", CERTAINTY)) %>%
  ## Or corporate service?
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), "2", ALT_TYPE)) %>%
  ## Policy work
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", SUBJECT, ignore.case = TRUE), "5", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", SUBJECT, ignore.case = TRUE), "1", CERTAINTY)) %>%
  ## Local government
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", SUBJECT, ignore.case = TRUE), "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", SUBJECT, ignore.case = TRUE), "1", CERTAINTY)) %>%
  ## Corporate service
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), "4", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), "2", CERTAINTY)) %>%
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), "5", ALT_TYPE)) %>%
  ## PUCs = nonprofits, right?
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("PUBLIC UTILITIES COMMISSION", SUBJECT, ignore.case = TRUE), "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("PUBLIC UTILITIES COMMISSION", SUBJECT, ignore.case = TRUE), "1", CERTAINTY)) 
```


```{r data-coverage-by-type}
d %>% 
  filter(Type != "To be coded") %>%  
  mutate(total = n()) %>% 
  group_by(Type, total) %>% summarise(nT = n()) %>% 
  mutate(percent = paste0(nT, " = ", 100*round(nT/total, 2), "%")) %>% 
  ggplot() + 
  geom_col(aes(x = Type, y = nT)) + 
  geom_text(aes(x = Type, y = nT, label = percent), vjust = -.1) +
  labs(x = "",
       y = paste("Number of Contacts, N =", sum(nrow(df))),
       title = "") +
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x.top = element_text())
```




## Energy committee members
TODO
```{r committees}
# per capita per year, energy committee, non-energy committee

```

## Members who write FERC the most
TODO
```{r top-members}
# Top members + committee membership and companies 
```

## Most 
```{r top-companies}
# companies + members 
```

## Members often co-sign letters 
FIXME, calculate real data when we have coding. This is a rough under-estimate: 
```{r cosigned}
data %>% 
  mutate(probably_cosigned = ifelse(str_detect(SUBJECT, "et al"), "et al",
                                 ifelse(str_detect(SUBJECT, "&"), "&", " neither"))) %>%
  group_by(year, probably_cosigned) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = maybe_cosigned) +
<<<<<<< HEAD
  geom_col() 
````

# About FERC 

FERC regulates electrictity markets, oil and gas pipelines, and hydropower and gas export terminal projects. 

FERC controls pipeline market entry. 



Refrences 

![Sources of Bureaucratic Delay: A Case Study of FERC Dam Relicensing](https://academic.oup.com/jleo/article/22/1/258/938707)

=======
  geom_col() + theme_minimal()
```


## Many letters are on behalf of projects in their districts
TODO

## Some letters are on behalf of donors
TODO

# Comparing FERC to other agencies
TODO 
```{r}

```
>>>>>>> f597251b33ffaf90cacc56a0f7109dc578fc2329
