
## PAC-specific contributions
```{r letters_PACs-data, fig.width=9.5, eval=FALSE}

# check to make sure it looks the same as the agregate data 
pac_amounts %>% 
  group_by(cycle, icpsr) %>% 
  summarise(total = sum(PAC_contributions, na.rm = TRUE)/1000000) %>% 
  ungroup() %>% 
  group_by(cycle) %>% 
  summarise(mean = mean(total)) %>% 
  ggplot() + 
  aes(x = factor(cycle), y = mean) + 
  geom_col() + 
  labs(y = "Average Energy-sector PAC contributions per member (millions) \n (ommitting energy extraction companies)", 
       x = "FEC Electoral Cycle")

contrib_matrix %>% 
  group_by(cycle, PACShort) %>% 
  summarise(total = sum(value, na.rm = TRUE)/1000000) %>%  # millions 
  ungroup() %>% 
    group_by(PACShort) %>% 
  mutate(PACtotal = sum(total, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(PAC = ifelse(PACtotal > quantile(PACtotal, .98), PACShort, NA)) %>% 
  ggplot() + 
  aes(x = factor(cycle), y = total, fill= PAC) + 
  geom_col() + 
  labs(y = "Energy-sector PAC contributions (millions) \n (ommitting energy extraction companies)", 
       x = "FEC Electoral Cycle",
       fill = "PACs in top 2%") + 
  scale_fill_viridis_d(option = "C", na.value = "grey50")

contrib_matrix %>% 
  mutate(cycle = str_sub(ICPSR, -4)) %>% 
  # FIXME
  filter(cycle < 2014) %>% 
  group_by(cycle, PACShort) %>% 
  summarise(PACcycle = sum(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
    group_by(PACShort) %>% 
  mutate(PACtotal = sum(PACcycle, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(PACtotal > quantile(PACtotal, .98)) %>%  
  arrange(-as.numeric(cycle)) %>% 
  kable()

# mere with letters data, d
contrib_matrix %<>% 
  dplyr::rename(icpsryear = ICPSR,
         PAC_contributions = value) %>% 
  mutate(cycle = str_sub(icpsryear, -4),
         icpsr = as.numeric(str_remove(icpsryear, cycle)),
         cycle = as.numeric(cycle)) %>% 
  filter(cycle > 1990)%>% 
  left_join(d %>% select(icpsr, name_state, party) %>% distinct())
```

We identify r length(unique(pac_amounts$comid)) PACs in the energy sector (oil, gas, and electricity) and match their PAC contributions to each member of congress. 

For example:

### The top PAC recipient in a single cycle
```{r letters_PACs, eval=FALSE}
letters_PACs <- d %>% 
  #FIXME
  filter(cycle <2014) %>% 
  filter(!is.na(ProBusiness)|!is.na(ProProject))%>% 
  group_by(icpsryear, cycle, name_state, party) %>%
  summarise(ProBusiness_Letters = n()) %>% 
  # join by ICPSR, adding a sum of sector PAC contributions per member
  left_join(contrib_matrix) %>% 
  ungroup() %>% 
  group_by(icpsr) %>% 
  mutate(party = paste(unique(party), collapse = ";")) %>% 
  mutate(party = str_remove(party, ";.*")) %>% 
  ungroup()

letters_PACs_cycle <- letters_PACs %>% 
  group_by(cycle, icpsr, name_state, party) %>%
  # delete PACs that did not give from list, but keep members that recieved no contributions
  mutate(PACShort = ifelse(PAC_contributions > 0, PACShort, NA)) %>% 
  summarise(PAC_contributions = sum(PAC_contributions),
            PACs = paste(unique(PACShort), collapse = ";")) %>% 
  ungroup() %>% 
  arrange(-PAC_contributions)

letters_PACs_cycle %>% top_n(1, PAC_contributions) %>% knitr::kable()
```

### The top PAC recipient overall 
```{r letters_PACs-total, eval = FALSE}
letters_PACs_total <- letters_PACs %>% 
  ungroup() %>% 
  group_by(icpsr, name_state) %>% 
  summarise(PAC_contributions = sum(PAC_contributions),
            PACs = str_c(unique(PACShort), collapse = ";")) %>% 
  filter(!is.na(name_state)) %>% 
  ungroup()

letters_PACs_total %>% top_n(1, PAC_contributions) %>% knitr::kable()
```



## PAC-level

### Before matching projects and companies to their parent companies: 
```{r pacs-corps, eval= FALSE}
# letter count per pac ~ pac contributions (lots of 0$-0letter pairs )
# 1. id pacs per letter - spit letters matching several pacs 
# 2. count up per member 
# 3. add 0s for all other pac-member-cycle compinations 
# merge in with contributions per pac per member 

# First, clean up the contributions data a bit

# a helper function to concat unique strings
unique_string <- . %>% 
  str_split(";") %>% 
  # select unique ones
  unlist() %>% 
  unique() %>% 
  trimws() %>% 
  # paste them back together to retrun a single value 
  paste(collapse = ";") %>%
  str_remove_all("na;|;na$|NA;|;NA$")

# Just the PAC names and IDs from the contributions matrix (will merge in relevent contributions later)
PACs <- contrib_matrix %>% 
  select(comid, UltOrg,Affiliate,PACShort) %>% distinct() %>% 
  # make a full list of pac-affiliated orgs
  group_by(comid) %>%
  mutate(UltOrg2 = str_c(UltOrg,Affiliate,PACShort, sep = ";") %>% 
           tolower() %>% 
           # select unique ones
           unique_string())

# A function to get matching names
get_pac <- function(corp, PAC){
  ifelse(str_detect(tolower(PAC), tolower(corp)), PAC, NA)
}

# A function to get IDs where names match 
get_pacID <- function(corp, PAC, PACid){
  ifelse(str_detect(tolower(PAC), tolower(corp)), PACid, NA) 
}


# corp = "Exxon"

# A function to augment the PAC data with any matching company names 
get_pacs <- function(corp){
PACs %>% 
    mutate(pacs = get_pac(tolower(corp), UltOrg2),
           pacIDs = get_pacID(tolower(corp), UltOrg2, comid)) %>% 
    ungroup() %>% 
    select(pacs, pacIDs) %>% 
    distinct() %>% 
    summarise_all(unique_string) %>% 
    mutate(company_short = corp)
}

# TESTING 
# corp = "Exxon"
# get_pacs(corp)
# corp <- dcorps$company_short[1]
# get_pacs(corp)

crosswalk <- map_dfr(dcorps$company_short, get_pacs)

crosswalk %<>% distinct()

# use crosswalk to merge in contribution data 
dpacs <- dcorps %>% 
  full_join(crosswalk) %>% 
  # letters per year per pac
  select(ID, position, company_short, position, pacs, pacIDs) %>% 
  distinct() %>% 
  mutate(pacIDs = str_split(pacIDs, ";")) %>% 
  unnest(pacIDs) %>% 
  distinct() %>% 
  # merge in pac totals
  dplyr::rename(comid = pacIDs) %>% 
  # merge in contribution data
  left_join(contrib_matrix) # %>% group_by(comid, position) %>% summarise(PAC_contributions)

dpacs %<>% 
  ungroup() %>% 
  filter(!is.na(ID), !is.na(comid)) %>% 
  select(ID, icpsryear, cycle, name_state, position, company_short, pacs, comid, PAC_contributions) %>% 
  distinct()
```


#### Pro-business letters linked to PAC contributions:
```{r pro-pacs, eval = FALSE}
dpacs %>% 
  filter(position %in% c("ProBusiness", "ProProject")) %>% 
  # select letters with an identified person
  drop_na(name_state, ID) %>%
  group_by(name_state, cycle, position, company_short, pacs, comid) %>% 
  distinct()%>%  summarise(PAC_contributions = sum(PAC_contributions, na.rm = T),
                           # FIXME 
                           # SHOULD NOT NEED UNIQUE HERE 
            Letter_IDs = paste(unique(ID), collapse = ";")) %>% 
  ungroup() %>% 
  group_by(position)  %>%
  top_n(10, PAC_contributions) %>% 
  knitr::kable()
```

#### Anti-business letters linked to PAC contributions:
```{r anti-pacs, eval = FALSE}
dpacs %>% 
  filter(position %in% c("AntiBusiness", "AntiProject")) %>% 
  left_join(d %>% select(ID, Constituent) %>% distinct() ) %>% 
  filter(Constituent == "No") %>%
  # select letters with an identified person
  drop_na(name_state, ID) %>%
  group_by(name_state, cycle, position, company_short, pacs, comid) %>% 
  distinct()%>%  summarise(PAC_contributions = sum(PAC_contributions, na.rm = T),
                           # FIXME 
                           # SHOULD NOT NEED UNIQUE HERE 
            Letter_IDs = paste(unique(ID), collapse = ";")) %>% 
  ungroup() %>% 
  group_by(position)  %>%
  top_n(10, PAC_contributions) %>% 
  knitr::kable()

#Before connecting companies to the PAC donations of their parent companies, we find `r sum(!is.na(dpacs$ID))` letters with a pack donation.
```
 



```{}
################################################   
# merge in and split out parent corps 

# TABLE 
letterID 
date
member
district 
committee 
position 
company
pac 
ammount 


# risiduals 
```



# References 

<!--
![Sources of Bureaucratic Delay: A Case Study of FERC Dam Relicensing](https://academic.oup.com/jleo/article/22/1/258/938707)
-->

