---
title: "Tidy text example: web scraping and RegEx"
subtitle: "Companies that lobby the U.S. Federal Energy Regulatory Commission (FERC)"
author:
output:
    html_document:
      toc: true
      toc_float: true
      # code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
## Run a setup.R script to load R packages and set defaults
#source("setup.R") ## Alternatively: source("https://raw.githubusercontent.com/judgelord/PS811/master/setup.R")

## Modify some defaults for this example
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 8,
                      warning = FALSE,
                      message = FALSE)
```


This example uses the `rvest`, `stringr`, `purrr`, `here` and `magrittr` packages. 

- [`stringr` cheatsheet](https://www.rstudio.com/resources/cheatsheets/#stringr)

- [RegEx cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/regex.pdf)  

- [`rvest` tutorial](https://www.datacamp.com/community/tutorials/r-web-scraping-rvest) 

- [`purrr` cheatsheet](https://www.rstudio.com/resources/cheatsheets/#purrr)

```{r libraries}
library(tidyverse)
library(rvest)
library(magrittr)
library(here)
```

The aim is to get the names of oil, gas, electric, and hydropower companies that lobby FERC from the [FERC website](https://www.ferc.gov/docs-filing/corp-off.asp?csrt=16593465655017166281) and match them to (1) [letters Members of Congress wrote to FERC](https://judgelord.github.io/correspondence/functions/DOE_FERC-scraper.html) and (2) [corporate and executive campaign contributions from DIME](https://data.stanford.edu/dime#download-data).


>**Note:** The R Markdown file that made this document is [here](https://github.com/judgelord/correspondence/blob/master/functions/DOE_FERC-company-scraper.Rmd).


# Get corporations and corporate officials from the FERC website

### 1: Instpect the URLs and source html 
(in Chrome: view -> developer -> view source)

Here is the first page under the "Oil Matters" tab, [oil companies with "A" names](https://www.ferc.gov/docs-filing/corp-off/oil.asp):
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/oil.asp") 

html %>% 
  html_nodes("strong") %>% # company names appear with the HTML tag "<strong>"
  html_text() %>% # to plain text
  .[1:6] # the first 3 rows seem to be web page headers
```

Gas companies with "A" names. Notice how the URL changed:
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/gas.asp") 

html %>% 
  html_nodes("strong") %>%
  html_text() %>% 
  .[4:6]
```


Gas companies with "B" names. *Notice how the URL changed:*
```{r}
html <- read_html("https://www.ferc.gov/docs-filing/corp-off/gas/gas-B.asp") 

# "strong" is bold in HTML
# in this case bolded text is company names
html %>% 
  html_nodes("strong") %>% 
  html_text() %>%
  .[4:6]
```


In addition to "oil" and "gas," we have "electric" and "hydro" with pages A-Z (4 x 26 = 104 pages!), so let's make a function to grab the names from each page. 

### 2. Make a function, turning things that vary into variables.

A test run using `str_c` to combine strings:
```{r}
industry <- "gas"
letter <- "B"
str_c("https://www.ferc.gov/docs-filing/corp-off/", industry, "/", industry, "-", letter, ".asp")
```

Looks good! Forward!

`cross()` lists each possible combination of URL parts. Because it returns a list, we use `lift()` to allow `str_c()` to take a list and paste it together. `map()` then does this for each. 

```{r}
url_parts <- list(
  base_url = "https://www.ferc.gov/docs-filing/corp-off/",
  industry = c("oil/oil-", "gas/gas-", "electric/electric-", "hydro/hydro-"),
  letter = LETTERS, # LETTERS (A-Z) is built in to R
  end = ".asp"
)

url <- url_parts %>%
  cross() %>%
  map_chr(lift(str_c)) %>%
  str_remove("/[a-z]*-A") # remove "/industry-A"

## Add odd ULS
url <- c(url,
         "https://www.ferc.gov/docs-filing/corp-off/gas/gas-U-V.asp",
         "https://www.ferc.gov/docs-filing/corp-off/gas/gas-X-Y-Z.asp")

head(url)
```

Define a function to apply to each URL.
```{r, include = TRUE}
scraper <- function(url){
  html <-  read_html(url) 

  ## Extract company names
  corps <- html %>% 
    html_nodes("strong") %>% 
    html_text() %>%
    .[-c(1:3)]
  
  ## Extract the industry back out of the URL
  industry <- str_extract(url, "off/[a-z]*") %>% 
    str_remove("off/")

  ## Return a data frame with two variables, company and industry
  d <- tibble(company = str_squish(corps),
              industry = industry) %>% 
    distinct()
  
  ## Get the names and addresses of company reps
  ## "ul" is an unordered list in HTML
  ## in this case, ul nodes contain the names and addresses of company representatives 
  contacts <- html %>% 
    html_nodes("strong, ul") %>%
    # instead of using html_text(), here I am just collapse the raw HTML into a single string
    str_c(collapse = "") %>% 
    # and split it out by the strong node so that each string starts with the company names I extracted above
    str_split("<strong>") %>% 
    unlist()
  
  ## Make a second dataframe of company names and addresses
  d2 <- tibble(contacts = contacts) %>% 
    separate(contacts, sep = "</strong>",
             into = c("company", "contacts"),
             extra = "merge") %>% 
    ## Clean up a bit
    mutate(company = str_remove(company, "^[^A-Z]*")) %>%
      mutate(company = str_remove(company, "amp;")) %>% # remove & symbol
    mutate(contacts = str_remove(contacts, "^[^A-Z]*")) %>% 
    mutate_all(str_squish) # remove extra white space
  
  ## keep just one contact per company
  d2 %<>% 
    distinct() %>% 
    filter(!is.na(contacts)) %>% 
    group_by(company) %>% 
    top_n(1)
  
  ## Join the company-contact data to the company-industry data
  # FIXME may fail where specials other than anp&, also Penola line break
  d %<>% left_join(d2) %>% distinct()
  
  return(d)
}
```

### 3. Apply the function to each URL

`map()` each URL into the function, i.e. *apply* the function to each. I wrap the `scraper` function in `possibly()` so that if a URL does not work, it keeps going, just returning `NA` rather than stopping at an error. Specifically, I use `map_dfr` which returns a *data frame*, combining results with `rbind()`. See `?map()` and the `purrr` [cheatsheet](https://www.rstudio.com/resources/cheatsheets/#purrr).


```{r}
# Test function on one url
FERC_corps <- map_dfr(url[1], possibly(scraper, NA_real_) ) 

# Apply to all urls
FERC_corps <- map_dfr(url, possibly(scraper, NA_real_) )  %>% distinct()
head(FERC_corps)

```

Clean up a bit, using `stringr` functions to make this list of companies more likely to be found in other datasets.
```{r}
FERC_corps$company %<>% 
  str_replace_all("\r\n", ", ") %>% 
  str_remove_all("^, ") %>%
  trimws() # trim white space before and after company names

FERC_corps %<>% 
  filter(nchar(company)>1) %>% # filter out names less than 2 characters 
  filter(!company %in% c("FERC Online Support", "Note:","LLC", "Transportation, LLC")) %>% # not companies
  filter(!str_detect(company, "[0-9]{2}/[0-9]{2}/[0-9]{4}")) %>% # dates not companies
  distinct() # drop duplicates

## For matching, remove endings like ", Inc." etc. 
trim <- . %>%
  str_remove_all("Companies of |Village of |\\(.*|,.*| -.*| Pipe.*| Company.*| Corp.*| Energy.*| Holdings.*| Gas$| Project.*| Co\\.| Co$| Gen.| LLC| L.L.C.|  L.P.| Inc.| L.P.| Ltd.| LP| Limited Partnership| Limited Liability| Transportation and Storage| Storage and Transportation| Arkansas$") %>% 
  str_remove_all("^, ") %>%
  trimws()  # filter out names less than 2 characters 

FERC_corps$company_short <- trim(FERC_corps$company) %>% trim()

FERC_corps %<>% filter(nchar(company_short)>1,
                       company_short != "Â")

head(FERC_corps %>% select(company_short, everything()))
```


```{r, include = FALSE}
## Correct over-trimmed names
FERC_corps %<>% 
  mutate(company_short = ifelse(company == "Columbia Energy Power Marketing Corporation", "Columbia Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Michigan Energy Exchange, LLC", "Michigan Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Midwest Energy, Inc.", "Midwest Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Northwest Pipeline LLC", "Northwest Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Peak Energy, Inc.", "Peak Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Public Service Company of New Mexico", "Public Service Company of New Mexico", company_short))%>%
  mutate(company_short = ifelse(company == "Salt Lake Energy Systems, LLC", "Salt Lake Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Natural Gas Pipeline Company of America", "Natural Gas Pipeline Company of America", company_short))%>%
  mutate(company_short = ifelse(company == "Natural Gas Trading Corporation", "Natural Gas Trading Corporation", company_short))%>%
  mutate(company_short = ifelse(company == "Energy, USA-TPC Corp.", "TPC", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Partners, L.L.C.", "New Energy Partners", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Service, LLC", "New Energy Service", company_short))%>%
  mutate(company_short = ifelse(company == "North Energy Associates, A Limited Partnership", "North Energy Associates", company_short))%>%
  mutate(company_short = ifelse(company == "Pipeline Company LLC", "Pipeline Company LLC", company_short))%>%
  mutate(company_short = ifelse(company == "Express Pipeline LLC", "Express Pipeline LLC", company_short))%>%
  mutate(company_short = ifelse(company == "American Energy Savings, Inc.", "American Energy Savings", company_short))%>%
  mutate(company_short = ifelse(company == "Electric Energy, Inc.", "Electric Energy, Inc.", company_short))%>%
  mutate(company_short = ifelse(company == "System Energy Resources, Inc., Llano Estacado Wind, LLC, System Energy Resources, Inc., Northern Iowa Windpower, LLC, and RS Cogen, L.L.C.", "System Energy Resources", company_short))%>%
  mutate(company_short = ifelse(company == "Public Service Company of Colorado", "Public Service Company of Colorado", company_short))%>%
  mutate(company_short = ifelse(company == "Southern Company Services, Inc.", "Southern Company", company_short))%>%
  mutate(company_short = ifelse(company == "International Energy Consultants", "International Energy Consultants", company_short))%>%
  mutate(company_short = ifelse(company == "Jackson Pipeline Company", "Jackson Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Southern Energy California", "Southern Energy California", company_short))%>%
  mutate(company_short = ifelse(company == "Tennessee Gas Pipeline Company, L.L.C.", "Tennessee Gas Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Select Energy New York, Inc.", "Select Energy New York", company_short))%>%
  mutate(company_short = ifelse(company == "Inland Corporation", "Inland Corporation", company_short))%>%
  mutate(company_short = ifelse(company == "Advanced Energy Systems, Inc.", "Advanced Energy Systems", company_short))%>%
  mutate(company_short = ifelse(company == "Consumers Energy Company", "Consumers Energy Company", company_short))%>%
  mutate(company_short = ifelse(company == "Boston Energy Trading and Marketing LLC", "Boston Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Complete Energy Services, Inc.", "Complete Energy Services", company_short))%>%
  mutate(company_short = ifelse(company == "El Paso Energy Intrastate, L.P.", "El Paso Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Houston Pipe Line Company LP", "Houston Pipe Line", company_short))%>%
  mutate(company_short = ifelse(company == "North American Energy, Inc.", "North American Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Spokane Energy, LLC", "Spokane Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Salem Energy Systems, LLC", "Salem Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "Direct", "Direct Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "DC", "DC Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "PS", "PS Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Coastal", "Coastal Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "CT", "CT Corporation", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Forest", "Forest Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Minnesota", "Minnesota Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "NW", "NW Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Rio Grande", "Rio Grande Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Plains", "Plains Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Portland", "Portland Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "AP", "AP Holdings", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Boundary", "Boundary Gas", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Columbia", "Columbia Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Independence", "Independence Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Lakeside", "Lakeside Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Mitchell", "Mitchell Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Stream", "Stream Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "AI", "AI Energy", company_short))

## Inspect over-trimmed company names
FERC_corps %>% filter(company_short %in% c("", "LLC", "Energy", "Pipeline", "Natural", "North", "New", "Express", "American", "Electric", "System", "Direct", "DC", "PS", "CT", "Forest", "International", "Tennessee", "Salt Lake", "Lakeside", "NW", "Jackson", "Public Service", "Peak", "Independence", "Select", "Portland", "Michigan", "Boundary", "Coastal", "Minnesota", "Midwest", "Columbia", "Plains", "Stream", "Mitchell", "AP", "Southern", "Ohio River", "Northwest", "Rio Grande", "AI", "Transportation", "12/20/2018", "Salem", "Boston", "Spokane", "El Paso", "Houston", "North American", "Consumers", "Advanced", "Complete", "Inland", "Limited Partnership", "RTO")) %>% select(company_short)

## Companies with a comma in their name
FERC_corps %>% filter(str_detect(company_short, ","))

## Count by company
FERC_corps %>% group_by(company_short) %>% tally() %>% arrange(-n) 

## Count by company arranged by length of company name (short to long)
FERC_corps %>% group_by(company_short) %>% tally() %>% arrange(nchar(company_short)) %>% mutate(nchar = nchar(company_short))

## Count by company arranged by length of company name (long to short)
FERC_corps %>% group_by(company_short) %>% tally() %>% arrange(-nchar(company_short)) 
```

Inspect especially short and long company names:
```{r}
## Short to long names refrence variable
FERC_corps %<>% group_by(company_short) %>% 
  mutate(company_short_refs = str_c(company, collapse = "; "),
         contacts_refs = str_c(contacts, collapse = "; ")) %>% 
  ungroup() %>% 
  distinct()

FERC_corps %>% count(company_short, company_short_refs) %>% arrange(-n)

```


## Get congressional districts by company zipcode

Here we use `psvR` to access VoteSmart data via their API (this requires an API key)
```{r votesmart, eval=FALSE, include=FALSE}
# look up congressional districts with psvR
FERC_corps %<>% 
  mutate(zip = str_extract(contacts_refs, "[0-9]{5}") ) 

FERC_corps %>% count(company, industry) %>% arrange(-n)

d <- filter(FERC_corps, !is.na(zip)) %>% 
  select(company, zip, industry) %>% 
  distinct() %>% 
  group_by(company, zip) %>% 
  summarise(industry = str_c(industry, collapse  = ";"),
            n = n()) %>% 
  arrange(-n)

head(d) 

zips <- list(d$zip)

# install.packages("pvsR")
library(pvsR)
source("assets/pvs-key.R")

district <- District.getByZip(list(10001,10002))

d$districts <- districts 

d %<>% mutate(industry = str_split(industry, ";")) %>% 
unnest()

FERC_corps %<>% full_join(d)

FERC_corps %>% 
  group_by(company_short, company_short_refs, contacts_refs) %>% 
  summarise(industry = str_c(industry, sep = ";", collapse = ";"))
```

These data are saved as `DOE_FERC-corps.Rdata` in the `data` folder of this repository.
```{r save}
# Save 
save(FERC_corps, file = here("data", "DOE_FERC-corps.Rdata"))
```


```{r unknown-zips, eval=FALSE, include=FALSE}
# Note cases where company is in Canada
FERC_corps %<>% mutate(zip = ifelse(is.na(zip) & str_detect(contacts_refs, "Alberta|Ontario|Canada|Quebec|Tiverton, ON"), "Canada", zip))

found <- FERC_corps %>% select(company, company_short, industry, zip) %>% filter(!is.na(zip))

unfound <- FERC_corps %>% select(company_short, industry, zip, contacts_refs) %>% filter(is.na(zip)) %>% distinct()

unfound_from_letters <- dcorps %>% filter(!company_short %in% found$company_short,
                                          !company %in% found$company) %>%
  count(company_short) %>%
  arrange(-n)




parent_companies <- gs_title("parent_companies") %>% gs_read() # get data

parent_companies_found <- partent_companies %>% 
  # add zips for companies
  left_join(FERC_corps %>% select(company_short,zip)) %>% 
  filter(!is.na(zip))

parents_found <- parent_companies %>% 
  # remove cases where company zip is found
  anti_join(parent_companies_found) %>%
  # add zips for parent companies
  left_join(FERC_corps %>% select(company_short, zip) %>% rename(parent_short = company_short)) %>% 
  filter(!is.na(zip)) %>% distinct()

parent_companies_found %<>% full_join(parents_found) %>% distinct()

parent_companies %<>% full_join(parent_companies_found) %>% distinct()

parent_companies %<>% full_join(FERC_letters %>% select(company_short, zip) %>% distinct()) %>% distinct()


```
