---
title: "How to convert pdfs to a data frames in **R**"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
                      #fig.path = "data")
source(here::here("setup.R"))
```

This example uses the `tidyverse` packages `stringr`, `purrr`, as well as `here` and `magrittr`. 

- [`stringr` cheatsheet](https://www.rstudio.com/resources/cheatsheets/#stringr)

- [RegEx cheatsheet](https://github.com/rstudio/cheatsheets/raw/master/regex.pdf)  

- [`purrr` cheatsheet](https://www.rstudio.com/resources/cheatsheets/#purrr)

```{libraries, echo = FALSE}
library(here)
library(tidyverse) # includes stringr and dplyr
library(magrittr)
library(pdftools)
```

Say we have a bunch of pdfs that look like [this](https://github.com/judgelord/correspondence/blob/master/data/Congressional%20logs%20Dec%202017-May%202019.pdf). This one has over 200 pages, so this would be a lot to re-arange by hand. 

Let us start by cleaning one file
```{r}
text <- pdf_text(here("data/Congressional logs Dec 2017-May 2019.pdf")) 

text[1:2]

# replace all line breaks ("\n") with a space
text %<>% str_replace_all("\n", " ")

# replace one or more spaces with a single space using the regular expression "+" for a pattern repeating one or more times
text %<>% str_replace_all(" +", " ")

# remove white space from the beginning and end of the string
text %<>% str_trim() 

# str_squish is equivelent to both str_trim()/trimws() and str_replace_all(" +", " ")
text %<>% str_squish()


text[1:2] 


# make it a tibble (a tidy data frame) 
d <- tibble(text = text)

d[1:2, ]

# split into columns by a Regex pattern "sep = "[regex]"
d %<>%
  separate(text, into = c("header", "text"), sep = "Title:") %>% 
  # drop header
  select(-header)


d

# split out additional columns
d %<>% 
  tidyr::separate(text, 
           into = c("Title", "Subject", "Control", "Assigned","Created", "Signature", "DATE", "Addressee", "Received", "Action", "Completed", "Priority", "Due", "Point of Contact", "Status"), 
           sep = c("Subject:|Control:|Assigned To:|Created Date:|Signature Level:|Correspondence Date:|Addressee Office:|Received Date:|Action Requested:|Completed Date:|Priority:|Due Date:|Point of Contact:|Status:"), # RegEx pattern of separators
           extra = "merge") # past any extra text at the end rather than dropping it
  
d %>% select(Title, Subject, DATE)
```


Trim white space at the beginning and end of each cell with `str_squish`. Apply to all columns with `mutate_all()`.
```{r}
d %<>% mutate_all(str_squish)

d %>% select(Title, Subject, DATE)
```


Save as .csv
```{r}
d %<>% write_csv(path = "DOE Dec 2017-May 2019.csv")
```

# Make a function

Turn the code we used to clean one file above in a function:

```{r}
# the new function, pdf_to_dataframe(), takes one argument, a file name
pdf_to_dataframe <- function(file){
  
text <- pdf_text(here(file)) # the only change is that I replaced the file string with a *variable* called file.

  # replace all line breaks ("\n") with a space
  text %<>% str_replace_all("\n", " ")
  
  # make it a tibble (a tidy data frame) 
  d <- tibble(text = text)
  
  # split into columns by a Regex pattern "sep = "[regex]"
  d %<>%
    separate(text, into = c("header", "text"), sep = "Title:") %>% 
    # drop header
    select(-header)
  
  # split out additional columns
  d %<>% 
    tidyr::separate(text, 
             into = c("Title", "Subject", "Control", "Assigned","Created", "Signature", "DATE", "Addressee", "Received", "Action", "Completed", "Priority", "Due", "Point of Contact", "Status"), 
             sep = c("Subject:|Control:|Assigned To:|Created Date:|Signature Level:|Correspondence Date:|Addressee Office:|Received Date:|Action Requested:|Completed Date:|Priority:|Due Date:|Point of Contact:|Status:"), # RegEx pattern of separators
             extra = "merge") # past any extra text at the end rather than dropping it
    
  d %<>% mutate_all(str_squish)
  
  return(d) # return the output of the function 
}
```

Let us test out our new function
```{r}
pdf_to_dataframe("data/Congressional logs Dec 2017-May 2019.pdf")
```

# Apply our function to all pdfs with `map_dfr` from `purrr`
```{r}
files <- c("data/Congressional logs Dec 2017-May 2019.pdf")

# apply (map) our function onto each of our files and make a data frame (df) by combining them by row (r)
d <- map_dfr(files, pdf_to_dataframe)

d %<>% write_csv(path = "DOE_combined.csv")
```