---
title: "company-crosswalk"
author: "Devin Judge-Lord"
date: "10/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("setup.R")
```

```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='Figs/',
                      warning=FALSE, 
                      message=FALSE)
```

# Data
```{r data}
# Coded letters, one obs per member per letter 
load(here("data/DOE_FERC-letters-coded.RData")) 

dcorps <- FERC_letters %<>% 
  filter(year > 1999) %>% 
  select(ID, 
         Freelancer,
         # Cosigned_House, Cosigned_Senate,
         # text_clean, 
         # year,
         # lace_State, Place_District, Place_District, 
         ProBusiness, AntiBusiness, ProProject, AntiProject) %>%
  distinct() %>% 
  group_by(ID, Freelancer)
```

## Top companies in pro-business letters
These data have four variables `ProBusiness`, `AntiBusiness`, `ProProject`, and `AntiProject`. To identify company names, I consolidate business and project variables for each side, and then split out each named business or project, making pro or and anti a new variable called `position`.
```{r probusiness-letters}
# Combine business and project 
dcorps %<>%
  summarise(pro = str_c(ProBusiness, ProProject, sep = ";", collapse = ";"),
            anti = str_c(AntiBusiness, AntiProject, sep = ";", collapse = ";")) %>% 
  arrange(rev(ID))

# Split out to one obs per letter per business
# First, turn Pro and Anti Business to be variable describings names in business
dcorps %<>% 
  gather(-ID, -Freelancer, key = "position", value = "company")

# Then split out multiple names 
dcorps %<>%
  mutate(company = company %>% str_split(";")) %>%
  unnest(company) %>% 
  distinct()
```

Businesses most often supported
```{r probusiness_top10}
# Inspect top 10% pro
dcorps %>%
  filter(position == "pro",
         !is.na(company),
         !str_detect(company, "Regional Transmission Organization") ) %>%
  group_by(company) %>%
  distinct() %>%
  summarise( n = n() , 
             ID = str_c(unique(ID), collapse = "; ")) %>%
  filter(n>quantile(n,.9))%>%
  arrange(-n) %>%
  knitr::kable(label = "probusiness")
```

Businesses most often opposed
```{r antibusiness_top10}
# Inspect top 10% pro
dcorps %>%
  filter(position == "anti",
         !is.na(company),
         !str_detect(company, "Regional Transmission Organization") ) %>%
  group_by(company) %>%
  distinct() %>%
  summarise( n = n() , 
             ID = str_c(unique(ID), collapse = "; ")) %>%
  filter(n>quantile(n,.9))%>%
  arrange(-n) %>%
  knitr::kable(label = "antibusiness")
```


## Letters citing companies registered with FERC
Of the companies registered to file with FERC, several appear in the letter texts. Here `company_short` is a shortened version a name that refrences several affiliated companies, each of which are registered separatly. 
*TO DO:* 

- (1) Identify linked corporations for other top companies in the data using [this sheet](https://docs.google.com/spreadsheets/d/1FjZIuz8T97nczCbYskjT7-Hl6we6hoa6VndOnFmKDGU/edit#gid=0)

```{r}
# business names from FERC website
load(here("data", "DOE_FERC-corps.Rdata"))

## Make a single string of short corp names
ferc_short <- unique(FERC_corps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

# bad string? 
# str_detect("", ferc_short)

save(ferc_short, file = here("data/ferc_short.Rdata"))
```




---

## Company lookup table

Clean companies names extracted from letters and create shortened name that is more likely to be found in other datasets (like done with FERC-registerd companies above).
```{r company-inspect}
# Clean things up
dcorps %<>% mutate(company = company %>%
                     # spell out RTO
                     str_replace("RTO", 
                                 "Regional Transmission Organization") %>%
                     # trim white space before and after company name
                     str_squish()  )





## For matching, remove endings like ", Inc." etc. 
trim <- . %>%
  # remove common endings 
  str_remove_all(" Company.*| \\(.*| Inc.*| LLC.*| Energy.*") %>% 
  # remove other common strings that don't help
  str_remove_all("Village of |\\(.*|,.*| -.*|^Proposed | Pipe.*| pipe.*| project$| Proiects$| Company.*| Comnany| Corp.*| Co$| Co.$| Energy$| energy$| power$| Power marketing$| Holdings.*| Group$| Gas$| Project.*| LLC| L.L.C.|  L.P.|^The | Inc.| L.P.| Ltd.| LP| Limited Partnership| Limited Liability|  Facility| Transportation and Storage| Storage and Transportation") %>% 
  str_remove_all("^, ") %>%
  str_squish()  # filter out names less than 2 characters 

# make a shortened version of the
dcorps %<>% 
  mutate(company_short = trim(company) %>% trim() ) %>% 
  distinct()


```

Problem company names that may need to be fixed (e.g. to remove special characters or spell out abbreviated name)
```{r problem-names}
# Problem Names?
# Inspect short company names
dcorps %>% filter(nchar(company)<2) %>% knitr::kable()
dcorps %>% filter(nchar(company_short)<2) %>% knitr::kable()

# drop names 1 character or less (not "BP")
dcorps %<>%   
  filter(nchar(company)>1) %>%
  filter(nchar(company_short)>1) %>%
  distinct() # drop duplicates
```


Identify short names by hand: 
```{r, lookup-table}
## Correct over-trimmed company short names
dcorps %<>% 
  mutate(company_short = ifelse(company == "Columbia Energy Power Marketing Corporation", "Columbia Energy", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "NED|Northeast Energy Direct|Northeast Energy District"), "Kinder Morgan", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "Sun Pipeline|Sun Pipe Line"), "Sun Pipe Line", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "Michigan Energy Exchange, LLC"), "Michigan Energy", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "Midwest Energy, Inc."), "Midwest Energy", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "Northwest Pipeline LLC"), "Northwest Pipeline", company_short))%>%
  mutate(company_short = ifelse( str_detect(company, "^Dominion"), 
                                 "Dominion", company_short))%>%
  mutate(company_short = ifelse(company == "Peak Energy, Inc.", "Peak Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Public Service Company of New Mexico", "Public Service Company of New Mexico", company_short))%>%
  mutate(company_short = ifelse(company == "Salt Lake Energy Systems, LLC", "Salt Lake Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Natural Gas Pipeline Company of America", "Natural Gas Pipeline Company of America", company_short))%>%
  mutate(company_short = ifelse(company == "Natural Gas Trading Corporation", "Natural Gas Trading Corporation", company_short))%>%
  mutate(company_short = ifelse(company == "Energy, USA-TPC Corp.", "TPC", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Partners, L.L.C.", "New Energy Partners", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Service, LLC", "New Energy Service", company_short))%>%
  mutate(company_short = ifelse(company == "North Energy Associates, A Limited Partnership", "North Energy Associates", company_short))%>%
  mutate(company_short = ifelse(company == "Pipeline Company LLC", "Pipeline Company LLC", company_short))%>%
  mutate(company_short = ifelse(company == "Express Pipeline LLC", "Express Pipeline LLC", company_short))%>%
  mutate(company_short = ifelse(company == "American Energy Savings, Inc.", "American Energy Savings", company_short))%>%
  mutate(company_short = ifelse(company == "Electric Energy, Inc.", "Electric Energy, Inc.", company_short))%>%
  mutate(company_short = ifelse(company == "System Energy Resources, Inc., Llano Estacado Wind, LLC, System Energy Resources, Inc., Northern Iowa Windpower, LLC, and RS Cogen, L.L.C.", "System Energy Resources", company_short))%>%
  mutate(company_short = ifelse(company == "Public Service Company of Colorado", "Public Service Company of Colorado", company_short))%>%
  mutate(company_short = ifelse(company == "Southern Company Services, Inc.", "Southern Company", company_short))%>%
  mutate(company_short = ifelse(company == "International Energy Consultants", "International Energy Consultants", company_short))%>%
  mutate(company_short = ifelse(company == "Jackson Pipeline Company", "Jackson Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Southern Energy California", "Southern Energy California", company_short))%>%
  mutate(company_short = ifelse(company == "Tennessee Gas Pipeline Company, L.L.C.", "Tennessee Gas Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Select Energy New York, Inc.", "Select Energy New York", company_short))%>%
  mutate(company_short = ifelse(company == "Inland Corporation", "Inland Corporation", company_short))%>%
  mutate(company_short = ifelse(company == "Advanced Energy Systems, Inc.", "Advanced Energy Systems", company_short))%>%
  mutate(company_short = ifelse(company == "Consumers Energy Company", "Consumers Energy Company", company_short))%>%
  mutate(company_short = ifelse(company == "Boston Energy Trading and Marketing LLC", "Boston Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Complete Energy Services, Inc.", "Complete Energy Services", company_short))%>%
  mutate(company_short = ifelse(company == "El Paso Energy Intrastate, L.P.", "El Paso Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Houston Pipe Line Company LP", "Houston Pipe Line", company_short))%>%
  mutate(company_short = ifelse(company == "North American Energy, Inc.", "North American Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Spokane Energy, LLC", "Spokane Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Salem Energy Systems, LLC", "Salem Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "Direct", "Direct Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "DC", "DC Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "PS", "PS Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Coastal", "Coastal Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "CT", "CT Corporation", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Forest", "Forest Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Minnesota", "Minnesota Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "NW", "NW Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Rio Grande", "Rio Grande Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Plains", "Plains Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Portland", "Portland Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "AP", "AP Holdings", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Boundary", "Boundary Gas", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Columbia", "Columbia Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Independence", "Independence Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Lakeside", "Lakeside Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Mitchell", "Mitchell Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Stream", "Stream Energy", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "^Northwest Pipeline"), "Northwest Pipeline", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "^Tennessee Gas"), "Tennessee Gas", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "Juniper Hills Country Club"), "Juniper Hills Country Club", company_short))%>%
    mutate(company_short = ifelse(str_detect(company, regex("Columbia Gas", ignore_case = T)), "Columbia Gas", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, regex("Algonquin", ignore_case = T)), "Algonquin", company_short))%>%
    mutate(company_short = ifelse(str_detect(company, regex("Spectra", ignore_case = T)), "Spectra", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, regex("Jordan Cove", ignore_case = T)), "Jordan Cove", company_short))%>%
    mutate(company_short = ifelse(str_detect(company, regex("Enron", ignore_case = T)), "Enron", company_short))%>%
     mutate(company_short = ifelse(str_detect(company, regex("Nexus", ignore_case = T)), "Nexus", company_short))%>%

  mutate(company_short = ifelse(company == "Express Pipeline", "Express Pipeline", company_short))%>%
  mutate(company_short = ifelse(company %in% c("American Energy", "American energy"), "American Energy", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "PG&E|Pacific Gas & Electric|Pacific Gas and Electric"), "PG&E", company_short)) %>% 
    mutate(company_short = ifelse(str_detect(company, "Cove Point"), "Dominion", company_short)) %>% 
  mutate(company_short = ifelse(company %in% c("Pacific Corp.", "Pacific Corps"), "PacifiCorp", company_short)) %>% 
  mutate(company_short = ifelse(company_short == "AI", "AI Energy", company_short))
```

Not companies?
```{r non-companies} 
dcorps %<>% 
  mutate(company_short = ifelse(company_short %in% c("N/A","Na","NO",
                                                     "Clean Water Act","Na",
                                                     "Energy", "West", "NA",
                                                     "Central", "Power", "Natural",
                                                     "Consumers", "LNG"),
         "NOT A COMPANY?",  company_short))

dcorps %>% filter(company_short == "NOT A COMPANY?") %>% kable()

# dcorps %>% filter(str_detect(company, "Cove Point")) %>% kable()

```

Short company names, e.g. "Duke" may refer to many affiliated companies. The variable `company_short_refs` lists these affiliated companies. 
```{r}
#FIXME
# ADD company_short_refs 
dcorps %<>% 
  group_by(company_short) %>% 
  mutate(company_short_refs = str_c(unique(company), collapse = "; ")) %>% ungroup()
```

Look for problematic company names. For example what should we do with companies that are just state, region, or city names? (e.g. El Paso Corporation, Tennessee Gas, American Energy, Southern, etc.) 
```{r}
## Inspect for over-trimmed company names
dcorps %>% filter(company_short %in% c("", "NA", "na", "Na", "LLC", "Energy", "Pipeline", "Natural", "North", "New", "Express", "gas", "American", "Electric", "System", "Direct", "DC", "PS", "CT", "Forest", "International", "Tennessee", "Salt Lake", "Lakeside", "NW", "Jackson", "Public Service", "Peak", "Independence", "Select", "Portland", "Michigan", "Boundary", "Coastal", "Minnesota", "Midwest", "Northeast", "Columbia", "Plains", "Stream", "Mitchell", "AP", "Southern", "Ohio River", "Northwest", "Rio Grande", "AI", "Transportation", "12/20/2018", "Salem", "Boston", "Spokane", "El Paso", "Houston", "North American", "Consumers", "Advanced", "Complete", "Inland", "Limited Partnership", "Sun", "RTO", "Pacific", "LNG")) %>% select(company_short, company_short_refs, ID) %>% 
  group_by(company_short) %>%
  summarise(company_short_refs = str_c(unique(company_short_refs), collapse = "; "),
            IDs = str_c(unique(ID), collapse = "; ")) %>%
  distinct() %>% knitr::kable()

##  did I acidentally delete everything before a comma? 
# dcorps %>% filter(str_detect(company_short, ","))
```

## Top 10 cited companies pro or con
```{r top-corps}
# top corps
topcorps <- dcorps %>% group_by(company_short) %>% tally() %>% arrange(-n) %>% top_n(10)

filter(dcorps, company_short %in% topcorps$company_short) %>%   
  group_by(company_short) %>%
  summarise(#IDs = str_c(unique(ID), collapse = "; ")
    company_short_refs = str_c(unique(company_short_refs), collapse = "; ") ) %>%
  distinct() %>% knitr::kable() 

# corps with short names 
shortcorps <- dcorps %>% 
  ungroup() %>% 
  group_by(company_short) %>% 
  tally() %>% 
  arrange(nchar(company_short)) %>% 
  mutate(nchar = nchar(company_short))%>%
  top_n(10, -nchar) %>% distinct()

filter(dcorps, company_short %in% shortcorps$company_short) %>% 
  group_by(company_short) %>%
  summarise(company_short_refs = str_c(unique(company_short_refs), collapse = "; "),
            IDs = str_c(unique(ID), collapse = "; ")) %>%
  distinct() %>% knitr::kable()


```


[This sheet](https://docs.google.com/spreadsheets/d/1-QNgeiMnH97jN_0vCqFKEGEB5Ztpito3iRsqK8jN3Cs/edit#gid=0) tracks non-companies in our data.
```{r, eval=FALSE}
library(googlesheets)
library(httpuv)

# log in to google drive
gs_auth() 

notcorps <- gs_title("not_companies") %>% gs_read() 


dcorps %<>% ungroup() %>% 
  mutate(company_short = ifelse(company_short %in% notcorps$not_companies,
                                "NOT A COMPANY?", company_short) )
         
#FIXME
# ADD company_short_refs again after corrections
dcorps %<>% 
  group_by(company_short) %>% 
  mutate(company_short_refs = str_c(unique(company), collapse = "; ")) %>% ungroup()

dcorps %>% 
  filter(position %in% c("ProProject", "ProBusiness")) %>% 
  select(ID, company_short, company)%>% 
  group_by(company_short) %>% 
  distinct() %>%
  add_count() %>% 
  arrange(-n) %>% 
  #write_csv(path = here("FERC/ProBusinesses.csv"))
  head()

# sum(is.na(unique(dcorps$company_short)))

## Make a single string of short corp names
dcorp_short <- unique(dcorps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

# bad string? 
# str_detect("", dcorp_short)


save(dcorp_short, file = here("data/dcorp_short.Rdata"))
save(dcorps, file = here("data/dcorps.Rdata"))

# notcorps$company


```

Drop non-company observations
```{r}
load(here("data/dcorp_short.Rdata"))
load(here("data/dcorps.Rdata"))
notcorps <- filter(dcorps, company_short == "NOT A COMPANY?")


sum(!is.na(d$ProBusiness))
d %<>% 
  mutate(ProBusiness = ifelse(ProBusiness %in% notcorps$company, NA, ProBusiness)) %>% 
  mutate(ProProject = ifelse(ProProject %in% notcorps$company, NA, ProProject))
  
sum(!is.na(d$ProBusiness))
```
