---
title: "Matching companies with campaign donations"
subtitle: "Companies that lobby the U.S. Federal Energy Regulatory Commission (FERC)"
author:
output:
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
## Run a setup.R script to load R packages and set defaults
#source(here::here("setup.R")) ## Alternatively: source("https://raw.githubusercontent.com/judgelord/PS811/master/setup.R")

## Modify some defaults for this example
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 8,
                      warning = FALSE,
                      message = FALSE)
```


Required packages: [`stringr`](https://www.rstudio.com/resources/cheatsheets/#stringr) (for [regular expressions](https://github.com/rstudio/cheatsheets/raw/master/regex.pdf)), [`purrr`](https://www.rstudio.com/resources/cheatsheets/#purrr), [`here`](https://github.com/jennybc/here_here) and [`magrittr`](https://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html).

```{r libraries}
library(tidyverse)
library(magrittr)
library(here)
```

(mostly a to-do list right now)

# Match companies from FERC website and congressoinal letters

### Load data
- companies registered with FERC
- letters from members
```{r, eval = FALSE}
load(here("data", "DOE_FERC-corps.Rdata"))
load(here("data", "DOE_FERC-letters.Rdata"))
d <- FERC_letters

## Make a single string of short corp names
ferc_short <- unique(FERC_corps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

# bad string
# str_detect("", ferc_short)
```

### Extract company names that coders may have missed
```{r, eval = FALSE}
## Combine letter summary and letter text
FERC_letters %<>% 
  mutate(text = str_c(SUBJECT, text_clean, sep = ". Letter Text: ")) 

## A helper function to select and combine a set of unique strings
str_unique <- function(x){
  str_c(unique(x), collapse="; ")
}

## Find corporation names in combined summary and text
FERC_letters$company_short_detected <- str_extract_all(FERC_letters$text, ferc_short) %>% map_chr(str_unique) %>% str_remove_all("^; |; ; |; $")

## Number of letters where a company from the FERC website was found:
sum(FERC_letters$company_short_detected!="")

## Companies found
unique(FERC_letters$company_short_detected)
```






# Match corporations and officials to their campaign donations.

## Get DIME campaign contributions data
```{r, eval=FALSE}

## GET DIME DATA (>3GB)
download.file("https://dataverse.harvard.edu/api/access/datafile/2865300?gbrecs=true",
           destfile = here("data/dime_contributors.gz") )

list.files("data")
filename <- 'data/dime_contributors.gz'
# install.packages("R.util")
R.utils::gunzip(filename, destname = str_replace(filename, "[.]gz$", ".csv"))

## LOAD DIME DATA
dime <- read.csv(here("data/dime_contributors.csv"))

## CORPORATE CONTRIBUTORS
dime %<>% filter(contributor.type == "C") # type C = corporation
save(dime, file = here("data/dime_corps.Rdata"))

load("data/dime_corps.Rdata")

dim(dime)
names(dime)

## TRIM DOWN TO POSSIBLE MATCHES
dime_ferc <- dime %>% 
  mutate(corpname = tolower(most.recent.contributor.name)) %>% 
  filter(str_detect(corpname, tolower(ferc_short))) %>% 
  mutate(company_short = str_extract_all(corpname, tolower(ferc_short)))

dim(dime_ferc)

head(dime_ferc)

## SAVE
save(dime_ferc, file = here("data/dime_ferc_corp_matches.Rdata"))
```

## Get PAC id - industry code crosswalk from CRP
(notice industry codes included and excluded)
```{r CRP-data}
read_crp <- . %>% {read_delim(file = here(str_c("CRP Data/cmtes/", .)),
                  delim = ",", 
                  quote = "|",
                  col_names = c("Cycle", "CmteID", "PACShort","Affiliate",
                    "UltOrg","RecipID","RecipCode", "FECCandID",
                    "Party", "PrimCode","Source", "Sensitive", 
                    "Foreign", "Active"))}

crp <- map_dfr(list.files(here("CRP Data/cmtes")), read_crp)

## INDUSTRY CODES

industry <- readxl::read_xls(here("CRP Data/CRP_IDs.xls"), sheet = "CRP Industry Codes")
names(industry) <- industry[5,]

industry %<>% 
  filter(Sector %in% "Energy/Nat Resource",
         !Industry %in% c("Mining", "Waste Management" , "Fisheries & Wildlife", "Misc. Energy"),
         !Catname %in% c("Nuclear energy", 
                         "Nuclear plant construction, equipment & svcs",
                         "Water Utilities",
                         "Oilfield service, equipment & exploration"))


crpEnergy <- crp %>% 
  filter(PrimCode %in% industry$Catcode) %>% 
  mutate(comid = CmteID) %>% 
  select(comid, UltOrg, Affiliate, PACShort) %>% 
  distinct() %>% 
  group_by(comid) %>%
  summarise(UltOrg = str_c(unique(UltOrg), collapse = "; "),
            Affiliate = paste(unique(Affiliate), collapse = "; "),
            PACShort = str_c(unique(PACShort), collapse = "; ")) %>%
  distinct()

write_csv(crpEnergy, path = "data/crpEnergy.csv")
```

## Companies with PACs linked to companies registered with FERC's website
```{r crp-ferc-match}
# Load a string of companies from FERC website
load(here("data/ferc_short.Rdata"))

## Companies to look out for
crpEnergy %>% filter(str_detect(UltOrg, ferc_short)|str_detect(Affiliate, ferc_short)) %>% mutate(company_short = str_extract(UltOrg, ferc_short)) %>% select(company_short, UltOrg) %>% distinct() %>% knitr::kable()
```

## Companies with PACs matching companies in member letters to FERC
```{r}
# Load a string of companies from FERC website
load(here("data/dcorp_short.Rdata"))

crpEnergy %>% 
  filter(str_detect(UltOrg, dcorp_short)|str_detect(Affiliate, dcorp_short)) %>%
  mutate(company_short = str_extract(UltOrg, dcorp_short)) %>%
  select(company_short, UltOrg)  %>% 
  distinct()%>% 
  knitr::kable()
```


# PAC contributions from DIME
```{r, eval=TRUE}
source("setup.R")
library(purrr)
# load dime data

## 2014 DIME DATA (2014 is partial)
# load(here("data/DIME_79_14.rda"))
# dime <- aresults

## Updated DIME DATA (2018 is partial)
load(here("data/dime_contributors_1979_2018.rdata"))
dime <- contribs
glimpse(dime)



# pluck out the candidate data 
cands <- dime %>% 
  purrr::pluck("cands") %>% 
  as_tibble() 

# inspect problem observations
cands %>% filter(str_detect(Name,"MARINO, THOMAS")) %>% select(Name, ICPSR, ICPSR2, cycle)  %>% distinct()

# inspect paul ryan
cands %>% filter(str_detect(Name,"PELOSI, NANCY")) %>% select(Name, ICPSR, ICPSR2, cycle)  %>% distinct()


# trim it down
cands %<>%  
  select(Name, cycle, ICPSR, ICPSR2, votesmart_id, Cand.ID, FEC.ID, unq_fecids, unq_candids, recipient_nid, bonica_rid) %>%
  # icpsr = ICPSR without cycle at the end
  mutate(icpsr = str_remove(ICPSR, cycle))%>%
  # trim down to members serving in since the 106th
  filter(icpsr %in% members$icpsr | icpsr %in% members_106to109th$icpsr)  # %>% 
  # FIXME 
  # TESTING WITH A FEW
  # filter(icpsr %in% c(21170,21112))

dim(cands)

# pluck out PAC data matrix
cmdat <- dime %>% 
  purrr::pluck("cmdat") %>% 
  as_tibble() %>% 
  # Select CRP PAC IDs
  filter(comid.crp %in% crpEnergy$comid) 

glimpse(cmdat)

# pluck out the other PAC data matrix with the right comid
contributors <- dime %>% 
  purrr::pluck("contributors") %>% 
  as_tibble() %>% 
  # why is comid not the same between contributors and cmdat?
  # rename as it seems cmdat$comid = contributor_ext_id here...not sure
  rename(comid_fixed_width = comid) %>% 
  # fec_id = contributor_ext_id
  rename(comid = contributor_ext_id) %>% 
  # first merge with cmdat?
  left_join(cmdat) %>% 
  # trim it down to those in CRP data (could just fliter these data to energy companies)
  filter(comid.crp %in% crpEnergy$comid)  

glimpse(contributors)

# pluck out the contribution sparse matrix (mostly zeros)
contrib_matrix <- dime %>% 
  purrr::pluck("contrib.matrix.am") %>% 
  # select comids and ICPSR numbers matched above
  .[contributors$comid_fixed_width, cands$ICPSR] %>% 
  as.matrix() %>% 
  as_tibble(rownames = "comid_fixed_width") %>% 
  # make long format tidy data
  gather(key = ICPSR, value = value, -comid_fixed_width)

contrib_matrix %<>% 
  # drop zeros to speed things up, make a smaller file
  #filter(value >0) %>%
  # make comid not fixed width
  left_join(contributors %>% select(comid_fixed_width, comid) %>%
              distinct() ) %>% 
  # merge with CRP data 
  left_join(crpEnergy) %>% 
  distinct() %>% 
  arrange(-value)

contrib_matrix %>% select(PACShort, Affiliate, value)
```

## Companies with PACs linked to companies registered with FERC's website
```{r crp-ferc-match}
# Load a string of companies from FERC website
load(here("data/ferc_short.Rdata"))

## Find companies from FERC website 
contrib_matrix %>% 
  mutate(company_short = str_extract(UltOrg, ferc_short)) 

contrib_matrix %>% select(company_short, UltOrg) %>% distinct() %>% knitr::kable()
```

## Companies with PACs matching companies in member letters to FERC
```{r}
# Load a string of companies from FERC website
load(here("data/dcorp_short.Rdata"))

# Find these companies in UltOrg
contrib_matrix %<>% 
  mutate(dcorp_short = str_extract(UltOrg, dcorp_short)) 

contrib_matrix %>%
  select(dcorp_short, UltOrg)  %>% 
  distinct()%>% 
  knitr::kable()
```


Corrections to DIME 
```{r, eval=FALSE}

# ALL OF THESE CORRECTOINS NEED TO GO AFTER MERGE WITH CONTRIBUTIONS MATRIX BECAUSE THAT USES BONICA'S NUMBERS 

## Fixing incorrect ICPSR scores in the DIME Candidate Data
contrib_matrix$ICPSR2[contrib_matrix$ICPSR2==29334 & contrib_matrix$cycle >2001]<-"20358" ## Separating Carrie Meek and her son Kendrick Meek
contrib_matrix$ICPSR[contrib_matrix$ICPSR2==29334 & contrib_matrix$cycle >2001]<-"20358" ## Separating Carrie Meek and her son Kendrick Meek
contrib_matrix$ICPSR2[contrib_matrix$ICPSR2==8883 &contrib_matrix$Cand.ID=="H8MS04040"]<-"H8MS04040" ## Separating Senator John C. Stennis from his sone John Hampton Stennis who ran for the House
contrib_matrix$bonica.rid[contrib_matrix$Cand.ID=="H8MS04040"]<-"cand3319a" ## Separating Senator John C. Stennis from his son John Hampton Stennis who ran for the House, and giving them separate bonica scores by adding a to the son's score
contrib_matrix$bonica.cid[contrib_matrix$Cand.ID=="H8MS04040"]<-"3787950641a" ## Separating Senator John C. Stennis from his son John Hampton Stennis who ran for the House, and giving them separate bonica scores by adding a to the son's score
contrib_matrix<-contrib_matrix[!(contrib_matrix$ICPSR=="H8TX060271984"),] ## Removing duplicate row for Senator Phil Gramm.  (in 1984 he ran for senate not house)
contrib_matrix<-contrib_matrix[!(contrib_matrix$ICPSR=="S6TX000401982"),] ## Removing duplicate row for Senator Phil Gramm.  (in 1982 he ran for house not senate)
contrib_matrix$ICPSR2[contrib_matrix$bonica.rid=="cand134709" & contrib_matrix$cycle==1980]<-"94628" #Fixing the ICPSR2 score for Phil Gramm (party switch)
contrib_matrix<-contrib_matrix[!(contrib_matrix$ICPSR=="ID129951990"),] ## Removing duplicates for Senator Mike Crapo (confusion with state legislature)
contrib_matrix<-contrib_matrix[!(contrib_matrix$ICPSR=="ID129951992"),] ## Removing duplicates for Senator Mike Crapo (confusion with state legislature)
contrib_matrix<-contrib_matrix[!(contrib_matrix$ICPSR=="ID129951996"),] ## Removing duplicates for Senator Mike Crapo (confusion with state legislature)
contrib_matrix<-contrib_matrix[!(contrib_matrix$ICPSR=="ID129951996"),] ## Removing duplicates for Senator Mike Crapo (confusion with state legislature)
contrib_matrix<-contrib_matrix[!(contrib_matrix$ICPSR=="AK174572002"),] ## Removing duplicates for Senator Lisa Murkowski (confusion with state legislature & father mid replace)
contrib_matrix<-contrib_matrix[!(contrib_matrix$ICPSR=="ID185872008"),] ## Removing duplicates for Senator Jim Risch (confusion with gov)
contrib_matrix<-contrib_matrix[!(contrib_matrix$ICPSR=="S0ND000932010"),] ## Removing duplicates for Senator John Hoeven (confusion with gov)
contrib_matrix<-contrib_matrix[!(contrib_matrix$ICPSR=="IL138871998"),] ## Removing duplicates for Senator Peter Fitzgerald (confusion with state legislature)
contrib_matrix<-contrib_matrix[!(contrib_matrix$ICPSR=="H8NJ011432008"),] ## Removing CAMILLE SPINELLO ANDREWS, who temporarily ran for the primary for her husband's house seat , while he was running for senate.  He lost the Senate primary, and then she withdrew from House race.  In this case she is erroniously credited with her husband's ICPSR #.  She never served in Congress.  


contrib_matrix$ICPSR2[contrib_matrix$bonica.rid=="cand121877" & contrib_matrix$cycle >2005]<-"20538" #Fixing the ICPSR2 scores for Doris Matsui, her husband Bob scores are correct
## Parker Griffith changed parties from Dem to Rep.  Bonica wanted a single consistent ICPSR score so used 90901, but voteview and others use separate scores for party switch
#contrib_matrix$ICPSR2[contrib_matrix$ICPSR2==91901 & contrib_matrix$cycle==2008]<-"15617"
#contrib_matrix$ICPSR2[contrib_matrix$ICPSR2==91901 & contrib_matrix$cycle==2010]<-"95617"
# Wes Watkins changed parties, so others changed his ICPSR score.  Changing to match NOMINATE/Stewart
contrib_matrix$ICPSR2[contrib_matrix$ICPSR2=="14462" & contrib_matrix$cycle>1994]<-"29749"
# Billy Tauzin changed parties, so others changed his ICPSR score.  Changing to match NOMINATE/Stewart
contrib_matrix$ICPSR2[contrib_matrix$ICPSR2=="14679" & contrib_matrix$cycle>1996]<-"94679"
# Bill Grant changed parties, In earlier years should have earlier number
contrib_matrix$ICPSR2[contrib_matrix$ICPSR2=="95415" & contrib_matrix$cycle>1988]<-"15415"
# GARDNER, CORY had and FEC ID instead of an ICPSR 
contrib_matrix %<>% 
  mutate(ICPSR = ifelse(Name=="GARDNER, CORY" & contrib_matrix$cycle>2009,
                        str_c(21112,cycle),ICPSR)) %>%
  mutate(ICPSR = ifelse(Name=="MARINO, THOMAS ANTHONY" & contrib_matrix$cycle>2009,
                        str_c(21170,cycle),ICPSR))
```

Save results
```{r save}
#########################################################
save(contrib_matrix, file =  "data/contrib_matrix.rds")

# collapse to all sector-level donations for now
contrib_total <- contrib_matrix %>% 
  group_by(ICPSR) %>% 
  summarise(value = sum(value))

save(contrib_total, file =  "data/contrib_total.rds")
```







## Campaign contributions of individuals at Fortune 500 companies listed on the FERC website

#### Step 1. Match companies from the FERC webiste to DIME Fortune 500 dataset
```{r, eval= FALSE}
## Fortune 500 companies
download.file("https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/6R1HAS/DP6TOL", destfile = here("data", "DIME500.csv") )

dime500 <- read_csv(here("data", "DIME500.csv"))

# dime %<>% extractMemberName(members, recipient.name)

fortune500 <- unique(dime500$corpname) %>% 
  str_c(sep = "|", collapse = "|")


## DIME records that match a shortened version of a FERC company name
dime500_ferc <- dime500 %>% filter(str_detect(corpname, ferc_short))
save(dime500_ferc, file = here("data", "FERC_DIME-corps.Rdata"))

dime500_ferc_corps <- str_c(unique(dime500_ferc$corpname), collapse = "|")

## Fortune 500 indicator in corps data 
FERC_corps %<>% mutate(Fortune500 = str_detect(company, dime500_ferc_corps))
sum(FERC_corps$Fortune500)


## Fortune 500 indicator in letters data 
FERC_letters %<>% mutate(Fortune500 = str_detect(company_short, dime500_ferc_corps))
sum(FERC_letters$Fortune500)


## edit google sheet
# gs_title("DOE_FERC Extended") %>% gs_edit_cells(input = FERC_letters, trim = F, byrow = T)
```


#### Step 2: Identify contributions to Members of Congress in DIME Fortune 500 data:
```{r}
## ID member names among donation recipients 
# dime500_ferc %<>% extractMemberName(members = members, col_name =  recipient.name)
```

## Campaign contributions of individuals listed on the FERC website

### Step 1: Get corporate contacts from FERC website

```{r}
#TO DO
```

### Step 2: Match with Individual DIME contributors
```{r}
# DIME DATA
# dime <- read.csv(here("data/dime_contributors.csv"))

# TRIM DOWN TO INDIVIDUALS FROM FERC WEBSITE
# dime %<>% filter(contributor.type == "I") # type I = individual
# dime %<>% mutate(last_name = str_extract(dime$most.recent.contributor.name, "[a-z]*") )

# SUBSET TO PEOPLE IN FERC DATA 
# dime %<>% filter(last_name %in% ferc$last_name)

# Clean up DIME names 
# dime %<>% mutate(name = str_replace(most.recent.contributor.name, " dr | jr |[0-9]", " ") )
# dime %<>% mutate(name = str_replace(most.recent.contributor.name, "  ", " ") )
# dime %<>% mutate(first_name = str_extract(name, ", [a-z][a-z]*") )
# dime %<>% mutate(first_name = str_replace(first_name, ", ", ""))
# dime %<>% mutate(first_name2 = str_extract(dime$most.recent.contributor.name, ", [a-z]{2}*") )
# dime %<>% mutate(middle_initial = str_extract(name, " [a-z]$") )
# dime %<>% mutate(middle_initial = str_replace(middle_initial, " ", "") )
# dime$first_initial <- str_sub(dime$first_name, 1,1)

# SAVE
# save(dime, file = here("data/dime_ferc_fortune500_people_matches.Rdata"))
```



```{r not run, include = FALSE, eval=FALSE}
rm(list=ls())
q()
n
ssh -Y judgelord@linstat.ssc.wisc.edu
cd /project/judgelord/correspondence

Rscript -e 'library(rmarkdown); rmarkdown::render("/FERC/DOE_FERC-money-matching.Rmd", "html_document")'

git add "data/contrib_matrix.rds"
git add "data/contrib_total.rds"
git commit -m "add dime data"
git pull
git push
judgelord
```