---
title: "Matching companies with campaign donations"
subtitle: "Companies that lobby the U.S. Federal Energy Regulatory Commission (FERC)"
author:
output:
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
## Run a setup.R script to load R packages and set defaults
#source(here::here("setup.R")) ## Alternatively: source("https://raw.githubusercontent.com/judgelord/PS811/master/setup.R")

## Modify some defaults for this example
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 8,
                      warning = FALSE,
                      message = FALSE)
```


Required packages: [`stringr`](https://www.rstudio.com/resources/cheatsheets/#stringr) (for [regular expressions](https://github.com/rstudio/cheatsheets/raw/master/regex.pdf)), [`purrr`](https://www.rstudio.com/resources/cheatsheets/#purrr), [`here`](https://github.com/jennybc/here_here) and [`magrittr`](https://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html).

```{r libraries}
library(tidyverse)
library(magrittr)
library(here)
```

(mostly a to-do list right now)

# Match companies from FERC website and congressoinal letters

### Load data
- companies registered to lobby FERC
- letters from members
```{r, eval = FALSE}
load(here("data", "DOE_FERC-corps.Rdata"))
load(here("data", "DOE_FERC-letters.Rdata"))
d <- FERC_letters

## Make a single string of short corp names
ferc_short <- unique(FERC_corps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

# bad string
# str_detect("", ferc_short)
```

### Extract company names that coders may have missed
```{r, eval = FALSE}
## Combine letter summary and letter text
FERC_letters %<>% 
  mutate(text = str_c(SUBJECT, text_clean, sep = ". Letter Text: ")) 

## A helper function to select and combine a set of unique strings
str_unique <- function(x){
  str_c(unique(x), collapse="; ")
}

## Find corporation names in combined summary and text
FERC_letters$company_short_detected <- str_extract_all(FERC_letters$text, ferc_short) %>% map_chr(str_unique) %>% str_remove_all("^; |; ; |; $")

## Number of letters where a company from the FERC website was found:
sum(FERC_letters$company_short_detected!="")

## Companies found
unique(FERC_letters$company_short_detected)
```






# Match corporations and officials to their campaign donations.

## Get DIME campaign contributions data
```{r, eval=FALSE}
## To load FERC data 
load(here("data", "DOE_FERC-letters-corps.Rdata"))
load(here("data", "DOE_FERC-corps.Rdata"))

## Make a single string of short corp names
# FIXME add company names extracted from letters
ferc_short <- unique(FERC_corps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

## GET DIME DATA (>3GB)
download.file("https://dataverse.harvard.edu/api/access/datafile/2865300?gbrecs=true",
           destfile = here("data/dime_contributors.gz") )

list.files("data")
filename <- 'data/dime_contributors.gz'
# install.packages("R.util")
R.utils::gunzip(filename, destname = str_replace(filename, "[.]gz$", ".csv"))

## LOAD DIME DATA
dime <- read.csv(here("data/dime_contributors.csv"))

## CORPORATE CONTRIBUTORS
dime %<>% filter(contributor.type == "C") # type C = corporation
save(dime, file = here("data/dime_corps.Rdata"))

load("data/dime_corps.Rdata")

dim(dime)
names(dime)

## TRIM DOWN TO POSSIBLE MATCHES
dime_ferc <- dime %>% 
  mutate(corpname = tolower(most.recent.contributor.name)) %>% 
  filter(str_detect(corpname, tolower(ferc_short))) %>% 
  mutate(company_short = str_extract_all(corpname, tolower(ferc_short)))

dim(dime_ferc)

head(dime_ferc)

## SAVE
save(dime_ferc, file = here("data/dime_ferc_corp_matches.Rdata"))
```

## Get PAC id - industry code crosswalk from CRP
```{r CRP-data}
crp <- read_delim("CRP Data/cmtes00.txt", 
                  delim = ",", 
                  quote = "|",
                  col_names = c("Cycle", "CmteID", "PACShort","Affiliate",
                    "UltOrg","RecipID","RecipCode", "FECCandID",
                    "Party", "PrimCode","Source", "Sensitive", 
                    "Foreign", "Active"))

## INDUSTRY CODES

industry <- readxl::read_xls("CRP Data/CRP_IDs.xls", sheet = "CRP Industry Codes")
names(industry) <- industry[5,]

industry %>% 
  filter(Sector %in% "Energy/Nat Resource", )

```




## Campaign contributions of individuals at Fortune 500 companies listed on the FERC website

#### Step 1. Match companies from the FERC webiste to DIME Fortune 500 dataset
```{r, eval= FALSE}
## Fortune 500 companies
download.file("https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/6R1HAS/DP6TOL", destfile = here("data", "DIME500.csv") )

dime500 <- read_csv(here("data", "DIME500.csv"))

# dime %<>% extractMemberName(members, recipient.name)

fortune500 <- unique(dime500$corpname) %>% 
  str_c(sep = "|", collapse = "|")


## DIME records that match a shortened version of a FERC company name
dime500_ferc <- dime500 %>% filter(str_detect(corpname, ferc_short))
save(dime500_ferc, file = here("data", "FERC_DIME-corps.Rdata"))

dime500_ferc_corps <- str_c(unique(dime500_ferc$corpname), collapse = "|")

## Fortune 500 indicator in corps data 
FERC_corps %<>% mutate(Fortune500 = str_detect(company, dime500_ferc_corps))
sum(FERC_corps$Fortune500)


## Fortune 500 indicator in letters data 
FERC_letters %<>% mutate(Fortune500 = str_detect(company_short, dime500_ferc_corps))
sum(FERC_letters$Fortune500)


## edit google sheet
# gs_title("DOE_FERC Extended") %>% gs_edit_cells(input = FERC_letters, trim = F, byrow = T)
```


#### Step 2: Identify contributions to Members of Congress in DIME Fortune 500 data:
```{r}
## ID member names among donation recipients 
# dime500_ferc %<>% extractMemberName(members = members, col_name =  recipient.name)
```

## Campaign contributions of individuals listed on the FERC website

### Step 1: Get corporate contacts from FERC website

```{r}
#TO DO
```

### Step 2: Match with Individual DIME contributors
```{r}
# DIME DATA
# dime <- read.csv(here("data/dime_contributors.csv"))

# TRIM DOWN TO INDIVIDUALS FROM FERC WEBSITE
# dime %<>% filter(contributor.type == "I") # type I = individual
# dime %<>% mutate(last_name = str_extract(dime$most.recent.contributor.name, "[a-z]*") )

# SUBSET TO PEOPLE IN FERC DATA 
# dime %<>% filter(last_name %in% ferc$last_name)

# Clean up DIME names 
# dime %<>% mutate(name = str_replace(most.recent.contributor.name, " dr | jr |[0-9]", " ") )
# dime %<>% mutate(name = str_replace(most.recent.contributor.name, "  ", " ") )
# dime %<>% mutate(first_name = str_extract(name, ", [a-z][a-z]*") )
# dime %<>% mutate(first_name = str_replace(first_name, ", ", ""))
# dime %<>% mutate(first_name2 = str_extract(dime$most.recent.contributor.name, ", [a-z]{2}*") )
# dime %<>% mutate(middle_initial = str_extract(name, " [a-z]$") )
# dime %<>% mutate(middle_initial = str_replace(middle_initial, " ", "") )
# dime$first_initial <- str_sub(dime$first_name, 1,1)

# SAVE
# save(dime, file = here("data/dime_ferc_fortune500_people_matches.Rdata"))
```

