---
title: "FERC letter coding status"
subtitle: ""
author:
output:
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
## Run a setup.R script to load R packages and set defaults
#source(here::here("setup.R")) ## Alternatively: source("https://raw.githubusercontent.com/judgelord/PS811/master/setup.R")

## Modify some defaults for this example
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 8,
                      warning = FALSE,
                      message = FALSE)
```

Required packages: [`gs_sheets`](https://cran.r-project.org/web/packages/googlesheets/vignettes/basic-usage.html), [`stringr`](https://www.rstudio.com/resources/cheatsheets/#stringr) (for [regular expressions](https://github.com/rstudio/cheatsheets/raw/master/regex.pdf)), [`purrr`](https://www.rstudio.com/resources/cheatsheets/#purrr), [`here`](https://github.com/jennybc/here_here) and [`magrittr`](https://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html).


```{r libraries}
library(tidyverse)
library(googlesheets)
library(magrittr)
library(here)
```

Updated: `r  Sys.time()`

# Load coded congressional letters data:
```{r}
# log in to google docs
gs_auth() 

## Load coded data
FERC_coders <- gs_title("FERC Data Assignments") %>% gs_read() %>% 
  rename(coder_sheet = `Sheets Assigned`) %>%
  select(coder_sheet, Freelancer) %>% 
  drop_na(coder_sheet)

# a helper function to read sheets from url
gs_read_url <- function(coder_sheet){
  coder_sheet %>% gs_url() %>% 
    gs_read() %>%
    mutate(coder_sheet = coder_sheet)
}

# read and merge sheets into a data frame
FERC_coded <- map_dfr(FERC_coders$coder_sheet, gs_read_url) 

FERC_coded %<>% 
  # drop uncoded obs
  drop_na(CongressPerson) %>% 
  # drop file_name, so we merge only on doc ID
  select(-file_name) %>% 
  # merge in Freelancer names, drop urls
  full_join(FERC_coders) %>% 
  select(-coder_sheet) %>%
  # drop duplicates
  distinct() %>% 
  # name ID the same as master sheet
  rename(ID = `Document ID`) %>% 
  # Id double coded obs
  group_by(ID) %>% 
  mutate(n = n()) %>% 
  mutate(Freelancer = ifelse(n>1, "double coded", Freelancer)) %>% 
  select(-n) %>%
  distinct() 

```

# Potential coding issues:

Lara and Priyal have much fewer Place_ codings. 

Gabriela may be over-coding state and District, but maybe not. 

Priyal finds much less Pro-business, and Lara finds much less Anti-business.

Lara finds a lot more case proceedings, probably understanding it differently. 

Gabriela used "No" in Constituent, whereas the others used NA more. \

Maki is suspiciously low on identifying co-signing. This is difficult to audit, but we can search the summary/SUBJECT column for "et al", indicating co-signing. 

```{r}
# coded
n_coded <- FERC_coded %>% 
  group_by(Freelancer) %>%
  count() 
n_coded%>% 
  knitr::kable(caption = "Cases coded")

# percent coded
FERC_coded %>% 
  group_by(Freelancer) %>%
  mutate_all(is.na) %>%
  summarise_all(sum) %>% 
  full_join(n_coded) %>% 
  mutate_at(vars(-n, -Freelancer), funs(round((1-(./n) )*100))) %>% 
  arrange(Freelancer) %>% 
  select(-CongressPerson, -ID, -SUBJECT, -n) %>%
  filter(Freelancer != "double coded") %>%
   gather(var, value, -Freelancer) %>% 
   spread(Freelancer, value) %>%
  knitr::kable(caption = "Percent coded")

```


```{r}
# differences in cosigned coding
FERC_coded %>% 
  mutate(cosigned = !is.na(Cosigned_House) | !is.na(Cosigned_Senate)) %>%
  group_by(Freelancer, cosigned) %>%
  count() %>% 
  arrange(Freelancer) %>% 
  filter(Freelancer != "double coded") %>% 
  spread(Freelancer, n) %>%
  knitr::kable()

# differences in pro and anti coding
FERC_coded %>% 
  mutate(company_identified = !is.na(ProBusiness) | !is.na(AntiBusiness)) %>%
  group_by(Freelancer, company_identified) %>%
  count() %>% 
  arrange(Freelancer)%>% 
  filter(Freelancer != "double coded") %>% 
    spread(Freelancer, n) %>%
  knitr::kable()

# differences in cosigned coding
FERC_coded %>% 
  mutate(Constituent = tolower(Constituent)) %>%
  group_by(Freelancer, Constituent) %>%
  count() %>% 
  arrange(Freelancer)%>% 
  filter(Freelancer != "double coded") %>% 
    spread(Freelancer, n) %>%
  knitr::kable()
```


# Merge coded letters into master sheet:

Duplicates?
```{r}
# duplicates?
FERC_coded %>% 
  group_by(ID) %>%
  count() %>% 
  arrange(-n) %>% 
  filter(n>1)%>% 
  knitr::kable()

# Drop duplicates
FERC_coded %<>% group_by(ID) %>% top_n(1)

# get master data
FERC_letters <- gs_title("DOE_FERC") %>% gs_read()

# duplicates?
FERC_letters %>% 
  group_by(ID) %>%
  count() %>% 
  arrange(-n) %>% 
  filter(n>1)%>% 
  knitr::kable()

# merge coded sheets into master data
combined <- FERC_letters %>% full_join(FERC_coded %>% select(-SUBJECT))

# duplicates?
combined %>% 
  group_by(ID) %>%
  count() %>% 
  arrange(-n) %>% 
  filter(n>1)%>% 
  knitr::kable()
```

---

# Letters citing companies registered to lobby FERC
## Pro-business letters
```{r}
load(here("data", "DOE_FERC-corps.Rdata"))
FERC_corps %<>% ungroup() %>% group_by(company_short) %>% mutate(industry = str_c(unique(industry), collapse = ";")) %>% select(-company, -Fortune500) %>% distinct() 

## Make a single string of short corp names
ferc_short <- unique(FERC_corps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

# bad string? 
# str_detect("", ferc_short)

d <- combined
d %>% 
  mutate(company_short = str_extract(ProBusiness, ferc_short)) %>% 
  drop_na(company_short) %>% 
  mutate(members = paste(CongressPerson, Cosigned_House, Cosigned_Senate, sep = ";")) %>%
  mutate(members = str_remove_all(members, ";NA")) %>% 
  group_by(company_short) %>% 
  mutate(members = str_c(unique(members), collapse = ";")) %>% 
  select(company_short, members) %>%  distinct() %>%
  left_join(FERC_corps) %>% distinct() %>% 
  knitr::kable(caption = "Pro Businesses matching those registered with FERC")
```

## Anti-business letters

```{r}
d %>% 
  mutate(company_short = str_extract(AntiBusiness, ferc_short)) %>% 
  drop_na(company_short) %>% 
  mutate(members = paste(CongressPerson, Cosigned_House, Cosigned_Senate, sep = ";")) %>%
  mutate(members = str_remove_all(members, ";NA")) %>% 
  group_by(company_short) %>% 
  mutate(members = str_c(unique(members), collapse = ";")) %>% 
  select(company_short, members) %>%  distinct() %>%
  left_join(FERC_corps) %>% distinct() %>% 
  knitr::kable(caption = "Anti Businesses matching those registered with FERC")

```


---


Save coded letters data:
```{r, eval=FALSE}
# Save
FERC_letters <- combined
save(FERC_letters, file = here("data", "DOE_FERC-letters-corps.Rdata"))

## edit master google sheet
# gs_title("DOE_FERC") %>% gs_edit_cells(input = FERC_letters, trim = F, byrow = T)
```






















