---
title: "FERC letter coding status"
subtitle: ""
author:
output:
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
## Run a setup.R script to load R packages and set defaults
#source(here::here("setup.R")) ## Alternatively: source("https://raw.githubusercontent.com/judgelord/PS811/master/setup.R")

## Modify some defaults for this example
knitr::opts_chunk$set(fig.height = 4,
                      fig.width = 8,
                      warning = FALSE,
                      message = FALSE)
```

Required packages: [`gs_sheets`](https://cran.r-project.org/web/packages/googlesheets/vignettes/basic-usage.html), [`stringr`](https://www.rstudio.com/resources/cheatsheets/#stringr) (for [regular expressions](https://github.com/rstudio/cheatsheets/raw/master/regex.pdf)), [`purrr`](https://www.rstudio.com/resources/cheatsheets/#purrr), [`here`](https://github.com/jennybc/here_here) and [`magrittr`](https://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html).


```{r libraries}
library(tidyverse)
library(googlesheets)
library(magrittr)
library(here)
```

Updated: `r  Sys.time()`

Load coded congressional letters data:
```{r}
# log in to google docs
gs_auth() 

## Load coded data
FERC_coders <- gs_title("FERC Data Assignments") %>% gs_read() %>% 
  rename(coder_sheet = `Sheets Assigned`) %>%
  select(coder_sheet, Freelancer) %>% 
  drop_na(coder_sheet)

# a helper function to read sheets from url
gs_read_url <- function(coder_sheet){
  coder_sheet %>% gs_url() %>% 
    gs_read() %>%
    mutate(coder_sheet = coder_sheet) %>% 
    rownames_to_column() %>% 
    mutate(rowname = as.numeric(rowname))
}

# read and merge sheets into a data frame
FERC_coded <- map_dfr(FERC_coders$coder_sheet, gs_read_url) 

FERC_coded %<>% 
  # drop uncoded obs
  drop_na(CongressPerson) %>% 
  # drop file_name, so we merge only on doc ID
  select(-file_name) %>% 
  # merge in Freelancer names, drop urls
  full_join(FERC_coders) %>% 
  select(-coder_sheet) %>%
  # drop duplicates
  filter(Freelancer == "Ellie" | rowname>5)  %>%
  distinct() %>% 
  # name ID the same as master sheet
  rename(ID = `Document ID`) %>% 
  # Id double coded obs
  group_by(ID) %>% 
  mutate(n = n()) %>% 
  mutate(Freelancer = ifelse(n>1, "double coded", Freelancer)) %>% 
  select(-n) %>%
  distinct() 

```

# Potential coding issues:

Lara is identifying fewer companies than the others.

Lara and Priyal have fewer Place_ codings. 

Gabriela may be over-coding state and District, but maybe not. 

Priyal finds much less Pro-business, and Lara finds much less Anti-business.

Lara finds a lot more Case Proceedings, probably understanding it differently. 

Gabriela used "No" in Constituent, where the others used NA.

Maki is suspiciously low on identifying co-signing. This is difficult to audit, but we can search the summary/SUBJECT column for "et al", indicating co-signing. 

```{r}
# coded
n_coded <- FERC_coded %>% 
  group_by(Freelancer) %>%
  count() 
n_coded%>% 
  knitr::kable(caption = "Cases coded")

# percent coded
FERC_coded %>% 
  group_by(Freelancer) %>%
  mutate_all(is.na) %>%
  summarise_all(sum) %>% 
  full_join(n_coded) %>% 
  mutate_at(vars(-n, -Freelancer), funs(round((1-(./n) )*100))) %>% 
  arrange(Freelancer) %>% 
  select(-CongressPerson, -ID, -SUBJECT, -n) %>%
  filter(!Freelancer %in% c("Ellie", "double coded")) %>%
   gather(var, value, -Freelancer) %>% 
   spread(Freelancer, value) %>%
  knitr::kable(caption = "Percent coded")

```


```{r}
# differences in cosigned coding
FERC_coded %>% 
  mutate(cosigned = !is.na(Cosigned_House) | !is.na(Cosigned_Senate)) %>%
  group_by(Freelancer, cosigned) %>%
  count() %>% 
  arrange(Freelancer) %>% 
  filter(!Freelancer %in% c("Ellie", "double coded")) %>%
  spread(Freelancer, n) %>%
  knitr::kable()

# differences in pro and anti coding
FERC_coded %>% 
  mutate(company_identified = !is.na(ProBusiness) | !is.na(AntiBusiness)) %>%
  group_by(Freelancer, company_identified) %>%
  count() %>% 
  arrange(Freelancer)%>% 
  filter(!Freelancer %in% c("Ellie", "double coded")) %>% 
    spread(Freelancer, n) %>%
  knitr::kable()

# differences in cosigned coding
FERC_coded %>% 
  mutate(Constituent = tolower(Constituent)) %>%
  group_by(Freelancer, Constituent) %>%
  count() %>% 
  arrange(Freelancer)%>% 
  filter(!Freelancer %in% c("Ellie", "double coded")) %>% 
    spread(Freelancer, n) %>%
  knitr::kable()
```


# Merge coded letters into master sheet:

Duplicates?
```{r}
# duplicates?
FERC_coded %>% 
  group_by(rowname, ID) %>%
  count() %>% 
  arrange(-n) %>% 
  filter(n>1)%>% 
  knitr::kable()

# Drop duplicates
FERC_coded %<>% group_by(rowname, ID) %>% top_n(1)

# get master data
FERC_letters <- gs_title("DOE_FERC") %>% gs_read()

# duplicates?
FERC_letters %>% 
  group_by(ID) %>%
  count() %>% 
  arrange(-n) %>% 
  filter(n>1)%>% 
  knitr::kable()

# merge coded sheets into master data
d <- FERC_letters %>% full_join(FERC_coded %>% select(-SUBJECT))

# duplicates?
d %>% 
  group_by(rowname, ID) %>%
  count() %>% 
  arrange(-n) %>% 
  filter(n>1)%>% 
  knitr::kable()
```

---


## Use of commas and semi-colons
```{r}
# Find problems with "," instead of ";" sep
d %>% select(ID, CongressPerson, Freelancer) %>%
  filter(str_detect(CongressPerson, ";") ) %>%
  knitr::kable(caption = "More than one primary member")  

# Find problems with "," instead of ";" sep
d %>% select(ID, Cosigned_House, Cosigned_Senate, Freelancer) %>%
  filter(str_detect(Cosigned_House, ", R|,R") | str_detect(Cosigned_Senate, ", S|,S") ) %>%
  knitr::kable(caption = "Wrong list breaks")  

# Find problems with "," instead of ";" sep
d %>% select(ID, ProBusiness, AntiBusiness, Freelancer) %>%
  filter(str_detect(AntiBusiness, ",") | str_detect(ProBusiness, ",") ) %>%
  filter(!(str_detect(AntiBusiness, ",L|, L|,I|, I") | str_detect(ProBusiness, ",L|, L|,I|, I") ) ) %>%
  knitr::kable(caption = "Suspicious comma use to look at") 
```

## Chamber errors
```{r}
d %>% 
  mutate(Senate = ifelse(str_detect(CongressPerson,"^Sen"), 
                         str_c(CongressPerson, Cosigned_Senate, sep = ";"),
                         Cosigned_Senate) ) %>%
  mutate(House = ifelse(str_detect(CongressPerson,"^Rep"), 
                         str_c(CongressPerson, Cosigned_House, sep = ";"),
                        Cosigned_House) ) %>%
  mutate(Senate = Senate %>% str_split(";")) %>%
  unnest(Senate) %>% 
  mutate(House = House %>% str_split(";")) %>%
  unnest(House) %>%
  select(House, Senate, ID, Freelancer) %>% 
  filter(str_detect(Senate, "Rep")|str_detect(House, "Sen")) %>% 
  knitr::kable()
```

## Member name errors
Coders vs names extracted from letter summary (should also do this with names extracted from letter text)

```{r}
# Add auto-extracted member names that coders may have missed
d %>% 
  group_by(ID) %>%
  mutate(missed = !str_detect(
  tolower(str_c
          (str_replace_na(
    c(CongressPerson, Cosigned_House, Cosigned_Senate)
    ), collapse = ";")),
  tolower(last_name) ) ) %>% 
  filter(!is.na(FROM)) %>% 
  filter(missed == T, !str_detect(tolower(CongressPerson), "badfiles|bad files")) %>% 
  select(Freelancer, ID, FROM, CongressPerson, Cosigned_House, Cosigned_Senate) %>% 
  knitr::kable()
```

---


# Letters citing companies registered to lobby FERC
## Pro-business letters
```{r}
load(here("data", "DOE_FERC-corps.Rdata"))
FERC_corps %<>% ungroup() %>% group_by(company_short) %>% mutate(industry = str_c(unique(industry), collapse = ";")) %>% select(-company, -Fortune500) %>% distinct() 

## Make a single string of short corp names
ferc_short <- unique(FERC_corps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

# bad string? 
# str_detect("", ferc_short)


d %>% 
  mutate(company_short = str_extract(ProBusiness, ferc_short)) %>% 
  drop_na(company_short) %>% 
  mutate(members = paste(CongressPerson, Cosigned_House, Cosigned_Senate, sep = ";")) %>%
  mutate(members = str_remove_all(members, ";NA")) %>% 
  group_by(company_short) %>% 
  mutate(members = str_c(unique(members), collapse = ";")) %>% 
  select(company_short, members) %>%  distinct() %>%
  left_join(FERC_corps) %>% distinct() %>% 
  knitr::kable(caption = "Pro Businesses matching those registered with FERC")
```

## Anti-business letters

```{r}
d %>% 
  mutate(company_short = str_extract(AntiBusiness, ferc_short)) %>% 
  drop_na(company_short) %>% 
  mutate(members = paste(CongressPerson, Cosigned_House, Cosigned_Senate, sep = ";")) %>%
  mutate(members = str_remove_all(members, ";NA")) %>% 
  group_by(company_short) %>% 
  mutate(members = str_c(unique(members), collapse = ";")) %>% 
  select(company_short, members) %>%  distinct() %>%
  left_join(FERC_corps) %>% distinct() %>% 
  knitr::kable(caption = "Anti Businesses matching those registered with FERC")

```

---

# Organize as one observation per letter per member
```{r}
# Letters with members identified by coders
sum(!is.na(d$CongressPerson))

# Letters with members identified by auto-detection
sum(!is.na(d$CongressPerson))

# Add auto-extracted member names that coders may have missed
d %<>% 
  group_by(ID) %>% 
  mutate(Notes = ifelse(
    str_detect(tolower(CongressPerson), "badfiles|bad files|noncongress|non congress|bad links"),
    paste(CongressPerson, Notes),
    Notes) ) %>% 
  mutate(CongressPerson = ifelse(
    is.na(CongressPerson)|str_detect(tolower(CongressPerson), "badfiles|bad files|noncongress|non congress|bad links"),
    FROM,
    CongressPerson) )

# Letters with members identified by coders or auto-detection
sum(!is.na(d$CongressPerson))

# Id ones still missed and paste auto-extracted FROM onto CongressPerson
d %<>% 
  group_by(ID) %>%
  mutate(missed = !str_detect(
  tolower(paste(CongressPerson, Cosigned_House, Cosigned_Senate, 
          collapse = ";")),
  tolower(last_name) ) )  %>% 
  mutate(CongressPerson = ifelse(missed,
                                 paste(CongressPerson, FROM, sep = ";"),
                                 CongressPerson) ) # %>% select(missed, FROM, CongressPerson)
  

# Letters with members identified by coders or auto-detection
sum(!is.na(d$CongressPerson))


# Helper function for combining strings
str_unique <- function(x){
  paste(unique(x), collapse="; ")
}


# Split out members
d %<>% 
  # add senators
  mutate(Senate = ifelse(str_detect(CongressPerson,"^Sen"), 
                         paste(CongressPerson, Cosigned_Senate, sep = ";"),
                         Cosigned_Senate) ) %>%
  # add reps
  mutate(House = ifelse(str_detect(CongressPerson,"^Rep"), 
                         paste(CongressPerson, Cosigned_House, sep = ";"),
                        Cosigned_House) ) %>%
  mutate(Senate = Senate %>% str_split(";")) %>%
  # split senators and add prefix where missing
  unnest(Senate) %>% 
  mutate(Senate = ifelse(!str_detect(Senate, "Sen"),
                         str_c("Sen. ", Senate),
                         Senate) ) %>%
  # split reps and add prefix where missing
  mutate(House = House %>% str_split(";")) %>%
  unnest(House) %>%
  mutate(House = ifelse(!str_detect(House, "Rep"),
                         str_c("Rep. ", House),
                         House) ) %>%
  # paste unique house, senate, and auto-detected names
  group_by(ID) %>%
  mutate(members = str_unique(c(CongressPerson, House, Senate))) %>% 
  # split out these
  mutate(members = members %>% str_split(";")) %>%
  unnest(members) %>%
  # remove temp house and senate vars 
  select(-House, -Senate) %>%
  # remove trailing whitespace 
  mutate(members = trimws(members)) %>%
  # drop non-member observations
  add_count(ID) %>% 
  filter(n==1|!members %in% c("NA", "Rep. NA", "Sen. NA", "bad files", "badfiles", "BAD FILES"))%>%
  distinct()  
```

Corrected names
```{r}
d %>%
  filter(str_detect(CongressPerson, ";")&missed)  %>% select(Freelancer, ID, CongressPerson) %>% distinct() %>% knitr::kable()
```

Observations dropped:
```{r}
FERC_letters %>% 
  filter(ID %in% d$ID) %>% select(ID, FROM, SUBJECT) %>% 
  knitr::kable()
```

Save coded letters data:
```{r, eval=TRUE}
## Split availability status from summary
d %<>% separate(SUBJECT, into = c("SUBJECT", "availability"), sep = "Availability: ") 

# Save combined data
FERC_letters <- d %>% select(-CongressPerson, -FROM, -last_name, -first_name, -n) %>% distinct()

save(FERC_letters, file = here("data", "DOE_FERC-letters-coded.Rdata"))

## edit master google sheet
# gs_title("DOE_FERC") %>% gs_edit_cells(input = FERC_letters, trim = F, byrow = T)
```






















