---
title: "Campaign Contributions and Bureaucratic Oversight"
subtitle: A Case Study of the Federal Energy Regulatory Commission"
author: "Eleanor Neff Powell, Devin Judge-Lord, Justin Grimmer"
output:
  #pdf_document
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r, eval=FALSE, include=FALSE}
git pull
Rscript -e 'library(rmarkdown);rmarkdown::render("FERC/FERCsummary.Rmd", "html_document")'
```

```{r setup, include=FALSE}
# Rscript -e 'library(rmarkdown); rmarkdown::render("gh-pages/summary.Rmd", "html_document")'

requires <- c("tidyverse", "broom", "knitr","ineq", "dplyr", "ggplot2", "magrittr", "stargazer", "maps", "fiftystater", "mapproj", "dotwhisker", "here", "devtools")
  to_install <- c(!requires %in% rownames(installed.packages() ) )
  install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )

  if(!"fiftystater" %in% rownames(installed.packages())){
    devtools::install_github("wmurphyrd/fiftystater")
  }

```

```{r, include=FALSE}
  library(tidyverse)
  library(ggplot2); theme_set(theme_bw())
  library(magrittr)
  library(maps)
  library(fiftystater)
  library(mapproj)
  library(knitr)
  library(broom)
  library(dotwhisker)
  library(here)
  library(dplyr)
```

```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='Figs/',
                      warning=FALSE, 
                      message=FALSE)
```

# Data
```{r data}
load(here("data/all_contacts.RData"))
# one obs per member per letter for all agencies
d <- all_contacts %>%
  ungroup() %>% 
  # define d as just FERC
  filter(agency=="DOE_FERC") %>% 
  #mutate(ID = NOTES) %>% 
  # FIXME
  # filter(nchar(ID)>8) %>%
  select(-SUBJECT) %>% 
  mutate(majority = ifelse(majority == 1, "Majority", "Minority")) %>%
  # FIXME 
  # GOODE needs to be fixed in party switchers portion of merge.R
  filter(!(last_name == "GOODE"& party == "(I)"))
  

## one obs per member per letter per committee for all agencies
# load(here("data/all_contacts_committees.RData"))
## define dcommittees as just FERC
#dcommittees <- all_contacts_committees %<>% filter(agency == "DOE_FERC")

# Coded letters, one obs per member per letter 
load(here("data/DOE_FERC-letters-clean.Rdata")) 


# TO DO: replace with DOE_FERC-letters-corps.Rdata when corps added
FERC_letters %<>% 
  select(ID, SUBJECT, 
         Freelancer, Cosigned_House, Cosigned_Senate,
         text_clean, Constituent, year,
         Place_State, Place_District, Place_District, 
         ProBusiness, AntiBusiness, ProProject, AntiProject) %>% 
  mutate(ID = ID %>% as.character()) %>% 
  distinct()

# merge in coded letters
# FIXME THIS IS FAILING DUE TO LACK OF ID IN DATA
d %<>% left_join(FERC_letters) %>% filter(year <2019, !is.na(ID)) 

# Add hand-coding to auto-coding of letter type 
d %<>%  
  mutate(Type = as.character(Type)) %>% 
  mutate(Type = ifelse(tolower(Constituent) == "yes", "Indiv. Constituent", Type)) %>% 
  mutate(Type = ifelse(!is.na(ProBusiness)|!is.na(ProProject), "Corp. Constituent", Type)) %>%
  # define Constituent as "Indiv. Constituent"
  mutate(Constituent = ifelse(Type == "Indiv. Constituent", "Indiv. Constituent", "Non_constituent"),
         Constituent = replace_na(Constituent, "Not coded") ) 
  

# For this analysis, treat corp policy letters as Policy
d$Type %>% unique()
d$Constituent %>% unique()
all_contacts$Type %<>% fct_recode(Policy = "Corp. Policy")
d$Type %<>% fct_recode(Policy = "Corp. Policy")

# make a variable for the pro or anti business position of each letter
d %<>% 
  mutate(letter_position = ifelse(!is.na(ProBusiness)|!is.na(ProProject), "ProBusiness", "Other"),
         letter_position = ifelse(!is.na(AntiBusiness)|!is.na(AntiProject), "AntiBusiness", letter_position),
         letter_position = ifelse(!is.na(AntiBusiness)&!is.na(ProBusiness), "Both", letter_position)) 

unique(d$letter_position)

d %<>% 
  # FIXME
  # rounding years up is approximate, rewrite to go Nov-Nov?
  #mutate(cycle = congress*2+1786 ) %>% 
  mutate(icpsryear = str_c(icpsr, congress)) %>% 
  # FIXME 
  mutate(bioname != "GOODE, Virgil H., Jr.")
```

In all, we have `r nrow(distinct(FERC_letters %>% select(ID)))` letters received by FERC and marked "congressional" since 1990. Most, but not all of these are from Members of the U.S. Congress. For this paper, we focus on `r nrow(distinct(FERC_letters %>% filter(year >1999) %>% select(ID) ) )` letters from `r min(d$year)`-`r max(d$year)`. 

Of the `r nrow(distinct(FERC_letters %>% filter(year >1999) %>% select(ID) ) )` letters from `r min(d$year)`-`r max(d$year)`, we identified Members of Congress in `r length(unique(d$ID))`. Because many are cosigned, this yeild `r nrow(d)` instances of a member writing to FERC.

---

## By party 


```{r part-constituent, fig.height=3, fig.width=4}
d %>% 
  mutate(For = Constituent,
         For = ifelse(letter_position == "ProBusiness", "Pro-Business", For),
         For = ifelse(For == "Non_constituent", "Other", For)) %>% 
  count(party_name, For, majority) %>% 
  filter(party_name != "Independent",
         !is.na(For),
         For != "Not coded",
         For != "Other",
         !is.na(majority)) %>% 
  group_by(party_name, majority) %>% 
  mutate(percent = n / sum(n) * 100 ) %>% 
  ggplot() + 
  aes(y = percent, x = "", fill = For) + 
  geom_col(position = "dodge") + 
  #geom_text(aes(label = n)) +
  facet_grid(majority ~ party_name) + 
  scale_fill_viridis_d(option = "C", end = .8) + 
    labs(x = "",
       fill = "Advocating for",
       y = "Percent") + 
  theme_minimal() + 
  theme(panel.grid.major.x  = element_blank())
```

Looking at letters that are explicitly pro- or anti- business, Democrats write more Anti-business letters, whereas, for Republicans, it depends on chamber control. Whe in the majority, Republicans write more pro-business letters. 
```{r part-business, fig.height=3, fig.width=4}
d %>% 
  count(party_name, letter_position, majority) %>% 
    filter(party_name != "Independent",
           letter_position != "Other",
         !is.na(letter_position),
         !is.na(majority)) %>% 
  group_by(party_name, majority) %>% 
  mutate(percent = n / sum(n) * 100 ) %>% 
  ggplot() + 
  aes(y = percent, x = "", fill = letter_position) + 
  geom_col(position = "dodge") + 
  facet_grid(majority ~ party_name)+ 
  scale_fill_viridis_d(option = "C", end = .8) + 
  labs(x = "",
       fill = "",
       y = "Percent") + 
  theme_minimal() + 
  theme(panel.grid.major.x  = element_blank())
```

---

## Coding of constituent type 
Our coding of letter type is a mix of hand coding "Pro-business" and "Constituent" letters, as well as some coding rules applied to letters that were not put in either group by human coders using [inductively-developed coding rules](https://github.com/judgelord/correspondence/blob/master/agencies/DOE_FERC.R).

FERC has an especially high ratio of letters written on behalf of businesses compared other agencies that mostly recieve letters from legislators on behalf of their constituents. 

```{r data-by-type, fig.width=7, fig.height=4}
all_percent <- all_contacts %>% 
  filter(Type != "To be coded") %>%  
  mutate(total = n()) %>% 
  group_by(Type, total) %>% summarise(nT = n()) %>% 
  mutate(percent = 100*round(nT/total, 2) ) %>% 
  mutate(agency = "Overall") %>% 
  ungroup()


d_percent <- d %>% 
  filter(Type != "To be coded") %>%  
  mutate(total = n()) %>% 
  group_by(Type, total) %>% summarise(nT = n()) %>% 
  mutate(percent = 100*round(nT/total, 2) ) %>% 
  mutate(agency = "DOE FERC") %>% 
  ungroup()

full_join( all_percent, d_percent)%>% 
  ggplot() + 
  aes(x = Type, y = percent, fill = agency, color = agency, label = nT) + 
  geom_col(position = "dodge") + 
  geom_text(vjust = -.1,
            aes(hjust = ifelse(agency == "Overall", 0,1))) +
  labs(x = "",
       fill = "",
       color = "",
       y = "Percent", #paste("Number of Contacts, N =", sum(nrow(all_contacts))),
       title = "Legislator Contacts with FERC") +
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x.top = element_text()) + 
  scale_color_viridis_d(option = "C", end = .8) +
  scale_fill_viridis_d(option = "C", end = .8) + 
    theme_minimal() + 
  theme(panel.grid.major.x  = element_blank())
```

```{r constituent-non-constituent, fig.height=3, fig.width=7}
d  %>% 
  filter(Constituent != "Not coded") %>% 
  ggplot() + 
  aes(x = letter_position) + 
  geom_bar() + 
  facet_wrap("Constituent") +
  labs(x = "",
       y = paste("Letters 2000-2018, N =", as.character(d%>%drop_na(letter_position, Constituent) %>% nrow() %>% as.character() )))

d  %>% 
  ggplot() + 
  aes(x = letter_position) + 
  geom_bar() + 
  facet_wrap("Constituent") +
  labs(title = "Including letters without constituent coding", 
       x = "",
       y = paste("Letters 2000-2018, N =", as.character(d %>% nrow() %>% as.character() )))
```

---

# Members



Of the `r nrow(distinct(FERC_letters %>% filter(year >1999) %>% select(ID) ) )` letters from 2000-2018, we identified Members of Congress in `r length(unique(d$ID))`. Because many are cosigned, this yeild `r nrow(d)` instances of a member writing to FERC.

### Senators vs. state population 

```{r population, fig.height= 3.7, fig.width=6}
d %>% 
  filter(chamber == "Senate") %>% 
    group_by(member_state, year, pop2010) %>% summarise(n = n()) %>%
    group_by(member_state, pop2010) %>% summarise(mean = mean(n)) %>% ungroup() %>% 
    ggplot() + 
    geom_point(aes(x = log(pop2010), y = mean), color = "light blue") + 
  geom_smooth(aes(x = log(pop2010), y = mean)) + 
  geom_text(aes(x = log(pop2010), 
                y = mean, 
                label = ifelse(mean > mean(mean)*1.5 | mean < mean(mean)*0.5, 
                               member_state, "")), 
            check_overlap = TRUE, 
            size = 2.5, 
            hjust = 0) + 
  theme_bw() +
  labs(title = "Senator Requests per Year by State Population",
       x = "Log State Population",
       y = "Average Number of Requests per Year")

```

```{r sentate_percapita_map}
Chamber = "Senate"

d %>% 
  ungroup() %>%
  filter(chamber == Chamber) %>% 
  group_by(state) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) # + facet_grid(. ~ Constituent)

d %>% 
  ungroup() %>% 
  filter(chamber == Chamber) %>% 
  group_by(state, pop2010) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(Per_Capita = n/pop2010*1000000) %>% 
  # map_id creates the aesthetic mapping to the state name column in your data
  ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Contacts Per Million Residents from Members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", 
        legend.title = element_blank() )#+facet_grid(. ~ Constituent)

# By type2
d %>% 
  filter(chamber == Chamber) %>% 
  filter(Constituent != "Not coded") %>% 
  group_by(state, Constituent) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) + facet_grid(. ~ Constituent)

d %>% 
  filter(chamber == Chamber) %>%
  filter(Constituent != "Not coded") %>% 
  group_by(state, pop2010, Constituent) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(Per_Capita = n/pop2010*1000000) %>% 
  # map_id creates the aesthetic mapping to the state name column in your data
  ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Contacts Per Million Residents from Members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", 
        legend.title = element_blank() )+
  facet_grid(. ~ Constituent)
```


---

### Members who contact FERC more than average: 

```{r members_barcoded, fig.height=4, fig.width=9}
# barcode plot of committee members 
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 


Chamber <- "House" # "House" #  
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 
```

### Members who contact FERC more, relative to other agencies: 
```{r ferc_vs_all_rate}
all_contacts %>%
  mutate(FERC = agency == "DOE_FERC") %>%
  group_by(chamber, FERC, name_state, state) %>%
  summarise(n = n() ) %>%
  ungroup() %>%
  spread(key = "FERC", value = "n") %>% 
  mutate(ShareToFERC = round(`TRUE`/(`TRUE`+`FALSE`),2) ) %>% 
  arrange(-ShareToFERC) %>% 
  mutate(total = `TRUE` + `FALSE`) %>% 
  select(name_state, chamber, total, ShareToFERC) %>% 
  filter(ShareToFERC>.3) %>%
  knitr::kable()
```


### Members who contact FERC more in a Congress, relative to other agencies: 
```{r ferc_vs_all_rate_committees}
all_contacts %>%
  mutate(FERC = agency == "DOE_FERC") %>%
  group_by(congress, chamber, committees, FERC, name_state, state) %>%
  summarise(n = n() ) %>%
  ungroup() %>%
  spread(key = "FERC", value = "n") %>% 
  mutate(ShareToFERC = round(`TRUE`/(`TRUE`+`FALSE`),2) )%>% 
  arrange(-ShareToFERC) %>% 
  mutate(total = `TRUE` + `FALSE`) %>% 
  select(name_state, congress, chamber, committees, total, ShareToFERC) %>% 
  filter(ShareToFERC>.5, total>5) %>%
  knitr::kable()
```


## Interesting cases

From [Sen. Dianne Feinstein's website section on accomplishements in the 107th congress](https://www.feinstein.senate.gov/public/index.cfm?p=107th-congress):

"**Significant Negotiations:**

Just and Reasonable Electricity Rates – With the electricity rates skyrocketing because of market manipulation during the California energy crisis, Senator Feinstein lobbied the President, other members of Congress and the Federal Energy Regulatory Commission to cap electricity and natural gas rates.  She also introduced S.26, which would have authorized the Department of Energy to impose price caps, S.287, to direct FERC to impose cost of service based rates on electricity and S.764 to give FERC the choice of either price caps based on demand or cost of service rates.  While the bills did not come up for a vote, Senator Feinstein was finally successful in convincing FERC, after new commissioners were sworn in, to impose price caps on their own."

---

From the [West Virginia Gazette](https://www.wvgazettemail.com/news/politics/wv-republican-congressmen-s-funding-dwarfs-challengers/article_2e9bcb96-9021-56a6-ac0f-57f2917a6bef.html):

In an article titled "Republican congressmen’s funding dwarfs challengers’", the Charleston Gazee-Mail noted how energy companies backed Representative Alex Mooney (R-WV). Indeed, Mooney wrote to FERC more than any other agency, always on behalf of energy projects, mostly pipelines. 
In 2017, he wrote on behalf of the 
Dominion Energy Supply Header Project,
National Fuel Gas Distribution Corporation's [Northern Access Project](https://www.natfuel.com/supply/NorthernAccess2016/default.aspx),
Transcontinental Gas Pipe Line Company's [Atlantic Sunrise Project](https://blog.williams.com/projects-and-operations/atlantic-sunrise/atlantic-sunrise-project-placed-into-full-service/), 
Columbia Gas Transmission's proposed Eastern Panhandle Expansion project,
Columbia's WB Xpress Project to build new compressor stations,
In 2015 he wrote on behalf of the
Columbia s Mountaineer XPress Project,
Atlantic Coast Pipeline ACP project. 
The parent companies of these projects spend millions of dollars on lobbying (Lobbyview). The WV Gazette reports funding from Dominion that is not included in Lobbyview totals. 


---

## Committee Leadership

```{r committeechiars_barcode, fig.height=5, eval=FALSE}
dcommittees %>%  
  mutate(chair = str_remove(chair,"[0-9]* |^NA "),
         committee = paste(chamber, committee))%>% 
  dplyr::select(committee, position, chair, DATE, assigneddate, terminationdate) %>% 
  distinct() %>% 
  filter(str_detect(committee, "ENERGY$|ENVIRONMENT|NATURAL")) %>% 
  mutate(position = ifelse(position == "Other", NA, position)) %>%
  #filter(# !is.na(position),chair_since_2007 == T) %>%
  drop_na(chair) %>% 
  dplyr::select(DATE, chair, position, assigneddate, terminationdate, committee) %>% 
  distinct() %>% 
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = chair),
    shape = 73,
    size=2 
  ) +
  geom_segment(aes(y = chair, yend = chair, 
                   x = assigneddate, xend = terminationdate, 
                   linetype = factor(position)),
               position = position_nudge(y = -0.3)) +
  labs(title = paste("Letters to FERC from Committee Leadership"),
       y = "", 
       x = "",
       linetype = "Leadership position") +
  scale_y_discrete(position = "right") +
  theme(
    strip.text.y = element_text(angle = 180, size = 5),
    # legend.title = element_blank(),
    axis.text.y = element_text(size=5),
    axis.text.x = element_text(angle = 0)
  ) + 
  facet_grid(committee ~ ., scales = "free_y", space = "free_y", switch = "both") 
```

## Many letters to FERC are cosigned

```{r cosigned_estimated, eval=FALSE}
#A rough under-estimate based on whether "et al" or "&" appears in the summary:

FERC_letters %>% 
  filter(year>1999,
         year<2019) %>% 
  group_by(ID) %>% 
  top_n(1) %>% 
  mutate(probably_cosigned = ifelse(str_detect(SUBJECT, "et al"), "et al",
                                 ifelse(str_detect(SUBJECT, "&"), "&", " neither"))) %>%
  group_by(year, probably_cosigned) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = probably_cosigned) +
  geom_col() +
  scale_fill_viridis_d(option = "C", end = .8)
```

Cosigned letters identified by coders
```{r cosigned_coded}
FERC_letters %>% 
  filter(!is.na(Freelancer),
         year>1999,
         year<2019) %>% 
  mutate(Cosigned = ifelse(!is.na(Cosigned_House)|!is.na(Cosigned_Senate),
                                 T, F)) %>%
  group_by(year, Cosigned) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = Cosigned) +
  geom_col() +
  scale_fill_viridis_d(option = "C", end = .8)
```
















---

# Companies 
(see company-crosswalk.Rmd)

---

# PAC Contributions from the Energy Sector
Using CRP industry codes for PACs and DIME contribution matrix, sum up sector-level contributions by memeber per cycle, matching a congress with the cycle when it was elected (e.g. 116th congress = 2018 cycle). 

```{r pac_amounts}
library(tidyverse)
  
load(here::here("data/pac_amounts.Rdata"))

# drop NA industry
pac_amounts %<>% filter(!is.na(industry)) %>% select(icpsr, party_name, congress, cycle, industry, amounts) %>% distinct()

# pac_amounts %>% arrange(-amounts)

pac_amounts %<>% 
  rename(PAC_contributions = amounts) 


# join in members data
load(here::here("members/members.Rdata"))

members %<>% filter(congress > 106)

# chamber switchers
members %<>% group_by(congress, icpsr) %>% mutate(icpsrs_per_congress = n()) 

# chamber or party switchers
# members %>% filter(icpsrs_per_congress>1)

# drop independents who were also part of a major party 
members %<>% filter(icpsrs_per_congress<2 | party_name != "Independent")


pac_amounts %<>% left_join(members %>% select(congress, icpsr, bioname) %>% distinct()) 

# drop any member-congress observations not in members file (i.e. outside timerange )
pac_amounts %<>%  filter(!is.na(bioname)) %>% distinct()

pac_amounts %<>% mutate(cycle = (congress - 107)*2 + 2000)


pac_amounts %>% arrange(icpsr)

# inspect coverage 
pac_amounts %>%
  group_by(cycle, icpsr, party_name, industry) %>% 
  summarise(total = sum(PAC_contributions, na.rm = TRUE)) %>% 
  ungroup() %>% 
  group_by(cycle, party_name, industry) %>% 
  summarise(mean = mean(total)) %>%  
  filter(!is.na(industry)) %>% 
  ggplot() + 
  aes(x = factor(cycle), y = mean, fill = party_name) + 
  geom_col() + 
  facet_wrap(. ~ industry, scales = "free") +
  labs(y = "Average Energy-sector PAC contributions per member \n (ommitting energy extraction companies)", 
       x = "FEC Electoral Cycle")

pac_amounts %<>% distinct()

# problems with duplicate icpsrs? 
# pac_amounts %>% group_by(icpsr, congress,  industry) %>% mutate(n = n() ) %>% filter(n>1)  %>% arrange(icpsr)

# problems with dupliate bioname + party
# pac_amounts %>% group_by(bioname, congress, party_name,  industry) %>% mutate(n = n() ) %>% filter(n>1)  %>% arrange(bioname)

# party switchers 
pac_amounts %<>% group_by(bioname, congress, industry) %>% mutate(parties = n() ) 

# pac_amounts %>% filter(parties>1)  %>% arrange(bioname)

# select the party with the most contributions
pac_amounts %<>% ungroup() %>% group_by(bioname, congress, industry) %>%  top_n(1, PAC_contributions) %>% ungroup()

pac_amounts %<>% filter(parties < 2 | party_name!="Independent")

# pac_amounts %>% filter(party_name=="Independent") %>% arrange(-PAC_contributions, bioname)

# d %>% select(letter_position, congress, icpsr) %>% distinct() %>%  count(letter_position, congress, icpsr, sort= T)

# d %>% count(letter_position, congress)

d$letter_position %<>% replace_na("other")

# letters data
letters <- d %>% 
  # modify_if(is.character, as.factor) %>% 
  # modify_if(is.double, as.factor) %>%  
  count(letter_position, congress, icpsr) %>% 
  ungroup() 

members %<>%  filter(congress >106) %>% filter(chamber %in% c("House", "Sentate")) 

# unique(d$letter_position)
# unique(letters$letter_position)

# add letters to members file to get zero counts
letters <- members %>% select(congress, icpsr) %>% distinct() %>% 
  left_join(letters) %>% # introduces NA letter position, which we can remove after completing
  ungroup() %>% 
  # mutate(letter_position = as.factor(letter_position)) %>% 
    complete(letter_position, nesting(congress, icpsr),
             fill = list(n = 0)) %>% 
  ungroup() %>% 
  filter(!is.na(letter_position)) %>% 
  distinct() 

# should be the same icpsrs
members %>% select(congress, icpsr) %>% ungroup() %>% top_n(10, icpsr) %>% arrange(-icpsr) %>% kable()
letters %>% ungroup() %>% top_n(10, icpsr) %>% arrange(-icpsr) %>% kable()
```

# Merge letters with PAC contribution data
```{r, letters_money}
# merge with PAC amounts
letters_money <-  letters %>% 
  left_join(pac_amounts %>% ungroup()) %>% 
  left_join(letters %>% ungroup() ) %>%
  left_join(members %>% select(congress, icpsr, bioname, chamber)) %>% 
  # drop observations that don't match in members file
  filter(!is.na(bioname)) %>% distinct()

letters_money %>%  top_n(1, icpsr) %>% arrange(-icpsr) %>% kable()


# inspect for 0 counts 
# letters_money %>% count(n, sort = T)

# pull out counts for models 
letters_money %<>%
  mutate(ProBusiness_Letters = ifelse(letter_position == "ProBusiness", n, NA)) %>%
  mutate(AntiBusiness_Letters = ifelse(letter_position == "AntiBusiness", n, NA))


# should be twice as many obs with both industries 
#nrow(letters_money)
#head(letters_money)

# inspect for correct 0 counts (should be equal across years per industry)
# letters_money %>% count(congress, industry, letter_position) %>% arrange(industry)

# compare to memebers data counts #FIXME we are losing a few obs
# members %>% ungroup() %>% count(congress) 

# members that are not in the pac data 
# members %>% anti_join(letters_money) 

# top 10 by contributions in a cycle 
letters_money %>% 
  filter(!is.na(ProBusiness_Letters), industry == "energy" ) %>% 
  dplyr::select(-icpsr, -congress) %>% arrange(-PAC_contributions) %>% 
  top_n(10, PAC_contributions) %>% knitr::kable()
```



## Overall top ten PAC recepients.

Fred Upton (R-Mich.) was chair of the House Energy and Commerce Committee 2011-2017.

U.S. Senator Mary L. Landrieu was Chair of the Senate Committee on Energy and Natural Resources 2014-2015.

Count pro-business and pro-project letters:
```{r letters_money_total}

# total 2000-2018
letters_money %<>% 
  # FIXME should be no NA PAC_contributions
  # FIXME make sure we are only counting congresses in which members served 
  ungroup() %>% 
  group_by(icpsr, industry) %>% 
  mutate(ProBusiness_Letters_Per_Cycle = mean(ProBusiness_Letters, na.rm = TRUE),
         AntiBusiness_Letters_Per_Cycle = mean(AntiBusiness_Letters, na.rm = TRUE),
         PAC_contributions_total = sum(PAC_contributions, na.rm = TRUE)) %>% 
  ungroup()


letters_money %>% 
  select(ProBusiness_Letters_Per_Cycle, PAC_contributions_total, bioname) %>% distinct( )%>% 
  top_n(10, PAC_contributions_total) %>% 
  knitr::kable()
```



Count non-constituent letters:
```{r constituent}

#FIXME
# constituent letters
Non_Constituent_money <- d %>% 
  #FIXME
  # filter(cycle <2014) %>% 
  drop_na(Constituent) %>% 
  #filter(Type %in% c("Corp. Constituent", "Policy")) %>% 
  group_by(name_state, party, congress, icpsr, chamber, oversight_committee) %>%
  mutate(Non_Constituent_Letters = n()) %>% distinct()

# join letters and DIME data by ICPSR, adding a sum of sector PAC contributions per member
Non_Constituent_money %<>% 
  ungroup() %>% 
  full_join(pac_amounts) %>% 
  group_by(icpsr) %>% 
  # FIXME
  # one party per member, need to deal with party switchers
  mutate(party = paste(unique(party), collapse = ";")) %>% 
  mutate(party = str_remove(party, ";.*")) %>% 
  ungroup()%>% distinct()

# Add zero-letter-cycle observations:
Non_Constituent_money %<>% 
 mutate(Non_Constituent_Letters = ifelse(is.na(Non_Constituent_Letters) & cycle > 1997, 0, Non_Constituent_Letters)) %>% distinct()

Non_Constituent_money_total <- Non_Constituent_money %>% 
  # FIXME should be no NAs
  drop_na(PAC_contributions) %>% 
  group_by(icpsr, name_state, party) %>% 
  summarise(Non_Constituent_Letters_Per_Cycle = mean(Non_Constituent_Letters, na.rm = TRUE),
            PAC_contributions = sum(PAC_contributions, na.rm = TRUE)) %>% 
  ungroup()%>% distinct()
```



### Pro-business letters per cycle
```{r, letter_money}
letters_money %<>% filter(bioname != "GOODE, Virgil H., Jr.")

letters_money %<>% left_join(members %>% select(icpsr, congress, state_abbrev)) %>% 
  mutate(name_state = str_c(str_remove(bioname, " .*"), state_abbrev))

top1 <- top_n(letters_money %>% ungroup(), 50, PAC_contributions) %>%
  .$name_state %>% unique()

top2 <- top_n(letters_money, 50, ProBusiness_Letters_Per_Cycle) %>% 
  .$name_state %>% unique()

letters_money %>% 
  mutate(name_state = as.character(name_state)) %>%
  ggplot() + 
  aes(x = PAC_contributions, 
      y = ProBusiness_Letters_Per_Cycle) + 
  geom_point(alpha = .5) + 
  geom_text(aes(label = ifelse(name_state %in% top2,
                               name_state, NA)), 
            check_overlap = TRUE, 
            hjust = 0, 
            color = "blue") + 
  labs(x = "PAC Contributions 1990-2014",
       y = "Average Pro-Business Letters sent to FERC per Cycle") + 
  facet_wrap("industry", scales= "free")

letters_money %>% 
  mutate(name_state = as.character(name_state)) %>%
  ggplot() + 
  coord_flip() + 
  aes(x = PAC_contributions, 
      y = ProBusiness_Letters_Per_Cycle) + 
  geom_point(alpha = .5) + 
  geom_text(aes(label = ifelse(name_state %in% top1, name_state, NA)), 
            check_overlap = TRUE, 
            hjust = 0, 
            color = "blue") + 
  labs(x = "PAC Contributions 1990-2014",
       y = "Average Pro-Business Letters sent to FERC per Cycle") + 
  facet_wrap("industry", scales= "free")
  
```

```{r, eval=FALSE}
library(dplyr)

# MERGE IN LETTERS DATA TO PRO-BUSINESS LETTERS
# FIXME 
# CALLE THIS Pro_letters and Antiletters Anti_letters 
nrow(letters_money)
letters_money %<>% 
           left_join(d %>% dplyr::select(icpsr, congress, # nominate.dim1, #chair_since_2007,
              #oversight_committee, 
              chamber) %>% distinct() #%>% dplyr::rename(chair_since_2000 = chair_since_2007)
) %>% distinct()

letters_money
```

# Models
```{r mplot_function}
library(broom)
library(tidyverse)
mplot <- function(m){m %>%
  tidy(conf.int = TRUE) %>%
    filter(term!="(Intercept)") %>%
ggplot() + 
  aes(x = term,
      y = estimate, 
      ymin = conf.low, 
      ymax = conf.high)+ 
    geom_hline(yintercept = 0, linetype =2) + 
  geom_pointrange() + coord_flip() }

letters_money %<>% 
  group_by(icpsr, congress, industry) %>% 
  mutate(Log_PAC_contributions = log(PAC_contributions+1),
         PAC_Millions = PAC_contributions/1000000,
         total_letters = sum(n) ) %>% 
  ungroup()
```

## Energy Sector-level Models (Arnold book chapter models)

## All Letters per cycle ~ Energy Sector PAC contributions per cycle 1998-2014
```{r all-letters-per-cycle-model, fig.height=1}
mAll <- glm(total_letters ~ PAC_Millions, 
            data = letters_money %>% filter(industry == "energy") %>% select(icpsr, congress, PAC_Millions, total_letters) %>% distinct(), 
         family = poisson)  
# tidy(mAll)
mAll %>% mplot()+
  labs(x="", y="Total additional letters per congress per million dollars")
```

## Non-Constituent Letters
```{r non-constituent models, fig.height=1}
Non_Constituent_money %<>% mutate(PAC_Millions = PAC_contributions/10000)

mNonConstituent <- glm(Non_Constituent_Letters ~ PAC_Millions, 
                       data = Non_Constituent_money %>%
                         filter(industry == "energy") %>% 
                         select(icpsr, congress, PAC_Millions, Non_Constituent_Letters)%>% 
                         distinct() , 
                       family = poisson  ) 
# tidy(mNonConstituent)
mNonConstituent %>% mplot()+
  labs(x="", y="Additional non-constituent letters per congress per million dollars")

mNonConstituentLog <- glm(Non_Constituent_Letters ~ Log_PAC_contributions, 
                          data = Non_Constituent_money %>% 
                            filter(industry == "energy") %>% 
                            select(icpsr, congress, PAC_contributions, Non_Constituent_Letters)%>%
                            distinct() %>% 
                            filter(!is.na(PAC_contributions)) %>% #FIXME why is this NA
                            mutate(Log_PAC_contributions = log(PAC_contributions+1)),
                          family = poisson  ) 
# tidy(mNonConstituent)
mNonConstituentLog %>% mplot()+
  labs(x="", y="Additional non-constituent letters per congress per logged million dollars")
```

## Pro-Business Letters per cycle ~ Energy Sector PAC contributions per cycle 1998-2018
```{r money-letters-per-cycle-model, fig.height=1}
mPro <- glm(ProBusiness_Letters ~ PAC_Millions,
            data = letters_money %>% 
              filter(industry == "energy") %>% 
              select(icpsr, congress, PAC_Millions, ProBusiness_Letters) %>% 
              distinct(),
            family = poisson)  

mPro %>% mplot()+
  labs(x="", y="Additional pro-business letters per congress per million dollars")


mProLog <- glm(ProBusiness_Letters ~ Log_PAC_contributions, 
              data = letters_money %>% 
              filter(industry == "energy") %>% 
              select(icpsr, congress, Log_PAC_contributions, ProBusiness_Letters) %>% 
              distinct(),
            family = poisson) 
mProLog %>% mplot()+
  labs(x="", y="Additional letters per congress per Log(PAC Contributions)")
```



### Pro-business letters by party
```{r letters-per-cycle-model-party, fig.height=1}
mProParty <- glm(ProBusiness_Letters ~ party_name,
                 data = letters_money %>% 
                   filter(industry == "energy") %>% 
                   filter(party_name != "Independent") %>% 
                   select(icpsr, congress, party_name, ProBusiness_Letters) %>% 
              distinct(),
            family = poisson) 

# tidy(mProParty)
mplot(mProParty) +
  labs(x="", y="Additional pro-business letters per congress")
```
Republicans send an additional `r round(mProParty$coefficients[2], 1)` letters per Congress, on average.



### Pro-business letters ~ Party + PAC
```{r multivariate_model, fig.height=1, include =TRUE}
# PAC + party:
mPro_pac_party <- glm(ProBusiness_Letters ~ PAC_Millions + party_name,
                      data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_Millions, party_name, ProBusiness_Letters) %>% 
              distinct(),
            family = poisson)

# tidy(mPro_pac_party)

mplot(mPro_pac_party)+
  labs(x="", y="Additional letters per congress")

# PAC*party interaction:
mPro_pacXparty <- glm(ProBusiness_Letters ~ PAC_Millions * party_name, 
                      data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_Millions, party_name, ProBusiness_Letters) %>%
                      distinct(),
            family = poisson)

# tidy(mPro_pacXparty)

mplot(mPro_pacXparty)+
  labs(x="", y="Additional letters per congress")



# DW NOMINATE 
#mPro_nominate <-glm(ProBusiness_Letters ~  nominate.dim1, data = letters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  
#tidy(mPro_nominate)
#mplot(mPro_nominate)+labs(x="", y="Additional letters per congress")

# PAC + ideology:
# mPro_pac_nominate <-glm(ProBusiness_Letters ~ PAC_contributions * nominate.dim1, data = letters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  

# tidy(mPro_pac_nominate)

# mplot(mPro_pac_nominate)+ labs(x="", y="Additional letters per congress")
```

#### Full (multivariate) models 
```{r full-model, fig.height=1}
# Full model, all letters
mAll_Full <- glm(total_letters ~ PAC_Millions + party_name, 
                 data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_Millions, party_name, total_letters) %>%
                      distinct(),
            family = poisson)

# tidy(mAll_Full)

mplot(mAll_Full)+
  labs(x="", y="Additional letters per congress")

# Full model with interaction:
mAll_Fullx <- glm(total_letters ~ PAC_Millions*party_name, 
                                   data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_Millions, party_name, total_letters) %>%
                      distinct(),
            family = poisson)
# tidy(mAll_Fullx)

mplot(mAll_Fullx)+
  labs(x="", y="Additional letters per congress")



# Full model, pro business letters 
mPro_Full <- glm(ProBusiness_Letters ~ PAC_Millions + party_name, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_Millions, party_name, ProBusiness_Letters) %>%
                      distinct(),
            family = poisson)

# tidy(mPro_Full)

mplot(mPro_Full)+
  labs(x="", y="Additional letters per congress")

# Full model with interaction:
mPro_Fullx <- glm(ProBusiness_Letters ~ PAC_Millions * party_name, 
                                  data = letters_money %>% 
                        filter(industry == "energy",
                               party_name != "Independent",
                               !is.na(ProBusiness_Letters)) %>% 
                        select(icpsr, congress, PAC_Millions, party_name, ProBusiness_Letters) %>%
                      distinct(),
            family = poisson)

# tidy(mPro_Fullx)

mplot(mPro_Fullx)+
  labs(x="", y="Additional letters per congress")


mAnti_Full <- glm(AntiBusiness_Letters ~ PAC_Millions + party_name, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_Millions, party_name, AntiBusiness_Letters) %>%
                      distinct(),
            family = poisson)

# tidy(mAnti_Full)

mplot(mAnti_Full)+
  labs(x="", y="Additional letters per congress")

# full model with interaction 
mAnti_Fullx <- glm(AntiBusiness_Letters ~ PAC_Millions * party_name, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_Millions, party_name, AntiBusiness_Letters) %>%
                      distinct(),
            family = poisson)

# tidy(mAnti_Fullx)
mplot(mAnti_Fullx)+
  labs(x="", y="Additional letters per congress")

# FULL MODEL WITH NON- CONSTITUENT 
# FIXME
#mNonConstituent_Fullx <- glm(NonConstituent_Letters ~ PAC_contributions*party, data = NonConstituent_letters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  
#tidy(mNonConstituent_Fullx)
#mplot(mNonConstituent_Fullx)+labs(x="", y="Additional non-constituent letters per congress")
```



## Average Pro-Business letters per cycle ~ total Energy Sector PAC contributions 1990-2014
```{r money-letters-total, fig.height=1}
# many fewer observations over time period (about 1000 members served)
mProTotal <- glm(ProBusiness_Letters_Per_Cycle ~ PAC_Millions_total, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, PAC_contributions_total, ProBusiness_Letters_Per_Cycle) %>%
                   mutate(PAC_Millions_total = PAC_contributions_total/100000) %>% 
                      distinct(),
            family = poisson)

# tidy(mProTotal)
mplot(mProTotal)+
  labs(x="", y="Average additional letters per cycle per million dollars 1990-2014")
```

## Anti-Business Letters per cycle ~ Energy Sector PAC contributions per cycle 1998-2014
```{r money-Antiletters-per-cycle-model, fig.height=1}
mAnti <- glm(AntiBusiness_Letters ~ PAC_Millions, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, PAC_Millions, AntiBusiness_Letters) %>%
                      distinct(),
            family = poisson)
# tidy(mAnti)
mAnti %>% mplot()+
  labs(x="", y="Additional anti-buisness letters per congress per million dollars")

mAntiLog <- glm(AntiBusiness_Letters ~ Log_PAC_contributions, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        # filter(party_name != "Independent") %>% 
                        select(icpsr, Log_PAC_contributions, AntiBusiness_Letters) %>%
                      distinct(),
            family = poisson)
# tidy(mAntiLog)
mAntiLog %>% mplot()+
  labs(x="", y="Additional anti-business Letters per congress per Log(PAC Contributions)")
```

#### By party:
```{r Antiletters-per-cycle-model-party, fig.height=1}
mAntiParty <- glm(AntiBusiness_Letters ~ party_name,
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, PAC_Millions, AntiBusiness_Letters, party_name) %>%
                      distinct(),
            family = poisson)
# tidy(mAntiParty)
mplot(mAntiParty) +
  labs(x="", y="Additional anti-business  letters per congress")
```

Democrats send an additional `r -round(mAntiParty$coefficients[2], 1)` Anti-Business letters per Congress, on average.

```{r money-Antiletters-per-cycle-model-party, fig.height=1, include=TRUE}
#PAC*party interaction:
mAnti_pac_party <- glm(AntiBusiness_Letters ~ PAC_Millions + party_name, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, PAC_Millions, AntiBusiness_Letters, party_name) %>%
                      distinct(),
            family = poisson)

# tidy(mAnti_pac_party)
mplot(mAnti_pac_party)+ labs(x="", y="Additional anti-business letters per congress")


#PAC*party interaction:
mAnti_pacXparty <- glm(AntiBusiness_Letters ~ PAC_Millions*party_name, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, PAC_Millions, AntiBusiness_Letters, party_name) %>%
                      distinct(),
            family = poisson)

# tidy(mAnti_pacXparty)

# FIXME odd error
mplot(mAnti_pacXparty)+ labs(x="", y="Additional anti-business letters per congress")
```



#### Average Anti-Business letters per cycle ~ total Energy Sector PAC contributions 1990-2014
```{r money-Antiletters-total, fig.height=1}
mAntiTotal <- glm(AntiBusiness_Letters_Per_Cycle ~ PAC_Millions_total, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, PAC_contributions_total, AntiBusiness_Letters_Per_Cycle) %>%
                   mutate(PAC_Millions_total = PAC_contributions_total/100000) %>% 
                      distinct(),
            family = poisson)

# tidy(mProTotal)
mplot(mAntiTotal)+
  labs(x="", y="Average additional letters per cycle per million dollars 1990-2014")
```

# Combined models 

```{r models, fig.height=2, results='hide'}
library(dplyr)
dplot <- function(x){dwplot(x) +
    aes(shape = model) + 
    geom_vline(xintercept = 0, linetype = 2) +
    scale_color_viridis_d(option = "C", end = .8) + 
    labs(color = "Dependent Variable",
         shape = "Dependent Variable") +
  theme(panel.grid.major.y  = element_blank())
}

# Basic PAC money models 
models <- full_join(
  tidy(mAll) %>% mutate(model = "All Letters per Cycle"),
  tidy(mPro) %>% mutate(model = "Pro-business Letters per Cycle") ) %>% 
  full_join(tidy(mNonConstituent) %>% mutate(model = "Non-constituent Letters per Cycle")) %>%
  full_join(tidy(mAnti)  %>% mutate(model = "Anti-business Letters per Cycle")) 

dplot(models)+ 
    labs(color = "Dependent Variable",
         shape = "Dependent Variable",
         x = "Additional letters per million dollars per cycle")

library(stargazer)
library(dplyr)
write_lines(stargazer(mAll, mPro, mAnti, mNonConstituent, float=F),
  path = here("FERC/tables/All-mPro-mAnti-mNonConstituent.tex"))

table <- stargazer(mAll, mPro, mAnti, mNonConstituent, 
                type = "html",
                notes = "FERC/tables/All-mPro-mAnti-mNonConstituent.tex")
```


```{r, results="asis"}
htmltools::HTML(table)
```

### logged PAC money models 
```{r models-log, fig.height=2, results='hide'}
## logged PAC money models 
models <- tidy(mProLog) %>% mutate(model = "Pro-business Letters per Cycle") %>%  
full_join(tidy(mAntiLog) %>% mutate(model = "Anti-business Letters per Cycle")) 

dplot(models)+ 
    labs(x = "Additional letters per million dollars per cycle")

write_lines(
  stargazer::stargazer(mProLog, mAntiLog,
                       float=F),
  path = here("FERC/tables/mProLog-mAntiLog.tex"))

table <- stargazer(mProLog, mAntiLog, 
                type = "html",
                notes = "FERC/tables/mProLog-mAntiLog.tex")
```

```{r, results="asis"}
htmltools::HTML(table)
```

### PAC contributions over entire time period 
```{r models-total, fig.height=2, results = 'hide'}
## PAC contributions over entire time period 
models <- tidy(mProTotal) %>% 
  mutate(model = "Pro-business Letters per Cycle") %>% 
  full_join(tidy(mAntiTotal) %>% mutate(model = "Anti-business Letters per Cycle")) 

dplot(models) + 
    labs(x = "Average additional letters per cycle per million dollars 1990-2014")

write_lines(
  stargazer::stargazer(mProTotal, mAntiTotal, float=F),
  path = here("FERC/tables/mProTotal-mAntiTotal.tex"))

table <- stargazer(mProTotal, mAntiTotal, 
                type = "html",
                notes = "FERC/tables/mProTotal-mAntiTotal.tex")
```

```{r, results="asis"}
htmltools::HTML(table)
```

### Party
```{r models-party, fig.height=2, results='hide'}
## With party IV 
models <- tidy(mProParty) %>% 
  mutate(model = "Pro-business Letters per Cycle") %>%
  full_join(tidy(mAntiParty) %>%
              mutate(model = "Anti-business Letters per Cycle")) %>%
  # mutate(term = str_replace(term, "party\\(R\\)", "Republican")) %>% 
  filter(term != "party(I)")

dplot(models) + 
    labs(x = "Additional letters per cycle")

write_lines(
  stargazer::stargazer(mProParty, mAntiParty, float=F),
  path = here("FERC/tables/mProParty-mAntiParty.tex"))

table <- stargazer(mProParty, mAntiParty, 
                type = "html",
                notes = "FERC/tables/mProParty-mAntiParty.tex")
```

```{r, results="asis"}
htmltools::HTML(table)
```



### All univariate models 
```{r models-ALL, fig.height=2, results='hide'}
# All models 
write_lines(
  stargazer::stargazer(mAll, mPro, mAnti,mNonConstituent, mProLog, mAntiLog, mProParty, mProTotal, mAntiTotal, mAntiParty, float = F),
  path = here("FERC/tables/mUnivariate.tex"))

table <-stargazer(mAll, mPro, mAnti, mNonConstituent, mProLog, mAntiLog, mProParty, mProTotal, mAntiTotal, mAntiParty, 
                type = "html",
                notes = "FERC/tables/mUnivariate.tex")
```

```{r, results="asis"}
htmltools::HTML(table)
```



### All Full (multivariate) Models
```{r models-full, fig.height=2, results='hide'}
## Full models
models <- tidy(mAll_Full) %>% 
  mutate(model = "Total Letters per Cycle") %>%
  full_join(tidy(mPro_Full) %>%
              mutate(model = "Pro-business Letters per Cycle")) %>%
  full_join(tidy(mAnti_Full) %>%
              mutate(model = "Anti-business Letters per Cycle"))
dplot(models) + 
    labs(x = "Additional letters per cycle")

## Full models + interactions
models <- tidy(mAll_Full) %>% 
  mutate(model = "Total Letters per Cycle") %>%
  full_join(tidy(mPro_Full) %>%
              mutate(model = "Pro-business Letters per Cycle")) %>%
  full_join(tidy(mPro_Fullx) %>% mutate(model = "Pro-business Letters per Cycle, with interaction")) %>%
  full_join(tidy(mAnti_Full) %>%
              mutate(model = "Anti-business Letters per Cycle")) %>%
  full_join(tidy(mAnti_Fullx) %>% mutate(model = "Anti-business Letters per Cycle, with interaction")) # %>%  mutate(term = str_replace(term, "party\\(R\\)", "Republican"))

dplot(models) + 
    labs(x = "Additional letters per cycle")

write_lines(
  stargazer::stargazer(mAll_Full, mAll_Fullx, mPro_Full, mAnti_Full,mPro_Fullx, mAnti_Fullx, float=F),
  path = here("FERC/tables/mFull.tex"))

table <- stargazer(mPro_Full, mAnti_Full, mPro_Fullx, mAnti_Fullx,
                type = "html",
                notes = "FERC/tables/mFull.tex")

table <- stargazer(mPro_Full, mAnti_Full, mPro_Fullx, mAnti_Fullx,
                type = "html",
                notes = "FERC/tables/mFull.tex")
```

```{r, results="asis"}
htmltools::HTML(table)
```



# About FERC 

FERC regulates electricity markets, oil and gas pipelines, and hydropower and gas export projects. Many of these decisions have major implications for business profets. For example, because many natual gas pipelines cross state lines, FERC largely controls pipeline market entry. Similarly, because electricity grids are regional. 


## Letters on behalf of projects in their districts
TODO

```{r}
d %>% 
  mutate(Place_District = tolower(Place_District)) %>% 
  # FIXME 
  # dropping odd observations, will correct in DOE_FERC.R script 
  filter(Place_District %in% c("yes", "no", NA)) %>% 
  filter(letter_position %in% c("AntiBusiness", "ProBusiness")) %>% 
  filter(Constituent != "Not coded") %>% 
  count(Place_District, letter_position, Constituent) %>% 
  ggplot() +
  aes(x = Place_District, y = n, fill = letter_position) +
  geom_col() + 
  facet_grid(Constituent ~ .)+ 
  labs(x = "Is the proposed project in the member's district?",
       y = "Number of letters",
       fill = "")
```




# TO DO 

## DONE
- add clean text from scraper to google sheet 
- fix clean function to pull and combine new data
- link industry codes to CRP PAC committee classification: 
 1. Identify relevent industry codes 
 2. Get cycle-specific PAC classification for those industry codes 
 3. Subset dime to those PAC classification 
- Add 2015-2018 DIME
- Fix DIME ICPSRs 

 
 ## FERC Paper 1
- Fix Goode, and other party switchers who are double counted as an R and I (dropped for now)
- Identify companies that did not match a PAC and see if they match a parent company 


## FERC Paper 2 
- letters per company 
- letters per company pac (before and after merging in partent companies)
- add company names from company scraper to google sheet
- template to match company names to donation (lobbyview, DIME)
- template match company names to industry codes (center for responsive politics)

- Letters are on behalf of donors
TODO

- Comparing FERC to other agencies
TODO 
