---
title: "Lobbying the U.S. Federal Energy Regulatory Commission (FERC)"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# Rscript -e 'library(rmarkdown); rmarkdown::render("gh-pages/summary.Rmd", "html_document")'

requires <- c("tidyr", "broom", "knitr","ineq", "dplyr", "ggplot2", "magrittr", "stargazer", "maps", "fiftystater", "mapproj", "dotwhisker", "here")
  to_install <- c(requires %in% rownames(installed.packages()) == FALSE)
  install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )
  devtools::install_github("wmurphyrd/fiftystater")
  library(tidyverse)
  library(tidyr)
  library(ineq)
  library(dplyr)
  library(ggplot2); theme_set(theme_bw())
  library(magrittr)
  library(maps)
  library(fiftystater)
  library(mapproj)
  library(knitr)
  library(broom)
  library(dotwhisker)
  library(here)
```

```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = F, 
                      fig.width=8.5, 
                      fig.align = 'center', 
                      fig.path='Figs/',
                      warning=FALSE, 
                      message=FALSE)
```

# Data
```{r data}
load(here("data/correspondence.RData"))
dcommittees %<>% filter(agency == "DOE_FERC")
all <- df 
df %<>% filter(agency=="DOE_FERC")

load(here("data/logs.RData"))
logs %<>% filter(agency=="DOE_FERC Extended") 

load(here("data/DOE_FERC-letters-corps.RData"))
FERC_letters %<>% mutate(year = as.numeric(str_sub(doc_date, 1,4))) %>% 
  rename(ID =id)

d <- full_join(logs, FERC_letters)
```

In all, we have `r nrow(distinct(FERC_letters %>% select(ID)))` letters received by FERC and marked "congressional" since 1990. Most, but not all of these are from Members of the U.S. Congress. For this paper, we focus on `r nrow(distinct(FERC_letters %>% filter(year >1999) %>% select(ID) ) )` letters from 2000-2018. 

So far we have matched `r nrow(logs)` of these letters to member names for years `r unique(logs$year)`. 


Rule-based coding of constituent type (click `CODE` to see inductively-developed coding rules):
```{r code, eval=FALSE}
d %<>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CONSTITUENT", SUBJECT, ignore.case = TRUE), 
                        "1", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CONSTITUENT", SUBJECT, ignore.case = TRUE), 
                             "2", CERTAINTY)) %>%
  ## Corporate service?
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), 
                        "2", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), 
                             "3", CERTAINTY)) %>%
  ## or policy
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), 
                            "5", ALT_TYPE)) %>%
  ## Policy work
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", SUBJECT, ignore.case = TRUE), 
                        "5", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", SUBJECT, ignore.case = TRUE), 
                             "1", CERTAINTY)) %>%
  ## Local government
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", SUBJECT, ignore.case = TRUE), 
                        "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", SUBJECT, ignore.case = TRUE), 
                             "1", CERTAINTY)) %>%
  ## Corporate service
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), 
                        "4", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), 
                             "2", CERTAINTY)) %>%
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), 
                            "5", ALT_TYPE)) %>%
  ## PUCs = nonprofits, right?
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("PUBLIC UTILITIES COMMISSION", SUBJECT, ignore.case = TRUE), 
                        "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("PUBLIC UTILITIES COMMISSION", SUBJECT, ignore.case = TRUE), 
                             "1", CERTAINTY)) 
```


```{r data-coverage-by-type}
d %>% 
  filter(Type != "To be coded") %>%  
  mutate(total = n()) %>% 
  group_by(Type, total) %>% summarise(nT = n()) %>% 
  mutate(percent = paste0(nT, " = ", 100*round(nT/total, 2), "%")) %>% 
  ggplot() + 
  geom_col(aes(x = Type, y = nT)) + 
  geom_text(aes(x = Type, y = nT, label = percent), vjust = -.1) +
  labs(x = "",
       y = paste("Number of Contacts, N =", sum(nrow(df))),
       title = "") +
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x.top = element_text())
```


---


### Companies
Of the companies registered to lobby FERC, several appear in the letter texts:
```{r}
d %>% group_by(company_short) %>% 
  select(id, last_name, company_short) %>% 
  filter(company_short != "")%>%
  distinct() %>% 
  summarise( n = n() , members = str_c(last_name, collapse = "; ")) %>% 
  arrange(-n) %>%
  knitr::kable()
```

### Senators vs. state population 

```{r population, fig.height= 3.7, fig.width=6}
d %>% 
  filter(chamber == "Senate") %>% 
    group_by(member_state, year, pop2010) %>% summarise(n = n()) %>%
    group_by(member_state, pop2010) %>% summarise(mean = mean(n)) %>% ungroup() %>% 
    ggplot() + 
    geom_point(aes(x = log(pop2010), y = mean), color = "light blue") + 
    geom_smooth(aes(x = log(pop2010), y = mean)) + 
  geom_text(aes(x = log(pop2010), y = mean, label = ifelse(mean > mean(mean)*1.75, member_state, "")), check_overlap = F, size = 2.5, hjust = 0) + theme_bw() +
  labs(title = "Senator Requests per Year by State Population",
       x = "Log State Population",
       y = "Average Number of Requests per Year")

```

```{r sentate_percapita_map}
Chamber = "Senate"

d %>% 
  filter(chamber == Chamber) %>% 
  group_by(state, Type) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank())# + facet_grid(. ~ Type)

d %>% 
  filter(chamber == Chamber) %>% 
  group_by(state, pop2010, Type) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(Per_Capita = n/pop2010*1000000) %>% 
  # map_id creates the aesthetic mapping to the state name column in your data
  ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Contacts Per Million Residents from Members of the", Chamber)) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) #+
  #facet_grid(. ~ Type)
```


---

### Members who contact FERC more than average: 

```{r members_barcoded, fig.height=4, fig.width=9}
# barcode plot of committee members 

Chamber <- "Senate" # "House" #  
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 


Chamber <- "House" # "House" #  
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 
```

### Members who contact FERC more, relative to other agencies: 


```{r ferc_vs_all_rate}
all %>%
  mutate(FERC = agency == "DOE_FERC") %>%
  group_by(chamber, committees, FERC, name_state, state) %>%
  summarise(n = n() ) %>%
  ungroup() %>%
  spread(key = "FERC", value = "n") %>% 
  mutate(ShareToFERC = round(`TRUE`/(`TRUE`+`FALSE`),2) )%>% 
  arrange(-ShareToFERC) %>% 
  mutate(total = `TRUE` + `FALSE`) %>% 
  select(name_state, chamber, committees, total, ShareToFERC) %>% 
  filter(ShareToFERC>.1) %>%
  knitr::kable()
  
```

## Interesting cases

In an article titled "Republican congressmen’s funding dwarfs challengers’", the Charleston Gazee-Mail noted how energy companies backed Representative Alex Mooney (R-WV). Indeed, Mooney wrote to FERC more than any other agency, always on behalf of energy projects, mostly pipelines. 
In 2017, he wrote on behalf of the 
Dominion Energy Supply Header Project,
National Fuel Gas Distribution Corporation's [Northern Access Project](https://www.natfuel.com/supply/NorthernAccess2016/default.aspx),
Transcontinental Gas Pipe Line Company's [Atlantic Sunrise Project](https://blog.williams.com/projects-and-operations/atlantic-sunrise/atlantic-sunrise-project-placed-into-full-service/), 
Columbia Gas Transmission's proposed Eastern Panhandle Expansion project,
Columbia's WB Xpress Project to build new compressor stations,
In 2015 he wrote on behalf of the
Columbia s Mountaineer XPress Project,
Atlantic Coast Pipeline ACP project. 
The parent companies of these projects spend millions of dollars on lobbying (Lobbyview). The WV Gazette reports funding from Dominion that is not included in Lobbyview totals. 





## Committee Chairs

```{r committeechiars_barcode_senate, fig.height=10}
Chamber = "Senate"
dcommittees %>%  
  mutate(position = ifelse(position == "Other", NA, position)) %>% 
  filter(chamber == Chamber, 
         chair_since_2007 == T,  
         DATE < as.Date("2017-01-01"),
        DATE > as.Date("2007-01-01"),
        assigneddate < as.Date("2017-01-01"),
        terminationdate > as.Date("2007-01-01")) %>%
  select(DATE, chair, position, department, assigneddate, terminationdate, chamber, committee) %>% 
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = chair),
    shape = 73,
    size=2 
  ) +
  geom_segment(aes(y = chair, yend = chair, 
                   x = assigneddate, xend = terminationdate, 
                   linetype = factor(position)),
               position = position_nudge(y = -0.3)) +
  labs(title = paste(Chamber, "Committee Chairs"),
       y = "", 
       x = "" ) +
  scale_y_discrete(position = "right") +
  theme(
    strip.text.y = element_text(angle = 180, size = 5),
    legend.title = element_blank(),
    axis.text.y = element_text(size=5),
    axis.text.x = element_text(angle = 0)
  ) + 
  facet_grid(committee ~ ., scales = "free_y", space = "free_y", switch = "both") 
```

```{r committeechiars_barcode_house, fig.height=10, include= TRUE}
Chamber = "House"
dcommittees %>%  
  mutate(position = ifelse(position == "Other", NA, position)) %>% 
  filter(chamber == Chamber, 
         chair_since_2007 == T,  
         DATE < as.Date("2017-01-01"),
        DATE > as.Date("2007-01-01"),
        assigneddate < as.Date("2017-01-01"),
        terminationdate > as.Date("2007-01-01")) %>%
  select(DATE, chair, position, department, assigneddate, terminationdate, chamber, committee) %>% 
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = chair),
    shape = 73,
    size=2 
  ) +
  geom_segment(aes(y = chair, yend = chair, 
                   x = assigneddate, xend = terminationdate, 
                   linetype = factor(position)),
               position = position_nudge(y = -0.3)) +
  labs(title = paste(Chamber, "Committee Chairs"),
       y = "", 
       x = "" ) +
  scale_y_discrete(position = "right") +
  theme(
    strip.text.y = element_text(angle = 180, size = 5),
    legend.title = element_blank(),
    axis.text.y = element_text(size=5),
    axis.text.x = element_text(angle = 0)
  ) + 
  facet_grid(committee ~ ., scales = "free_y", space = "free_y", switch = "both") 
```  


## Many letters to FERC are cosigned

FIXME, calculate real data when we have coding. This is a rough under-estimate: 
```{r cosigned}
FERC_letters %>% 
  mutate(probably_cosigned = ifelse(str_detect(summary, "et al"), "et al",
                                 ifelse(str_detect(summary, "&"), "&", " neither"))) %>%
  group_by(year, probably_cosigned) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = probably_cosigned) +
  geom_col() 
```

# About FERC 

FERC regulates electricity markets, oil and gas pipelines, and hydropower and gas export terminal projects. 

FERC controls pipeline market entry. 


## Letters on behalf of projects in their districts
TODO

## Letters are on behalf of donors
TODO

# Comparing FERC to other agencies
TODO 


# TO DO 

## Before upwork data
- add clean text from scraper to google sheet 
- add company names from company scraper to google sheet
- template to match company names to donation (lobbyview, DIME)
- template match company names to industry codes (center for responsive politics)

## After upwork data 
- fix clean function to pull and combine new data

# References 

![Sources of Bureaucratic Delay: A Case Study of FERC Dam Relicensing](https://academic.oup.com/jleo/article/22/1/258/938707)
