---
title: "Lobbying the U.S. Federal Energy Regulatory Commission (FERC)"
output:
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# Rscript -e 'library(rmarkdown); rmarkdown::render("gh-pages/summary.Rmd", "html_document")'

requires <- c("tidyr", "broom", "knitr","ineq", "dplyr", "ggplot2", "magrittr", "stargazer", "maps", "fiftystater", "mapproj", "dotwhisker", "here")
  to_install <- c(requires %in% rownames(installed.packages()) == FALSE)
  install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )
  devtools::install_github("wmurphyrd/fiftystater")
  library(tidyverse)
  library(ineq)
  library(ggplot2); theme_set(theme_bw())
  library(magrittr)
  library(maps)
  library(fiftystater)
  library(mapproj)
  library(knitr)
  library(broom)
  library(dotwhisker)
  library(here)
```

```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = F, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='Figs/',
                      warning=FALSE, 
                      message=FALSE)
```

# Data
```{r data}
load(here("data/all_contacts.RData"))
# one obs per member per letter for all agencies
d <- all_contacts %>% 
  # define d as just FERC
  filter(agency=="DOE_FERC") %>% 
  select(-SUBJECT) %>% 
  mutate(majority = ifelse(majority == 1, "Majority", "Minority")) %>%
  # FIXME 
  # GOODE needs to be fixed in party switchers portion of merge.R
  filter(!(last_name == "GOODE"&party == "(I)"))
  

# one obs per member per letter per committee for all agencies
load(here("data/all_contacts_committees.RData"))
# define dcommittees as just FERC
dcommittees <- all_contacts_committees %<>% filter(agency == "DOE_FERC")

# Coded letters, one obs per member per letter 
load(here("data/DOE_FERC-letters-coded.RData")) 
# TO DO: replace with DOE_FERC-letters-corps.Rdata when corps added
FERC_letters %<>% 
  select(ID, SUBJECT, 
         Freelancer, Cosigned_House, Cosigned_Senate,
         text_clean, Constituent, year,
         Place_State, Place_District, Place_District, 
         ProBusiness, AntiBusiness, ProProject, AntiProject) %>% 
  distinct()

# merge in coded letters
d %<>% left_join(FERC_letters) %>% filter(year <2019)
```

In all, we have `r nrow(distinct(FERC_letters %>% select(ID)))` letters received by FERC and marked "congressional" since 1990. Most, but not all of these are from Members of the U.S. Congress. For this paper, we focus on `r nrow(distinct(FERC_letters %>% filter(year >1999) %>% select(ID) ) )` letters from 2000-2018. 

Many letters are cosigned, yeilding `r d %>% filter(year >1999, !is.na(bioname)) %>% nrow()` members-level observations for years `r min(d$year)`-`r max(d$year)`. 

---

## By party 


```{r part-constituent, fig.height=2}
d %>% 
  mutate(For = ifelse(tolower(Constituent) =="yes", "Constituent", NA),
         For = ifelse(!is.na(ProBusiness), "Business", For)) %>% 
  count(party, For, majority) %>% 
  filter(party != "(I)",
         !is.na(For),
         !is.na(majority)) %>% 
  ggplot() + 
  aes(y = n, x = party, fill = For) + 
  geom_col( position = "dodge") + 
  coord_flip() + facet_grid(. ~ majority) + 
  scale_fill_viridis_d(option = "A")
```

Some letters oppose businesses: 
```{r part-business, fig.height=2}
d %>% 
  mutate(position = ifelse(!is.na(ProBusiness), "ProBusiness", NA),
         position = ifelse(!is.na(AntiBusiness), "AntiBusiness", position)#,
         #position = ifelse(!is.na(AntiBusiness)&!is.na(ProBusiness), "Both", position),
         #position = ifelse(is.na(position)&!is.na(Constituent), "Neutral Constituent", position)
         ) %>% 
  count(party, position, majority) %>% 
  filter(party != "(I)",
         !is.na(position),
         !is.na(majority)) %>% 
  ggplot() + 
  aes(y = n, x = party, fill = position) + 
  geom_col( position = "dodge") + 
  coord_flip() + facet_grid(. ~ majority)+ 
  scale_fill_viridis_d(option = "C")
```

---

## Coding of constituent type 
Our coding of letter type is a mix of hand coding "Pro-business" and "Constituent" letters, as well as some coding rules applied to letters that were not put in either group by human coders (click `CODE` to see inductively-developed coding rules):
```{r code, eval=FALSE}
# TYPE 1: Indiv. constituent service 
# TYPE 2: Corp. contituent service 
# TYPE 3: 501c3 constituent service 
# TYPE 4: Corp./Industry serving policy 
# TYPE 5: General policy 
d %<>%
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CONSTITUENT", SUBJECT, ignore.case = TRUE), 
                        "1", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CONSTITUENT", SUBJECT, ignore.case = TRUE), 
                             "2", CERTAINTY)) %>%
  ## Corporate service?
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), 
                        "2", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), 
                             "3", CERTAINTY)) %>%
  ## or policy
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), 
                            "5", ALT_TYPE)) %>%
  ## Policy work
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", SUBJECT, ignore.case = TRUE), 
                        "5", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", SUBJECT, ignore.case = TRUE), 
                             "1", CERTAINTY)) %>%
  ## Local government
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", SUBJECT, ignore.case = TRUE), 
                        "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", SUBJECT, ignore.case = TRUE), 
                             "1", CERTAINTY)) %>%
  ## Corporate service
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), 
                        "4", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), 
                             "2", CERTAINTY)) %>%
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), 
                            "5", ALT_TYPE)) %>%
  ## PUCs = nonprofits, right?
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("PUBLIC UTILITIES COMMISSION", SUBJECT, ignore.case = TRUE), 
                        "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("PUBLIC UTILITIES COMMISSION", SUBJECT, ignore.case = TRUE), 
                             "1", CERTAINTY)) 
```

FERC has an especially high ratio of letters written on behalf of businesses compared other agencies that mostly recieve letters from legislators on behalf of their constituents. 

```{r data-by-type}
d %<>%  
  mutate(Type = as.character(Type)) %>% 
  mutate(Type = ifelse(tolower(Constituent) =="yes", "Indiv. Constituent", Type)) %>% 
  mutate(Type = ifelse(!is.na(ProBusiness), "Corp. Constituent", Type)) 

all_contacts$Type %<>% fct_recode(Policy = "Corp. Policy")

all_percent <- all_contacts %>% 
  filter(Type != "To be coded") %>%  
  mutate(total = n()) %>% 
  group_by(Type, total) %>% summarise(nT = n()) %>% 
  mutate(percent = 100*round(nT/total, 2) ) %>% 
  mutate(agency = "Overall")

d$Type %<>% fct_recode(Policy = "Corp. Policy")
d_percent <- d%>% 
  filter(Type != "To be coded") %>%  
  mutate(total = n()) %>% 
  group_by(Type, total) %>% summarise(nT = n()) %>% 
  mutate(percent = 100*round(nT/total, 2) ) %>% 
  mutate(agency = "DOE FERC")

full_join( all_percent, d_percent)%>% 
  ggplot() + 
  aes(x = Type, y = percent, fill = agency, color = agency, label = nT) + 
  geom_col(position = "dodge") + 
  geom_text(vjust = -.1,
            aes(hjust = ifelse(agency == "Overall", 0,1))) +
  labs(x = "",
       fill = "",
       color = "",
       y = "Percent", #paste("Number of Contacts, N =", sum(nrow(all_contacts))),
       title = "Legislator Contacts with FERC") +
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x.top = element_text()) + 
  scale_color_viridis_d() +
  scale_fill_viridis_d()
```

---

# Members

### Senators vs. state population 

```{r population, fig.height= 3.7, fig.width=6}
d %>% 
  filter(chamber == "Senate") %>% 
    group_by(member_state, year, pop2010) %>% summarise(n = n()) %>%
    group_by(member_state, pop2010) %>% summarise(mean = mean(n)) %>% ungroup() %>% 
    ggplot() + 
    geom_point(aes(x = log(pop2010), y = mean), color = "light blue") + 
    geom_smooth(aes(x = log(pop2010), y = mean)) + 
  geom_text(aes(x = log(pop2010), y = mean, label = ifelse(mean > mean(mean)*1.75, member_state, "")), check_overlap = F, size = 2.5, hjust = 0) + theme_bw() +
  labs(title = "Senator Requests per Year by State Population",
       x = "Log State Population",
       y = "Average Number of Requests per Year")

```

```{r sentate_percapita_map}
Chamber = "Senate"

d %>% 
  filter(chamber == Chamber) %>% 
  group_by(state, Type) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank())# + facet_grid(. ~ Type)

d %>% 
  filter(chamber == Chamber) %>% 
  group_by(state, pop2010, Type) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(Per_Capita = n/pop2010*1000000) %>% 
  # map_id creates the aesthetic mapping to the state name column in your data
  ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Contacts Per Million Residents from Members of the", Chamber)) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) #+
  #facet_grid(. ~ Type)
```


---

### Members who contact FERC more than average: 

```{r members_barcoded, fig.height=4, fig.width=9}
# barcode plot of committee members 

Chamber <- "Senate" # "House" #  
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 


Chamber <- "House" # "House" #  
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 
```

### Members who contact FERC more, relative to other agencies: 
```{r ferc_vs_all_rate}
all_contacts %>%
  mutate(FERC = agency == "DOE_FERC") %>%
  group_by(chamber, FERC, name_state, state) %>%
  summarise(n = n() ) %>%
  ungroup() %>%
  spread(key = "FERC", value = "n") %>% 
  mutate(ShareToFERC = round(`TRUE`/(`TRUE`+`FALSE`),2) )%>% 
  arrange(-ShareToFERC) %>% 
  mutate(total = `TRUE` + `FALSE`) %>% 
  select(name_state, chamber, total, ShareToFERC) %>% 
  filter(ShareToFERC>.3) %>%
  knitr::kable()
```


### Members who contact FERC more in a Congress, relative to other agencies: 
```{r ferc_vs_all_rate_committees}
all_contacts %>%
  mutate(FERC = agency == "DOE_FERC") %>%
  group_by(congress, chamber, committees, FERC, name_state, state) %>%
  summarise(n = n() ) %>%
  ungroup() %>%
  spread(key = "FERC", value = "n") %>% 
  mutate(ShareToFERC = round(`TRUE`/(`TRUE`+`FALSE`),2) )%>% 
  arrange(-ShareToFERC) %>% 
  mutate(total = `TRUE` + `FALSE`) %>% 
  select(name_state, congress, chamber, committees, total, ShareToFERC) %>% 
  filter(ShareToFERC>.5) %>%
  knitr::kable()
```


## Interesting cases

In an article titled "Republican congressmen’s funding dwarfs challengers’", the Charleston Gazee-Mail noted how energy companies backed Representative Alex Mooney (R-WV). Indeed, Mooney wrote to FERC more than any other agency, always on behalf of energy projects, mostly pipelines. 
In 2017, he wrote on behalf of the 
Dominion Energy Supply Header Project,
National Fuel Gas Distribution Corporation's [Northern Access Project](https://www.natfuel.com/supply/NorthernAccess2016/default.aspx),
Transcontinental Gas Pipe Line Company's [Atlantic Sunrise Project](https://blog.williams.com/projects-and-operations/atlantic-sunrise/atlantic-sunrise-project-placed-into-full-service/), 
Columbia Gas Transmission's proposed Eastern Panhandle Expansion project,
Columbia's WB Xpress Project to build new compressor stations,
In 2015 he wrote on behalf of the
Columbia s Mountaineer XPress Project,
Atlantic Coast Pipeline ACP project. 
The parent companies of these projects spend millions of dollars on lobbying (Lobbyview). The WV Gazette reports funding from Dominion that is not included in Lobbyview totals. 


---

## Committee Chairs

```{r committeechiars_barcode_senate, fig.height=10}
Chamber = "Senate"
dcommittees %>%  
  mutate(position = ifelse(position == "Other", NA, position)) %>%
  filter(!str_detect(chair, "^NA ")) %>% 
  filter(!is.na(position)) %>% 
  filter(chamber == Chamber, 
         chair_since_2007 == T,  
         DATE < as.Date("2017-01-01"),
        DATE > as.Date("2007-01-01"),
        assigneddate < as.Date("2017-01-01"),
        terminationdate > as.Date("2007-01-01")) %>%
  select(DATE, chair, position, department, assigneddate, terminationdate, chamber, committee) %>% 
  distinct() %>% 
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = chair),
    shape = 73,
    size=2 
  ) +
  geom_segment(aes(y = chair, yend = chair, 
                   x = assigneddate, xend = terminationdate, 
                   linetype = factor(position)),
               position = position_nudge(y = -0.3)) +
  labs(title = paste(Chamber, "Committee Chairs who wrote to FERC"),
       y = "", 
       x = "" ) +
  scale_y_discrete(position = "right") +
  theme(
    strip.text.y = element_text(angle = 180, size = 5),
    legend.title = element_blank(),
    axis.text.y = element_text(size=5),
    axis.text.x = element_text(angle = 0)
  ) + 
  facet_grid(committee ~ ., scales = "free_y", space = "free_y", switch = "both") 
```

```{r committeechiars_barcode_house, fig.height=10, include= TRUE}
Chamber = "House"
dcommittees %>%  
  mutate(position = ifelse(position == "Other", NA, position)) %>% 
  filter(!str_detect(chair, "^NA ")) %>% 
  filter(!is.na(position)) %>% 
  filter(chamber == Chamber, 
         chair_since_2007 == T,  
         DATE < as.Date("2017-01-01"),
        DATE > as.Date("2007-01-01"),
        assigneddate < as.Date("2017-01-01"),
        terminationdate > as.Date("2007-01-01")) %>%
  select(DATE, chair, position, department, assigneddate, terminationdate, chamber, committee) %>% 
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = chair),
    shape = 73,
    size=2 
  ) +
  geom_segment(aes(y = chair, yend = chair, 
                   x = assigneddate, xend = terminationdate, 
                   linetype = factor(position)),
               position = position_nudge(y = -0.3)) +
  labs(title = paste(Chamber, "Committee Chairs who wrote to FERC"),
       y = "", 
       x = "" ) +
  scale_y_discrete(position = "right") +
  theme(
    strip.text.y = element_text(angle = 180, size = 5),
    legend.title = element_blank(),
    axis.text.y = element_text(size=5),
    axis.text.x = element_text(angle = 0)
  ) + 
  facet_grid(committee ~ ., scales = "free_y", space = "free_y", switch = "both") 
```  


## Many letters to FERC are cosigned

```{r cosigned_estimated, eval=FALSE}
#A rough under-estimate based on whether "et al" or "&" appears in the summary:

FERC_letters %>% 
  group_by(ID) %>% 
  top_n(1) %>% 
  mutate(probably_cosigned = ifelse(str_detect(SUBJECT, "et al"), "et al",
                                 ifelse(str_detect(SUBJECT, "&"), "&", " neither"))) %>%
  group_by(year, probably_cosigned) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = probably_cosigned) +
  geom_col() 
```

Identified cosigned letters of those coded so far:
```{r cosigned_coded, eval=FALSE}
FERC_letters %>% 
  filter(!is.na(Freelancer)) %>% 
  mutate(cosigned = ifelse(!is.na(Cosigned_House)|!is.na(Cosigned_Senate),
                                 T, F)) %>%
  group_by(year, cosigned) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = cosigned) +
  geom_col() 
```

---

# Companies 

## Top companies in pro-business letters
```{r probusiness-letters}
# Split out to one obs per member per letter per business
dcorps <- d %>%
  mutate(ProBusiness = ProBusiness %>% str_split(";")) %>%
  unnest(ProBusiness)

dcorps %<>% mutate(ProBusiness = ProBusiness %>%
                     str_replace("RTO", 
                                 "Regional Transmission Organization") %>%  
         str_remove_all(" Company.*| \\(.*| Inc.*| LLC.*| Energy.*") )%>%
  mutate(AntiBusiness = AntiBusiness %>% 
           str_replace("RTO", 
                       "Regional Transmission Organization") %>%  
         str_remove_all(" Company.*| \\(.*| Inc.*| LLC.*| Energy.*") )

dcorps %>%
  filter(!is.na(ProBusiness),
         !str_detect(ProBusiness, "Regional Transmission Organization") ) %>%
  group_by(ProBusiness) %>%
  select(id, last_name, ProBusiness, ID) %>%
  distinct() %>%
  summarise( n = n() , 
             members = str_c(unique(last_name), collapse = "; "),
             ID = str_c(unique(ID), collapse = "; ")) %>%
  filter(n>quantile(n,.9))%>%
  arrange(-n) %>%
  knitr::kable()
```


## Letters citing companies registered with FERC
Of the companies registered to interact with FERC, several appear in the letter texts. Here `company_short` is a shortened version a name that refrences several affiliated companies, each of which are registered separatly. 
*TO DO:* 
- (1) Identify linked corporations for other top companies in the data
- (2) extract company contact persons and information from the FERC website.
```{r}
load(here("data", "DOE_FERC-corps.Rdata"))
FERC_corps %<>% ungroup() %>% group_by(company_short) %>% mutate(industry = str_c(unique(industry), collapse = ";")) %>% select(-company, -Fortune500) %>% distinct() 

## Make a single string of short corp names
ferc_short <- unique(FERC_corps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

# bad string? 
# str_detect("", ferc_short)

save(ferc_short, file = here("data/ferc_short.Rdata"))
```


## Pro-business letters
```{r probusiness-letters-ferc}
dcorps %>%
  mutate(company_short = str_extract(ProBusiness, ferc_short)) %>%
  left_join(FERC_corps) %>% 
  distinct() %>%
  group_by(company_short_refs) %>%
  select(ID, last_name, company_short, company_short_refs) %>%
  filter(company_short != "")%>%
  distinct() %>%
  summarise( n = n() , 
             company_short = str_c(unique(company_short), collapse = "; "),
             members = str_c(unique(last_name), collapse = "; "),
             ID = str_c(unique(ID), collapse = "; ")) %>%
  filter(n>quantile(n,.9))%>%
  select(company_short, n, everything()) %>%
  arrange(-n) %>%
  knitr::kable()

## Longer list with company full names
# d %>%
#   mutate(company_short = str_extract(ProBusiness, ferc_short)) %>%
#   drop_na(company_short) %>%
#   mutate(members = paste(CongressPerson, Cosigned_House, Cosigned_Senate, sep = ";")) %>%
#   mutate(members = str_remove_all(members, ";NA")) %>%
#   group_by(company_short) %>%
#   mutate(members = str_c(unique(members), collapse = ";")) %>%
#   select(company_short, members) %>%  distinct() %>%
#   left_join(FERC_corps) %>% distinct() %>%
#   knitr::kable(caption = "Pro Businesses matching those registered with FERC")
```

## Anti-business letters

```{r antibusiness-letters-ferc}
dcorps %>%
  mutate(company_short = str_extract(AntiBusiness, ferc_short)) %>%
  left_join(FERC_corps) %>% 
  distinct() %>%
  group_by(company_short_refs) %>%
  select(ID, last_name, company_short, company_short_refs) %>%
  filter(company_short != "")%>%
  distinct() %>%
  summarise( n = n() , 
             company_short = str_c(unique(company_short), collapse = "; "),
             members = str_c(unique(last_name), collapse = "; "),
             ID = str_c(unique(ID), collapse = "; ")) %>%
  filter(n>quantile(n,.9))%>%
  select(company_short, n, everything()) %>%
  arrange(-n) %>%
  knitr::kable()

## Longer list with company full names
# d %>% 
#   mutate(company_short = str_extract(AntiBusiness, ferc_short)) %>% 
#   drop_na(company_short) %>% 
#   mutate(members = paste(CongressPerson, Cosigned_House, Cosigned_Senate, sep = ";")) %>%
#   mutate(members = str_remove_all(members, ";NA")) %>% 
#   group_by(company_short) %>% 
#   mutate(members = str_c(unique(members), collapse = ";")) %>% 
#   select(company_short, members) %>%  distinct() %>%
#   left_join(FERC_corps) %>% distinct() %>% 
#   knitr::kable(caption = "Anti Businesses matching those registered with FERC")

```


---

## Company lookup table

Clean companies names extracted from letters and create shortened name that is more likely to be found in other datasets (like done with FERC-registerd companies above).
```{r company-inspect}
# Split out to one obs per member per letter per business
dcorps <- d %>%
  select(ID, bioname, ProBusiness, AntiBusiness, ProProject, AntiProject) %>% 
  gather(value = "company", key = "position", -ID, -bioname) %>%
  mutate(company = company %>% str_split(";")) %>%
  unnest(company) %>% distinct()

dcorps %<>% mutate(company = company %>%
                     str_replace("RTO", 
                                 "Regional Transmission Organization") %>%  
         str_remove_all(" Company.*| \\(.*| Inc.*| LLC.*| Energy.*") )

dcorps$company %<>%
  trimws()  # trim white space before and after company names

dcorps %<>%   filter(nchar(company)>1) %>%# drop names less than 1 character
  distinct() # drop duplicates

## For matching, remove endings like ", Inc." etc. 
trim <- function(d){
d %>%
  str_remove_all("Village of |\\(.*|,.*| -.*|^Proposed | Pipe.*| pipe.*| project$| Proiects$| Company.*| Comnany| Corp.*| Co$| Co.$| Energy$| energy$| power$| Power marketing$| Holdings.*| Group$| Gas$| Project.*| LLC| L.L.C.|  L.P.|^The | Inc.| L.P.| Ltd.| LP| Limited Partnership| Limited Liability|  Facility| Transportation and Storage| Storage and Transportation") %>% 
  str_remove_all("^, ") %>%
  trimws()  # filter out names less than 2 characters 
}



dcorps$company_short <- trim(dcorps$company) %>% trim()
```

Problem company names that may need to be fixed (e.g. to remove special characters or spell out abbreviated name)
```{r problem-names}
# Problem Names
dcorps %>% filter(nchar(company_short)<2) %>% knitr::kable()

dcorps %<>% filter(nchar(company_short)>1)
```


Identify short names by hand: 
```{r, lookup-table}
## Correct over-trimmed names
dcorps %<>% 
  mutate(company_short = ifelse(company == "Columbia Energy Power Marketing Corporation", "Columbia Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Michigan Energy Exchange, LLC", "Michigan Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Midwest Energy, Inc.", "Midwest Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Northwest Pipeline LLC", "Northwest Pipeline", company_short))%>%
  mutate(company_short = ifelse( str_detect(company, "^Dominion"), 
                                 "Dominion", company_short))%>%
  mutate(company_short = ifelse(company == "Peak Energy, Inc.", "Peak Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Public Service Company of New Mexico", "Public Service Company of New Mexico", company_short))%>%
  mutate(company_short = ifelse(company == "Salt Lake Energy Systems, LLC", "Salt Lake Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Natural Gas Pipeline Company of America", "Natural Gas Pipeline Company of America", company_short))%>%
  mutate(company_short = ifelse(company == "Natural Gas Trading Corporation", "Natural Gas Trading Corporation", company_short))%>%
  mutate(company_short = ifelse(company == "Energy, USA-TPC Corp.", "TPC", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Partners, L.L.C.", "New Energy Partners", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Service, LLC", "New Energy Service", company_short))%>%
  mutate(company_short = ifelse(company == "North Energy Associates, A Limited Partnership", "North Energy Associates", company_short))%>%
  mutate(company_short = ifelse(company == "Pipeline Company LLC", "Pipeline Company LLC", company_short))%>%
  mutate(company_short = ifelse(company == "Express Pipeline LLC", "Express Pipeline LLC", company_short))%>%
  mutate(company_short = ifelse(company == "American Energy Savings, Inc.", "American Energy Savings", company_short))%>%
  mutate(company_short = ifelse(company == "Electric Energy, Inc.", "Electric Energy, Inc.", company_short))%>%
  mutate(company_short = ifelse(company == "System Energy Resources, Inc., Llano Estacado Wind, LLC, System Energy Resources, Inc., Northern Iowa Windpower, LLC, and RS Cogen, L.L.C.", "System Energy Resources", company_short))%>%
  mutate(company_short = ifelse(company == "Public Service Company of Colorado", "Public Service Company of Colorado", company_short))%>%
  mutate(company_short = ifelse(company == "Southern Company Services, Inc.", "Southern Company", company_short))%>%
  mutate(company_short = ifelse(company == "International Energy Consultants", "International Energy Consultants", company_short))%>%
  mutate(company_short = ifelse(company == "Jackson Pipeline Company", "Jackson Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Southern Energy California", "Southern Energy California", company_short))%>%
  mutate(company_short = ifelse(company == "Tennessee Gas Pipeline Company, L.L.C.", "Tennessee Gas Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Select Energy New York, Inc.", "Select Energy New York", company_short))%>%
  mutate(company_short = ifelse(company == "Inland Corporation", "Inland Corporation", company_short))%>%
  mutate(company_short = ifelse(company == "Advanced Energy Systems, Inc.", "Advanced Energy Systems", company_short))%>%
  mutate(company_short = ifelse(company == "Consumers Energy Company", "Consumers Energy Company", company_short))%>%
  mutate(company_short = ifelse(company == "Boston Energy Trading and Marketing LLC", "Boston Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Complete Energy Services, Inc.", "Complete Energy Services", company_short))%>%
  mutate(company_short = ifelse(company == "El Paso Energy Intrastate, L.P.", "El Paso Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Houston Pipe Line Company LP", "Houston Pipe Line", company_short))%>%
  mutate(company_short = ifelse(company == "North American Energy, Inc.", "North American Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Spokane Energy, LLC", "Spokane Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Salem Energy Systems, LLC", "Salem Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "Direct", "Direct Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "DC", "DC Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "PS", "PS Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Coastal", "Coastal Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "CT", "CT Corporation", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Forest", "Forest Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Minnesota", "Minnesota Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "NW", "NW Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Rio Grande", "Rio Grande Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Plains", "Plains Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Portland", "Portland Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "AP", "AP Holdings", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Boundary", "Boundary Gas", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Columbia", "Columbia Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Independence", "Independence Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Lakeside", "Lakeside Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Mitchell", "Mitchell Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Stream", "Stream Energy", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "^Northwest Pipeline"), "Northwest Pipeline", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "^Tennessee Gas"), "Tennessee Gas", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "Juniper Hills Country Club"), "Juniper Hills Country Club", company_short))%>%
    mutate(company_short = ifelse(str_detect(company, regex("Columbia Gas", ignore_case = T)), "Columbia Gas", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, regex("Algonquin", ignore_case = T)), "Algonquin", company_short))%>%
    mutate(company_short = ifelse(str_detect(company, regex("Spectra", ignore_case = T)), "Spectra", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, regex("Jordan Cove", ignore_case = T)), "Jordan Cove", company_short))%>%
    mutate(company_short = ifelse(str_detect(company, regex("Enron", ignore_case = T)), "Enron", company_short))%>%
     mutate(company_short = ifelse(str_detect(company, regex("Nexus", ignore_case = T)), "Nexus", company_short))%>%

  mutate(company_short = ifelse(company == "Express Pipeline", "Express Pipeline", company_short))%>%
  mutate(company_short = ifelse(company %in% c("American Energy", "American energy"), "American Energy", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "PG&E|Pacific Gas & Electric|Pacific Gas and Electric"), "PG&E", company_short)) %>% 
  mutate(company_short = ifelse(company %in% c("Pacific Corp.", "Pacific Corps"), "PacifiCorp", company_short)) %>% 
  mutate(company_short = ifelse(company_short == "AI", "AI Energy", company_short)) %>% 
  mutate(company_short = ifelse(company_short %in% c("N/A","Na","NO",
                                                     "Clean Water Act","Na",
                                                     "Energy", "West", "NA",
                                                     "Central", "Power", "Natural",
                                                     "Consumers", "LNG"),
         "NOT A COMPANY?",  company_short))
```

Short company names, e.g. "Duke" may refer to many affiliated companies. The variable `company_short_refs` lists these affiliated companies. 
```{r}
#FIXME
# ADD company_short_refs 
dcorps %<>% 
  group_by(company_short) %>% 
  mutate(company_short_refs = str_c(unique(company), collapse = "; ")) %>% ungroup()
```

Look for problematic company names. For example what should we do with companies that are just state, region, or city names? (e.g. El Paso Corporation, Tennessee Gas, American Energy, Southern, etc.) 
```{r}
## Inspect over-trimmed company names
dcorps %>% filter(company_short %in% c("", "NA", "na", "Na", "LLC", "Energy", "Pipeline", "Natural", "North", "New", "Express", "gas", "American", "Electric", "System", "Direct", "DC", "PS", "CT", "Forest", "International", "Tennessee", "Salt Lake", "Lakeside", "NW", "Jackson", "Public Service", "Peak", "Independence", "Select", "Portland", "Michigan", "Boundary", "Coastal", "Minnesota", "Midwest", "Northeast", "Columbia", "Plains", "Stream", "Mitchell", "AP", "Southern", "Ohio River", "Northwest", "Rio Grande", "AI", "Transportation", "12/20/2018", "Salem", "Boston", "Spokane", "El Paso", "Houston", "North American", "Consumers", "Advanced", "Complete", "Inland", "Limited Partnership", "Sun", "RTO", "Pacific", "LNG")) %>% select(company_short, company_short_refs, ID) %>% 
  group_by(company_short) %>%
  summarise(company_short_refs = str_c(unique(company_short_refs), collapse = "; "),
            IDs = str_c(unique(ID), collapse = "; ")) %>%
  distinct() %>% knitr::kable()

##  did I acidentally delete everything before a comma? 
# dcorps %>% filter(str_detect(company_short, ","))
```

## Top 10 cited parent companies pro or con
```{r top-corps}
# top corps
topcorps <- dcorps %>% group_by(company_short) %>% tally() %>% arrange(-n) %>% top_n(10)

filter(dcorps, company_short %in% topcorps$company_short) %>%   
  group_by(company_short) %>%
  summarise(#IDs = str_c(unique(ID), collapse = "; ")
    company_short_refs = str_c(unique(company_short_refs), collapse = "; ") ) %>%
  distinct() %>% knitr::kable() 

# corps with short names 
shortcorps <- dcorps %>% 
  ungroup() %>% 
  group_by(company_short) %>% 
  tally() %>% 
  arrange(nchar(company_short)) %>% 
  mutate(nchar = nchar(company_short))%>%
  top_n(10, -nchar) %>% distinct()

filter(dcorps, company_short %in% shortcorps$company_short) %>% 
  group_by(company_short) %>%
  summarise(company_short_refs = str_c(unique(company_short_refs), collapse = "; "),
            IDs = str_c(unique(ID), collapse = "; ")) %>%
  distinct() %>% knitr::kable()

#dcorps %>% filter(!position %in% c("ProProject", "AntiProject")) %>%  group_by(company_short) %>% tally() %>% arrange(-nchar(company_short))  %>% top_n(20) %>% knitr::kable()
```


[This sheet](https://docs.google.com/spreadsheets/d/1-QNgeiMnH97jN_0vCqFKEGEB5Ztpito3iRsqK8jN3Cs/edit#gid=0) tracks non-companies in our data.
```{r, eval=TRUE}
library(googlesheets)
library(httpuv)

# log in to google drive
gs_auth() 

notcorps <- gs_title("not_companies") %>% gs_read() 


dcorps %<>% ungroup() %>% 
  mutate(company_short = ifelse(company_short %in% notcorps$not_companies,
                                "NOT A COMPANY?", company_short) )
         
#FIXME
# ADD company_short_refs again after corrections
dcorps %<>% 
  group_by(company_short) %>% 
  mutate(company_short_refs = str_c(unique(company), collapse = "; ")) %>% ungroup()

dcorps %>% 
  filter(position %in% c("ProProject", "ProBusiness")) %>% 
  select(ID, company_short, company)%>% 
  group_by(company_short) %>% 
  distinct() %>%
  add_count() %>% 
  arrange(-n) %>% 
  #write_csv(path = here("FERC/ProBusinesses.csv"))
  head()

# sum(is.na(unique(dcorps$company_short)))

## Make a single string of short corp names
dcorp_short <- unique(dcorps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

# bad string? 
# str_detect("", dcorp_short)


save(dcorp_short, file = here("data/dcorp_short.Rdata"))
save(dcorps, file = here("data/dcorps.Rdata"))

notcorps <- filter(dcorps, company_short == "NOT A COMPANY?")
# notcorps$company


```

Drop non-company observations
```{r}
sum(!is.na(d$ProBusiness))
d %<>% mutate(ProBusiness = ifelse(ProBusiness %in% notcorps$company, NA, ProBusiness)) %>% 
  mutate(ProProject = ifelse(ProProject %in% notcorps$company, NA, ProProject))
  
sum(!is.na(d$ProBusiness))
```

---

# PAC Contributions from the Energy Sector
Using CRP industry codes for PACs and DIME contribution matrix, sum up sector-level contributions by memeber per cycle, matching a congress with the cycle when it was elected (e.g. 116th congress = 2018 cycle). 

```{r letters_money}
load(here("data/contrib_total.rds"))
contrib_total %<>% 
  rename(icpsryear = ICPSR,
         PAC_contributions = value) %>% 
  mutate(cycle = str_sub(icpsryear, -4),
         icpsr = as.numeric(str_remove(icpsryear, cycle)),
         cycle = as.numeric(cycle)) %>% 
  filter(cycle > 1990) %>% 
  left_join(d %>% select(icpsr, name_state, party) %>% distinct())

d %<>% 
  # rounding years up is approximate, rewrite to go Nov-Nov?
  mutate(cycle = congress*2+1786 ) %>% 
  mutate(icpsryear = str_c(icpsr, cycle)) 

letters_money <- d %>% 
  #FIXME
  filter(cycle <2016) %>% 
  filter(!is.na(ProBusiness)|!is.na(ProProject))%>% 
  #filter(Type %in% c("Corp. Constituent", "Policy")) %>% 
  group_by(icpsryear, cycle, name_state, party, congress, icpsr) %>%
  summarise(ProBusiness_Letters = n())

# join letters and DIME data by ICPSR, adding a sum of sector PAC contributions per member
letters_money %<>% 
  ungroup() %>% 
  full_join(contrib_total) %>% 
  group_by(icpsr) %>% 
  # FIXME
  # one party per member, need to deal with party switchers
  mutate(party = paste(unique(party), collapse = ";")) %>% 
  mutate(party = str_remove(party, ";.*")) %>% 
  ungroup()

# top 10 by contributions in a cycle 
letters_money %>% 
  filter(!is.na(ProBusiness_Letters)) %>% 
  select(-icpsryear, -icpsr, -congress) %>% 
  top_n(10, PAC_contributions) %>% knitr::kable()
```

Add zero-letter-cycle observations:
```{r add-zeros}
letters_money %<>% 
 mutate(ProBusiness_Letters = ifelse(is.na(ProBusiness_Letters) & cycle > 1997, 0, ProBusiness_Letters)) 
```

## Overall top ten PAC recepients.

Fred Upton (R-Mich.) was chair of the House Energy and Commerce Committee 2011-2017.

U.S. Senator Mary L. Landrieu was Chair of the Senate Committee on Energy and Natural Resources 2014-2015.

```{r letters_money_total}
letters_money_total <- letters_money %>% 
  filter(!is.na(PAC_contributions)) %>% 
  group_by(icpsr, name_state, party) %>% 
  summarise(ProBusiness_Letters_Per_Cycle = mean(ProBusiness_Letters, na.rm = TRUE),
            PAC_contributions = sum(PAC_contributions, na.rm = TRUE)) %>% 
  ungroup()

# add zeros 
letters_money_total %<>% 
 mutate(ProBusiness_Letters_Per_Cycle = ifelse(is.na(ProBusiness_Letters_Per_Cycle), 0, ProBusiness_Letters_Per_Cycle)) 

letters_money_total %>% filter(!is.na(name_state)) %>%  top_n(10, PAC_contributions) %>% knitr::kable()
```

```{r antibusiness}
Antiletters_money <- d %>% 
  #FIXME
  filter(cycle <2016) %>% 
  filter(!is.na(AntiBusiness)|!is.na(AntiProject))%>% 
  #filter(Type %in% c("Corp. Constituent", "Policy")) %>% 
  group_by(icpsryear, cycle, name_state, party, congress, icpsr) %>%
  summarise(AntiBusiness_Letters = n())

# join letters and DIME data by ICPSR, adding a sum of sector PAC contributions per member
Antiletters_money %<>% 
  ungroup() %>% 
  full_join(contrib_total) %>% 
  group_by(icpsr) %>% 
  # FIXME
  # one party per member, need to deal with party switchers
  mutate(party = paste(unique(party), collapse = ";")) %>% 
  mutate(party = str_remove(party, ";.*")) %>% 
  ungroup()

# Add zero-letter-cycle observations:
Antiletters_money %<>% 
 mutate(AntiBusiness_Letters = ifelse(is.na(AntiBusiness_Letters) & cycle > 1997, 0, AntiBusiness_Letters)) 

Antiletters_money_total <- Antiletters_money %>% 
  filter(!is.na(PAC_contributions)) %>% 
  group_by(icpsr, name_state, party) %>% 
  summarise(AntiBusiness_Letters_Per_Cycle = mean(AntiBusiness_Letters, na.rm = TRUE),
            PAC_contributions = sum(PAC_contributions, na.rm = TRUE)) %>% 
  ungroup()
```

## PAC-specific contributions
```{r letters_PACs-data}
load(here("data/contrib_matrix.rds"))
contrib_matrix %<>% 
  rename(icpsryear = ICPSR,
         PAC_contributions = value) %>% 
  mutate(cycle = str_sub(icpsryear, -4),
         icpsr = as.numeric(str_remove(icpsryear, cycle)),
         cycle = as.numeric(cycle)) %>% 
  filter(cycle > 1990)%>% 
  left_join(d %>% select(icpsr, name_state, party) %>% distinct())
```

We identify `r length(unique(contrib_matrix$comid))` PACs in the energy sector (oil, gas, and electricity) and match their PAC contributions to each member of congress. 

For example:

### The top PAC recipient in a single cycle
```{r letters_PACs}
letters_PACs <- d %>% 
  #FIXME
  filter(cycle <2016) %>% 
  filter(!is.na(ProBusiness)|!is.na(ProProject))%>% 
  group_by(icpsryear, cycle, name_state, party) %>%
  summarise(ProBusiness_Letters = n()) %>% 
  # join by ICPSR, adding a sum of sector PAC contributions per member
  left_join(contrib_matrix) %>% 
  ungroup() %>% group_by(icpsr) %>% 
  mutate(party = paste(unique(party), collapse = ";")) %>% 
  mutate(party = str_remove(party, ";.*")) %>% 
  ungroup()

letters_PACs_cycle <- letters_PACs %>% 
  group_by(cycle, icpsr, name_state, party) %>%
  # delete PACs that did not give from list, but keep members that recieved no contributions
  mutate(PACShort = ifelse(PAC_contributions > 0, PACShort, NA)) %>% 
  summarise(PAC_contributions = sum(PAC_contributions),
            PACs = paste(unique(PACShort), collapse = ";")) %>% 
  ungroup() %>% 
  arrange(-PAC_contributions)

letters_PACs_cycle %>% top_n(1, PAC_contributions) %>% knitr::kable()
```

### The top PAC recipient overall 
```{r letters_PACs-total}
letters_PACs_total <- letters_PACs %>% 
  ungroup() %>% 
  group_by(icpsr, name_state) %>% 
  summarise(PAC_contributions = sum(PAC_contributions),
            PACs = str_c(unique(PACShort), collapse = ";")) %>% 
  filter(!is.na(name_state)) %>% 
  ungroup()

letters_PACs_total %>% top_n(1, PAC_contributions) %>% knitr::kable()
```


### Pro-business letters per cycle
```{r, letter_money}
top1 <- top_n(letters_money_total %>% filter(!is.na(name_state)), 5, PAC_contributions) %>% .$name_state
top2 <- top_n(letters_money_total, 5, ProBusiness_Letters_Per_Cycle) %>% .$name_state

letters_money_total %>% 
  ggplot() + 
  aes(x = PAC_contributions, 
      y = ProBusiness_Letters_Per_Cycle) + 
  geom_point(alpha = .5) + 
  geom_text(aes(label = ifelse(name_state %in% top2,
                               name_state, NA)), check_overlap = TRUE, hjust = 0, color = "blue") + 
  
  labs(x = "PAC Contributions 1990-2014",
       y = "Average Pro-Business Letters sent to FERC per Cycle")

letters_money_total %>% 
  ggplot() + 
  coord_flip() + 
  aes(x = PAC_contributions, 
      y = ProBusiness_Letters_Per_Cycle) + 
  geom_point(alpha = .5) + 
  geom_text(aes(label = ifelse(name_state %in% top1,
                               name_state, NA)), check_overlap = TRUE, hjust = 0, color = "blue") + 
  
  labs(x = "PAC Contributions 1990-2014",
       y = "Average Pro-Business Letters sent to FERC per Cycle")
  
```

# Models

## Sector-level

#### Pro-Business Letters per cycle ~ Energy Sector PAC contributions per cycle 1998-2014
```{r money-letters-per-cycle-model, fig.height=1}
mplot <- function(m){m %>%
  tidy(conf.int = TRUE) %>%
    filter(term!="(Intercept)") %>%
ggplot() + 
  aes(x = term,
      y = estimate, 
      ymin = conf.low, 
      ymax = conf.high)+ 
    geom_hline(yintercept = 0, linetype =2) + 
  geom_pointrange() + coord_flip() }

letters_money%<>% drop_na(ProBusiness_Letters, PAC_contributions) %>% mutate(Log_PAC_contributions = log(PAC_contributions+1)) 

m <- glm(ProBusiness_Letters ~ PAC_contributions, data = letters_money %>% mutate(PAC_contributions = PAC_contributions/1000000), family = poisson)  
tidy(m)
m %>% mplot()+
  labs(x="", y="Additional letters per congress per million dollars")

m <- glm(ProBusiness_Letters ~ Log_PAC_contributions, data = letters_money, family = poisson  ) 
tidy(m)
m %>% mplot()+
  labs(x="", y="Additional letters per congress per Log(PAC Contributions)")
```

By party:
```{r letters-per-cycle-model-party, fig.height=1}
m <- glm(ProBusiness_Letters ~ party, data = letters_money %>% filter(party !="NA"), family = "poisson" ) 

tidy(m)
mplot(m) +
  labs(x="", y="Additional letters per congress")
```
Republicans send an additional `r round(m$coefficients[2], 1)` letters per Congress, on average.




```{r money-letters-per-cycle-model-party, fig.height=1, include = FALSE }
# PAC*party interaction:
  m<-glm(ProBusiness_Letters ~ PAC_contributions * party, data = letters_money %>% filter(party !="NA")%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  
tidy(m)
mplot(m)+
  labs(x="", y="Additional letters per congress")
```



#### Average Pro-Business letters per cycle ~ total Energy Sector PAC contributions 1990-2014
```{r money-letters-total, fig.height=1}
m <- glm(ProBusiness_Letters_Per_Cycle ~ PAC_contributions, data = letters_money_total%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson")  

tidy(m)
mplot(m)+
  labs(x="", y="Average additional letters per cycle per million dollars 1990-2014")
```

#### Anti-Business Letters per cycle ~ Energy Sector PAC contributions per cycle 1998-2014
```{r money-Antiletters-per-cycle-model, fig.height=1}
Antiletters_money%<>% drop_na(AntiBusiness_Letters, PAC_contributions) %>% mutate(Log_PAC_contributions = log(PAC_contributions+1)) 

m <- glm(AntiBusiness_Letters ~ PAC_contributions, data = Antiletters_money %>% mutate(PAC_contributions = PAC_contributions/1000000), family = poisson)  
tidy(m)
m %>% mplot()+
  labs(x="", y="Additional anti-buisness letters per congress per million dollars")

m <- glm(AntiBusiness_Letters ~ Log_PAC_contributions, data = Antiletters_money, family = poisson  ) 
tidy(m)
m %>% mplot()+
  labs(x="", y="Additional anti-business Letters per congress per Log(PAC Contributions)")
```

By party:
```{r Antiletters-per-cycle-model-party, fig.height=1}
m <- glm(AntiBusiness_Letters ~ party, data = Antiletters_money %>% filter(party !="NA"), family = "poisson" ) 

tidy(m)
mplot(m) +
  labs(x="", y="Additional anti-business  letters per congress")
```
Democrats send an additional `r -round(m$coefficients[2], 1)` Anti-Business letters per Congress, on average.




```{r money-Antiletters-per-cycle-model-party, fig.height=1, include=FALSE}
#PAC*party interaction:
m<-glm(AntiBusiness_Letters ~ PAC_contributions*party, data = Antiletters_money %>% filter(party !="NA")%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  
tidy(m)
mplot(m)+
  labs(x="", y="Additional anti-business letters per congress")
```



#### Average Anti-Business letters per cycle ~ total Energy Sector PAC contributions 1990-2014
```{r money-Antiletters-total, fig.height=1}
m <- glm(AntiBusiness_Letters_Per_Cycle ~ PAC_contributions, data = Antiletters_money_total%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson")  

tidy(m)
mplot(m)+
  labs(x="", y="Average additional anti-business letters per cycle per million dollars 1990-2014")
```

## PAC-level

### Before matching projects and companies to their parent companies: 
```{r pacs-corps}
# letter count per pac ~ pac contributions (lots of 0$-0letter pairs )
# 1. id pacs per letter - spit letters matching several pacs 
# 2. count up per member 
# 3. add 0s for all other pac-member-cycle compinations 
# merge in with contributions per pac per member 

# First, clean up the contributions data a bit

# a helper function to concat unique strings
unique_string <- . %>% 
  str_split(";") %>% 
  # select unique ones
  unlist() %>% 
  unique() %>% 
  trimws() %>% 
  # paste them back together to retrun a single value 
  paste(collapse = ";") %>%
  str_remove_all("na;|;na$|NA;|;NA$")

# Just the PAC names and IDs from the contributions matrix (will merge in relevent contributions later)
PACs <- contrib_matrix %>% 
  select(comid, UltOrg,Affiliate,PACShort) %>% distinct() %>% 
  # make a full list of pac-affiliated orgs
  group_by(comid) %>%
  mutate(UltOrg2 = str_c(UltOrg,Affiliate,PACShort, sep = ";") %>% 
           tolower() %>% 
           # select unique ones
           unique_string())

# A function to get matching names
get_pac <- function(corp, PAC){
  ifelse(str_detect(tolower(PAC), tolower(corp)), PAC, NA) 
}

# A function to get IDs where names match 
get_pacID <- function(corp, PAC, PACid){
  ifelse(str_detect(tolower(PAC), tolower(corp)), PACid, NA) 
}


# corp = "Exxon"

# A function to augment the PAC data with any matching company names 
get_pacs <- function(corp){
PACs %>% 
    mutate(pacs = get_pac(tolower(corp), UltOrg2),
           pacIDs = get_pacID(tolower(corp), UltOrg2, comid)) %>% 
    ungroup() %>% 
    select(pacs, pacIDs) %>% 
    distinct() %>% 
    summarise_all(unique_string) %>% 
    mutate(company_short = corp)
}

# TESTING 
# corp = "Exxon"
# get_pacs(corp)
# corp <- dcorps$company_short[1]
# get_pacs(corp)

crosswalk <- map_dfr(dcorps$company_short, get_pacs)

crosswalk %<>% distinct()

# use crosswalk to merge in contribution data 
dpacs <- dcorps %>% 
  full_join(crosswalk) %>% 
  # letters per year per pac
  select(ID, position, company_short, position, pacs, pacIDs) %>% 
  distinct() %>% 
  mutate(pacIDs = str_split(pacIDs, ";")) %>% 
  unnest(pacIDs) %>% 
  distinct() %>% 
  # merge in pac totals
  rename(comid = pacIDs) %>% 
  # merge in contribution data
  left_join(contrib_matrix) # %>% group_by(comid, position) %>% summarise(PAC_contributions)

dpacs %<>% 
  ungroup() %>% 
  filter(!is.na(ID), !is.na(comid)) %>% 
  select(ID, icpsryear, cycle, name_state, position, company_short, pacs, comid, PAC_contributions) %>% 
  distinct()
```

#### Pro-business letters linked to PAC contributions:
```{r pro-pacs}
dpacs %>% 
  filter(position %in% c("ProBusiness", "ProProject")) %>% 
  # select letters with an identified person
  drop_na(name_state, ID) %>%
  group_by(name_state, cycle, position, company_short, pacs, comid) %>% 
  distinct()%>%  summarise(PAC_contributions = sum(PAC_contributions, na.rm = T),
                           # FIXME 
                           # SHOULD NOT NEED UNIQUE HERE 
            Letter_IDs = paste(unique(ID), collapse = ";")) %>% 
  ungroup() %>% 
  group_by(position)  %>%
  top_n(10, PAC_contributions) %>% 
  knitr::kable()
```

#### Anti-business letters linked to PAC contributions:
```{r anti-pacs}
dpacs %>% 
  filter(position %in% c("AntiBusiness", "AntiProject")) %>% 
  # select letters with an identified person
  drop_na(name_state, ID) %>%
  group_by(name_state, cycle, position, company_short, pacs, comid) %>% 
  distinct()%>%  summarise(PAC_contributions = sum(PAC_contributions, na.rm = T),
                           # FIXME 
                           # SHOULD NOT NEED UNIQUE HERE 
            Letter_IDs = paste(unique(ID), collapse = ";")) %>% 
  ungroup() %>% 
  group_by(position)  %>%
  top_n(10, PAC_contributions) %>% 
  knitr::kable()

#Before connecting companies to the PAC donations of their parent companies, we find `r sum(!is.na(dpacs$ID))` letters with a pack donation.
```
 



```{}
################################################   
# merge in and split out parent corps 

# TABLE 
letterID 
date
member
district 
committee 
position 
company
pac 
ammount 


# risiduals 
```




# About FERC 

FERC regulates electricity markets, oil and gas pipelines, and hydropower and gas export terminal projects. 

FERC controls pipeline market entry. 


## Letters on behalf of projects in their districts
TODO

## Letters are on behalf of donors
TODO

## Comparing FERC to other agencies
TODO 


# TO DO 
- Fix Goode, who is being double counted as an R and I
- add company names from company scraper to google sheet
- template to match company names to donation (lobbyview, DIME)
- template match company names to industry codes (center for responsive politics)

## SHORT TERM
- letters per company 
- letters per company pac (before and after merging in partent companies)

## LONG TERM 

## DONE
- add clean text from scraper to google sheet 
- fix clean function to pull and combine new data
- link industry codes to CRP PAC committee classification 
 1. Identify relevent industry codes 
 2. Get cycle-specific PAC classification for those industry codes 
 3. Subset dime to those PAC classification 

# References 

<!--
![Sources of Bureaucratic Delay: A Case Study of FERC Dam Relicensing](https://academic.oup.com/jleo/article/22/1/258/938707)
-->

```{r, include = FALSE, eval = FALSE}
source(here("setup.R"))

# Load corrected members from voteview to identify members with zero letters
members2 <- full_join(members, members_106to109th) %>%
  select(congress, icpsr) %>% distinct() %>% 
  filter(congress >106) %>% 
  mutate(cycle = congress*2+1786 ) %>% 
  mutate(icpsryear = str_c(icpsr, cycle)) 

letters_money %<>% 
  full_join(members2)
```