---
title: "Lobbying the U.S. Federal Energy Regulatory Commission (FERC)"
output:
  #pdf_document
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, eval = FALSE}
# Rscript -e 'library(rmarkdown); rmarkdown::render("gh-pages/summary.Rmd", "html_document")'

requires <- c("tidyr", "broom", "knitr","ineq", "dplyr", "ggplot2", "magrittr", "stargazer", "maps", "fiftystater", "mapproj", "dotwhisker", "here")
  to_install <- c(requires %in% rownames(installed.packages()) == FALSE)
  install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )
  devtools::install_github("wmurphyrd/fiftystater")
```

```{r}
  library(tidyverse)
  library(ineq)
  library(ggplot2); theme_set(theme_bw())
  library(magrittr)
  library(maps)
  library(fiftystater)
  library(mapproj)
  library(knitr)
  library(broom)
  library(dotwhisker)
  library(here)
  library(dplyr)
```

```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='Figs/',
                      warning=FALSE, 
                      message=FALSE)
```

# Data
```{r data}
load(here("data/all_contacts.RData"))
# one obs per member per letter for all agencies
d <- all_contacts %>% 
  ungroup() %>% 
  # define d as just FERC
  filter(agency=="DOE_FERC") %>% 
  select(-SUBJECT) %>% 
  mutate(majority = ifelse(majority == 1, "Majority", "Minority")) %>%
  # FIXME 
  # GOODE needs to be fixed in party switchers portion of merge.R
  filter(!(last_name == "GOODE"&party == "(I)"))
  

# one obs per member per letter per committee for all agencies
load(here("data/all_contacts_committees.RData"))
# define dcommittees as just FERC
dcommittees <- all_contacts_committees %<>% filter(agency == "DOE_FERC")

# Coded letters, one obs per member per letter 
load(here("data/DOE_FERC-letters-coded.RData")) 
# TO DO: replace with DOE_FERC-letters-corps.Rdata when corps added
FERC_letters %<>% 
  select(ID, SUBJECT, 
         Freelancer, Cosigned_House, Cosigned_Senate,
         text_clean, Constituent, year,
         Place_State, Place_District, Place_District, 
         ProBusiness, AntiBusiness, ProProject, AntiProject) %>% 
  distinct()

# merge in coded letters
d %<>% left_join(FERC_letters) %>% filter(year <2019)

# Add hand-coding to auto-coding of letter type 
d %<>%  
  mutate(Type = as.character(Type)) %>% 
  mutate(Type = ifelse(tolower(Constituent) == "yes", "Indiv. Constituent", Type)) %>% 
  mutate(Type = ifelse(!is.na(ProBusiness)|!is.na(ProProject), "Corp. Constituent", Type))%>%
  # define Constituent as "Indiv. Constituent"
  mutate(Constituent = ifelse(Type == "Indiv. Constituent", "Indiv. Constituent", "Non_constituent"),
         Constituent = replace_na(Constituent, "Not coded") ) 
  

# For this analysis, treat corp policy letters as Policy
all_contacts$Type %<>% fct_recode(Policy = "Corp. Policy")
d$Type %<>% fct_recode(Policy = "Corp. Policy")

# make a variable for the pro or anti business position of each letter
d %<>% 
  mutate(letter_position = ifelse(!is.na(ProBusiness)|!is.na(ProProject), "ProBusiness", "Other"),
         letter_position = ifelse(!is.na(AntiBusiness)|!is.na(AntiProject), "AntiBusiness", letter_position),
         letter_position = ifelse(!is.na(AntiBusiness)&!is.na(ProBusiness), "Both", letter_position)) 

d %<>% 
  # FIXME
  # rounding years up is approximate, rewrite to go Nov-Nov?
  mutate(cycle = congress*2+1786 ) %>% 
  mutate(icpsryear = str_c(icpsr, cycle)) 
```

In all, we have `r nrow(distinct(FERC_letters %>% select(ID)))` letters received by FERC and marked "congressional" since 1990. Most, but not all of these are from Members of the U.S. Congress. For this paper, we focus on `r nrow(distinct(FERC_letters %>% filter(year >1999) %>% select(ID) ) )` letters from `r min(d$year)`-`r max(d$year)`. 

Of the `r nrow(distinct(FERC_letters %>% filter(year >1999) %>% select(ID) ) )` letters from `r min(d$year)`-`r max(d$year)`, we identified Members of Congress in `r length(unique(d$ID))`. Because many are cosigned, this yeild `r nrow(d)` instances of a member writing to FERC.

---

## By party 


```{r part-constituent, fig.height=3, fig.width=4}
d %>% 
  mutate(For = Constituent,
         For = ifelse(letter_position == "ProBusiness", "Pro-Business", For),
         For = ifelse(For == "Non_constituent", "Other", For)) %>% 
  count(party_name, For, majority) %>% 
  filter(party_name != "Independent",
         !is.na(For),
         For != "Not coded",
         For != "Other",
         !is.na(majority)) %>% 
  group_by(party_name, majority) %>% 
  mutate(percent = n / sum(n) * 100 ) %>% 
  ggplot() + 
  aes(y = percent, x = "", fill = For) + 
  geom_col(position = "dodge") + 
  #geom_text(aes(label = n)) +
  facet_grid(majority ~ party_name) + 
  scale_fill_viridis_d(option = "C", end = .8) + 
    labs(x = "",
       fill = "Advocating for",
       y = "Percent") + 
  theme_minimal() + 
  theme(panel.grid.major.x  = element_blank())
```

Looking at letters that are explicitly pro- or anti- business, Democrats write more Anti-business letters, whereas, for Republicans, it depends on chamber control. Whe in the majority, Republicans write more pro-business letters. 
```{r part-business, fig.height=3, fig.width=4}
d %>% 
  count(party_name, letter_position, majority) %>% 
    filter(party_name != "Independent",
           letter_position != "Other",
         !is.na(letter_position),
         !is.na(majority)) %>% 
  group_by(party_name, majority) %>% 
  mutate(percent = n / sum(n) * 100 ) %>% 
  ggplot() + 
  aes(y = percent, x = "", fill = letter_position) + 
  geom_col(position = "dodge") + 
  facet_grid(majority ~ party_name)+ 
  scale_fill_viridis_d(option = "C", end = .8) + 
  labs(x = "",
       fill = "",
       y = "Percent") + 
  theme_minimal() + 
  theme(panel.grid.major.x  = element_blank())
```

---

## Coding of constituent type 
Our coding of letter type is a mix of hand coding "Pro-business" and "Constituent" letters, as well as some coding rules applied to letters that were not put in either group by human coders (click `CODE` to see inductively-developed coding rules):
```{r code, eval=FALSE}
# TYPE 1: Indiv. constituent service 
# TYPE 2: Corp. contituent service 
# TYPE 3: 501c3 constituent service 
# TYPE 4: Corp./Industry serving policy 
# TYPE 5: General policy 
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CONSTITUENT", SUBJECT, ignore.case = TRUE), 
                        "1", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CONSTITUENT", SUBJECT, ignore.case = TRUE), 
                             "2", CERTAINTY)) %>%
  ## Corporate service?
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), 
                        "2", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), 
                             "3", CERTAINTY)) %>%
  ## or policy
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("ROCKIES EXPRESS PIPELINE|ELECTRIC GENERATOR PROJECT", SUBJECT, ignore.case = TRUE), 
                            "5", ALT_TYPE)) %>%
  ## Policy work
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", SUBJECT, ignore.case = TRUE), 
                        "5", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("COMMENTS OF US SENATOR|REQUEST INFORMATION|SENATOR.*COMMENTS|HEARING|MEETING|US SENATE SUBMITS|OVERSIGHT OF THE|EXPRESSING CONCERNS|SENATE SUBMITS COMMENTS", SUBJECT, ignore.case = TRUE), 
                             "1", CERTAINTY)) %>%
  ## Local government
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", SUBJECT, ignore.case = TRUE), 
                        "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("CITY OF.*APPLICATION|APPLICATION.*CITY OF|ON BEHALF OF.*COUNTY", SUBJECT, ignore.case = TRUE), 
                             "1", CERTAINTY)) %>%
  ## Corporate service
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), 
                        "4", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), 
                             "2", CERTAINTY)) %>%
  mutate(ALT_TYPE = ifelse (!grepl("[0-9]", ALT_TYPE) & grepl("NEW COAL", SUBJECT, ignore.case = TRUE), 
                            "5", ALT_TYPE)) %>%
  ## PUCs = nonprofits, right?
  mutate(TYPE = ifelse (!grepl("[0-9]", TYPE) & grepl("PUBLIC UTILITIES COMMISSION", SUBJECT, ignore.case = TRUE), 
                        "3", TYPE)) %>%
  mutate(CERTAINTY = ifelse (!grepl("[0-9]", CERTAINTY) & grepl("PUBLIC UTILITIES COMMISSION", SUBJECT, ignore.case = TRUE), 
                             "1", CERTAINTY)) 
```

FERC has an especially high ratio of letters written on behalf of businesses compared other agencies that mostly recieve letters from legislators on behalf of their constituents. 

```{r data-by-type, fig.width=7, fig.height=4}
all_percent <- all_contacts %>% 
  filter(Type != "To be coded") %>%  
  mutate(total = n()) %>% 
  group_by(Type, total) %>% summarise(nT = n()) %>% 
  mutate(percent = 100*round(nT/total, 2) ) %>% 
  mutate(agency = "Overall") %>% 
  ungroup()


d_percent <- d%>% 
  filter(Type != "To be coded") %>%  
  mutate(total = n()) %>% 
  group_by(Type, total) %>% summarise(nT = n()) %>% 
  mutate(percent = 100*round(nT/total, 2) ) %>% 
  mutate(agency = "DOE FERC") %>% 
  ungroup()

full_join( all_percent, d_percent)%>% 
  ggplot() + 
  aes(x = Type, y = percent, fill = agency, color = agency, label = nT) + 
  geom_col(position = "dodge") + 
  geom_text(vjust = -.1,
            aes(hjust = ifelse(agency == "Overall", 0,1))) +
  labs(x = "",
       fill = "",
       color = "",
       y = "Percent", #paste("Number of Contacts, N =", sum(nrow(all_contacts))),
       title = "Legislator Contacts with FERC") +
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x.top = element_text()) + 
  scale_color_viridis_d(option = "C", end = .8) +
  scale_fill_viridis_d(option = "C", end = .8) + 
    theme_minimal() + 
  theme(panel.grid.major.x  = element_blank())
```

```{r constituent-non-constituent, fig.height=3, fig.width=7}
d  %>% 
  filter(Constituent != "Not coded") %>% 
  ggplot() + 
  aes(x = letter_position) + 
  geom_bar() + 
  facet_wrap("Constituent") +
  labs(x = "",
       y = paste("Letters 2000-2018, N =", as.character(d%>%drop_na(letter_position, Constituent) %>% nrow() %>% as.character() )))

d  %>% 
  ggplot() + 
  aes(x = letter_position) + 
  geom_bar() + 
  facet_wrap("Constituent") +
  labs(title = "Including letters without constituent coding", 
       x = "",
       y = paste("Letters 2000-2018, N =", as.character(d %>% nrow() %>% as.character() )))
```

---

# Members



Of the `r nrow(distinct(FERC_letters %>% filter(year >1999) %>% select(ID) ) )` letters from 2000-2018, we identified Members of Congress in `r length(unique(d$ID))`. Because many are cosigned, this yeild `r nrow(d)` instances of a member writing to FERC.

### Senators vs. state population 

```{r population, fig.height= 3.7, fig.width=6}
d %>% 
  filter(chamber == "Senate") %>% 
    group_by(member_state, year, pop2010) %>% summarise(n = n()) %>%
    group_by(member_state, pop2010) %>% summarise(mean = mean(n)) %>% ungroup() %>% 
    ggplot() + 
    geom_point(aes(x = log(pop2010), y = mean), color = "light blue") + 
    geom_smooth(aes(x = log(pop2010), y = mean)) + 
  geom_text(aes(x = log(pop2010), y = mean, label = ifelse(mean > mean(mean)*1.75, member_state, "")), check_overlap = F, size = 2.5, hjust = 0) + theme_bw() +
  labs(title = "Senator Requests per Year by State Population",
       x = "Log State Population",
       y = "Average Number of Requests per Year")

```

```{r sentate_percapita_map}
Chamber = "Senate"

d %>% 
  ungroup() %>%
  filter(chamber == Chamber) %>% 
  group_by(state) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) # + facet_grid(. ~ Constituent)

d %>% 
  ungroup() %>% 
  filter(chamber == Chamber) %>% 
  group_by(state, pop2010) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(Per_Capita = n/pop2010*1000000) %>% 
  # map_id creates the aesthetic mapping to the state name column in your data
  ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Contacts Per Million Residents from Members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", 
        legend.title = element_blank() )#+facet_grid(. ~ Constituent)

# By type2
d %>% 
  filter(chamber == Chamber) %>% 
  filter(Constituent != "Not coded") %>% 
  group_by(state, Constituent) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) + facet_grid(. ~ Constituent)

d %>% 
  filter(chamber == Chamber) %>%
  filter(Constituent != "Not coded") %>% 
  group_by(state, pop2010, Constituent) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(Per_Capita = n/pop2010*1000000) %>% 
  # map_id creates the aesthetic mapping to the state name column in your data
  ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Contacts Per Million Residents from Members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", 
        legend.title = element_blank() )+
  facet_grid(. ~ Constituent)
```


---

### Members who contact FERC more than average: 

```{r members_barcoded, fig.height=4, fig.width=9}
# barcode plot of committee members 
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 


Chamber <- "House" # "House" #  
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 
```

### Members who contact FERC more, relative to other agencies: 
```{r ferc_vs_all_rate}
all_contacts %>%
  mutate(FERC = agency == "DOE_FERC") %>%
  group_by(chamber, FERC, name_state, state) %>%
  summarise(n = n() ) %>%
  ungroup() %>%
  spread(key = "FERC", value = "n") %>% 
  mutate(ShareToFERC = round(`TRUE`/(`TRUE`+`FALSE`),2) )%>% 
  arrange(-ShareToFERC) %>% 
  mutate(total = `TRUE` + `FALSE`) %>% 
  select(name_state, chamber, total, ShareToFERC) %>% 
  filter(ShareToFERC>.3) %>%
  knitr::kable()
```


### Members who contact FERC more in a Congress, relative to other agencies: 
```{r ferc_vs_all_rate_committees}
all_contacts %>%
  mutate(FERC = agency == "DOE_FERC") %>%
  group_by(congress, chamber, committees, FERC, name_state, state) %>%
  summarise(n = n() ) %>%
  ungroup() %>%
  spread(key = "FERC", value = "n") %>% 
  mutate(ShareToFERC = round(`TRUE`/(`TRUE`+`FALSE`),2) )%>% 
  arrange(-ShareToFERC) %>% 
  mutate(total = `TRUE` + `FALSE`) %>% 
  select(name_state, congress, chamber, committees, total, ShareToFERC) %>% 
  filter(ShareToFERC>.5) %>%
  knitr::kable()
```


## Interesting cases

In an article titled "Republican congressmen’s funding dwarfs challengers’", the Charleston Gazee-Mail noted how energy companies backed Representative Alex Mooney (R-WV). Indeed, Mooney wrote to FERC more than any other agency, always on behalf of energy projects, mostly pipelines. 
In 2017, he wrote on behalf of the 
Dominion Energy Supply Header Project,
National Fuel Gas Distribution Corporation's [Northern Access Project](https://www.natfuel.com/supply/NorthernAccess2016/default.aspx),
Transcontinental Gas Pipe Line Company's [Atlantic Sunrise Project](https://blog.williams.com/projects-and-operations/atlantic-sunrise/atlantic-sunrise-project-placed-into-full-service/), 
Columbia Gas Transmission's proposed Eastern Panhandle Expansion project,
Columbia's WB Xpress Project to build new compressor stations,
In 2015 he wrote on behalf of the
Columbia s Mountaineer XPress Project,
Atlantic Coast Pipeline ACP project. 
The parent companies of these projects spend millions of dollars on lobbying (Lobbyview). The WV Gazette reports funding from Dominion that is not included in Lobbyview totals. 


---

## Committee Leadership

```{r committeechiars_barcode, fig.height=5}
dcommittees %>%  
  mutate(chair = str_remove(chair,"[0-9]* |^NA "),
         committee = paste(chamber, committee))%>% 
  dplyr::select(committee, position, chair, DATE, assigneddate, terminationdate) %>% 
  distinct() %>% 
  filter(str_detect(committee, "ENERGY$|ENVIRONMENT|NATURAL")) %>% 
  mutate(position = ifelse(position == "Other", NA, position)) %>%
  #filter(# !is.na(position),chair_since_2007 == T) %>%
  drop_na(chair) %>% 
  dplyr::select(DATE, chair, position, assigneddate, terminationdate, committee) %>% 
  distinct() %>% 
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = chair),
    shape = 73,
    size=2 
  ) +
  geom_segment(aes(y = chair, yend = chair, 
                   x = assigneddate, xend = terminationdate, 
                   linetype = factor(position)),
               position = position_nudge(y = -0.3)) +
  labs(title = paste("Letters to FERC from Committee Leadership"),
       y = "", 
       x = "",
       linetype = "Leadership position") +
  scale_y_discrete(position = "right") +
  theme(
    strip.text.y = element_text(angle = 180, size = 5),
    # legend.title = element_blank(),
    axis.text.y = element_text(size=5),
    axis.text.x = element_text(angle = 0)
  ) + 
  facet_grid(committee ~ ., scales = "free_y", space = "free_y", switch = "both") 
```

## Many letters to FERC are cosigned

```{r cosigned_estimated, eval=FALSE}
#A rough under-estimate based on whether "et al" or "&" appears in the summary:

FERC_letters %>% 
  filter(year>1999,
         year<2019) %>% 
  group_by(ID) %>% 
  top_n(1) %>% 
  mutate(probably_cosigned = ifelse(str_detect(SUBJECT, "et al"), "et al",
                                 ifelse(str_detect(SUBJECT, "&"), "&", " neither"))) %>%
  group_by(year, probably_cosigned) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = probably_cosigned) +
  geom_col() +
  scale_fill_viridis_d(option = "C", end = .8)
```

Cosigned letters identified by coders
```{r cosigned_coded}
FERC_letters %>% 
  filter(!is.na(Freelancer),
         year>1999,
         year<2019) %>% 
  mutate(Cosigned = ifelse(!is.na(Cosigned_House)|!is.na(Cosigned_Senate),
                                 T, F)) %>%
  group_by(year, Cosigned) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = Cosigned) +
  geom_col() +
  scale_fill_viridis_d(option = "C", end = .8)
```

---

# Companies 

## Top companies in pro-business letters
```{r probusiness-letters}
# Split out to one obs per member per letter per business
dcorps <- d %>%
  mutate(ProBusiness = ProBusiness %>% str_split(";")) %>%
  unnest(ProBusiness)

dcorps %<>% mutate(ProBusiness = ProBusiness %>%
                     str_replace("RTO", 
                                 "Regional Transmission Organization") %>%  
         str_remove_all(" Company.*| \\(.*| Inc.*| LLC.*| Energy.*") )%>%
  mutate(AntiBusiness = AntiBusiness %>% 
           str_replace("RTO", 
                       "Regional Transmission Organization") %>%  
         str_remove_all(" Company.*| \\(.*| Inc.*| LLC.*| Energy.*") )

dcorps %>%
  filter(!is.na(ProBusiness),
         !str_detect(ProBusiness, "Regional Transmission Organization") ) %>%
  group_by(ProBusiness) %>%
  select(id, last_name, ProBusiness, ID) %>%
  distinct() %>%
  summarise( n = n() , 
             members = str_c(unique(last_name), collapse = "; "),
             ID = str_c(unique(ID), collapse = "; ")) %>%
  filter(n>quantile(n,.9))%>%
  arrange(-n) %>%
  knitr::kable()
```


## Letters citing companies registered with FERC
Of the companies registered to interact with FERC, several appear in the letter texts. Here `company_short` is a shortened version a name that refrences several affiliated companies, each of which are registered separatly. 
*TO DO:* 

- (1) Identify linked corporations for other top companies in the data using [this
sheet](https://docs.google.com/spreadsheets/d/1FjZIuz8T97nczCbYskjT7-Hl6we6hoa6VndOnFmKDGU/edit#gid=0)
- (2) extract company contact persons and information from the FERC website.
```{r}
load(here("data", "DOE_FERC-corps.Rdata"))
FERC_corps %<>% ungroup() %>% group_by(company_short) %>% mutate(industry = str_c(unique(industry), collapse = ";")) %>% select(-company, -Fortune500) %>% distinct() 

## Make a single string of short corp names
ferc_short <- unique(FERC_corps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

# bad string? 
# str_detect("", ferc_short)

save(ferc_short, file = here("data/ferc_short.Rdata"))
```


## Pro-business letters
```{r probusiness-letters-ferc}
dcorps %>%
  mutate(company_short = str_extract(ProBusiness, ferc_short)) %>%
  left_join(FERC_corps) %>% 
  distinct() %>%
  group_by(company_short_refs) %>%
  select(ID, last_name, company_short, company_short_refs) %>%
  filter(company_short != "")%>%
  distinct() %>%
  summarise( n = n() , 
             company_short = str_c(unique(company_short), collapse = "; "),
             members = str_c(unique(last_name), collapse = "; "),
             ID = str_c(unique(ID), collapse = "; ")) %>%
  filter(n>quantile(n,.9))%>%
  select(company_short, n, everything()) %>%
  arrange(-n) %>%
  knitr::kable()

## Longer list with company full names
# d %>%
#   mutate(company_short = str_extract(ProBusiness, ferc_short)) %>%
#   drop_na(company_short) %>%
#   mutate(members = paste(CongressPerson, Cosigned_House, Cosigned_Senate, sep = ";")) %>%
#   mutate(members = str_remove_all(members, ";NA")) %>%
#   group_by(company_short) %>%
#   mutate(members = str_c(unique(members), collapse = ";")) %>%
#   select(company_short, members) %>%  distinct() %>%
#   left_join(FERC_corps) %>% distinct() %>%
#   knitr::kable(caption = "Pro Businesses matching those registered with FERC")
```

## Anti-business letters

```{r antibusiness-letters-ferc}
dcorps %>%
  mutate(company_short = str_extract(AntiBusiness, ferc_short)) %>%
  left_join(FERC_corps) %>% 
  distinct() %>%
  group_by(company_short_refs) %>%
  select(ID, last_name, company_short, company_short_refs) %>%
  filter(company_short != "")%>%
  distinct() %>%
  summarise( n = n() , 
             company_short = str_c(unique(company_short), collapse = "; "),
             members = str_c(unique(last_name), collapse = "; "),
             ID = str_c(unique(ID), collapse = "; ")) %>%
  filter(n>quantile(n,.9))%>%
  select(company_short, n, everything()) %>%
  arrange(-n) %>%
  knitr::kable()

## Longer list with company full names
# d %>% 
#   mutate(company_short = str_extract(AntiBusiness, ferc_short)) %>% 
#   drop_na(company_short) %>% 
#   mutate(members = paste(CongressPerson, Cosigned_House, Cosigned_Senate, sep = ";")) %>%
#   mutate(members = str_remove_all(members, ";NA")) %>% 
#   group_by(company_short) %>% 
#   mutate(members = str_c(unique(members), collapse = ";")) %>% 
#   select(company_short, members) %>%  distinct() %>%
#   left_join(FERC_corps) %>% distinct() %>% 
#   knitr::kable(caption = "Anti Businesses matching those registered with FERC")

```


---

## Company lookup table

Clean companies names extracted from letters and create shortened name that is more likely to be found in other datasets (like done with FERC-registerd companies above).
```{r company-inspect}
# Split out to one obs per member per letter per business
dcorps <- d %>%
  select(ID, bioname, ProBusiness, AntiBusiness, ProProject, AntiProject) %>% 
  gather(value = "company", key = "position", -ID, -bioname) %>%
  mutate(company = company %>% str_split(";")) %>%
  unnest(company) %>% distinct()

dcorps %<>% mutate(company = company %>%
                     str_replace("RTO", 
                                 "Regional Transmission Organization") %>%  
         str_remove_all(" Company.*| \\(.*| Inc.*| LLC.*| Energy.*") )

dcorps$company %<>%
  trimws()  # trim white space before and after company names

dcorps %<>%   filter(nchar(company)>1) %>%# drop names less than 1 character
  distinct() # drop duplicates

## For matching, remove endings like ", Inc." etc. 
trim <- function(d){
d %>%
  str_remove_all("Village of |\\(.*|,.*| -.*|^Proposed | Pipe.*| pipe.*| project$| Proiects$| Company.*| Comnany| Corp.*| Co$| Co.$| Energy$| energy$| power$| Power marketing$| Holdings.*| Group$| Gas$| Project.*| LLC| L.L.C.|  L.P.|^The | Inc.| L.P.| Ltd.| LP| Limited Partnership| Limited Liability|  Facility| Transportation and Storage| Storage and Transportation") %>% 
  str_remove_all("^, ") %>%
  trimws()  # filter out names less than 2 characters 
}



dcorps$company_short <- trim(dcorps$company) %>% trim()
```

Problem company names that may need to be fixed (e.g. to remove special characters or spell out abbreviated name)
```{r problem-names}
# Problem Names
dcorps %>% filter(nchar(company_short)<2) %>% knitr::kable()

dcorps %<>% filter(nchar(company_short)>1)
```


Identify short names by hand: 
```{r, lookup-table}
## Correct over-trimmed names
dcorps %<>% 
  mutate(company_short = ifelse(company == "Columbia Energy Power Marketing Corporation", "Columbia Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Michigan Energy Exchange, LLC", "Michigan Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Midwest Energy, Inc.", "Midwest Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Northwest Pipeline LLC", "Northwest Pipeline", company_short))%>%
  mutate(company_short = ifelse( str_detect(company, "^Dominion"), 
                                 "Dominion", company_short))%>%
  mutate(company_short = ifelse(company == "Peak Energy, Inc.", "Peak Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Public Service Company of New Mexico", "Public Service Company of New Mexico", company_short))%>%
  mutate(company_short = ifelse(company == "Salt Lake Energy Systems, LLC", "Salt Lake Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Natural Gas Pipeline Company of America", "Natural Gas Pipeline Company of America", company_short))%>%
  mutate(company_short = ifelse(company == "Natural Gas Trading Corporation", "Natural Gas Trading Corporation", company_short))%>%
  mutate(company_short = ifelse(company == "Energy, USA-TPC Corp.", "TPC", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Partners, L.L.C.", "New Energy Partners", company_short))%>%
  mutate(company_short = ifelse(company == "New Energy Service, LLC", "New Energy Service", company_short))%>%
  mutate(company_short = ifelse(company == "North Energy Associates, A Limited Partnership", "North Energy Associates", company_short))%>%
  mutate(company_short = ifelse(company == "Pipeline Company LLC", "Pipeline Company LLC", company_short))%>%
  mutate(company_short = ifelse(company == "Express Pipeline LLC", "Express Pipeline LLC", company_short))%>%
  mutate(company_short = ifelse(company == "American Energy Savings, Inc.", "American Energy Savings", company_short))%>%
  mutate(company_short = ifelse(company == "Electric Energy, Inc.", "Electric Energy, Inc.", company_short))%>%
  mutate(company_short = ifelse(company == "System Energy Resources, Inc., Llano Estacado Wind, LLC, System Energy Resources, Inc., Northern Iowa Windpower, LLC, and RS Cogen, L.L.C.", "System Energy Resources", company_short))%>%
  mutate(company_short = ifelse(company == "Public Service Company of Colorado", "Public Service Company of Colorado", company_short))%>%
  mutate(company_short = ifelse(company == "Southern Company Services, Inc.", "Southern Company", company_short))%>%
  mutate(company_short = ifelse(company == "International Energy Consultants", "International Energy Consultants", company_short))%>%
  mutate(company_short = ifelse(company == "Jackson Pipeline Company", "Jackson Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Southern Energy California", "Southern Energy California", company_short))%>%
  mutate(company_short = ifelse(company == "Tennessee Gas Pipeline Company, L.L.C.", "Tennessee Gas Pipeline", company_short))%>%
  mutate(company_short = ifelse(company == "Select Energy New York, Inc.", "Select Energy New York", company_short))%>%
  mutate(company_short = ifelse(company == "Inland Corporation", "Inland Corporation", company_short))%>%
  mutate(company_short = ifelse(company == "Advanced Energy Systems, Inc.", "Advanced Energy Systems", company_short))%>%
  mutate(company_short = ifelse(company == "Consumers Energy Company", "Consumers Energy Company", company_short))%>%
  mutate(company_short = ifelse(company == "Boston Energy Trading and Marketing LLC", "Boston Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Complete Energy Services, Inc.", "Complete Energy Services", company_short))%>%
  mutate(company_short = ifelse(company == "El Paso Energy Intrastate, L.P.", "El Paso Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Houston Pipe Line Company LP", "Houston Pipe Line", company_short))%>%
  mutate(company_short = ifelse(company == "North American Energy, Inc.", "North American Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Spokane Energy, LLC", "Spokane Energy", company_short))%>%
  mutate(company_short = ifelse(company == "Salem Energy Systems, LLC", "Salem Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "Direct", "Direct Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "DC", "DC Energy", company_short))%>%
  mutate(company_short = ifelse(company_short == "PS", "PS Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Coastal", "Coastal Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "CT", "CT Corporation", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Forest", "Forest Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Minnesota", "Minnesota Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "NW", "NW Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Rio Grande", "Rio Grande Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Plains", "Plains Pipeline", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Portland", "Portland Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "AP", "AP Holdings", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Ohio River", "Ohio River Pipe Line", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Boundary", "Boundary Gas", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Columbia", "Columbia Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Independence", "Independence Energy Group", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Lakeside", "Lakeside Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Mitchell", "Mitchell Energy", company_short)) %>%
  mutate(company_short = ifelse(company_short == "Stream", "Stream Energy", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "^Northwest Pipeline"), "Northwest Pipeline", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "^Tennessee Gas"), "Tennessee Gas", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "Juniper Hills Country Club"), "Juniper Hills Country Club", company_short))%>%
    mutate(company_short = ifelse(str_detect(company, regex("Columbia Gas", ignore_case = T)), "Columbia Gas", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, regex("Algonquin", ignore_case = T)), "Algonquin", company_short))%>%
    mutate(company_short = ifelse(str_detect(company, regex("Spectra", ignore_case = T)), "Spectra", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, regex("Jordan Cove", ignore_case = T)), "Jordan Cove", company_short))%>%
    mutate(company_short = ifelse(str_detect(company, regex("Enron", ignore_case = T)), "Enron", company_short))%>%
     mutate(company_short = ifelse(str_detect(company, regex("Nexus", ignore_case = T)), "Nexus", company_short))%>%

  mutate(company_short = ifelse(company == "Express Pipeline", "Express Pipeline", company_short))%>%
  mutate(company_short = ifelse(company %in% c("American Energy", "American energy"), "American Energy", company_short))%>%
  mutate(company_short = ifelse(str_detect(company, "PG&E|Pacific Gas & Electric|Pacific Gas and Electric"), "PG&E", company_short)) %>% 
  mutate(company_short = ifelse(company %in% c("Pacific Corp.", "Pacific Corps"), "PacifiCorp", company_short)) %>% 
  mutate(company_short = ifelse(company_short == "AI", "AI Energy", company_short)) %>% 
  mutate(company_short = ifelse(company_short %in% c("N/A","Na","NO",
                                                     "Clean Water Act","Na",
                                                     "Energy", "West", "NA",
                                                     "Central", "Power", "Natural",
                                                     "Consumers", "LNG"),
         "NOT A COMPANY?",  company_short))
```

Short company names, e.g. "Duke" may refer to many affiliated companies. The variable `company_short_refs` lists these affiliated companies. 
```{r}
#FIXME
# ADD company_short_refs 
dcorps %<>% 
  group_by(company_short) %>% 
  mutate(company_short_refs = str_c(unique(company), collapse = "; ")) %>% ungroup()
```

Look for problematic company names. For example what should we do with companies that are just state, region, or city names? (e.g. El Paso Corporation, Tennessee Gas, American Energy, Southern, etc.) 
```{r}
## Inspect over-trimmed company names
dcorps %>% filter(company_short %in% c("", "NA", "na", "Na", "LLC", "Energy", "Pipeline", "Natural", "North", "New", "Express", "gas", "American", "Electric", "System", "Direct", "DC", "PS", "CT", "Forest", "International", "Tennessee", "Salt Lake", "Lakeside", "NW", "Jackson", "Public Service", "Peak", "Independence", "Select", "Portland", "Michigan", "Boundary", "Coastal", "Minnesota", "Midwest", "Northeast", "Columbia", "Plains", "Stream", "Mitchell", "AP", "Southern", "Ohio River", "Northwest", "Rio Grande", "AI", "Transportation", "12/20/2018", "Salem", "Boston", "Spokane", "El Paso", "Houston", "North American", "Consumers", "Advanced", "Complete", "Inland", "Limited Partnership", "Sun", "RTO", "Pacific", "LNG")) %>% select(company_short, company_short_refs, ID) %>% 
  group_by(company_short) %>%
  summarise(company_short_refs = str_c(unique(company_short_refs), collapse = "; "),
            IDs = str_c(unique(ID), collapse = "; ")) %>%
  distinct() %>% knitr::kable()

##  did I acidentally delete everything before a comma? 
# dcorps %>% filter(str_detect(company_short, ","))
```

## Top 10 cited parent companies pro or con
```{r top-corps}
# top corps
topcorps <- dcorps %>% group_by(company_short) %>% tally() %>% arrange(-n) %>% top_n(10)

filter(dcorps, company_short %in% topcorps$company_short) %>%   
  group_by(company_short) %>%
  summarise(#IDs = str_c(unique(ID), collapse = "; ")
    company_short_refs = str_c(unique(company_short_refs), collapse = "; ") ) %>%
  distinct() %>% knitr::kable() 

# corps with short names 
shortcorps <- dcorps %>% 
  ungroup() %>% 
  group_by(company_short) %>% 
  tally() %>% 
  arrange(nchar(company_short)) %>% 
  mutate(nchar = nchar(company_short))%>%
  top_n(10, -nchar) %>% distinct()

filter(dcorps, company_short %in% shortcorps$company_short) %>% 
  group_by(company_short) %>%
  summarise(company_short_refs = str_c(unique(company_short_refs), collapse = "; "),
            IDs = str_c(unique(ID), collapse = "; ")) %>%
  distinct() %>% knitr::kable()

#dcorps %>% filter(!position %in% c("ProProject", "AntiProject")) %>%  group_by(company_short) %>% tally() %>% arrange(-nchar(company_short))  %>% top_n(20) %>% knitr::kable()
```


[This sheet](https://docs.google.com/spreadsheets/d/1-QNgeiMnH97jN_0vCqFKEGEB5Ztpito3iRsqK8jN3Cs/edit#gid=0) tracks non-companies in our data.
```{r, eval=FALSE}
library(googlesheets)
library(httpuv)

# log in to google drive
gs_auth() 

notcorps <- gs_title("not_companies") %>% gs_read() 


dcorps %<>% ungroup() %>% 
  mutate(company_short = ifelse(company_short %in% notcorps$not_companies,
                                "NOT A COMPANY?", company_short) )
         
#FIXME
# ADD company_short_refs again after corrections
dcorps %<>% 
  group_by(company_short) %>% 
  mutate(company_short_refs = str_c(unique(company), collapse = "; ")) %>% ungroup()

dcorps %>% 
  filter(position %in% c("ProProject", "ProBusiness")) %>% 
  select(ID, company_short, company)%>% 
  group_by(company_short) %>% 
  distinct() %>%
  add_count() %>% 
  arrange(-n) %>% 
  #write_csv(path = here("FERC/ProBusinesses.csv"))
  head()

# sum(is.na(unique(dcorps$company_short)))

## Make a single string of short corp names
dcorp_short <- unique(dcorps$company_short) %>% 
  str_c(collapse = "|") %>% 
  str_remove_all("||")

# bad string? 
# str_detect("", dcorp_short)


save(dcorp_short, file = here("data/dcorp_short.Rdata"))
save(dcorps, file = here("data/dcorps.Rdata"))

# notcorps$company


```

Drop non-company observations
```{r}
notcorps <- filter(dcorps, company_short == "NOT A COMPANY?")


sum(!is.na(d$ProBusiness))
d %<>% 
  mutate(ProBusiness = ifelse(ProBusiness %in% notcorps$company, NA, ProBusiness)) %>% 
  mutate(ProProject = ifelse(ProProject %in% notcorps$company, NA, ProProject))
  
sum(!is.na(d$ProBusiness))
```

---

# PAC Contributions from the Energy Sector
Using CRP industry codes for PACs and DIME contribution matrix, sum up sector-level contributions by memeber per cycle, matching a congress with the cycle when it was elected (e.g. 116th congress = 2018 cycle). 

```{r letters_money}
library(tidyverse)
library(dplyr)
# load data 
load(here("data/contrib_total.rds"))

contrib_total %<>% 
    mutate(cycle = str_sub(ICPSR, -4)) %>% 
  filter(cycle < 2014) %>% distinct()
  

# inspect coverage 
contrib_total %>% 
  group_by(cycle, ICPSR) %>% 
  summarise(total = sum(value, na.rm = TRUE)/1000000) %>% 
  ungroup() %>% 
  group_by(cycle) %>% 
  summarise(mean = mean(total)) %>% 
  ggplot() + 
  aes(x = factor(cycle), y = mean) + 
  geom_col() + 
  labs(y = "Average Energy-sector PAC contributions (millions) \n (ommitting energy extraction companies)", 
       x = "FEC Electoral Cycle")

# merge with letters data, d
contrib_total %<>% 
  dplyr::rename(icpsryear = ICPSR,
         PAC_contributions = value) %>% 
  mutate(cycle = str_sub(icpsryear, -4),
         icpsr = as.numeric(str_remove(icpsryear, cycle)),
         cycle = as.numeric(cycle)) %>% 
  filter(cycle > 1989) %>% 
  left_join(d %>% dplyr::select(icpsr, name_state, party) %>% distinct())

# inspect for coverage
contrib_total %>% 
  drop_na(party) %>% 
  group_by(cycle, party, icpsr) %>% 
  summarise(total = sum(PAC_contributions, na.rm = TRUE)) %>% 
  ungroup() %>% 
  group_by(cycle, party) %>% 
  summarise(mean = mean(total)) %>% 
  ggplot() + 
  aes(x = factor(cycle), y = mean, fill = party) + 
  geom_col() + 
  scale_fill_grey() + 
  labs(y = "Average Energy-sector PAC contributions \n (ommitting energy extraction companies)", 
       fill = "Party", 
       x = "FEC Electoral Cycle")

letters_money <- d %>% 
  #FIXME
  filter(cycle <2014) %>% 
  filter(!is.na(ProBusiness)|!is.na(ProProject))%>% 
  #filter(Type %in% c("Corp. Constituent", "Policy")) %>% 
  group_by(icpsryear, cycle, name_state, party, congress, icpsr, chamber, oversight_committee) %>%
  summarise(ProBusiness_Letters = n()) %>% 
  #FIXME
  filter(cycle <2014) %>% 
  distinct()

nrow(letters_money)

# join letters and DIME data by ICPSR, adding a sum of sector PAC contributions per member
letters_money %<>% 
  ungroup() %>% 
  full_join(contrib_total) %>% 
  group_by(icpsr) %>% 
  # FIXME
  # one party per member, need to deal with party switchers
  mutate(party = paste(unique(party), collapse = ";")) %>% 
  mutate(party = str_remove(party, ";.*")) %>% 
  ungroup()%>% distinct()

nrow(letters_money)

# top 10 by contributions in a cycle 
letters_money %>% 
  filter(!is.na(ProBusiness_Letters)) %>% 
  dplyr::select(-icpsryear, -icpsr, -congress) %>% 
  top_n(10, PAC_contributions) %>% knitr::kable()
```

Add zero-letter-cycle observations:
```{r add-zeros}
letters_money %<>% 
 mutate(ProBusiness_Letters = ifelse(is.na(ProBusiness_Letters) & cycle > 1997, 0, ProBusiness_Letters)) %>% distinct()

nrow(letters_money)
```

## Overall top ten PAC recepients.

Fred Upton (R-Mich.) was chair of the House Energy and Commerce Committee 2011-2017.

U.S. Senator Mary L. Landrieu was Chair of the Senate Committee on Energy and Natural Resources 2014-2015.

Count pro-business and pro-project letters:
```{r letters_money_total}
letters_money_total <- letters_money %>% 
  filter(!is.na(PAC_contributions)) %>% 
  group_by(icpsr, name_state, party) %>% 
  summarise(ProBusiness_Letters_Per_Cycle = mean(ProBusiness_Letters, na.rm = TRUE),
            PAC_contributions = sum(PAC_contributions, na.rm = TRUE)) %>% 
  ungroup()

# add zeros 
letters_money_total %<>% 
 mutate(ProBusiness_Letters_Per_Cycle = ifelse(is.na(ProBusiness_Letters_Per_Cycle), 0, ProBusiness_Letters_Per_Cycle)) %>% distinct()

nrow(letters_money_total)


letters_money_total %>% filter(!is.na(name_state)) %>%  top_n(10, PAC_contributions) %>% knitr::kable()
```

Count anti-business and anti-project letters:
```{r antibusiness}
Antiletters_money <- d %>%
  #FIXME
  filter(cycle <2014) %>% 
  filter(!is.na(AntiBusiness)|!is.na(AntiProject))%>% 
  #filter(Type %in% c("Corp. Constituent", "Policy")) %>% 
  group_by(icpsryear, cycle, name_state, party, congress, icpsr, chamber, oversight_committee) %>% distinct() %>% 
  summarise(AntiBusiness_Letters = n())

nrow(Antiletters_money)


# join letters and DIME data by ICPSR, adding a sum of sector PAC contributions per member
Antiletters_money %<>% 
  ungroup() %>% 
  full_join(contrib_total) %>% 
  group_by(icpsr) %>% 
  # FIXME
  # one party per member, need to deal with party switchers
  mutate(party = paste(unique(party), collapse = ";")) %>% 
  mutate(party = str_remove(party, ";.*")) %>% 
  ungroup() %>% distinct()

nrow(Antiletters_money)
unique(Antiletters_money$party)


# Add zero-letter-cycle observations:
Antiletters_money %<>% 
 mutate(AntiBusiness_Letters = ifelse(is.na(AntiBusiness_Letters) & cycle > 1997, 0, AntiBusiness_Letters)) 

Antiletters_money_total <- Antiletters_money %>% 
  filter(!is.na(PAC_contributions)) %>% 
  group_by(icpsr, name_state, party) %>% 
  summarise(AntiBusiness_Letters_Per_Cycle = mean(AntiBusiness_Letters, na.rm = TRUE),
            PAC_contributions = sum(PAC_contributions, na.rm = TRUE)) %>% 
  ungroup()%>% distinct()

nrow(Antiletters_money)
```

Count all letters:
```{r all_letters_money}
# constituent letters
All_Letters_money <- d %>% 
  #FIXME
  filter(cycle <2014) %>% 
  group_by(icpsryear, cycle, name_state, party, congress, icpsr, chamber, oversight_committee) %>%
  summarise(All_Letters = n()) %>% distinct()

# join letters and DIME data by ICPSR, adding a sum of sector PAC contributions per member
All_Letters_money %<>% 
  ungroup() %>% 
  full_join(contrib_total) %>% 
  group_by(icpsr) %>% 
  # FIXME
  # one party per member, need to deal with party switchers
  mutate(party = paste(unique(party), collapse = ";")) %>% 
  mutate(party = str_remove(party, ";.*")) %>% 
  ungroup()%>% distinct()

# Add zero-letter-cycle observations:
All_Letters_money %<>% 
 mutate(All_Letters = ifelse(is.na(All_Letters) & cycle > 1997, 0, All_Letters)) 

# Sum all donations since 1990
All_Letters_money_total <- All_Letters_money %>% 
  drop_na(PAC_contributions) %>% 
  group_by(icpsr, name_state, party) %>% 
  summarise(All_Letters_Per_Cycle = mean(All_Letters, na.rm = TRUE),
            PAC_contributions = sum(PAC_contributions, na.rm = TRUE)) %>% 
  ungroup()
```

Count non-constituent letters:
```{r constituent}
# constituent letters
Non_Constituent_money <- d %>% 
  #FIXME
  filter(cycle <2014) %>% 
  drop_na(Constituent) %>% 
  #filter(Type %in% c("Corp. Constituent", "Policy")) %>% 
  group_by(icpsryear, cycle, name_state, party, congress, icpsr, chamber, oversight_committee) %>%
  summarise(Non_Constituent_Letters = n()) %>% distinct()

# join letters and DIME data by ICPSR, adding a sum of sector PAC contributions per member
Non_Constituent_money %<>% 
  ungroup() %>% 
  full_join(contrib_total) %>% 
  group_by(icpsr) %>% 
  # FIXME
  # one party per member, need to deal with party switchers
  mutate(party = paste(unique(party), collapse = ";")) %>% 
  mutate(party = str_remove(party, ";.*")) %>% 
  ungroup()%>% distinct()

# Add zero-letter-cycle observations:
Non_Constituent_money %<>% 
 mutate(Non_Constituent_Letters = ifelse(is.na(Non_Constituent_Letters) & cycle > 1997, 0, Non_Constituent_Letters)) %>% distinct()

Non_Constituent_money_total <- Non_Constituent_money %>% 
  drop_na(PAC_contributions) %>% 
  group_by(icpsr, name_state, party) %>% 
  summarise(Non_Constituent_Letters_Per_Cycle = mean(Non_Constituent_Letters, na.rm = TRUE),
            PAC_contributions = sum(PAC_contributions, na.rm = TRUE)) %>% 
  ungroup()%>% distinct()
```

## PAC-specific contributions
```{r letters_PACs-data, fig.width=9.5}
# load DIME data 
load(here("data/contrib_matrix.rds"))

contrib_matrix %<>% 
  mutate(cycle = str_sub(ICPSR, -4)) %>% 
  filter(cycle < 2014)

contrib_matrix %>% 
  mutate(cycle = str_sub(ICPSR, -4)) %>% 
  # FIXME 
  filter(cycle <2014) %>% 
  group_by(cycle, ICPSR) %>% 
  summarise(total = sum(value, na.rm = TRUE)/1000000) %>% 
  ungroup() %>% 
  group_by(cycle) %>% 
  summarise(mean = mean(total)) %>% 
  ggplot() + 
  aes(x = factor(cycle), y = mean) + 
  geom_col() + 
  labs(y = "Average Energy-sector PAC contributions per member (millions) \n (ommitting energy extraction companies)", 
       x = "FEC Electoral Cycle")

contrib_matrix %>% 
  mutate(cycle = str_sub(ICPSR, -4)) %>% 
  # FIXME
  filter(cycle < 2014) %>% 
  group_by(cycle, PACShort) %>% 
  summarise(total = sum(value, na.rm = TRUE)/1000000) %>%  # millions 
  ungroup() %>% 
    group_by(PACShort) %>% 
  mutate(PACtotal = sum(total, na.rm = TRUE)) %>% 
  ungroup() %>% 
  mutate(PAC = ifelse(PACtotal > quantile(PACtotal, .98), PACShort, NA)) %>% 
  ggplot() + 
  aes(x = factor(cycle), y = total, fill= PAC) + 
  geom_col() + 
  labs(y = "Energy-sector PAC contributions (millions) \n (ommitting energy extraction companies)", 
       x = "FEC Electoral Cycle",
       fill = "PACs in top 2%") + 
  scale_fill_viridis_d(option = "C", na.value = "grey50")

contrib_matrix %>% 
  mutate(cycle = str_sub(ICPSR, -4)) %>% 
  # FIXME
  filter(cycle < 2014) %>% 
  group_by(cycle, PACShort) %>% 
  summarise(PACcycle = sum(value, na.rm = TRUE)) %>% 
  ungroup() %>% 
    group_by(PACShort) %>% 
  mutate(PACtotal = sum(PACcycle, na.rm = TRUE)) %>% 
  ungroup() %>% 
  filter(PACtotal > quantile(PACtotal, .98)) %>%  
  arrange(-as.numeric(cycle)) %>% 
  kable()

# mere with letters data, d
contrib_matrix %<>% 
  dplyr::rename(icpsryear = ICPSR,
         PAC_contributions = value) %>% 
  mutate(cycle = str_sub(icpsryear, -4),
         icpsr = as.numeric(str_remove(icpsryear, cycle)),
         cycle = as.numeric(cycle)) %>% 
  filter(cycle > 1990)%>% 
  left_join(d %>% select(icpsr, name_state, party) %>% distinct())
```

We identify `r length(unique(contrib_matrix$comid))` PACs in the energy sector (oil, gas, and electricity) and match their PAC contributions to each member of congress. 

For example:

### The top PAC recipient in a single cycle
```{r letters_PACs}
letters_PACs <- d %>% 
  #FIXME
  filter(cycle <2014) %>% 
  filter(!is.na(ProBusiness)|!is.na(ProProject))%>% 
  group_by(icpsryear, cycle, name_state, party) %>%
  summarise(ProBusiness_Letters = n()) %>% 
  # join by ICPSR, adding a sum of sector PAC contributions per member
  left_join(contrib_matrix) %>% 
  ungroup() %>% 
  group_by(icpsr) %>% 
  mutate(party = paste(unique(party), collapse = ";")) %>% 
  mutate(party = str_remove(party, ";.*")) %>% 
  ungroup()

letters_PACs_cycle <- letters_PACs %>% 
  group_by(cycle, icpsr, name_state, party) %>%
  # delete PACs that did not give from list, but keep members that recieved no contributions
  mutate(PACShort = ifelse(PAC_contributions > 0, PACShort, NA)) %>% 
  summarise(PAC_contributions = sum(PAC_contributions),
            PACs = paste(unique(PACShort), collapse = ";")) %>% 
  ungroup() %>% 
  arrange(-PAC_contributions)

letters_PACs_cycle %>% top_n(1, PAC_contributions) %>% knitr::kable()
```

### The top PAC recipient overall 
```{r letters_PACs-total, eval = FALSE}
letters_PACs_total <- letters_PACs %>% 
  ungroup() %>% 
  group_by(icpsr, name_state) %>% 
  summarise(PAC_contributions = sum(PAC_contributions),
            PACs = str_c(unique(PACShort), collapse = ";")) %>% 
  filter(!is.na(name_state)) %>% 
  ungroup()

letters_PACs_total %>% top_n(1, PAC_contributions) %>% knitr::kable()
```


### Pro-business letters per cycle
```{r, letter_money}
top1 <- top_n(letters_money_total %>% filter(!is.na(name_state)), 5, PAC_contributions) %>% .$name_state
top2 <- top_n(letters_money_total, 5, ProBusiness_Letters_Per_Cycle) %>% .$name_state

letters_money_total %>% 
  ggplot() + 
  aes(x = PAC_contributions, 
      y = ProBusiness_Letters_Per_Cycle) + 
  geom_point(alpha = .5) + 
  geom_text(aes(label = ifelse(name_state %in% top2,
                               name_state, NA)), check_overlap = TRUE, hjust = 0, color = "blue") + 
  
  labs(x = "PAC Contributions 1990-2014",
       y = "Average Pro-Business Letters sent to FERC per Cycle")

letters_money_total %>% 
  ggplot() + 
  coord_flip() + 
  aes(x = PAC_contributions, 
      y = ProBusiness_Letters_Per_Cycle) + 
  geom_point(alpha = .5) + 
  geom_text(aes(label = ifelse(name_state %in% top1,
                               name_state, NA)), check_overlap = TRUE, hjust = 0, color = "blue") + 
  
  labs(x = "PAC Contributions 1990-2014",
       y = "Average Pro-Business Letters sent to FERC per Cycle")
  
```

```{r, eval=FALSE}
library(dplyr)

# MERGE IN LETTERS DATA TO PRO-BUSINESS LETTERS
# FIXME 
# CALLE THIS Pro_letters and Antiletters Anti_letters 
nrow(letters_money)
letters_money %<>% left_join(d %>% 
dplyr::select(icpsryear, # nominate.dim1, #chair_since_2007,
              #oversight_committee, 
              chamber) %>% distinct() #%>% dplyr::rename(chair_since_2000 = chair_since_2007)
) %>% distinct()
nrow(letters_money)

nrow(All_Letters_money)
All_Letters_money %<>% distinct() %>% 
  left_join(d %>% 
dplyr::select(icpsryear, #nominate.dim1, #chair_since_2007,
              #oversight_committee, 
              chamber) %>% distinct() #%>% dplyr::rename(chair_since_2000 = chair_since_2007)
) %>% distinct()
nrow(All_Letters_money)

nrow(Antiletters_money)
Antiletters_money %<>% left_join(d %>% 
dplyr::select(icpsryear, #nominate.dim1, chair_since_2007, 
              #oversight_committee, 
              chamber) %>% distinct() #%>% dplyr::rename(chair_since_2000 = chair_since_2007)
)%>% distinct()
nrow(Antiletters_money)

# MERGE IN LETTERS DATA TO NONCONSTITUENT LETTERS COUNTS  
# TO DO 


```

# Models

## Sector-level

### All Letters per cycle ~ Energy Sector PAC contributions per cycle 1998-2014
```{r all-letters-per-cycle-model, fig.height=1}
mplot <- function(m){m %>%
  tidy(conf.int = TRUE) %>%
    filter(term!="(Intercept)") %>%
ggplot() + 
  aes(x = term,
      y = estimate, 
      ymin = conf.low, 
      ymax = conf.high)+ 
    geom_hline(yintercept = 0, linetype =2) + 
  geom_pointrange() + coord_flip() }

All_Letters_money %<>% 
  mutate(Log_PAC_contributions = log(PAC_contributions+1))  

mAll <- glm(All_Letters ~ PAC_contributions, data = All_Letters_money %>%
           mutate(PAC_contributions = PAC_contributions/1000000), 
         family = poisson)  
tidy(mAll)
mAll %>% mplot()+
  labs(x="", y="Total additional letters per congress per million dollars")
```


#### Pro-Business Letters per cycle ~ Energy Sector PAC contributions per cycle 1998-2014
```{r money-letters-per-cycle-model, fig.height=1}
letters_money %<>% 
  #drop_na(ProBusiness_Letters, PAC_contributions) %>%
  mutate(Log_PAC_contributions = log(PAC_contributions+1))  

mPro <- glm(ProBusiness_Letters ~ PAC_contributions, data = letters_money %>% mutate(PAC_contributions = PAC_contributions/1000000), family = poisson)  
tidy(mPro)
mPro %>% mplot()+
  labs(x="", y="Additional pro-business letters per congress per million dollars")


mProLog <- glm(ProBusiness_Letters ~ Log_PAC_contributions, data = letters_money, family = poisson  ) 
tidy(mProLog)
mProLog %>% mplot()+
  labs(x="", y="Additional letters per congress per Log(PAC Contributions)")


mNonConstituent <- glm(Non_Constituent_Letters ~ PAC_contributions, data = Non_Constituent_money, family = poisson  ) 
tidy(mNonConstituent)
mNonConstituent %>% mplot()+
  labs(x="", y="Additional non-constituent letters per congress per million dollars")

mNonConstituentLog <- glm(Non_Constituent_Letters ~ Log_PAC_contributions, data = Non_Constituent_money %>% mutate(Log_PAC_contributions = log(PAC_contributions+1)), family = poisson  ) 
tidy(mNonConstituent)
mNonConstituent %>% mplot()+
  labs(x="", y="Additional non-constituent letters per congress per logged million dollars")
```

#### By party
```{r letters-per-cycle-model-party, fig.height=1}
mProParty <- glm(ProBusiness_Letters ~ party, data = letters_money %>% filter(!party %in% c("NA","(I)", "Independent")), family = "poisson" ) 

tidy(mProParty)
mplot(mProParty) +
  labs(x="", y="Additional pro-business letters per congress")
```
Republicans send an additional `r round(mProParty$coefficients[2], 1)` letters per Congress, on average.




```{r multivariate_model, fig.height=1, include =TRUE}
# PAC + party:
mPro_pac_party<- glm(ProBusiness_Letters ~ PAC_contributions + party, 
                     data = letters_money %>% 
                       filter(!party %in% c("NA","(I)", "Independent"))%>% 
                       mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )

tidy(mPro_pac_party)

mplot(mPro_pac_party)+
  labs(x="", y="Additional letters per congress")

# PAC*party interaction:
mPro_pacXparty<-glm(ProBusiness_Letters ~ PAC_contributions * party, 
                    data = letters_money %>% 
                      filter(!party %in% c("NA","(I)", "Independent"))%>%
                      mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  

tidy(mPro_pacXparty)

mplot(mPro_pacXparty)+
  labs(x="", y="Additional letters per congress")



# DW NOMINATE 
#mPro_nominate <-glm(ProBusiness_Letters ~  nominate.dim1, data = letters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  
#tidy(mPro_nominate)
#mplot(mPro_nominate)+labs(x="", y="Additional letters per congress")

# PAC + ideology:
# mPro_pac_nominate <-glm(ProBusiness_Letters ~ PAC_contributions * nominate.dim1, data = letters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  

# tidy(mPro_pac_nominate)

# mplot(mPro_pac_nominate)+ labs(x="", y="Additional letters per congress")
```

#### Full (multivariate) models 
```{r full-model}
# Full model, all letters
mAll_Full <- glm(All_Letters ~ PAC_contributions + party, data = All_Letters_money %>% 
                   filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  

tidy(mAll_Full)

mplot(mAll_Full)+
  labs(x="", y="Additional letters per congress")

# Full model with interaction:
mAll_Fullx <- glm(All_Letters ~ PAC_contributions*party, data = All_Letters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  

tidy(mAll_Fullx)

mplot(mAll_Fullx)+
  labs(x="", y="Additional letters per congress")



# Full model, pro business letters 
mPro_Full <- glm(ProBusiness_Letters ~ PAC_contributions + party, data = letters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  

tidy(mPro_Full)

mplot(mPro_Full)+
  labs(x="", y="Additional letters per congress")

# Full model with interaction:
mPro_Fullx <- glm(ProBusiness_Letters ~ PAC_contributions*party, data = letters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  

tidy(mPro_Fullx)

mplot(mPro_Fullx)+
  labs(x="", y="Additional letters per congress")

mAnti_Full <- glm(AntiBusiness_Letters ~ PAC_contributions + party, data = Antiletters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  

tidy(mAnti_Full)

mplot(mAnti_Full)+
  labs(x="", y="Additional letters per congress")

# full model with interaction 
mAnti_Fullx <- glm(AntiBusiness_Letters ~ PAC_contributions*party, data = Antiletters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  
tidy(mAnti_Fullx)
mplot(mAnti_Fullx)+
  labs(x="", y="Additional letters per congress")

# FULL MODEL WITH NON- CONSTITUENT 
# FIXME
#mNonConstituent_Fullx <- glm(NonConstituent_Letters ~ PAC_contributions*party, data = NonConstituent_letters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  
#tidy(mNonConstituent_Fullx)
#mplot(mNonConstituent_Fullx)+labs(x="", y="Additional non-constituent letters per congress")
```



#### Average Pro-Business letters per cycle ~ total Energy Sector PAC contributions 1990-2014
```{r money-letters-total, fig.height=1}

mProTotal <- glm(ProBusiness_Letters_Per_Cycle ~ PAC_contributions, data = letters_money_total%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson")  

tidy(mProTotal)
mplot(mProTotal)+
  labs(x="", y="Average additional letters per cycle per million dollars 1990-2014")
```

#### Anti-Business Letters per cycle ~ Energy Sector PAC contributions per cycle 1998-2014
```{r money-Antiletters-per-cycle-model, fig.height=1}
Antiletters_money %<>% 
  #drop_na(AntiBusiness_Letters, PAC_contributions) %>%
  mutate(Log_PAC_contributions = log(PAC_contributions+1)) 

mAnti <- glm(AntiBusiness_Letters ~ PAC_contributions, data = Antiletters_money %>% mutate(PAC_contributions = PAC_contributions/1000000), family = poisson)  
tidy(mAnti)
mAnti %>% mplot()+
  labs(x="", y="Additional anti-buisness letters per congress per million dollars")

mAntiLog <- glm(AntiBusiness_Letters ~ Log_PAC_contributions, data = Antiletters_money, family = poisson  ) 
tidy(mAntiLog)
mAntiLog %>% mplot()+
  labs(x="", y="Additional anti-business Letters per congress per Log(PAC Contributions)")
```

#### By party:
```{r Antiletters-per-cycle-model-party, fig.height=1}

mAntiParty <- glm(AntiBusiness_Letters ~ party, data = Antiletters_money %>% filter(!party %in% c("NA","(I)", "Independent")), family = "poisson" ) 

tidy(mAntiParty)
mplot(mAntiParty) +
  labs(x="", y="Additional anti-business  letters per congress")
```
Democrats send an additional `r -round(mAntiParty$coefficients[2], 1)` Anti-Business letters per Congress, on average.




```{r money-Antiletters-per-cycle-model-party, fig.height=1, include=TRUE}
#PAC*party interaction:
mAnti_pacXparty <-glm(AntiBusiness_Letters ~ PAC_contributions*party, data = Antiletters_money %>% filter(party !="NA")%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson" )  
tidy(mAnti_pacXparty)
mplot(mAnti_pacXparty)+
  labs(x="", y="Additional anti-business letters per congress")
```



#### Average Anti-Business letters per cycle ~ total Energy Sector PAC contributions 1990-2014
```{r money-Antiletters-total, fig.height=1}
mAntiTotal <- glm(AntiBusiness_Letters_Per_Cycle ~ PAC_contributions, data = Antiletters_money_total%>% mutate(PAC_contributions = PAC_contributions/1000000), family = "poisson")  

tidy(mAntiTotal)

mplot(mAntiTotal)+
  labs(x="", y="Average additional anti-business letters per cycle per million dollars 1990-2014")
```

# Combined models 

```{r models, fig.height=2, results='hide'}
library(dplyr)
dplot <- function(x){dwplot(x) +
    aes(shape = model) + 
    geom_vline(xintercept = 0, linetype = 2) +
    scale_color_viridis_d(option = "C", end = .8) + 
    labs(color = "Dependent Variable",
         shape = "Dependent Variable") +
  theme(panel.grid.major.y  = element_blank())
}

# Basic PAC money models 
models <- full_join(
  tidy(mAll) %>% mutate(model = "All Letters per Cycle"),
  tidy(mPro) %>% mutate(model = "Pro-business Letters per Cycle") ) %>% 
  full_join(tidy(mNonConstituent) %>% mutate(model = "Non-constituent Letters per Cycle")) %>%
  full_join(tidy(mAnti)  %>% mutate(model = "Anti-business Letters per Cycle")) 

dplot(models)+ 
    labs(color = "Dependent Variable",
         shape = "Dependent Variable",
         x = "Additional letters per million dollars per cycle")

library(stargazer)
library(dplyr)
write_lines(stargazer(mAll, mPro, mAnti, mNonConstituent, float=F),
  path = here("FERC/tables/All-mPro-mAnti-mNonConstituent.tex"))

table <- stargazer(mAll, mPro, mAnti, mNonConstituent, 
                type = "html",
                notes = "FERC/tables/All-mPro-mAnti-mNonConstituent.tex")
```

```{r}
kable(table)
```

### logged PAC money models 
```{r models-log, fig.height=2, results='hide'}
## logged PAC money models 
models <- tidy(mProLog) %>% mutate(model = "Pro-business Letters per Cycle") %>%  
full_join(tidy(mAntiLog) %>% mutate(model = "Anti-business Letters per Cycle")) 

dplot(models)+ 
    labs(x = "Additional letters per million dollars per cycle")

write_lines(
  stargazer::stargazer(mProLog, mAntiLog,
                       float=F),
  path = here("FERC/tables/mProLog-mAntiLog.tex"))

table <- stargazer(mProLog, mAntiLog, 
                type = "html",
                notes = "FERC/tables/mProLog-mAntiLog.tex")
```

```{r}
kable(table)
```

### PAC contributions over entire time period 
```{r models-total, fig.height=2, results = 'hide'}
## PAC contributions over entire time period 
models <- tidy(mProTotal) %>% 
  mutate(model = "Pro-business Letters per Cycle") %>% 
  full_join(tidy(mAntiTotal) %>% mutate(model = "Anti-business Letters per Cycle")) 

dplot(models) + 
    labs(x = "Average additional letters per cycle per million dollars 1990-2014")

write_lines(
  stargazer::stargazer(mProTotal, mAntiTotal, float=F),
  path = here("FERC/tables/mProTotal-mAntiTotal.tex"))

table <- stargazer(mProTotal, mAntiTotal, 
                type = "html",
                notes = "FERC/tables/mProTotal-mAntiTotal.tex")
```

```{r}
kable(table)
```

### Party
```{r models-party, fig.height=2, results='hide'}
## With party IV 
models <- tidy(mProParty) %>% 
  mutate(model = "Pro-business Letters per Cycle") %>%
  full_join(tidy(mAntiParty) %>%
              mutate(model = "Anti-business Letters per Cycle")) %>%
  mutate(term = str_replace(term, "party\\(R\\)", "Republican")) %>% 
  filter(term != "party(I)")

dplot(models) + 
    labs(x = "Additional letters per cycle")

write_lines(
  stargazer::stargazer(mProParty, mAntiParty, float=F),
  path = here("FERC/tables/mProParty-mAntiParty.tex"))

table <- stargazer(mProParty, mAntiParty, 
                type = "html",
                notes = "FERC/tables/mProParty-mAntiParty.tex")
```

```{r}
kable(table)
```


### All univariate models 
```{r models-ALL, fig.height=2, results='hide'}
# All models 
write_lines(
  stargazer::stargazer(mAll, mPro, mAnti,mNonConstituent, mProLog, mAntiLog, mProParty, mProTotal, mAntiTotal, mAntiParty, float = F),
  path = here("FERC/tables/mUnivariate.tex"))

table <-stargazer(mAll, mPro, mAnti, mNonConstituent, mProLog, mAntiLog, mProParty, mProTotal, mAntiTotal, mAntiParty, 
                type = "html",
                notes = "FERC/tables/mUnivariate.tex")
```

```{r}
kable(table)
```


### All Full (multivariate) Models
```{r models-full, fig.height=2, results='hide'}
## Full model
models <- tidy(mAll_Full) %>% 
  mutate(model = "Total Letters per Cycle") %>%
  full_join(tidy(mPro_Full) %>%
              mutate(model = "Pro-business Letters per Cycle")) %>%
  full_join(tidy(mPro_Fullx) %>% mutate(model = "Pro-business Letters per Cycle, with interaction")) %>%
  full_join(tidy(mAnti_Full) %>%
              mutate(model = "Anti-business Letters per Cycle")) %>%
  full_join(tidy(mAnti_Fullx) %>% mutate(model = "Anti-business Letters per Cycle, with interaction")) %>%
  mutate(term = str_replace(term, "party\\(R\\)", "Republican"))

dplot(models) + 
    labs(x = "Additional letters per cycle")

write_lines(
  stargazer::stargazer(mAll_Full, mAll_Fullx, mPro_Full, mAnti_Full,mPro_Fullx, mAnti_Fullx, float=F),
  path = here("FERC/tables/mFull.tex"))

table <- stargazer(mPro_Full, mAnti_Full, mPro_Fullx, mAnti_Fullx,
                type = "html",
                notes = "FERC/tables/mFull.tex")
```

```{r}
kable(table)
```

## PAC-level

### Before matching projects and companies to their parent companies: 
```{r pacs-corps, eval= FALSE}
# letter count per pac ~ pac contributions (lots of 0$-0letter pairs )
# 1. id pacs per letter - spit letters matching several pacs 
# 2. count up per member 
# 3. add 0s for all other pac-member-cycle compinations 
# merge in with contributions per pac per member 

# First, clean up the contributions data a bit

# a helper function to concat unique strings
unique_string <- . %>% 
  str_split(";") %>% 
  # select unique ones
  unlist() %>% 
  unique() %>% 
  trimws() %>% 
  # paste them back together to retrun a single value 
  paste(collapse = ";") %>%
  str_remove_all("na;|;na$|NA;|;NA$")

# Just the PAC names and IDs from the contributions matrix (will merge in relevent contributions later)
PACs <- contrib_matrix %>% 
  select(comid, UltOrg,Affiliate,PACShort) %>% distinct() %>% 
  # make a full list of pac-affiliated orgs
  group_by(comid) %>%
  mutate(UltOrg2 = str_c(UltOrg,Affiliate,PACShort, sep = ";") %>% 
           tolower() %>% 
           # select unique ones
           unique_string())

# A function to get matching names
get_pac <- function(corp, PAC){
  ifelse(str_detect(tolower(PAC), tolower(corp)), PAC, NA)
}

# A function to get IDs where names match 
get_pacID <- function(corp, PAC, PACid){
  ifelse(str_detect(tolower(PAC), tolower(corp)), PACid, NA) 
}


# corp = "Exxon"

# A function to augment the PAC data with any matching company names 
get_pacs <- function(corp){
PACs %>% 
    mutate(pacs = get_pac(tolower(corp), UltOrg2),
           pacIDs = get_pacID(tolower(corp), UltOrg2, comid)) %>% 
    ungroup() %>% 
    select(pacs, pacIDs) %>% 
    distinct() %>% 
    summarise_all(unique_string) %>% 
    mutate(company_short = corp)
}

# TESTING 
# corp = "Exxon"
# get_pacs(corp)
# corp <- dcorps$company_short[1]
# get_pacs(corp)

crosswalk <- map_dfr(dcorps$company_short, get_pacs)

crosswalk %<>% distinct()

# use crosswalk to merge in contribution data 
dpacs <- dcorps %>% 
  full_join(crosswalk) %>% 
  # letters per year per pac
  select(ID, position, company_short, position, pacs, pacIDs) %>% 
  distinct() %>% 
  mutate(pacIDs = str_split(pacIDs, ";")) %>% 
  unnest(pacIDs) %>% 
  distinct() %>% 
  # merge in pac totals
  dplyr::rename(comid = pacIDs) %>% 
  # merge in contribution data
  left_join(contrib_matrix) # %>% group_by(comid, position) %>% summarise(PAC_contributions)

dpacs %<>% 
  ungroup() %>% 
  filter(!is.na(ID), !is.na(comid)) %>% 
  select(ID, icpsryear, cycle, name_state, position, company_short, pacs, comid, PAC_contributions) %>% 
  distinct()
```


#### Pro-business letters linked to PAC contributions:
```{r pro-pacs, eval = FALSE}
dpacs %>% 
  filter(position %in% c("ProBusiness", "ProProject")) %>% 
  # select letters with an identified person
  drop_na(name_state, ID) %>%
  group_by(name_state, cycle, position, company_short, pacs, comid) %>% 
  distinct()%>%  summarise(PAC_contributions = sum(PAC_contributions, na.rm = T),
                           # FIXME 
                           # SHOULD NOT NEED UNIQUE HERE 
            Letter_IDs = paste(unique(ID), collapse = ";")) %>% 
  ungroup() %>% 
  group_by(position)  %>%
  top_n(10, PAC_contributions) %>% 
  knitr::kable()
```

#### Anti-business letters linked to PAC contributions:
```{r anti-pacs, eval = FALSE}
dpacs %>% 
  filter(position %in% c("AntiBusiness", "AntiProject")) %>% 
  left_join(d %>% select(ID, Constituent) %>% distinct() ) %>% 
  filter(Constituent == "No") %>%
  # select letters with an identified person
  drop_na(name_state, ID) %>%
  group_by(name_state, cycle, position, company_short, pacs, comid) %>% 
  distinct()%>%  summarise(PAC_contributions = sum(PAC_contributions, na.rm = T),
                           # FIXME 
                           # SHOULD NOT NEED UNIQUE HERE 
            Letter_IDs = paste(unique(ID), collapse = ";")) %>% 
  ungroup() %>% 
  group_by(position)  %>%
  top_n(10, PAC_contributions) %>% 
  knitr::kable()

#Before connecting companies to the PAC donations of their parent companies, we find `r sum(!is.na(dpacs$ID))` letters with a pack donation.
```
 



```{}
################################################   
# merge in and split out parent corps 

# TABLE 
letterID 
date
member
district 
committee 
position 
company
pac 
ammount 


# risiduals 
```




# About FERC 

FERC regulates electricity markets, oil and gas pipelines, and hydropower and gas export projects. Many of these decisions have major implications for business profets. For example, because many natual gas pipelines cross state lines, FERC largely controls pipeline market entry. Similarly, because electricity grids are regional. 


## Letters on behalf of projects in their districts
TODO

## Letters are on behalf of donors
TODO

## Comparing FERC to other agencies
TODO 


# TO DO 
- Fix Goode, who is being double counted as an R and I
- add company names from company scraper to google sheet
- template to match company names to donation (lobbyview, DIME)
- template match company names to industry codes (center for responsive politics)

## SHORT TERM
- letters per company 
- letters per company pac (before and after merging in partent companies)

## LONG TERM 

## DONE
- add clean text from scraper to google sheet 
- fix clean function to pull and combine new data
- link industry codes to CRP PAC committee classification 
 1. Identify relevent industry codes 
 2. Get cycle-specific PAC classification for those industry codes 
 3. Subset dime to those PAC classification 

# References 

<!--
![Sources of Bureaucratic Delay: A Case Study of FERC Dam Relicensing](https://academic.oup.com/jleo/article/22/1/258/938707)
-->

