---
title: "DOD Independent Study"
subtitle: "Insert Something Insightful Soon"
author: "Fatima Ali"
output:
  #pdf_document
    html_document:
      toc: true
      toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---



# Data

##Is there a way we can get this updated??
The full dataset of congressional correspondence can be found at `"data/all_contacts.RData"`.
More data from the text of FERC letters are saved as `"data/DOE_FERC-letters-clean.Rdata"`. ##How do I do this for DOD agencies


```{r data}
load(here("data/all_contacts.RData"))
# one obs per member per letter for all agencies
d <- all_contacts %>%
  ungroup() %>% 
  # define d as just FERC
  filter(agency=="DOD"|"VA") %>% 
  #mutate(ID = NOTES) %>% 
  # FIXME
  # filter(nchar(ID)>8) %>%
  #select(-SUBJECT) %>% 
  mutate(majority = ifelse(majority == 1, "Majority", "Minority")) %>%
  # FIXME 
  
  

## one obs per member per letter per committee for all agencies # DEPRECIATED 
# load(here("data/all_contacts_committees.RData"))
## define dcommittees as just FERC
#dcommittees <- all_contacts_committees %<>% filter(agency == "DOD"|"VA")

# Coded letters, one obs per member per letter 

#load(here("data/DOE_FERC-letters-clean.Rdata"))  ##Change this to DOD and VA


# TO DO: replace with DOE_FERC-letters-corps.Rdata when corps added
DOD_letters %<>% 
  select(SUBJECT, Notes, DATE, last_name, # last_name is aparently slightly different in d and FERC_letters
         Freelancer, 
         Cosigned_House, Cosigned_Senate,
         text_clean, Constituent, year,
         Place_State, Place_District, Place_District,
         ProBusiness, AntiBusiness, ProProject, AntiProject) %>%
  #mutate(ID = ID %>% as.character()) %>% 
  distinct()

## Make sure DOD  letter IDs are the same as in the main data
# DOD_letters %>% filter(year < 2019, !ID %in% d$ID)

# merge in coded letters

d %<>% left_join(DOD_letters) %>% filter(year <2017, !is.na(ID))  ##is this where I input 2007-2017?

# how many failed to merge?
d %>% count(is.na())  ##not sure why Freelancer was inside there

# Add hand-coding to auto-coding of letter type 
d %<>%  
  mutate(Type = as.character(Type)) %>% 
  mutate(Type = ifelse(tolower(Constituent) == "yes", "Indiv. Constituent", Type)) %>% 
  mutate(Type = ifelse(!is.na(ProBusiness)|!is.na(ProProject), "Corp. Constituent", Type)) %>%
  # define Constituent as "Indiv. Constituent"
  mutate(Constituent = ifelse(Type == "Indiv. Constituent", "Indiv. Constituent", "Non_constituent"),
         Constituent = replace_na(Constituent, "Not coded") ) 
  



# unique(d$letter_position)

d %<>% 
  # FIXME
  # rounding years up is approximate, rewrite to go Nov-Nov?
  #mutate(cycle = congress*2+1786 ) %>% 
  mutate(icpsryear = str_c(icpsr, congress))
```



In all, we have `r FERC_letters %>% select(Notes) %>% distinct() %>% nrow()` letters received by FERC and marked "congressional" since `r min(FERC_letters$year)`. Most, but not all of these are from Members of the U.S. Congress. Of the `r FERC_letters %>% filter(year >1999) %>% select(Notes) %>% distinct() %>% nrow()` letters from 2000-`r max(d$year)`, we identified Members of Congress in 3908. Because many are cosigned, this yeild `r nrow(d)` instances of a member writing to FERC.

---

# Outlier
##How do we figure this out??
 
```{r forwards}
# top overall
d %>% count(bioname,party, cqlabel, sort = T) %>% top_n(10, n) %>% kable(caption = "Legislators who wrote the most letters to DOD and VA")

# most with a given position
d %>% count(bioname, party, cqlabel, letter_position, sort = T) %>% filter(letter_position != "Other") %>% top_n(10, n) %>% kable(caption = "Most frequent letter positions for a given legislator")

# most with a given position in a cycle
d %>% count(bioname, party, cqlabel, letter_position, congress, sort = T) %>% filter(letter_position != "Other") %>% top_n(10, n) %>% kable(caption = "Most frequent letter positions for a given legislator in a cycle")

# d %>%   filter(str_detect(SUBJECT, "forwards")) %>% add_count(bioname, sort = T) %>% top_n(1, n) %>% select(bioname, SUBJECT) %>% kable(caption = "Letters from the legislator who forwards the most letters")

d %>%
  ggplot() +
  aes(x = congress, fill = letter_position) + 
  geom_bar(position = "dodge") + 
  facet_grid(party_name ~ chamber)
```


---

## By party and majority status


```{r part-constituent, fig.height=3, fig.width=4}
d %>% 
  mutate(For = Constituent,
         For = ifelse(letter_position == "ProBusiness", "Pro-Business", For),
         For = ifelse(For == "Non_constituent", "Other", For)) %>% 
  count(party_name, For, majority) %>% 
  filter(party_name != "Independent",
         !is.na(For),
         For != "Not coded",
         For != "Other",
         !is.na(majority)) %>% 
  group_by(party_name, majority) %>% 
  mutate(percent = n / sum(n) * 100 ) %>% 
  ggplot() + 
  aes(y = percent, x = "", fill = For) + 
  geom_col(position = "stack") + 
  #geom_text(aes(label = n)) +
  facet_grid(majority ~ party_name) + 
  scale_fill_viridis_d(option = "C", end = .8) + 
    labs(x = "",
       fill = "Advocating for",
       y = "Percent") + 
  theme_minimal() + 
  theme(panel.grid.major.x  = element_blank())

d %>% 
  mutate(For = Constituent,
         For = ifelse(letter_position == "ProBusiness", "Pro-Business", For),
         For = ifelse(For == "Non_constituent", "Other", For)) %>% 
  count(party_name, For, majority, congress) %>% 
  filter(party_name != "Independent",
         !is.na(For),
         For != "Not coded",
         For != "Other",
         !is.na(majority)) %>% 
  ggplot() + 
  aes(y = n, x = congress, fill = For) + 
  geom_col(position = "stack") + 
  #geom_text(aes(label = n)) +
  facet_grid(majority ~ party_name) + 
  scale_fill_viridis_d(option = "C", end = .8) + 
    labs(x = "",
       fill = "Advocating for",
       y = "n") + 
  theme_minimal() + 
  theme(panel.grid.major.x  = element_blank(),
        axis.text = element_text(angle = 45))
```

Looking at letters that are explicitly pro- or anti-business, Democrats write more anti-business letters, whereas, for Republicans, it depends on chamber control. When in the majority, Republicans write more pro-business letters. 
```{r part-business, fig.height=3, fig.width=4}
d %>% 
  count(party_name, letter_position, majority) %>% 
    filter(party_name != "Independent",
           letter_position != "Other",
         !is.na(letter_position),
         !is.na(majority)) %>% 
  group_by(party_name, majority) %>% 
  mutate(percent = n / sum(n) * 100 ) %>% 
  ggplot() + 
  aes(y = percent, x = "", fill = letter_position) + 
  geom_col(position = "stack") + 
  facet_grid(majority ~ party_name)+ 
  scale_fill_viridis_d(option = "C", end = .8) + 
  labs(x = "",
       fill = "",
       y = "Percent") + 
  theme_minimal() + 
  theme(panel.grid.major.x  = element_blank())

d %>% filter(party_name != "Independent",
             letter_position != "Other",
             !is.na(letter_position),
             !is.na(majority)) %>% 
  count(party_name, letter_position, majority, congress) %>% 
  ggplot() + 
  aes(y = n, x = factor(congress), fill = letter_position) + 
  geom_col(position = "stack") + 
  facet_grid(majority ~ party_name)+ 
  scale_fill_viridis_d(option = "C", end = .8) + 
  labs(x = "",
       fill = "",
       y = "n") + 
  theme_minimal() + 
  theme(panel.grid.major.x  = element_blank(),
        axis.text.x = element_text(angle = 45))
```

---

## Coding of constituent type 
Our coding of letter type is a mix of hand-coding "Pro-business" and "Constituent" letters, as well as some coding rules applied to letters that were not put in either group by human coders using [inductively-developed coding rules](https://github.com/judgelord/correspondence/blob/master/agencies/DOE_FERC.R).

FERC has an especially high ratio of letters written on behalf of businesses compared to other agencies that mostly receive letters from legislators on behalf of their constituents. 

```{r data-by-type, fig.width=7, fig.height=4}
all_percent <- all_contacts %>% 
  filter(Type != "To be coded") %>%  
  mutate(total = n()) %>% 
  group_by(Type, total) %>% summarise(nT = n()) %>% 
  mutate(percent = 100*round(nT/total, 2) ) %>% 
  mutate(agency = "Overall") %>% 
  ungroup()


d_percent <- d %>% 
  filter(Type != "To be coded") %>%  
  mutate(total = n()) %>% 
  group_by(Type, total) %>% summarise(nT = n()) %>% 
  mutate(percent = 100*round(nT/total, 2) ) %>% 
  mutate(agency = "DOD"|"VA") %>% 
  ungroup()

full_join( all_percent, d_percent)%>% 
  ggplot() + 
  aes(x = Type, y = percent, fill = agency, color = agency, label = nT) + 
  geom_col(position = "dodge") + 
  geom_text(vjust = -.1,
            aes(hjust = ifelse(agency == "Overall", 0,1))) +
  labs(x = "",
       fill = "",
       color = "",
       y = "Percent", #paste("Number of Contacts, N =", sum(nrow(all_contacts))),
       title = "Legislator Contacts with FERC") +
  theme(panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x.top = element_text()) + 
  scale_color_viridis_d(option = "C", end = .8) +
  scale_fill_viridis_d(option = "C", end = .8) + 
    theme_minimal() + 
  theme(panel.grid.major.x  = element_blank())
```

```{r constituent-non-constituent, fig.height=3, fig.width=7}
d  %>% 
  filter(Constituent != "Not coded") %>% 
  ggplot() + 
      theme_minimal() +
  aes(x = letter_position) + 
  geom_bar() + 
  facet_wrap("Constituent") +
  
  labs(x = "",
       y = paste("Letters 2007-2017, N =", as.character(d%>%drop_na(letter_position, Constituent) %>% nrow() %>% as.character() )))

d  %>% 
  ggplot() + 
      theme_minimal() +
  aes(x = letter_position) + 
  geom_bar() + 
  facet_wrap("Constituent") +
  labs(title = "Including letters without constituent coding", 
       x = "",
       y = paste("Letters 2007-2017, N =", as.character(d %>% nrow() %>% as.character() )))
```

---

# Members

### Senators vs. state population 

```{r population, fig.height= 3.7, fig.width=6}
d %>% 
  filter(chamber == "Senate") %>% 
    group_by(member_state, year, pop2010) %>% summarise(n = n()) %>%
    group_by(member_state, pop2010) %>% summarise(mean = mean(n)) %>% ungroup() %>% 
    ggplot() + 
    geom_point(aes(x = log(pop2010), y = mean), color = "light blue") + 
  geom_smooth(aes(x = log(pop2010), y = mean)) + 
  geom_text(aes(x = log(pop2010), 
                y = mean, 
                label = ifelse(mean > mean(mean)*1.5 | mean < mean(mean)*0.5, 
                               member_state, "")), 
            check_overlap = TRUE, 
            size = 2.5, 
            hjust = 0) + 
  theme_bw() +
  labs(title = "Senator Requests per Year by State Population",
       x = "Log State Population",
       y = "Average Number of Requests per Year")

```

```{r senate_percapita_map}
Chamber = "Senate"

d %>% 
  ungroup() %>%
  filter(chamber == Chamber) %>% 
  group_by(state) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) # + facet_grid(. ~ Constituent)

d %>% 
  ungroup() %>% 
  filter(chamber == Chamber) %>% 
  group_by(state, pop2010) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(Per_Capita = n/pop2010*1000000) %>% 
  # map_id creates the aesthetic mapping to the state name column in your data
  ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Contacts Per hundred thousand Residents from Members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", 
        legend.title = element_blank() )#+facet_grid(. ~ Constituent)

# By type2
d %>% 
  filter(chamber == Chamber) %>% 
  filter(Constituent != "Not coded") %>% 
  group_by(state, Constituent) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) + facet_grid(. ~ Constituent)

d %>% 
  filter(chamber == Chamber) %>%
  filter(Constituent != "Not coded") %>% 
  group_by(state, pop2010, Constituent) %>% summarise(n = n()) %>% ungroup() %>% 
  mutate(Per_Capita = n/pop2010*1000000) %>% 
  # map_id creates the aesthetic mapping to the state name column in your data
  ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) +
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Contacts Per hundred thousand Residents from Members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", 
        legend.title = element_blank() )+
  facet_grid(. ~ Constituent)
```


---

### Members who contact DOD and VA more than average: 

```{r members_barcoded, fig.height=5, fig.width=9}
# barcode plot of committee members 
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 


Chamber <- "House" # "House" #  
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 
```

```{r ferc_vs_all_rate}
all_contacts %>%
  filter(congress >109) %>% 
  mutate(FERC = agency == "DOD"|"VA") %>%
  count(chamber, DOD|VA, name_state, state) %>%
  spread(key = "DOD"|"VA", value = "n", 0) %>% 
  mutate(ShareToDOD_VA = round(`TRUE`/(`TRUE`+`FALSE`),2) ) %>% 
  arrange(-ShareToDOD_VA) %>% 
  mutate(total = `TRUE` + `FALSE`) %>% 
  select(name_state, chamber, total, ShareToDOD_VA) %>% 
  filter(ShareToDOD_VA>.3) %>%
  knitr::kable(caption = "Members who contact DOD and VA more, relative to other agencies" )


all_contacts %>% 
  filter(congress >109) %>% 
  mutate(FERC = agency == "DOD"|"VA") %>%
  count(chamber, congress, FERC, name_state, state) %>%
  spread(key = "DOD"|"VA", value = "n", 0) %>% 
  mutate(ShareToDOD_VA = round(`TRUE`/(`TRUE`+`FALSE`),2) ) %>% 
  arrange(-ShareToDOD_VA) %>% 
  mutate(total = `TRUE` + `FALSE`) %>% 
  select(name_state, chamber, congress, total, ShareToDOD_VA) %>% 
    filter(total >10) %>% 
  top_n(10) %>%
  knitr::kable(caption = "Members who contact DOD and VA more, relative to other agencies")
```


## Interesting cases


---



---




##Count non-constituent letters:
```{r constituent}
# letter counts by position
constituent_counts <- d %>% 
  mutate(constituent_position = Constituent) %>% 
  count(constituent_position, congress, chamber, icpsr) %>% 
  ungroup() # %>% tally(n)

# constituent_counts %>% filter(is.na(constituent_position))

# use voteview members file as base to make sure we are not missing anyone who wrote 0 letters
members %<>%  filter(congress >105) %>% filter(chamber %in% c("House", "Senate")) 

# add letters to members file to get zero counts
constituents <- members %>% select(congress, icpsr, chamber, cqlabel) %>% distinct() %>% 
  left_join(constituent_counts) %>% # introduces NA constituent position because not all members are in constituent_counts
  mutate(n = replace_na(n,0)) %>% 
  ungroup() %>% 
  # mutate(constituent_position = as.factor(constituent_position)) %>% 
    complete(constituent_position, nesting(congress, icpsr, chamber, cqlabel),
             fill = list(n = 0)) %>% 
  ungroup() %>% 
  filter(!is.na(constituent_position)) %>% 
  distinct() 

# constituents %>% count(constituent_position)

# # should be the same icpsrs
# members %>% select(congress, icpsr) %>% ungroup() %>% top_n(10, icpsr) %>% arrange(-icpsr) %>% kable()
# constituents %>% ungroup() %>% top_n(10, icpsr) %>% arrange(-icpsr) %>% kable()

# merge with PAC amounts
constituents_money <-  constituents %>% 
  full_join(pac_amounts %>% ungroup())  %>% distinct()

# constituents %>% filter(!icpsr %in% pac_amounts$icpsr)
# members %>% filter(!icpsr %in% pac_amounts$icpsr)
# pac_amounts %>% filter(!icpsr %in% constituents$icpsr)

# constituents_money %>% count(constituent_position)

constituents_money %<>% filter(!is.na(bioname))

constituents_money %>%  top_n(1, icpsr) %>% arrange(congress, -icpsr) %>% kable()

# make sure we have all members and no more 
# members %>% select(icpsr, congress, chamber) %>% left_join(constituents_money) %>% distinct()

# inspect for 0 counts 
# constituents_money %>% count(n, sort = T)

constituents_money %<>%
  mutate(Non_Constituent_Letters = ifelse(constituent_position == "Non_constituent", n, NA), #FIXME 
         Constituent_Letters = ifelse(constituent_position == "Indiv. Constituent", n, NA))
# inspect for correct 0 counts (should be equal across years per industry)
constituents_money %>% count(industry, constituent_position) %>% kable()
```




### Multivariate models 
```{r full-model, fig.height=1}
# Full model, all letters
mAll_Full <- glm(total_letters ~ PAC_100k + party_name, 
                 data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_100k, chamber,party_name, total_letters) %>%
                      distinct(),
            family = poisson)

# tidy(mAll_Full)

mplot(mAll_Full)+
  labs(x="", y="Additional letters per congress")

# Full model with interaction:
mAll_Fullx <- glm(total_letters ~ PAC_100k*party_name, 
                                   data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_100k, chamber,party_name, total_letters) %>%
                      distinct(),
            family = poisson)
# tidy(mAll_Fullx)

mplot(mAll_Fullx)+
  labs(x="", y="Additional letters per congress")



# Full model, pro business letters 
mPro_Full <- glm(ProBusiness_Letters ~ PAC_100k + party_name, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_100k, chamber,party_name, ProBusiness_Letters) %>%
                      distinct(),
            family = poisson)

# tidy(mPro_Full)

mplot(mPro_Full)+
  labs(x="", y="Additional letters per congress")

# Full model with interaction:
mPro_Fullx <- glm(ProBusiness_Letters ~ PAC_100k * party_name, 
                                  data = letters_money %>% 
                        filter(industry == "energy",
                               party_name != "Independent",
                               !is.na(ProBusiness_Letters)) %>% 
                        select(icpsr, congress, PAC_100k, chamber,party_name, ProBusiness_Letters) %>%
                      distinct(),
            family = poisson)

# tidy(mPro_Fullx)

mplot(mPro_Fullx)+
  labs(x="", y="Additional letters per congress")


mAnti_Full <- glm(AntiBusiness_Letters ~ PAC_100k + party_name, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_100k, party_name,chamber, AntiBusiness_Letters) %>%
                      distinct(),
            family = poisson)

# tidy(mAnti_Full)

mplot(mAnti_Full)+
  labs(x="", y="Additional letters per congress")

# full model with interaction 
mAnti_Fullx <- glm(AntiBusiness_Letters ~ PAC_100k * party_name, 
                                  data = letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        select(icpsr, congress, PAC_100k, party_name,chamber, AntiBusiness_Letters) %>%
                      distinct(),
            family = poisson)

letters_money %>% 
                        filter(industry == "energy") %>% 
                        filter(party_name != "Independent") %>% 
                        #filter(!is.na(AntiBusiness_Letters)) %>% 
                        select(icpsr, congress, PAC_100k, party_name,chamber, AntiBusiness_Letters, letter_position) %>%
                      distinct() %>% count(letter_position) #%>% filter(is.na(icpsr)|is.na(congress)|is.na(PAC_100k)|is.na(party_name)|is.na(AntiBusiness_Letters)&is.na(ProBusiness_Letters))

# tidy(mAnti_Fullx)
mplot(mAnti_Fullx)+
  labs(x="", y="Additional letters per congress")

# FULL MODEL WITH NON- CONSTITUENT 
# FIXME
#mNonConstituent_Fullx <- glm(NonConstituent_Letters ~ PAC_contributions*party, data = NonConstituent_letters_money %>% filter(!party %in% c("NA","(I)", "Independent"))%>% mutate(PAC_contributions = PAC_contributions/100000), family = "poisson" )  
#tidy(mNonConstituent_Fullx)
#mplot(mNonConstituent_Fullx)+labs(x="", y="Additional non-constituent letters per congress")
```



#### Edit Everything Below Accordingly
### Party
```{r models-party, fig.height=2, results='hide'}
## With party IV 
models <- tidy(mProParty) %>% 
  mutate(model = "Pro-business Letters per Cycle") %>%
  full_join(tidy(mAntiParty) %>%
              mutate(model = "Anti-business Letters per Cycle")) %>%
  # mutate(term = str_replace(term, "party\\(R\\)", "Republican")) %>% 
  filter(term != "party(I)")

dplot(models) + 
    labs(x = "Additional letters per cycle")

write_lines(
  stargazer::stargazer(mProParty, mAntiParty, float=F),
  path = here("FERC/tables/mProParty-mAntiParty.tex"))

table <- stargazer(mProParty, mAntiParty, 
                type = "html",
                notes = "FERC/tables/mProParty-mAntiParty.tex")
```

```{r, results="asis"}
htmltools::HTML(table)
```



### Univariate models 
```{r models-ALL, fig.height=2, results='hide'}
# All models 
write_lines(
  stargazer::stargazer(mAll, mPro, mAnti,mNonConstituent, mProLog, mAntiLog, mProParty, mProTotal, mAntiTotal, mAntiParty, float = F),
  path = here("FERC/tables/mUnivariate.tex"))

table <-stargazer(mAll, mPro, mAnti, mNonConstituent, mProLog, mAntiLog, mProParty, mProTotal, mAntiTotal, mAntiParty, 
                type = "html",
                notes = "FERC/tables/mUnivariate.tex")
```

```{r, results="asis"}
htmltools::HTML(table)
```



### Multivariate Models
```{r models-full, fig.height=2, results='hide'}
## Full models
models <- tidy(mAll_Full) %>% 
  mutate(model = "Total Letters per Cycle") %>%
  full_join(tidy(mPro_Full) %>%
              mutate(model = "Pro-business Letters per Cycle")) %>%
  full_join(tidy(mAnti_Full) %>%
              mutate(model = "Anti-business Letters per Cycle"))
dplot(models) + 
    labs(x = "Additional letters per cycle")

## Full models + interactions
models <- tidy(mAll_Full) %>% 
  mutate(model = "Total Letters per Cycle") %>%
  full_join(tidy(mPro_Full) %>%
              mutate(model = "Pro-business Letters per Cycle")) %>%
  full_join(tidy(mPro_Fullx) %>% mutate(model = "Pro-business Letters per Cycle, with interaction")) %>%
  full_join(tidy(mAnti_Full) %>%
              mutate(model = "Anti-business Letters per Cycle")) %>%
  full_join(tidy(mAnti_Fullx) %>% mutate(model = "Anti-business Letters per Cycle, with interaction")) # %>%  mutate(term = str_replace(term, "party\\(R\\)", "Republican"))

dplot(models) + 
    labs(x = "Additional letters per cycle")

write_lines(
  stargazer::stargazer(mAll_Full, mAll_Fullx, mPro_Full, mAnti_Full,mPro_Fullx, mAnti_Fullx, float=F),
  path = here("FERC/tables/mFull.tex"))

table <- stargazer(mPro_Full, mAnti_Full, mPro_Fullx, mAnti_Fullx,
                type = "html",
                notes = "FERC/tables/mFull.tex")

table <- stargazer(mPro_Full, mAnti_Full, mPro_Fullx, mAnti_Fullx,
                type = "html",
                notes = "FERC/tables/mFull.tex")
```

```{r, results="asis"}
htmltools::HTML(table)
```



# About DOD and VA



## Letters on behalf of projects in their districts
###Fix to make relevant

```{r}
d %>% 
  mutate(Place_District = tolower(Place_District)) %>% 
  # FIXME 
  # dropping odd observations, will correct in DOE_FERC.R script 
  filter(Place_District %in% c("yes", "no", NA)) %>% 
  filter(letter_position %in% c("AntiBusiness", "ProBusiness")) %>% 
  filter(Constituent != "Not coded") %>% 
  count(Place_District, letter_position, Constituent) %>% 
  ggplot() +
  aes(x = Place_District, y = n, fill = letter_position) +
  geom_col() + 
  facet_grid(Constituent ~ .)+ 
  labs(x = "Is the proposed project in the member's district?",
       y = "Number of letters",
       fill = "")
```





