---
title: "The Department of Defense and its relationship with Legislators"
author: "Fatima Ali"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
subtitle: 'PS 699: Independent Study'
editor_options:
  chunk_output_type: console
---


# Data

In all, we have 8005 letters received by the DoD marked “congressional” since 2003. All of these are from Members of the U.S. Congress. 

```{r, include=FALSE}
  library(tidyverse)
  library(ggplot2); theme_set(theme_bw())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  library(magrittr)
  library(maps)
  library(fiftystater)
  library(mapproj)
  library(knitr)
  library(broom)
  library(dotwhisker)
  library(here)
  library(dplyr)

# source(here("setup.R"))
```


```{r data}
load(here("data/all_contacts.RData"))
# one obs per member per letter for all agencies
d <- all_contacts %>% filter(str_detect(agency, "DOD")) 
```



---

# Top 10 Legislators who wrote to DoD and VA combined
 
```{r forwards}
# top overall
d %>% count(bioname,party,cqlabel, sort = T) %>% top_n(10, n) %>% kable(caption = "Legislators who wrote the most letters to DOD")
```


```{r}
d %>% count(TYPE,sort = T) %>% top_n(10, n) %>% kable(caption = "Most Common Policy Areas")

##Types of Policy each member dealt with
d %>% count(bioname,party, TYPE, cqlabel, sort = T) %>% top_n(10, n) %>% kable(caption = "Legislators who wrote the most letters to DOD")
```

###Senators and Veteran Population
###Still Working On this!!!!

```{r}
# d %>% 
#   filter(chamber == "Senate") %>% 
#     group_by(state, year, population) %>% summarise(n = n()) %>%
#     group_by(state, population) %>% summarise(mean = mean(n)) %>% ungroup() %>% 
#     ggplot() + 
#     geom_point(aes(x = log(population), y = mean), color = "light blue") + 
#   geom_smooth(aes(x = log(population), y = mean)) + 
#   geom_text(aes(x = log(population), 
#                 y = mean, 
#                 label = ifelse(mean > mean(mean)*1.5 | mean < mean(mean)*0.5, 
#                                state, "")), 
#             check_overlap = TRUE, 
#             size = 2.5, 
#             hjust = 0) + 
#   theme_bw() +
#   labs(title = "Senator Requests per Year by Veteran Population",
#        x = "Log State Population",
#        y = "Average Number of Requests per Year")
```


### Senators vs. state population 

```{r population, fig.height= 3.7, fig.width=6}
d %>% 
  filter(chamber == "Senate") %>% 
    group_by(member_state, year, pop2010) %>% summarise(n = n()) %>%
    group_by(member_state, pop2010) %>% summarise(mean = mean(n)) %>% ungroup() %>% 
    ggplot() + 
    geom_point(aes(x = log(pop2010), y = mean), color = "light blue") + 
  geom_smooth(aes(x = log(pop2010), y = mean)) + 
  geom_text(aes(x = log(pop2010), 
                y = mean, 
                label = ifelse(mean > mean(mean)*1.5 | mean < mean(mean)*0.5, 
                               member_state, "")), 
            check_overlap = TRUE, 
            size = 2.5, 
            hjust = 0) + 
  theme_bw() +
  labs(title = "Senator Requests per Year by State Population",
       x = "Log State Population",
       y = "Average Number of Requests per Year")

```






```{r senate_percapita_map}
Chamber = "Senate"

d %>% 
  ungroup() %>%
  filter(chamber == Chamber) %>% 
  group_by(state) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) # + facet_grid(. ~ Constituent)

# d %>% 
#   ungroup() %>% 
#   filter(chamber == Chamber) %>% 
#   group_by(state, pop2010) %>% summarise(n = n()) %>% ungroup() %>% 
#   mutate(Per_Capita = n/pop2010*1000000) %>% 
#   # map_id creates the aesthetic mapping to the state name column in your data
#   ggplot() + 
#   # map points to the fifty_states shape data
#   geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
#   expand_limits(x = fifty_states$long, y = fifty_states$lat) +
#   coord_map() +
#   scale_x_continuous(breaks = NULL) +
#   scale_y_continuous(breaks = NULL) +
#   labs(x = "", y = "", title = paste("Contacts Per hundred thousand Residents from Members of the", Chamber)) +
#   scale_fill_viridis_c(option = "C", end = .8) +
#   theme(legend.position = "bottom", 
#         legend.title = element_blank() )#+facet_grid(. ~ Constituent)



# d  %>% 
#   mutate(Per_Capita = n/pop2010*1000000) %>% ##FIXME non-numeric argument to binary operator
#   # map_id creates the aesthetic mapping to the state name column in your data
#   ggplot() + 
#   # map points to the fifty_states shape data
#   geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
#   expand_limits(x = fifty_states$long, y = fifty_states$lat) +
#   coord_map() +
#   scale_x_continuous(breaks = NULL) +
#   scale_y_continuous(breaks = NULL) +
#   labs(x = "", y = "", title = paste("Contacts Per hundred thousand Residents from Members of the", Chamber)) +
#   scale_fill_viridis_c(option = "C", end = .8) +
#   theme(legend.position = "bottom", 
#         legend.title = element_blank() )+
#   facet_grid(. ~ Constituent)
```

##House Contacts per State

```{r}

d %>% 
  filter(chamber == "House") %>% 
    group_by(member_state, year, pop2010) %>% summarise(n = n()) %>%
    group_by(member_state, pop2010) %>% summarise(mean = mean(n)) %>% ungroup() %>% 
    ggplot() + 
    geom_point(aes(x = log(pop2010), y = mean), color = "light blue") + 
  geom_smooth(aes(x = log(pop2010), y = mean)) + 
  geom_text(aes(x = log(pop2010), 
                y = mean, 
                label = ifelse(mean > mean(mean)*1.5 | mean < mean(mean)*0.5, 
                               member_state, "")), 
            check_overlap = TRUE, 
            size = 2.5, 
            hjust = 0) + 
  theme_bw() +
  labs(title = "House Requests per Year by State Population",
       x = "Log State Population",
       y = "Average Number of Requests per Year")


Chamber = "House"

d %>% 
  ungroup() %>%
  filter(chamber == Chamber) %>% 
  group_by(state) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) # + facet_grid(. ~ Constituent)
```

---

### Members who contact DOD and VA more than average: 

```{r members_barcoded, fig.height=5, fig.width=9}
# barcode plot of committee members 
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 


Chamber <- "Senate" # "Senate"  
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 


# Chamber <- "Senate" # "Senate"  
#  
# # member by year by agency 
# d %>% 
#   filter(chamber == Chamber) %>% 
#   group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
#   filter(n > mean(n)) %>%
#   ggplot() +
#   geom_point(
#     aes(x = DATE, 
#         y = reorder(name_state, n) ), 
#     # alpha = .6,
#     shape = 73,
#     size=2
#   ) +  
#   labs(title = paste(Chamber),
#        y = paste("Members by", "Total Number of Letters"), 
#        x = "Date of Correspondence" ) +
#   theme(
#     legend.title = element_blank(),
#     axis.text.y = element_text(size=5)
#   ) + 
#     guides(fill=guide_legend(ncol=1)) 
```


####Fix this, right now visualization is very messy
### Members who contact DOD more, relative to other agencies: 
```{r ferc_vs_all_rate}

# chamber <- "Senate" # "Senate" ##still is bringing in House members
# 
# all_contacts %>%
#   mutate(DOD = agency == "DOD$") %>%
#   group_by(chamber, DOD, name_state, state) %>%
#   summarise(n = n() ) %>%
#   ungroup() %>%
#   spread(key = "DOD", value = n) %>%
#   #mutate(ShareToDOD = round(`TRUE`/(`TRUE`+`FALSE`),2) ) %>%
#   #arrange(-ShareToDOD) %>%
#   # mutate(total = `TRUE` + `FALSE`) %>%
#   # select(name_state, chamber, total, ShareToDOD) %>%
#   # filter(ShareToDOD>.3) %>%
#   knitr::kable()
```


# Limitations

Throughout the course of this independent study, there were a few challanges and limitations I faced.

# References 

Amos A. Jordan, William J. Taylor, Jr. and Michael J. Mazar, American National Security (Baltimore: Johns Hopkins University Press, 2009)
 
John Kingdon. 1973. Congressmen’s voting decisions.
 
Keith T. Poole and Howard Rosenthal. 2007. Ideology and Congress, Transaction Publishers.
 
Kingdon, John W. “Models of Legislative Voting.” The Journal of Politics, vol. 39, no. 3, 1977, pp. 563–595. JSTOR, www.jstor.org/stable/2129644. Accessed 22 Jan. 2020.
 
Lawrence J. Korb, et al, Building a Military for the 21st Century
 
Nolan M. McCarty, Keith T. Poole, and Howard Rosenthal. 2006. Polarized America: The dance of ideology and unequal riches, MIT Press.
 
David W. Rohde. 1991. Parties and leaders in the post-reform House of Representatives, University of Chicago Press.
 
Fenno, Richard F., “U.S. House Members in Their Constituencies: An Exploration.” American Political Science Review 71 (3, 1977): 883-917.
 
Fenno, Richard F., The Challenge of Congressional Representation (Cambridge, MA: Harvard University Press, 2013), 138-184.
 
Congressional Procedures and the Policy Analysis, by Walter J. Oleszek, Congressional Quarterly Press, Ninth Edition, 2013
 
Laurance, Edward J. “The Changing Role of Congress in Defense Policy-Making.” The Journal of Conflict Resolution, vol. 20, no. 2, 1976, pp. 213–253. JSTOR, www.jstor.org/stable/173398. Accessed 22 Jan. 2020.
 
Lindsay, James M., and Randall B. Ripley. “How Congress Influences Foreign and Defense Policy.” Bulletin of the American Academy of Arts and Sciences, vol. 47, no. 6, 1994, pp. 7–32. JSTOR, www.jstor.org/stable/3824424. Accessed 22 Jan. 2020.
 
Lindsay, James M., and Randall B. Ripley. “Foreign and Defense Policy in Congress: A Research Agenda for the 1990s.” Legislative Studies Quarterly, vol. 17, no. 3, 1992, pp. 417–449. JSTOR, www.jstor.org/stable/439739. Accessed 22 Jan. 2020.
 
 
REIF, KINGSTON. “Congress Rewrites Missile Defense Policy.” Arms Control Today, vol. 47, no. 1, 2017, pp. 40–42. JSTOR, www.jstor.org/stable/90004330. Accessed 22 Jan. 2020.
  
Lowande, K. (2018). Who Polices the Administrative State? American Political Science Review, 112(4), 874–890. doi: 10.1017/s0003055418000497
 
Lowande, Kenneth (2018). Politicization and Responsiveness in Executive Agencies. *Journal of Politics*.
 
Ritchie, M.N. and You, H.Y. (2019), Legislators as Lobbyists. Legislative Studies Quarterly, 44: 65-95. doi:10.1111/lsq.12221
 
Ritchie, M. N. (2018). Back-Channel Representation: A Study of the Strategic Communication of Senators with the US Department of Labor. The Journal of Politics, 80(1), 240–253. doi: 10.1086/694395

Mia Costa Paper

FERC Paper


