---
title: "The Department of Defense and its relationship with Legislators"
author: "Fatima Ali"
#header-includes:
   # - \usepackage{setspace}\doublespacing
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
subtitle: 'PS 699: Independent Study'
editor_options:
  chunk_output_type: console
---

# Data

In all, we have 8005 letters received by the DoD marked “congressional” since 2003. All of these are from Members of the U.S. Congress. 

```{r, include=FALSE}
  library(tidyverse)
  library(ggplot2); theme_set(theme_bw())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
  library(magrittr)
  library(maps)
  library(fiftystater)
  library(mapproj)
  library(knitr)
  library(broom)
  library(dotwhisker)
  library(here)
  library(dplyr)

# source(here("setup.R"))
```


```{r data}
load(here("data/all_contacts.RData"))
# one obs per member per letter for all agencies
d <- all_contacts %>% filter(str_detect(agency, "DOD")) %>% filter(!(last_name == "GRASSLEY"& party == "(R)")) %>% filter(year <2018, year >2006, !is.na(ID)) 
#would Grassley be considered a good outlier?? 
# 2007-2017 Data Points
```



---

# Top 10 Legislators who wrote to DoD combined
 
```{r forwards}
# top overall
d %>% count(bioname,party,cqlabel, sort = T) %>% top_n(10, n) %>% kable(caption = "Legislators who wrote the most letters to DOD")
```


##FILTER OUT NA??

```{r}
d %>% count(TYPE,sort = T) %>% top_n(10, n) %>% kable(caption = "Most Common Policy Areas")

##Types of Policy each member dealt with
d %>% count(bioname,party, TYPE, cqlabel, sort = T) %>% top_n(10, n) %>% kable(caption = "Legislators who wrote the most letters to DOD")
```

##COULD ANYTHING BE DONE HERE

```{r}
# # most with a given position
# d %>% count(bioname, party, cqlabel, letter_position, sort = T) %>% filter(letter_position != "Other") %>% top_n(10, n) %>% kable(caption = "Most frequent letter positions for a given legislator")

# most with a given position in a cycle
d %>% count(bioname, party, cqlabel, TYPE, congress, sort = T) %>% filter(TYPE != "Other") %>% top_n(10, n) %>% kable(caption = "Most frequent letter positions for a given legislator in a cycle")

# 
# # d %>%   filter(str_detect(SUBJECT, "forwards")) %>% add_count(bioname, sort = T) %>% top_n(1, n) %>% select(bioname, SUBJECT) %>% kable(caption = "Letters from the legislator who forwards the most letters")
# 

d %>%
  ggplot() +
  aes(x = congress, fill = TYPE) +
  geom_bar(position = "dodge") +
  facet_grid(party_name ~ chamber)
```

###Senators and Veteran Population
###HELP WITH THIS
#Representative per district??

```{r}
# d %>% 
#   filter(chamber == "Senate") %>% 
#     group_by(member_state, year, vetpop2010) %>% summarise(n = n()) %>%
#     group_by(member_state, vetpop2010) %>% summarise(mean = mean(n)) %>% ungroup() %>%
#   ggplot() + 
#     geom_point(aes(x = log(vetpop2010), y = mean), color = "light blue") + 
#   geom_smooth(aes(x = log(vetpop2010), y = mean)) + 
#   geom_text(aes(x = log(vetpop2010), 
#                 y = mean, 
#                 label = ifelse(mean > mean(mean)*1.5 | mean < mean(mean)*0.5, 
#                                member_state, "")), 
#             check_overlap = TRUE, 
#             size = 2.5, 
#             hjust = 0) + 
#   theme_bw() +
#   labs(title = "Senator Requests per Year by State Population",
#        x = "Log State Population",
#        y = "Average Number of Requests per Year")

```


### Senators vs. state population 

```{r population, fig.height= 3.7, fig.width=6}
d %>% 
  filter(chamber == "Senate") %>% 
    group_by(member_state, year, pop2010) %>% summarise(n = n()) %>%
    group_by(member_state, pop2010) %>% summarise(mean = mean(n)) %>% ungroup() %>% 
    ggplot() + 
    geom_point(aes(x = log(pop2010), y = mean), color = "light blue") + 
  geom_smooth(aes(x = log(pop2010), y = mean)) + 
  geom_text(aes(x = log(pop2010), 
                y = mean, 
                label = ifelse(mean > mean(mean)*1.5 | mean < mean(mean)*0.5, 
                               member_state, "")), 
            check_overlap = TRUE, 
            size = 2.5, 
            hjust = 0) + 
  theme_bw() +
  labs(title = "Senator Requests per Year by State Population",
       x = "Log State Population",
       y = "Average Number of Requests per Year")

```





```{r senate_percapita_map}
Chamber = "Senate"

d %>% 
  ungroup() %>%
  filter(chamber == Chamber) %>% 
  group_by(state) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) # + facet_grid(. ~ Constituent)

##What on earth is happening here?

# d %>% 
#   ungroup() %>% 
#   filter(chamber == Chamber) %>% 
#   group_by(state, pop2010) %>% summarise(n = n()) %>% ungroup() %>% 
#   mutate(Per_Capita = n/pop2010*1000000) %>% 
#   # map_id creates the aesthetic mapping to the state name column in your data
#   ggplot() + 
#   # map points to the fifty_states shape data
#   geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
#   expand_limits(x = fifty_states$long, y = fifty_states$lat) +
#   coord_map() +
#   scale_x_continuous(breaks = NULL) +
#   scale_y_continuous(breaks = NULL) +
#   labs(x = "", y = "", title = paste("Contacts Per hundred thousand Residents from Members of the", Chamber)) +
#   scale_fill_viridis_c(option = "C", end = .8) +
#   theme(legend.position = "bottom", 
#         legend.title = element_blank() )#+facet_grid(. ~ Constituent)



# d  %>% 
#   mutate(Per_Capita = n/pop2010*1000000) %>% ##FIXME non-numeric argument to binary operator
#   # map_id creates the aesthetic mapping to the state name column in your data
#   ggplot() + 
#   # map points to the fifty_states shape data
#   geom_map(aes(map_id = state, fill = Per_Capita), map = fifty_states) + 
#   expand_limits(x = fifty_states$long, y = fifty_states$lat) +
#   coord_map() +
#   scale_x_continuous(breaks = NULL) +
#   scale_y_continuous(breaks = NULL) +
#   labs(x = "", y = "", title = paste("Contacts Per hundred thousand Residents from Members of the", Chamber)) +
#   scale_fill_viridis_c(option = "C", end = .8) +
#   theme(legend.position = "bottom", 
#         legend.title = element_blank() )+
#   facet_grid(. ~ Constituent)
```

##House Contacts per State

##Would this be relevannt??

```{r}

d %>% 
  filter(chamber == "House") %>% 
    group_by(member_state, year, pop2010) %>% summarise(n = n()) %>%
    group_by(member_state, pop2010) %>% summarise(mean = mean(n)) %>% ungroup() %>% 
    ggplot() + 
    geom_point(aes(x = log(pop2010), y = mean), color = "light blue") + 
  geom_smooth(aes(x = log(pop2010), y = mean)) + 
  geom_text(aes(x = log(pop2010), 
                y = mean, 
                label = ifelse(mean > mean(mean)*1.5 | mean < mean(mean)*0.5, 
                               member_state, "")), 
            check_overlap = TRUE, 
            size = 2.5, 
            hjust = 0) + 
  theme_bw() +
  labs(title = "House Requests per Year by State Population",
       x = "Log State Population",
       y = "Average Number of Requests per Year")


Chamber = "House"

d %>% 
  ungroup() %>%
  filter(chamber == Chamber) %>% 
  group_by(state) %>% summarise(n = n()) %>%
# map_id creates the aesthetic mapping to the state name column
ggplot() + 
  # map points to the fifty_states shape data
  geom_map(aes(map_id = state, fill = n), map = fifty_states) + 
  expand_limits(x = fifty_states$long, y = fifty_states$lat) +
  coord_map() +
  scale_x_continuous(breaks = NULL) + 
  scale_y_continuous(breaks = NULL) +
  labs(x = "", y = "", title = paste("Total Number of Contacts from members of the", Chamber)) +
  scale_fill_viridis_c(option = "C", end = .8) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        panel.background = element_blank()) # + facet_grid(. ~ Constituent)
```

---

### Members who contact DOD more than average: 

```{r members_barcoded, fig.height=5, fig.width=9}
# barcode plot of committee members 
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 


Chamber <- "Senate" # "Senate"  
 
# member by year by agency 
d %>% 
  filter(chamber == Chamber) %>% 
  group_by(name_state) %>% mutate(n = n()) %>% ungroup() %>% 
  filter(n > mean(n)) %>%
  ggplot() +
  geom_point(
    aes(x = DATE, 
        y = reorder(name_state, n) ), 
    # alpha = .6,
    shape = 73,
    size=2
  ) +  
  labs(title = paste(Chamber),
       y = paste("Members by", "Total Number of Letters"), 
       x = "Date of Correspondence" ) +
  theme(
    legend.title = element_blank(),
    axis.text.y = element_text(size=5)
  ) + 
    guides(fill=guide_legend(ncol=1)) 


```


### Members who contact DOD more, relative to other agencies: 
```{r ferc_vs_all_rate}

chamber <- "Senate" # "Senate" #why does it say False?

all_contacts %>%
  filter(chamber == "Senate") %>%  #
  mutate(DOD = agency == "DOD") %>%
  group_by(chamber, DOD, name_state, state) %>%
  summarise(n = n() ) %>%
  ungroup() %>%
  #spread(key = "DOD", value = n) %>%
  top_n(10, n) %>%
  knitr::kable()
  
  # mutate(ShareToDOD = round(`TRUE`/(`TRUE`+`FALSE`),2) ) %>%
  # arrange(-ShareToDOD) %>%
  # mutate(total = `TRUE` + `FALSE`) %>%
  # select(name_state, chamber, total, ShareToDOD) %>%
  # filter(ShareToDOD>.3) %>%


chamber <- "House" 

all_contacts %>%
  filter(chamber == "House") %>%  #why is this working this way??
  mutate(DOD = agency == "DOD$") %>%
  group_by(chamber, DOD, name_state, state) %>%
  summarise(n = n() ) %>%
  ungroup() %>%
  #spread(key = "DOD", value = n) %>%
  top_n(10, n) %>%
  knitr::kable()

 ## Members who contact FERC more in a Congress, relative to other agencies
  
```

## Many letters to DOD are cosigned
#A rough under-estimate based on whether "et al" or "&" appears in the summary:
# INVESTIGATE

```{r}
d %>% 
  group_by(ID) %>% 
  mutate(probably_cosigned = ifelse(str_detect(SUBJECT, "et al"), "et al",
                                 ifelse(str_detect(SUBJECT, "&"), "&", " neither"))) %>%
  group_by(year, probably_cosigned) %>% 
  tally %>% 
  ggplot() + 
  aes(x = year, y = n, fill = probably_cosigned) +
  geom_col() +
  scale_fill_viridis_d(option = "C", end = .8)
```

##How to fix this committee Code

```{r}
# d %>%  
#   mutate(chair = str_remove(chair,"[0-9]* |^NA "),
#          committee = paste(chamber, committees))%>% 
#   dplyr::select(committee, position, chair, DATE, assigneddate, terminationdate) %>% 
#   distinct() %>% 
#   filter(str_detect(committee, "ENERGY$|ENVIRONMENT|NATURAL")) %>% 
#   mutate(position = ifelse(position == "Other", NA, position)) %>%
#   #filter(# !is.na(position),chair_since_2007 == T) %>%
#   drop_na(chair) %>% 
#   dplyr::select(DATE, chair, position, assigneddate, terminationdate, committee) %>% 
#   distinct() %>% 
#   ggplot() +
#   geom_point(
#     aes(x = DATE, 
#         y = chair),
#     shape = 73,
#     size=2 
#   ) +
#   geom_segment(aes(y = chair, yend = chair, 
#                    x = date, xend = date, 
#                    linetype = factor(position)),
#                position = position_nudge(y = -0.3)) +
#   labs(title = paste("Letters to FERC from Committee Leadership"),
#        y = "", 
#        x = "",
#        linetype = "Leadership position") +
#   scale_y_discrete(position = "right") +
#   theme(
#     strip.text.y = element_text(angle = 180, size = 5),
#     # legend.title = element_blank(),
#     axis.text.y = element_text(size=5),
#     axis.text.x = element_text(angle = 0)
#   ) + 
#   facet_grid(committee ~ ., scales = "free_y", space = "free_y", switch = "both") 
```


# Limitations

Throughout the course of this independent study, there were a few challenges and limitations I faced.

# References 

Costa, Mia (2020). Citizen Evaluations of Legislator–Constituent Communication. *British Journal of Political Science*.

Fenno, Richard F. (1977). U.S. House Members in Their Constituencies: An Exploration. *American Political Science Review*, 883-917.

Fenno, Richard F. (2013). *The Challenge of Congressional Representation.* Harvard University Press, 138-184.

Jordan, Amos A, William J. Taylor, Jr, and Michael J. Mazar (2009).  *American National Security*, Johns Hopkins University Press.

# Judge-Lord, Devin, Eleanor Neff Powell, and Justin Grimmer (2020). Campaign Contributions and Bureaucratic Oversight: A Case Study of the Federal Energy Regulatory Commission. Unpublished Working Paper. Presented at APSA 2018.

Kingdon, John W (1977). Models of Legislative Voting. *The Journal of Politics (39)*, 563–595. 

Laurance, Edward J (1976). The Changing Role of Congress in Defense Policy-Making. *The Journal of Conflict Resolution (20)*, 213–253. 

Lindsay, James M., and Randall B. Ripley (1992). Foreign and Defense Policy in Congress: A Research Agenda for the 1990s. *Legislative Studies Quarterly*, 417–449. 

Lindsay, James M., and Randall B. Ripley (1994). How Congress Influences Foreign and Defense Policy. *Bulletin of the American Academy of Arts and Sciences, 47*, 7–32. 

Lowande, Kenneth (2018). Politicization and Responsiveness in Executive Agencies. *Journal of Politics*.

Lowande, Kenneth (2018). Who Polices the Administrative State? *American Political Science Review*, 874–890. 

McCarty, Nolan, Keith T. Poole, and Howard Rosenthal (2006). *Polarized America: The dance of ideology and unequal riches*, MIT Press.

Oleszek, Walter J (2013). *Congressional Procedures and the Policy Process*, Congressional Quarterly Press.

Poole, Keith T.  and Howard Rosenthal (2007) *Ideology and Congress*, Transaction Publishers.

Powell, Eleanor Neff and Justin Grimmer (2016). Money in Exile: Campaign Contributions and Committee Access. *The Journal of Politics 78(4)*, 974–88.

Reif, Kingston (2017). Congress Rewrites Missile Defense Policy. *Arms Control Today, 47*, 40–42.

Ritchie, Melinda N (2017). Back-Channel Representation: A Study of the Strategic Communication of Senators with the US Department of Labor. *Journal of Politics*.

Ritchie, M.N. and You, H.Y (2019). Legislators as Lobbyists. *Legislative Studies Quarterly*, 65-95.

Rohde, David W (1991). *Parties and leaders in the post-reform House of Representatives.* University of Chicago Press.

US Census Bureau (2018). Veterans Statistics. *The United States Census Bureau*. https://www.census.gov/library/visualizations/2015/comm/veterans-statistics.html. Date accessed: February 14, 2020.


#Notes:

1. Count letters by member by year (including zero counts)
2. Policy Stuff
3. Divide by years--annualized by years
4. Control with Gender--how long they’re in congress
5. Veterans--More likely to write, shared Veteran status. Veterans-gender-bias
6. What Kind of Variate Models??--Pro-business/anti-business/Constituent vs. everyone else/
  Party Explanatory
7. Best way to present paper..like this or should I hide code??
8. Electoral Interests?--how to measure that?

