---
title: "Who Gets Constituent Service?"
subtitle: 
author: "Rochelle Snyder, Justin Grimmer, Devin Judge-Lord, Eleanor Neff Powell"
output:
    # pdf_document:
    #   toc: true
    #   keep_tex: true
    html_document:
      highlight: zenburn
      #toc: true
      #toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

> These plots can be found in the [CorRep/figs](https://www.dropbox.com/home/CorRep/figs) folder on dropbox and the [APSA2020/figs](https://github.com/judgelord/correspondence/tree/master/APSA2020/Figs) folder on github.

```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = FALSE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)
```

```{r setup}
source(here::here("setup.R"))

library(ggplot2); theme_set(theme_bw())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
```


```{r data}
load(here::here("data/all_contacts.Rdata"))
d <- all_contacts

d %<>% 
    mutate(TYPE = replace_na(TYPE, "NA"),
           constituent = ifelse(TYPE == 1, "Indiv. Constituent Service", "Other")) %>% 
  add_count(icpsr, constituent, agency, year, name = "n_per_year_agency_type") %>% 
  add_count(icpsr, year, name = "n_per_year") %>% 
  mutate(percent_type_to_agency = (n_per_year_agency_type/n_per_year)*100)


d1 <- d %>% 
  filter(year > 2006, year <2020) %>% 
  select(icpsr, year, agency, constituent, n_per_year_agency_type, percent_type_to_agency, party_name) %>%
  filter(agency %in% c("VA", #"SSA", 
                       #"Treasury_Fiscal",
                       "Treasury_IRS",
                       #"NARA",
                       "DHHS_CMS", 
                       #"DHHS_CDC", 
                       "DHHS_HRSA")) %>% 
  distinct()

d1$agency %<>% 
  str_replace("VA", "Veterans Affairs (VA)") %>% 
  str_replace("DHHS_CMS", "Medicare & Medicaid (CMS)") %>% 
  str_replace("DHHS_CDC", "Centers for Disease Control (CDC)") %>% 
  str_replace("DHHS_HRSA", "Health Resources (HRSA)") %>%
  str_replace("Treasury_Fiscal", "Treasury Fiscal Services") %>%
  str_replace("Treasury_IRS", "IRS")
```

## Number of legislator contacts per agency per year 2007-2017
```{r n_per_year_agency, fig.width=8}
d1 %>%
  filter(party_name != "Independent") %>% 
  group_by(icpsr, party_name, agency, year) %>% 
  summarise(n_per_year_agency = sum(n_per_year_agency_type)) %>%
  ggplot() +
  aes(x = year, color = party_name, y = n_per_year_agency) +
  #geom_line(aes(group= icpsr), alpha = .1) + 
  geom_smooth() + 
  labs(x = "", y = "Number of contacts", color = "") + 
  facet_wrap(. ~ agency, scales = "free_y", nrow = 2) +
  scale_x_continuous(breaks = seq(2007,2019, 1)) +
  scale_color_viridis_d(option = "plasma", end = .55) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 

d1 %>%
  ggplot() +
  aes(x = year, color = constituent, y = n_per_year_agency_type) +
  #geom_line(aes(group= icpsr), alpha = .1) + 
  geom_smooth() + 
  labs(x = "", y = "Number of contacts", color = "") + 
  facet_wrap(. ~ agency, scales = "free_y", nrow = 2) +
  scale_x_continuous(breaks = seq(2007,2017, 2)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) 


```

## Percent of legislator contacts per agency per year 2007-2017
```{r percent_to_agency, fig.width=8}

d1 %>% 
  ggplot() +
  aes(x = year, y = percent_type_to_agency, color = constituent) +
  #geom_line(aes(group= icpsr), alpha = .1) + 
  geom_smooth() + 
  labs(x = "", y = "Percent of contacts", color = "") + 
  facet_wrap(. ~ agency, scales = "free_y", nrow = 2) +
  scale_x_continuous(breaks = seq(2007,2017, 2)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Constituent type count: 


```{r constituent_type_count, fig.height=6, fig.width=6, fig.show="hold", fig.cap= "Number of Legislator Letters per Type of Constituent"}
load(here::here("data", "dcounts_min.Rdata"))


dcounts_min$agency %<>% 
  str_replace("VA", "Veterans Affairs (VA)") %>% 
  str_replace("DHHS_CMS", "Medicare & Medicaid (CMS)") %>% 
  str_replace("DHHS_CDC", "Centers for Disease Control (CDC)") %>% 
  str_replace("DHHS_HRSA", "Health Resources (HRSA)") %>% 
  str_replace("Treasury_IRS", "IRS") %>%
  str_replace("NARA", "National Archives (NARA)") %>% 
  str_replace("DOL.*", "Labor (DOL VETS, SOL, OWCP, & OFCCP)") %>% 
  str_replace("Treasury_Fiscal", "Treasury Fiscal Service") %>% 
  str_replace("SSA", "Social Security (SSA)")

names(dcounts_min) %<>% str_replace("vet", "Veteran") %>%
                            str_replace("hardship", "Hardship situation") %>% 
                            str_replace("lowincome", "Low income")%>%
                            str_replace("military", "Military family or veteran") %>%
                            str_replace("senior", "Senior")

dcounts_min %>% 
  # melt count vars to long
  select(agency, starts_with("per")) %>% 
  gather("type", "count", -agency) %>%
  mutate(type = type %>% str_remove(".*_")) %>%
  # count
  group_by(agency, type) %>% 
  summarize(count = sum(count)) %>% 
  ungroup() %>%
  filter(count > 0) %>% #select(type) %>% distinct()
  filter(type %in% c("Hardship situation",
  #"Military family or veteran",
  "Senior",
  "Veteran",
  "Low income")) %>%
  group_by(type) %>% 
  add_count(name = "n_agency") %>% # n agencies per type 
    ungroup() %>%
  ggplot() + 
  aes(y = count, x = agency, label = count, width = .15*n_agency) +
  geom_col(position = "dodge", preserve = "single") +
  geom_text(hjust = -.1) + 
  coord_flip()+ 
  scale_y_continuous(expand = expand_scale(mult =  c(0,.2))) + # pad y axis so there is room for n text
    labs(y = "Number of Constituent Service Letters", #paste("Letters on Behalf", type), 
         x = "Agency") + 
  facet_wrap("type", scales = "free", ncol = 1) +
  theme_bw() + 
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank())
```

# Constituent type share of total per agency


```{r constituent_type_share, fig.width = 8, fig.height = 6, fig.cap="Share of Legislator Contacts by Type of Constituent" ,out.width='100%'}

dcounts_min %>% 
  #select(-per_icpsr_chamber_year_agency_type) %>%
  group_by(agency) %>% 
  summarise(across(starts_with("per_"), sum)) %>% 
  gather(key = type, value = count, -agency) %>%
  mutate(type = str_remove_all(type, ".*_") %>% str_replace("type", "All") ) %>%
  group_by(agency) %>% 
  mutate(agencycount = sum(count)) %>%
  filter(count >0, agencycount > count) %>%
  group_by(agency) %>% 
  add_count(name = "n_types") %>% 
  ggplot() + 
  aes(x = agency, y = count, fill = factor(type), label = count, width = .2*n_types) +
  geom_col(position = "dodge") +
  #geom_text(position = "dodge", hjust = 0) + 
  coord_flip()+ 
  scale_y_continuous()+#expand = expand_scale(mult =  c(0,.2))) +
    labs(y = "", 
         x = "Agency",
         fill = "Type of Constituent") + 
  facet_wrap("agency", scales = "free", ncol = 1) +
  theme_bw() + 
  theme(panel.border = element_blank(),
        axis.ticks = element_blank(),
         panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank())

```



# Member-Congress Percentiles

```{r percent_correp, fig.height=2.5, fig.width=5, fig.show="hold", fig.cap= "Average Legislator Requests per Congress by Constituent Type"}

load(here::here("data", "dcounts_mid.Rdata"))

dcounts %<>% filter(chamber != "President")

dcounts %<>% select(chamber, last_name, state_abbrev, party_name, congress, year, agency, icpsr, TYPE, starts_with("per_")) 


# save(dcounts, file = here::here("data" , "dcounts_mid.Rdata"))


dcounts %<>% 
    mutate(member_state = str_c(last_name, ", ", str_sub(party_name, 1, 1), "-", state_abbrev)) 

percentplot <- function(var, title, x){
  
  dcounts$var <- var

  dcounts %>%
      group_by(member_state, chamber, congress) %>% summarise(n = sum(var)) %>%
      group_by(member_state, chamber) %>% mutate(mean = mean(n)) %>% ungroup() %>% 
      group_by(chamber) %>% mutate(Percentile = ntile(mean, 100)) %>% 
    arrange(-Percentile) %>% 
    dplyr::select(member_state, Percentile, mean, chamber) %>% distinct() %>% 
      ggplot() + 
      geom_col(aes(x = Percentile, y = mean), color = "grey", position = "dodge") + 
    geom_point(aes(x = Percentile, y = mean), color = "grey") + 
    geom_text(aes(x = Percentile, y = mean, label = ifelse(Percentile > 90, member_state, "")), check_overlap = T, size = 2, hjust = "inward") + 
      facet_grid(. ~ chamber , scales = "free_y") + theme_bw() +
    labs(#title = "Average Legislator Requests per Congress by Percentile",
      title = title,
         y = "",
         x = x)
}


percentplot(dcounts$per_icpsr_chamber_year_agency_vet, "Veterans", x = "Percentile")
#percentplot(dcounts$per_icpsr_chamber_year_agency_military, "Military Families, Personal, and Veterans")
percentplot(dcounts$per_icpsr_chamber_year_agency_senior, "Seniors", x = "Percentile")
percentplot(dcounts$per_icpsr_chamber_year_agency_hardship, "Constituents Experiencing Hardship", x = "Percentile")
percentplot(dcounts$per_icpsr_chamber_year_agency_lowincome, "Low Income Constituents", x = "Percentile")

```

# TODO

> Maybe also any interesting patterns in the volume of total letters on behalf of constituent types over time?
Bars for each Congress broken down by constituent type
Basically, this would show how many letters there are on behalf of different constituent types, where the letters are in the agencies, who is writing the letters, and when the letters were written.