---
title: "Who Gets Constituent Service?"
subtitle: 
author: "Rochelle Snyder, Eleanor Neff Powell, Devin Judge-Lord, Justin Grimmer"
output:
    pdf_document:
      toc: true
      keep_tex: true
    html_document:
      highlight: zenburn
      #toc: true
      #toc_float: true
      code_folding: hide
editor_options: 
  chunk_output_type: console
---

> These plots can be found in the [CorRep/figs](https://www.dropbox.com/home/CorRep/figs) folder on dropbox and the [APSA2020/figs](https://github.com/judgelord/correspondence/tree/master/APSA2020/Figs) folder on github.

```{r global.options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      cache = TRUE, 
                      fig.width=8.5, 
                      split = T,
                      fig.align = 'center', 
                      fig.path='figs/',
                      warning=FALSE, 
                      message=FALSE)
```

```{r setup}
source(here::here("setup.R"))

library(ggplot2); theme_set(theme_bw())
  options(
    ggplot2.continuous.color = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  scale_color_discrete <- function(...)
    scale_color_viridis_d(...)
  scale_fill_discrete <- function(...)
    scale_fill_viridis_d(...)
```


```{r data}
load(here::here("data/all_contacts.Rdata"))
d <- all_contacts

d %<>% 
    mutate(TYPE = replace_na(TYPE, "NA"),
           constituent = ifelse(TYPE == 1, "Indiv. Constituent Service", "Other")) %>% 
  add_count(icpsr, constituent, agency, year, name = "n_per_year_agency_type") %>% 
  add_count(icpsr, year, name = "n_per_year") %>% 
  mutate(percent_type_to_agency = (n_per_year_agency_type/n_per_year)*100)


d1 <- d %>% 
  filter(year > 2006, year <2018) %>% 
  select(icpsr, year, agency, constituent, n_per_year_agency_type, percent_type_to_agency) %>%
  filter(agency %in% c("VA", #"SSA", 
                       "DHHS_CMS", "DHHS_CDC", "DHHS_HRSA")) %>% 
  distinct()

d1$agency %<>% 
  str_replace("VA", "Veterans Affairs (VA)") %>% 
  str_replace("DHHS_CMS", "Medicare & Medicaid (CMS)") %>% 
  str_replace("DHHS_CDC", "Centers for Disease Control (CDC)") %>% 
  str_replace("DHHS_HRSA", "Health Resources (HRSA)")
```

## Number of legislator contacts per agency per year 2007-2017
```{r n_per_year_agency, fig.width=8}
d1 %>%
  ggplot() +
  aes(x = year, color = constituent, y = n_per_year_agency_type) +
  #geom_line(aes(group= icpsr), alpha = .1) + 
  geom_smooth() + 
  labs(x = "", y = "Number of contacts", color = "") + 
  facet_wrap(. ~ agency, scales = "free_y", nrow = 1) +
  scale_x_continuous(breaks = seq(2007,2017, 2)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Percent of legislator contacts per agency per year 2007-2017
```{r percent_to_agency, fig.width=8}
d1 %>% 
  ggplot() +
  aes(x = year, y = percent_type_to_agency, color = constituent) +
  #geom_line(aes(group= icpsr), alpha = .1) + 
  geom_smooth() + 
  labs(x = "", y = "Percent of contacts", color = "") + 
  facet_wrap(. ~ agency, scales = "free_y", nrow = 1) +
  scale_x_continuous(breaks = seq(2007,2017, 2)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Constituent type count: 


```{r constituent_type_count, fig.height=2, fig.width=5, fig.show="hold", fig.cap= "Number of Legislator Letters per Type of Constituent"}
load(here::here("data", "dcounts_min.Rdata"))


dcounts_min$agency %<>% 
  str_replace("VA", "Veterans Affairs (VA)") %>% 
  str_replace("DHHS_CMS", "Medicare & Medicaid (CMS)") %>% 
  str_replace("DHHS_CDC", "Centers for Disease Control (CDC)") %>% 
  str_replace("DHHS_HRSA", "Health Resources (HRSA)") %>% 
  str_replace("Treasury_IRS", "IRS") %>%
  str_replace("NARA", "National Archives (NARA)") %>% 
  str_replace("DOL.*", "Labor (DOL VETS, SOL, OWCP, & OFCCP)") %>% 
  str_replace("Treasury_Fiscal", "Treasury Fiscal Service") %>% 
  str_replace("SSA", "Social Security (SSA)")




countplot <- function(countvar, title){
  dcounts_min$var <- countvar
  
dcounts_min %>% 
  group_by(agency) %>% 
  summarize(count = sum(var)) %>% 
  ungroup() %>% 
  filter(count > 0) %>% 
  ggplot() + 
  aes(y = count, x = agency, label = count) +
  geom_col(width = .1) +
  geom_text(hjust = -.1) + 
  coord_flip()+ 
  scale_y_continuous(expand = expand_scale(mult =  c(0,.2))) +
    labs(y = paste("Letters on Behalf", title), 
         x = "Agency") + 
  #facet_wrap("agency", scales = "free", ncol = 1) +
  theme_minimal() + 
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank())
}

countplot(dcounts_min$per_icpsr_chamber_year_agency_vet, "Veterans")
countplot(dcounts_min$per_icpsr_chamber_year_agency_military, "Military Families, Personal, and Veterans")
countplot(dcounts_min$per_icpsr_chamber_year_agency_lowincome, "Low Income Constituents")
countplot(dcounts_min$per_icpsr_chamber_year_agency_senior, "Seniors")
countplot(dcounts_min$per_icpsr_chamber_year_agency_hardship, "Constituents Experiencing Hardship")
```

# Constituent type share of total per agency


```{r constituent_type_share, fig.width = 8, fig.height = 8, fig.cap="Share of Legislator Contacts by Type of Constituent" ,out.width='100%'}
names(dcounts_min) %<>% str_replace("vet", "Veteran") %>%
                            str_replace("hardship", "Hardship situation") %>% 
                            str_replace("lowincome", "Low income")%>%
                            str_replace("military", "Military family or veteran") %>%
                            str_replace("senior", "Senior")
dcounts_min %>% 
  #select(-per_icpsr_chamber_year_agency_type) %>%
  group_by(agency) %>% 
  summarise(across(starts_with("per_"), sum)) %>% 
  gather(key = type, value = count, -agency) %>%
  mutate(type = str_remove_all(type, ".*_") %>% str_replace("type", "All") ) %>%
  group_by(agency) %>% 
  mutate(agencycount = sum(count)) %>%
  filter(count >0, agencycount > count) %>%
  ggplot() + 
  aes(x = agency, y = count, fill = factor(type), label = count) +
  geom_col(position = "dodge") +
  #geom_text(position = "dodge", hjust = 0) + 
  coord_flip()+ 
  scale_y_continuous()+#expand = expand_scale(mult =  c(0,.2))) +
    labs(y = "", 
         x = "Agency",
         fill = "Type of Constituent") + 
  facet_wrap("agency", scales = "free", ncol = 1) +
  theme_bw() + 
  theme(panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank())

```



# Member-Congress Percentiles

```{r percent_correp, fig.height=2.5, fig.width=5, fig.show="hold", fig.cap= "Average Legislator Requests per Congress by Constituent Type"}

load(here::here("data", "dcounts_mid.Rdata"))

dcounts %<>% filter(chamber != "President")

dcounts %<>% select(chamber, last_name, state_abbrev, party_name, congress, year, agency, icpsr, TYPE, starts_with("per_")) 


# save(dcounts, file = here::here("data" , "dcounts_mid.Rdata"))


dcounts %<>% 
    mutate(member_state = str_c(last_name, ", ", str_sub(party_name, 1, 1), "-", state_abbrev)) 

percentplot <- function(var, title, x){
  
  dcounts$var <- var

  dcounts %>%
      group_by(member_state, chamber, congress) %>% summarise(n = sum(var)) %>%
      group_by(member_state, chamber) %>% mutate(mean = mean(n)) %>% ungroup() %>% 
      group_by(chamber) %>% mutate(Percentile = ntile(mean, 100)) %>% 
    arrange(-Percentile) %>% 
    dplyr::select(member_state, Percentile, mean, chamber) %>% distinct() %>% 
      ggplot() + 
      geom_col(aes(x = Percentile, y = mean), color = "grey", position = "dodge") + 
    geom_point(aes(x = Percentile, y = mean), color = "grey") + 
    geom_text(aes(x = Percentile, y = mean, label = ifelse(Percentile > 90, member_state, "")), check_overlap = T, size = 2, hjust = "inward") + 
      facet_grid(. ~ chamber , scales = "free_y") + theme_bw() +
    labs(#title = "Average Legislator Requests per Congress by Percentile",
      title = title,
         y = "",
         x = x)
}


percentplot(dcounts$per_icpsr_chamber_year_agency_vet, "Veterans", x = "")
#percentplot(dcounts$per_icpsr_chamber_year_agency_military, "Military Families, Personal, and Veterans")
percentplot(dcounts$per_icpsr_chamber_year_agency_senior, "Seniors", x = "")
percentplot(dcounts$per_icpsr_chamber_year_agency_hardship, "Constituents Experiencing Hardship", x = "")
percentplot(dcounts$per_icpsr_chamber_year_agency_lowincome, "Low Income Constituents", x = "Percentile")

```

# TODO

> Maybe also any interesting patterns in the volume of total letters on behalf of constituent types over time?
Bars for each Congress broken down by constituent type
Basically, this would show how many letters there are on behalf of different constituent types, where the letters are in the agencies, who is writing the letters, and when the letters were written.